### 2018-02-26 FrascatiPlot/Paper/NucleiB2.tex
Adding paper folder.

\RequirePackage{ifpdf}

%\documentclass[a4paper,11pt]{scrartcl} % scrartcl scrreprt
\documentclass[a4paper,11pt]{scrartcl} % scrartcl scrreprt

\usepackage[margin=2.cm]{geometry}

\ifpdf
  \usepackage[pdftex]{graphicx}
\else
  \usepackage[dvips]{graphicx}
\fi

%\usepackage[utf8]{inputenc}

\usepackage[T1]{fontenc}

\usepackage{amsmath}
\usepackage[amssymb]{SIunits}
\usepackage{hyperref}

\usepackage{lineno}
\linenumbers

%
% DOCUMENT STARTS HERE
%
\input{./commands.tex}

\begin{document}
\begin{center}
{\Large {\bf Nuclei coalescence}}

\medskip

F. Bellini and A. Kalweit

\medskip

26th of February 2018
\end{center}

\bigskip

%
% Introduction 
%

\paragraph{Introduction.} 
The measured abundances of hadrons produced in heavy-ion collisions have been successfully described by statistical hadronization models over a wide range of energies~\cite{Andronic:2011yq,Cleymans:1998fq,Andronic:2005yp}. Thermal-statistical model calculations for central ultra-relativistic heavy-ion collisions are typically carried out in the grand-canonical ensemble. However, a grand-canonical description of particle production is only applicable if the volume $V=R^{3}$ of the system is large enough and as a rule of thumb one needs $VT^{3} > 1$ for a grand-canonical description to hold \cite{Hagedorn:1984uy,Rafelski:1980gk}. It must be noted, that this condition must be fulfilled for each conserved charge separately.
Several attempts were made to extend the picture of statistical hadronization to smaller systems such as pp or even e$^{+}$e$^{-}$ collisions~\cite{Redlich:2009xx,Becattini:1996gy,Kraus:2008fh}. While particle ratios of non-strange particles are observed to be very similar in small and large systems, the production of strangeness appears to be significantly suppressed in smaller systems. The data presented in~\cite{Adam:2016emw} shows for the first time, that there is a continuous increase of strangeness production with increasing event multiplicity across various collision systems. In the strangeness canonical approach, it is assumed that the total amount of strange hadrons in the volume is small with respect to non-strange hadrons. Thus the conservation of strangeness is guaranteed explicitly and not only on average while the bulk of the particles is still described in the grand-canonical ensemble. For further details on the this approach, we refer for instance to~\cite{BraunMunzinger:2003zd,BraunMunzinger:2001as,Hamieh:2000tk,Cleymans:2004bf,Kraus:2007hf}. The study presented here utilises the implementation in the THERMUS code~\cite{Wheaton:2004qb}.

%%%%% acknowledgements
\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}

The authors would like to thank themselves for the auto-critics.

\end{acknowledgement}

\bibliographystyle{utphys} 	
\bibliography{NucleiB2}

\end{document}

%%
%% End of file.

### 2018-02-26 FrascatiPlot/Paper/NucleiB2.tex
Adding abstract and table of contents

@@
 %\usepackage[utf8]{inputenc}
-
 \usepackage[T1]{fontenc}
@@
 \begin{center}
-{\Large {\bf Nuclei coalescence}}
+{\Large {\bf Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei at LHC energies with recent and future Run 3 and 4 data}}
 
@@
 %
+%\listoffigures
+%\listoftables
+%\newpage
 
-\paragraph{Introduction.} 
+\begin{abstract}
+(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies.
+At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models.
+While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals largely different predictions between the two approach for the production of 3He and hyper-tritons.
+Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions.
+The thermal-statistical model on the other hand is in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system.
+Our finding thus indicate the existence of a novel production mechanism for these objects.
+\end{abstract}
+
+\tableofcontents
+
+\section{Introduction} 
 The measured abundances of hadrons produced in heavy-ion collisions have been successfully described by statistical hadronization models over a wide range of energies~\cite{Andronic:2011yq,Cleymans:1998fq,Andronic:2005yp}.
@@
 The study presented here utilises the implementation in the THERMUS code~\cite{Wheaton:2004qb}.
+
+\section{Coalescence approach}
+
+\subsection{Source volume}
+
+\section{Statistical-thermal approach and Blast-wave}
+
+\section{Comparison with experimental data}
+
+\subsection{(Anti-)nuclei with $A$ = 2, 3, 4}
+
+\subsection{(Anti-)hyper-nuclei}
+
+\section{Projections for the LHC Run 3 and 4}
+
+\section{Summary and conclusions}
 

### 2018-02-26 FrascatiPlot/Paper/NucleiB2.tex
First part of introduction with references.

@@
 \linenumbers
+
+\usepackage{xcolor}
 
@@
 
+%%Table of contents - to be removed for submission%%
 \tableofcontents
@@
 \section{Introduction} 
-The measured abundances of hadrons produced in heavy-ion collisions have been successfully described by statistical hadronization models over a wide range of energies~\cite{Andronic:2011yq,Cleymans:1998fq,Andronic:2005yp}.
-Thermal-statistical model calculations for central ultra-relativistic heavy-ion collisions are typically carried out in the grand-canonical ensemble.
-However, a grand-canonical description of particle production is only applicable if the volume $V=R^{3}$ of the system is large enough and as a rule of thumb one needs $VT^{3} > 1$ for a grand-canonical description to hold \cite{Hagedorn:1984uy,Rafelski:1980gk}.
-It must be noted, that this condition must be fulfilled for each conserved charge separately.
-Several attempts were made to extend the picture of statistical hadronization to smaller systems such as pp or even e$^{+}$e$^{-}$ collisions~\cite{Redlich:2009xx,Becattini:1996gy,Kraus:2008fh}.
-While particle ratios of non-strange particles are observed to be very similar in small and large systems, the production of strangeness appears to be significantly suppressed in smaller systems.
-The data presented in~\cite{Adam:2016emw} shows for the first time, that there is a continuous increase of strangeness production with increasing event multiplicity across various collision systems.
-In the strangeness canonical approach, it is assumed that the total amount of strange hadrons in the volume is small with respect to non-strange hadrons.
-Thus the conservation of strangeness is guaranteed explicitly and not only on average while the bulk of the particles is still described in the grand-canonical ensemble.
-For further details on the this approach, we refer for instance to~\cite{BraunMunzinger:2003zd,BraunMunzinger:2001as,Hamieh:2000tk,Cleymans:2004bf,Kraus:2007hf}.
-The study presented here utilises the implementation in the THERMUS code~\cite{Wheaton:2004qb}.
+The formation of light anti- and hyper- nuclei in highly energetic proton-proton, proton-nucleus and nucleus-nucleus collisions provides unique observables for the study of the system created in these collisions.
+In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons, because their size is comparable to a fraction or the whole system created in the collision \cite{}.
+As quantum-mechanical objects, their size is typically defined as the rms of their wave function, which ranges from \textcolor{red}{xx fm for the 3He up to yy fm for the hyper-triton}. 
+Halo nuclei as 6He would be ideal for such studies, but they remain out of the experimental reach in high-energy experiments.
+
+Surprisingly, thermal-statistical models have been successful at describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
+In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem}$ = 156 MeV (near the temperature at the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{T from lattice}.
+Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
+Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
+Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically.
+This is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV.
+In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects.
+For instance, the binding energy of the deuteron is $E_{B, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
+As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products (check statement and refer to Juergen's QM proceedings) \cite{Garcilazo:1982yc, Bass:1998ca}.
+Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is \textcolor{red}{smaller than the breakup cross-section} \cite{Schukraft:2017nbn}.
+Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet they're production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
+\textcolor{Do similar estimates as Karel in Frascati}.
+In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
+Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects a compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk}.
+Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{}, thus strongly disfavouring hypothesis (a.). 
+While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
+
+To this purpose, we compare to models the existing data from the Large Hadron Collider which for the first time allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
+In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.
+
+- coalescence approaches
+
+- first time we see a plot where we compare directly the two main approaches with data
+
+- B2 as the observable for Run 3 and 4 where to learn the most
+
+- content of the paper
 
@@
 
+We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
+
 %%%%% acknowledgements

### 2018-03-10 FrascatiPlot/Paper/NucleiB2.tex
Update to introduction and bibliography on friday 10 march. Table with nuclei properties to be completed

@@
 \usepackage[margin=2.cm]{geometry}
+\usepackage{multirow}
+\usepackage{tabularx}
 
@@
 \begin{center}
-{\Large {\bf Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei at LHC energies with recent and future Run 3 and 4 data}}
+{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei at LHC energies with recent and future Run 3 and 4 data}}
 
@@
 \tableofcontents
+\newpage
 
@@
 In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons, because their size is comparable to a fraction or the whole system created in the collision \cite{}.
+The relevant properties of the objects under study are summarised in Table \ref{tab:nucleusradii}
 As quantum-mechanical objects, their size is typically defined as the rms of their wave function, which ranges from \textcolor{red}{xx fm for the 3He up to yy fm for the hyper-triton}. 
@@
 Surprisingly, thermal-statistical models have been successful at describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem}$ = 156 MeV (near the temperature at the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{T from lattice}.
+In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem}$ = 156 MeV (near the temperature at the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz}.
 Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
@@
 Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is \textcolor{red}{smaller than the breakup cross-section} \cite{Schukraft:2017nbn}.
-Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet they're production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-\textcolor{Do similar estimates as Karel in Frascati}.
+Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
+\textcolor{red}{Do similar estimates as Karel in Frascati}.
 In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
@@
 
-To this purpose, we compare to models the existing data from the Large Hadron Collider which for the first time allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
+\begin{table}[b]
+
+\centering
+\begin{tabularx}{\textwidth}{cccccc}
+\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
+A = 2                           & d                           & pn                              & 2.2                                          & 3.2                                                 &                           \\ \hline
+\multirow{3}{*}{A = 3}  & \tritium 	         & pnn                            &                                                &                                                     &                           \\
+                                   & \hethree                & ppn                            &                                                &                                                     &                           \\
+                                   & \hthreelambda      & p$\Lambda$n       &                                                &                                                     &                           \\ \hline
+\multirow{4}{*}{A = 4}  & \hefour                  & ppnn                                    &                                                &                                                     &                           \\
+                                   & \hfourlambda        & p$\Lambda$nn          &                                              &                                                     &                           \\
+                                   & \hfourtwolambda  &  p$\Lambda\Lambda$n                                   &                                              &                                                     &                           \\
+                                   & \hefourlambda      & pp$\Lambda$n                                    &                                              &                                                     &                           \\ \hline
+\end{tabularx}
+\caption{Properties of nuclei and hyper-nuclei.
+$B_{E}$ is the binding energy per nucleon in MeV and the radius is given in terms of the rms radius of the wavefunction.
+References are given in the last column.}
+\label{tab:nucleusradii}
+\end{table}
+
+To this purpose, we compare to models the existing data from the Large Hadron Collider.
+For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
 In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.
+The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}.
+In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as alternative approach.
+The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
+We find that a systematic study of the coalescence parameter \bA~exhibits a large discrimination power between the two approaches.
+In section \ref{sec:projections} we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
+As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
+Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments.
 
-- coalescence approaches
+\section{Coalescence approach} \label{sec:coalescence}
 
-- first time we see a plot where we compare directly the two main approaches with data
+\subsection{Simple coalescence}
+- nucleons close in phase space \cite{Butler}
 
-- B2 as the observable for Run 3 and 4 where to learn the most
+- at LHC energies at midrapidity same number of protons and neutrons and muB = 0: cite alice pp, PbPb, baryon-antibaryon papers
 
-- content of the paper
+- give formula of BA
 
-\section{Coalescence approach}
+- BA independent of pt, object size with respect to the source size
+
+- naive expectation is that if number of nucleons increases (as it does with multiplicity), the number of nuclei also increases
+
+- ALICE observations in PbPb: B2 decreases with centrality in PbPb collisions, which is in contrast with the simplest coalescence
+
+\subsection{Full coalescence}
+
+- summary of Uli's paper in understandable words
+
+- how does Uli's paper relates to the Wigner formalism
+
+- add two formulas from Uli on the quantum mechanical coefficient dependence on object and source size and BA
+
+- plot of Cd vs radius, B2 for point-like objects and realistic wavefunctions
+
+- add formula from Kfir for B3 and write how it relates to Uli's (or it is derived from it)
+
+\begin{figure}[htbp]
+\begin{center}
+%\epsfile{file=,scale=0.8}
+\caption{{Cd vs radius, B2 for point-like objects and realistic wavefunctions}}
+\label{fig:cd}
+\end{center}
+\end{figure}
 
 \subsection{Source volume}
+- describe what ALICE actually measures for multiplicity and say it is known that system size increases with multiplicity (linearly or approx.)
 
-\section{Statistical-thermal approach and Blast-wave}
+- assumption 1: parameterisation we propose, which is found to describe the deuteron data
 
-\section{Comparison with experimental data}
+- plot our parameterisation vs the HBT results
+
+\begin{figure}[htbp]
+\begin{center}
+%\epsfile{file=,scale=0.8}
+\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data.}
+\label{fig:cd}
+\end{center}
+\end{figure}
+
+\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
+-
+
+\section{Comparison with experimental data}\label{sec:comparison}
 
 \subsection{(Anti-)nuclei with $A$ = 2, 3, 4}
-
 \subsection{(Anti-)hyper-nuclei}
 
-\section{Projections for the LHC Run 3 and 4}
+\section{Projections for the LHC Run 3 and 4}\label{sec:projections}
 
@@
 %%%%% acknowledgements
-\newenvironment{acknowledgement}{\relax}{\relax}
+\newenvironment{acknowledgement}{\relax}{\relax
 \begin{acknowledgement}

### 2018-03-29 FrascatiPlot/Paper/NucleiB2.tex
Section on coalescence added with pocket formula and plot of Cd vs R and B2 vs R from model

@@
 As quantum-mechanical objects, their size is typically defined as the rms of their wave function, which ranges from \textcolor{red}{xx fm for the 3He up to yy fm for the hyper-triton}. 
-Halo nuclei as 6He would be ideal for such studies, but they remain out of the experimental reach in high-energy experiments.
+Halo nuclei as 6He would be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
 
@@
 In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects a compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk}.
+Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk}.
 Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{}, thus strongly disfavouring hypothesis (a.). 
@@
 The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}.
-In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as alternative approach.
+In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach.
 The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
-We find that a systematic study of the coalescence parameter \bA~exhibits a large discrimination power between the two approaches.
+We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches.
 In section \ref{sec:projections} we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
@@
 Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments.
+In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
 
@@
 \subsection{Simple coalescence}
-- nucleons close in phase space \cite{Butler}
+In simple coalescence, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}.
+For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$, which is defined as
 
-- at LHC energies at midrapidity same number of protons and neutrons and muB = 0: cite alice pp, PbPb, baryon-antibaryon papers
+\begin{equation}
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right,
+\label{eq:BA}
+\end{equation}
 
-- give formula of BA
-
-- BA independent of pt, object size with respect to the source size
-
-- naive expectation is that if number of nucleons increases (as it does with multiplicity), the number of nuclei also increases
-
-- ALICE observations in PbPb: B2 decreases with centrality in PbPb collisions, which is in contrast with the simplest coalescence
+\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{n,p}$ their energy.
+Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
+\begin{equation}
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.
+\label{eq:BA}
+\end{equation}
+%
+Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
+In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
+In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision.
+If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
+While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
+In addition, the elliptic flow of deuteron cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.
 
 \subsection{Full coalescence}
+In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
+While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.
+\textcolor{red}{Consider mentioning the approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
+In this formalism, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
+In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
 
-- summary of Uli's paper in understandable words
+\begin{equation}
+\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
+\label{eq:Cd}
+\end{equation}
+%
+where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lenghts of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
+The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
+%
+\begin{equation}
+\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
+\label{eq:B2cd}
+\end{equation}
+%
+which is the main result of \cite{Scheibl:1998tk}.
+It is interesting to note that the coalescence parameter decreases with increasing volume, as expected.
+In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability.
+If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
+\begin{equation}
+\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
+\label{eq:Cdapprox}
+\end{equation}
+%
+and
+%
+\begin{equation}
+\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
+\label{eq:B2approx}
+\end{equation}
+%
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus, (b.) $\dradius = 0.3$ fm as currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the current estimate of the rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
 
-- how does Uli's paper relates to the Wigner formalism
-
-- add two formulas from Uli on the quantum mechanical coefficient dependence on object and source size and BA
-
-- plot of Cd vs radius, B2 for point-like objects and realistic wavefunctions
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.eps}
+\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
+\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (righ panel, see Eq.
+\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a radius of the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
+\label{fig:radiusDependence}
+\end{center}
+\end{figure}
 
@@
 
+- excess binding energy needs to be released to the system to make coalescence work
+
 \section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
@@
 %%%%% acknowledgements
-\newenvironment{acknowledgement}{\relax}{\relax
+\newenvironment{acknowledgement}{\relax}{\relax}
 \begin{acknowledgement}

### 2018-03-29 FrascatiPlot/B2vsVolume.C

@@ -4,6 +4,7 @@
 #include "TMath.h"
 #include "./generateBWpredictionsB2.C" //ADAPT ME
 
+TF1 * MakeB2TheoryGraphQMfactor(Double_t objSize = 3.2);
 TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 3.2);
 TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 1.75);
 
@@ -79,16 +80,53 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   Double_t mT = TMath::Sqrt(pToA * pToA + 0.938 * 0.938);
   // objSize = 3.2; //fm for the deuteron
   // objSize = 1.75; //fm for the 3^He
+
+  TF1 * Cd_coalescence = (TF1*) MakeB2TheoryGraphQMfactor();
+  Cd_coalescence->SetLineWidth(3);
+  Cd_coalescence->SetLineStyle(1);
+  Cd_coalescence->SetLineColor(kBlack);
+
+  TF1 * Cd_coalescence_pointlike = (TF1*) MakeB2TheoryGraphQMfactor(0.0);
+  Cd_coalescence_pointlike->SetLineWidth(4);
+  Cd_coalescence_pointlike->SetLineStyle(6);
+  Cd_coalescence_pointlike->SetLineColor(kBlue);
+
+  TF1 * Cd_coalescence_radius1third = (TF1*) MakeB2TheoryGraphQMfactor(0.3);
+  Cd_coalescence_radius1third->SetLineWidth(3);
+  Cd_coalescence_radius1third->SetLineStyle(7);
+  Cd_coalescence_radius1third->SetLineColor(kRed);
+
+  TF1 * Cd_coalescence_largeradius = (TF1*) MakeB2TheoryGraphQMfactor(10.0);
+  Cd_coalescence_largeradius->SetLineWidth(3);
+  Cd_coalescence_largeradius->SetLineStyle(9);
+  Cd_coalescence_largeradius->SetLineColor(kGreen+1);
+
   
   TGraphErrors* hB2_coalescence = (TGraphErrors*) MakeB2TheoryGraphCoalescence(mT);
   hB2_coalescence->SetMarkerStyle(20);
   hB2_coalescence->SetLineWidth(3);
[…]

### 2018-03-30 FrascatiPlot/Paper/NucleiB2.tex
minor fix to rext

@@
 
-\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{n,p}$ their energy.
+\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
 Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
@@
 \textcolor{red}{Consider mentioning the approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
-In this formalism, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
+In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
 In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

### 2018-04-01 FrascatiPlot/Paper/NucleiB2.tex
adding generalised expression for CA

@@
 
+- describe qualitatively what is visible in the figure that heavy-ion collisions are similar while production of "large" objects is suppressed in small collsion systmes
+
+Following the approach and discussion presented in~\cite{KfirBlumPaper}, Eq.~\ref{eq:Cd} may be generalised as
+
+\begin{equation}
+\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
+\label{eq:CA_general}
+\end{equation}
+%
+for mass number $A$ and the radii $R_{i}$ which describe the volume of the emitting source.
+
 - add formula from Kfir for B3 and write how it relates to Uli's (or it is derived from it)

### 2018-04-01 FrascatiPlot/Paper/NucleiB2.tex
warning fix

@@
 \begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right,
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;,
 \label{eq:BA}
@@
 \begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
 \label{eq:BA}
@@
 - add formula from Kfir for B3 and write how it relates to Uli's (or it is derived from it)
+- add a reference to Stanislaw Mrowczinki who also proposed nuclei with very different wave functions which are however experimentally not accessible.
 

### 2018-04-18 FrascatiPlot/Paper/NucleiB2.tex
Ädded formulas for BA and started section on the source volume.

@@
 For instance, the binding energy of the deuteron is $E_{B, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
-As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products (check statement and refer to Juergen's QM proceedings) \cite{Garcilazo:1982yc, Bass:1998ca}.
+As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products (check statement) \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
 Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is \textcolor{red}{smaller than the breakup cross-section} \cite{Schukraft:2017nbn}.
@@
 Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk}.
-Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{}, thus strongly disfavouring hypothesis (a.). 
+Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
 While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
@@
 We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
+A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
+However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
 In section \ref{sec:projections} we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
@@
 Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus, (b.) $\dradius = 0.3$ fm as currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the current estimate of the rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
+As can be seen in Fig.
+\ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
 
@@
 \caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
-\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (righ panel, see Eq.
+\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
 \ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a radius of the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
@@
 
-- describe qualitatively what is visible in the figure that heavy-ion collisions are similar while production of "large" objects is suppressed in small collsion systmes
-
-Following the approach and discussion presented in~\cite{KfirBlumPaper}, Eq.~\ref{eq:Cd} may be generalised as
+Following the approach and discussion presented in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as
 
@@
 for mass number $A$ and the radii $R_{i}$ which describe the volume of the emitting source.
+Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised in \cite{Scheibl:1998tk} as
+\begin{equation}
+\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1}.
+\label{eq:BA_general}
+\end{equation}
+In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes Eq. 9 presented in \cite{Blum:2017qnn}:
+\begin{equation}
+\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
+\label{eq:B3}
+\end{equation}
 
-- add formula from Kfir for B3 and write how it relates to Uli's (or it is derived from it)
-- add a reference to Stanislaw Mrowczinki who also proposed nuclei with very different wave functions which are however experimentally not accessible.
+ where
 
-\begin{figure}[htbp]
-\begin{center}
-%\epsfile{file=,scale=0.8}
-\caption{{Cd vs radius, B2 for point-like objects and realistic wavefunctions}}
-\label{fig:cd}
-\end{center}
-\end{figure}
+ \begin{equation}
+\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1}.
+\label{eq:C3}
+\end{equation}
 
 \subsection{Source volume}
-- describe what ALICE actually measures for multiplicity and say it is known that system size increases with multiplicity (linearly or approx.)
+As in \cite{Scheibl:1998tk}, we identify the source volume as the effective sub-volume of the whole system which is governed by the homogeneity length of the interacting nucleons.
+In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
+Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e.
+different centrality classes \cite{Abelev:2013qoq}.
+In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
+In the following, we make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
+In contrast to \cite{Blum:2017qnn}, we therefore do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
 
-- assumption 1: parameterisation we propose, which is found to describe the deuteron data
+\begin{equation}
+R = a + b \avdNdeta^{1/3} 
+\label{eq:radiusParameterisation}
+\end{equation}
 
-- plot our parameterisation vs the HBT results
+The $a = 0.178$ and $b = 0.367$ coefficients have been determined empirically by interpolating linearly between the value of 0.85 fm and 4.5 fm.
+These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.8$ \GeVc~\cite{Adam:2015vna}.
+The highest $k_{\mathrm{T}}$ bin was chosen as it corresponds in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
+Ideally, one would use the proton femtoscopic radii for such study, but given that these measurements are not  available in all systems, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
+
+- mention that the parameterisation we propose is found to describe the deuteron data
+- mention we assume the three radii are the same, see line 127
+- plot our parameterisation vs the HBT results: take figure 9 from the femto p-Pb paper but do it at high kt and plot one radii which is the geometric average of the three.
 
@@
 \subsection{(Anti-)hyper-nuclei}
-
+- cite Che Ming Ko \cite{Zhang:2018euf} 
 \section{Projections for the LHC Run 3 and 4}\label{sec:projections}

### 2018-04-26 FrascatiPlot/HbtRadii.C
addign bht plot macro

@@ -1,0 +1,235 @@
+#include "B2vsVolume.C"
+
+TGraphErrors * GetPPbHbtRadius025KT();
+TGraphErrors * GetPPbHbtRadius0887KT();
+TGraphErrors * GetPbPbHbtRadius0887KT();
+
+
+void HbtRadii() {
+  //
+  // small macro to plot HBT radii versus multiplicity to compare
+  // them to the parameterisation
+  //
+  TCanvas * canvHbtPlot = new TCanvas("canvHbtPlot","canvHbtPlot");
+  TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{N}/d#it{#eta}#GT^{1/3}; R (fm)",200,0.0,13.0,200,0.0,6.0);
+  histFrame->Draw();
+  //
+  const Long_t nPoints = 500;
+  Double_t xP[nPoints];
+  Double_t yP[nPoints];
+  for (int i = 0; i<nPoints; i++){
+    xP[i] = 15.0 * i / nPoints; 
+    Double_t multi[2] = {xP[i]*xP[i]*xP[i], 0.0};
+    Double_t radius[2] = {0.0, 0.0};
+    getRadiusFromParameterisation(multi, radius);
+    yP[i] = radius[0];
+    //
+  }
+  //
+  TGraph * grRadiusVsMult = new TGraph(nPoints, xP, yP);
+  grRadiusVsMult->SetMarkerStyle(20);
+  grRadiusVsMult->SetMarkerColor(kAzure-7);
+  grRadiusVsMult->SetLineColor(kAzure-7);
+  grRadiusVsMult->SetLineWidth(3);
+  grRadiusVsMult->SetLineStyle(9);
+  //
+  grRadiusVsMult->Draw("L");
+  //
+  // add PPB points
+  //
+  TGraphErrors * grHbtRadiusPPB = GetPPbHbtRadius0887KT();
+  grHbtRadiusPPB->Draw("P");
+  //
+  // add PbPb points
+  //
+  TGraphErrors * grHbtRadiusPBPB = GetPbPbHbtRadius0887KT();
+  grHbtRadiusPBPB->Draw("P");
+  //
+  // add a pp point
[…]

### 2018-04-28 FrascatiPlot/Paper/NucleiB2.tex
adding a link to a summary of hyper-triton paper

@@
 \end{table}
+
+For the table: there seems to be a nice summary here (including that the hyper-triton is spin 1/2):
+https://books.google.fr/books?id=utBKDwAAQBAJ&pg=PA56&lpg=PA56&dq=spin+of+hypertriton&source=bl&ots=x-wqVWSIpJ&sig=k2tZUsruf2M5o-slqOp0Q9v-PCI&hl=de&sa=X&ved=0ahUKEwj1-NOo4t3aAhUCU1AKHbjVCAoQ6AEIczAJ#v=onepage&q=spin%20of%20hypertriton&f=false
+Properties And Interactions Of Hyperons - Proceedings Of U.s.-japan Seminar
+herausgegeben von Barnes Peter D,Nakai K,Gibson Benjamin F
 

### 2018-05-17 FrascatiPlot/HbtRadii.C
new macro for hbt plot

@@ -182,7 +182,7 @@ TGraphErrors * GetPPbHbtRadius0887KT() {
   //
   // Rout and dN/deta
   double p8772_d8x1y1_xval[] = { 2.53, 2.87, 3.27 };
-  double p8772_d8x1y1_xerrminus[] = { 0.0, 0.0, 0.0 };
+  double p8772_d8x1y1_xerrminus[] = { TMath::Power(2.53, -2./3.)*0.4/3, TMath::Power(2.87,-2./3.)*0.5/3., TMath::Power(3.27,-2./3.)*0.8/3. };
   double p8772_d8x1y1_xerrplus[] = { 0.0, 0.0, 0.0 };
   double p8772_d8x1y1_yval[] = { 0.68, 0.77, 0.94 };
   double p8772_d8x1y1_yerrminus[] = { 0.17, 0.18, 0.23 };
@@ -215,7 +215,7 @@ TGraphErrors * GetPPbHbtRadius0887KT() {
   //
   for (Int_t iP =0; iP <3; iP++) {
     xP[iP] = p8772_d8x1y1_xval[iP];
-    xPerr[iP] = p8772_d8x1y1_xerrplus[iP];
+    xPerr[iP] = p8772_d8x1y1_xerrminus[iP];
     yP[iP] = TMath::Power(p8772_d8x1y3_yval[iP]*p8772_d8x1y2_yval[iP]*p8772_d8x1y1_yval[iP], 1./3.);
     Double_t errSyst = TMath::Power(p8772_d8x1y3_yerrplus[iP]*p8772_d8x1y2_yerrplus[iP]*p8772_d8x1y1_yerrplus[iP], 1./3.);
     Double_t errStat = TMath::Power(p8772_d8x1y3_ystatplus[iP]*p8772_d8x1y2_ystatplus[iP]*p8772_d8x1y1_ystatplus[iP], 1./3.);

### 2018-05-17 FrascatiPlot/Paper/NucleiB2.tex
Added HBT radii plot in its latest version: now fitting ALICE data. Added Appendix A on correspondence of BP and TKP parameterisations for HBT radii

@@
 \usepackage{tabularx} 
+\usepackage{appendix}
 
@@
 
-\subsection{Full coalescence}
+\subsection{Full coalescence}{sec:coalescence}
 In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
@@
 In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
+The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
+As discussed in Appendix \ref{appendix1}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$, thus $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
+
 Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e.
@@
 \begin{equation}
-R = a + b \avdNdeta^{1/3} 
+R = a \avdNdeta^{1/3} + b
 \label{eq:radiusParameterisation}
@@
 
-The $a = 0.178$ and $b = 0.367$ coefficients have been determined empirically by interpolating linearly between the value of 0.85 fm and 4.5 fm.
+The coefficients, $a = 0.339$ and $b = 0.128$, have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig.
+\ref{fig:radiiparam}.
 These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.8$ \GeVc~\cite{Adam:2015vna}.
@@
 
-- mention that the parameterisation we propose is found to describe the deuteron data
-- mention we assume the three radii are the same, see line 127
-- plot our parameterisation vs the HBT results: take figure 9 from the femto p-Pb paper but do it at high kt and plot one radii which is the geometric average of the three.
-
 \begin{figure}[htbp]
 \begin{center}
-%\epsfile{file=,scale=0.8}
-\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data.}
-\label{fig:cd}
+\includegraphics[width=0.6\textwidth]{HbtRadiusParam.eps}
+\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Abelev:2012sq}.}
+\label{fig:radiiparam}
 \end{center}
@@
 
+\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
+\section{Comparison with experimental data}\label{sec:comparison}
 - excess binding energy needs to be released to the system to make coalescence work
-
-\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
--
-
-\section{Comparison with experimental data}\label{sec:comparison}
 
@@
 
+%%%%%%%%APPENDIX
+\begin{appendix}
+\section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}
+The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{sside}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
+The ALICE HBT results \cite{Aamodt:2011mr, Adam:2015pwa} are given in the Bertsch-Pratt convention, whereas the coalescence parameter is derived in \cite{Scheibl:1998tk} by expressing the dependence on the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
+The transformation between the two parameterisations is best presented in~\cite{Wiedemann:1999qn} in the equations (W 3.48) to (W 3.52)\footnote{The equations in~\cite{Wiedemann:1999qn} are denoted as (W...) in order to distinguish them from the equations presented in this paper.}:
+
+\begin{eqnarray}
+R_{side}^{2}    &=& R_{\perp}^{2}  \;, \\
+R_{diff}^{2} &=& R_{out}^{2} -  R_{side}^{2} = \beta_{\perp}^2 \gamma^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
+R_{long}^{2}     &=& (1 - \beta_l^2) R_{\parallel}^2 + \gamma^2 (\beta_l - v)^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
+R_{ol}^{2}   &=& \beta_{\perp} (-\beta_l R_{\parallel}^{2} +  \gamma^2 (\beta_l - v)(R_{0}^2 + v^2R_{\parallel}^2)) \,.
+\end{eqnarray}
+%
+We immediately identify that $R_{\perp}^2$ can be identified with $R_{side}^{2}$.
+Following the reasoning and the nomenclature in~\cite{Wiedemann:1999qn} (W 3.52-3.53), the above equations can be inverted and $R_{\parallel}^{2}$ can be expressed as
+%
+\begin{eqnarray}
+R_{\parallel}^{2} &=& B  - v \cdot C \;, \\
+                          &=& R_{long}^2 - 2{\beta_l \over \beta_\perp}  R_{ol}^2 + {\beta_l^2 \over \beta_\perp^2} R_{diff}^2 
+                          - v \cdot \Bigl(-{1 \over \beta_\perp } R_{ol}^2 + {\beta_l \over \beta_\perp^2} R_{diff}^2  \Bigr) \; .
+\end{eqnarray}
+%
+As it turns out all corrections which are subtracted from $R_{long}^{2}$ can be neglected.
+First, we notice that the cross term $R_{ol}$ vanishes if the measured fireball is longitudinally boost-invariant, which is a valid approximation for the rapidity ranges studied here.
+The remaining terms are all proportional to $\beta_l$, which is also $\beta_l = 0$ by definition of the rest frame for a longitudinally-boosted invariant system.
+In summary, we can consider $R_{\perp} = R_{side}$ and $R_{\parallel}=R_{long}$ for the present study.
+\end{appendix}
+
 %%%%% acknowledgements
@@
 \section*{Acknowledgements}
-
+We thank U. Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
 The authors would like to thank themselves for the auto-critics.

### 2018-05-17 FrascatiPlot/B2vsVolume.C

@@ -210,7 +210,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   legB2_coal->Draw();
 
   coalcanv->Print("theory_coalescence_Cd_B2.eps");
-  return 0;
+  //return 0;
   //------------------------------
   // PLOT FRASCATI PLOT
   //------------------------------
@@ -552,13 +552,18 @@ void getRadiusFromParameterisation(Double_t * multi, Double_t * radius)
   //
   // Here is the crucial mapping between HBT radii and multi^(1/3)
   //
-  // NEW VERSION (5th February 2018):
+  // VERSION (5th February 2018):
   // We assume 0.85fm for pp as Kfir (at dNdeta 6.01)
   // We assume R=4.5fm for central Pb-Pb based on arXiv:1012.4035 (figure 2)
   // We interpolate linearly and take the highest kT bin, because
   // a pT/A of 0.8 GeV/c corresponds to mT=1.23GeV which is a kT of pions of 1.2GeV
   //
-  Double_t radiusVal = 0.177825 + 0.36733 * multi3; 
+  //Double_t radiusVal = 0.177825 + 0.36733 * multi3;
+
+  // VERSION (17th May 2018):
+  // We fit linearly the ALICE data at the kT = 0.887
+
+  Double_t radiusVal = 0.128 + 0.339 * multi3; 
   //
   //
   // OLD versions:

### 2018-05-17 FrascatiPlot/HbtRadii.C

@@ -10,8 +10,31 @@ void HbtRadii() {
   // small macro to plot HBT radii versus multiplicity to compare
   // them to the parameterisation
   //
+  gStyle->SetOptStat(0);
+  gStyle->SetOptTitle(0);
+  gStyle->SetOptFit(0);
+  gStyle->SetLineWidth(1);
+  gStyle->SetOptTitle(0);
+  gStyle->SetTitleOffset(0.8,"y");
+  gStyle->SetPadTickX(1);
+  gStyle->SetPadTickY(1);
+  TGaxis::SetMaxDigits(4);
+  gStyle->SetPadLeftMargin(0.15);
+  gStyle->SetPadRightMargin(0.05);
+  gStyle->SetPadBottomMargin(0.15);
+  gStyle->SetPadTopMargin(0.05);
+
   TCanvas * canvHbtPlot = new TCanvas("canvHbtPlot","canvHbtPlot");
-  TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{N}/d#it{#eta}#GT^{1/3}; R (fm)",200,0.0,13.0,200,0.0,6.0);
+  TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{#it{N}_{ch}}/d#it{#eta}#GT^{1/3}; #it{R} (fm)",200,0.0,13.0,200,0.0,6.0);
+  histFrame->GetXaxis()->SetTitleSize(0.06);
+  histFrame->GetXaxis()->SetLabelSize(0.045);
+  histFrame->GetXaxis()->SetTitleOffset(1.1);
+  histFrame->GetYaxis()->SetTitleOffset(1.2);
+  histFrame->GetYaxis()->SetTitleSize(0.06);
+  histFrame->GetYaxis()->SetLabelOffset(0.01);
+  histFrame->GetYaxis()->SetLabelSize(0.045);
+
+  histFrame->GetYaxis()->SetTitleOffset(1.);
   histFrame->Draw();
   //
   const Long_t nPoints = 500;
@@ -26,24 +49,32 @@ void HbtRadii() {
     //
   }
   //
-  TGraph * grRadiusVsMult = new TGraph(nPoints, xP, yP);
-  grRadiusVsMult->SetMarkerStyle(20);
[…]

### 2018-05-22 FrascatiPlot/Paper/NucleiB2.tex
Minor updates to text

@@
 
-The coefficients, $a = 0.339$ and $b = 0.128$, have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig.
-\ref{fig:radiiparam}.
+The coefficients, $a = 0.339$ and $b = 0.128$, have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
 These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.8$ \GeVc~\cite{Adam:2015vna}.
 The highest $k_{\mathrm{T}}$ bin was chosen as it corresponds in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii for such study, but given that these measurements are not  available in all systems, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
+Ideally, one would use the proton femtoscopic radii for such study, but given that these measurements are not  available in all collision systems, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
 
@@
 \section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
+
+Nuclei form at chemical freeze-out and their yields are determined only by mass and chemical freeze-out temperature:  dN/dy ~ exp (-m/Tch)
+pT spectra have been modeled with a Blast-Wave parameterization, with params. fixed by fit to ?,K,p
+
+Normalisation for the spectra is fixed to the d/? (3He/?) ratio from thermal model times the measured ? yield.
+
+Normalisation for 3LH is extracted from the 3He and the S3 predicted by thermal model
+
 \section{Comparison with experimental data}\label{sec:comparison}

### 2018-05-22 FrascatiPlot/Paper/YanoKoonin.tex
Add Alex's write up on HBT radii parameterisation

\RequirePackage{ifpdf}

%\documentclass[a4paper,11pt]{scrartcl} % scrartcl scrreprt
\documentclass[a4paper,11pt]{scrartcl} % scrartcl scrreprt

\usepackage[margin=1.5cm]{geometry}

\ifpdf
  \usepackage[pdftex]{graphicx}
\else
  \usepackage[dvips]{graphicx}
\fi

\usepackage[utf8]{inputenc}

\usepackage[T1]{fontenc}

\usepackage{amsmath}
\usepackage[amssymb]{SIunits}
\usepackage{hyperref}

%\usepackage{lineno}
%\linenumbers

%
% DOCUMENT STARTS HERE
%

\begin{document}
\begin{center}
{\large {\bf HBT volume in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}}
\bigskip

A. Kalweit, 12th of June 2015
\end{center}

%\smallskip

%
% Introduction
%

\paragraph{Introduction.}

\noindent The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{o}$, $R_{s}$, $R_{l}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization. The ALICE HBT results \cite{Aamodt:2011mr} are given in the Bertsch-Pratt convention. However, for a comparison with coalescence models for deuteron production, the volume expressed in terms of the Yano-Koonin-Podgoretskii (YKP) is needed, because the coalescence parameter $B_{2}$ is given by

\begin{equation}
 B_{2} = \frac{3\pi^{3/2} \langle C_{\rm d}\rangle}{2m_{\rm T} R^{2}_{\perp}(m_{\rm T}) R_{\parallel}(m_{\rm T})}  \; ,
\label{B2nCd}
\end{equation}

\noindent as derived in \cite{Scheibl:1998tk}. We therefore need to express $R^{2}_{\perp}(m_{\rm T}) R_{\parallel}(m_{\rm T})$ in terms of the Bertsch-Pratt (BP) radii.

\paragraph{Transformation.} The transformation between the two parameterisations is best presented in~\cite{Wiedemann:1999qn} in the equations (W 3.48) to (W 3.52)\footnote{The equations in~\cite{Wiedemann:1999qn} are denoted as (W...) in order to distinguish them from the equations presented in this writeup.}:

\begin{eqnarray}
R_{s}^{2}    &=& R_{\perp}^{2}  \;, \\
R_{diff}^{2} &=& R_{o}^{2} -  R_{s}^{2} = \beta_{\perp}^2 \gamma^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
R_{l}^{2}     &=& (1 - \beta_l^2) R_{\parallel}^2 + \gamma^2 (\beta_l - v)^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
R_{ol}^{2}   &=& \beta_{\perp} (-\beta_l R_{\parallel}^{2} +  \gamma^2 (\beta_l - v)(R_{0}^2 + v^2R_{\parallel}^2)) \,.
\end{eqnarray}

\noindent From this we immediately identify that we can replace $R_{\perp}^2$ with $R_{s}^{2}$ in Equation~(\ref{B2nCd}). However, an expression for $R_{\parallel}$ is still needed. The inversion of the above equations is also explained in~\cite{Wiedemann:1999qn}. Following this nomenclature (W 3.52-3.53), $R_{\parallel}^{2}$ can thus be expressed as

%\begin{eqnarray}
% R_{\parallel}^{2} &=& B  - v \cdot C \;, \\
%                          &=& R_l^2 - 2{\beta_l \over \beta_\perp}  R_{ol}^2 + {\beta_l^2 \over \beta_\perp^2} R_{diff}^2 \\
%                           &  &  - v \cdot \Bigl(-{1 \over \beta_\perp } R_{ol}^2 + {\beta_l \over \beta_\perp^2} R_{diff}^2  \Bigr) \; .
%\end{eqnarray}
\begin{eqnarray}
R_{\parallel}^{2} &=& B  - v \cdot C \;, \\
                          &=& R_l^2 - 2{\beta_l \over \beta_\perp}  R_{ol}^2 + {\beta_l^2 \over \beta_\perp^2} R_{diff}^2 
                          - v \cdot \Bigl(-{1 \over \beta_\perp } R_{ol}^2 + {\beta_l \over \beta_\perp^2} R_{diff}^2  \Bigr) \; .
\end{eqnarray}

\noindent As it turns out all corrections which are subtracted from $R_{l}^{2}$ can be neglected.

\begin{itemize}
	\item As also stated in \cite{Aamodt:2011mr}, $R_{ol} \approx 0$ for symmetric collision systems. Since this is the case in Pb--Pb collisions (for p--Pb collisions one would probably need to be careful).
	\item The remaining terms are all proportional to $\beta_l$. Since the ALICE HBT results are always presented in the LCMS (longitudinally co-moving system) frame, $\beta_l = 0$ by the definition of the rest frame.

\end{itemize}

\noindent We can thus summarise our findings as: $R_{\perp}=R_{s}$ and $R_{\parallel}=R_{l}$ for symmetric collision systems and results presented in the LCMS.

\bigskip

\begin{thebibliography}{9} % !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! ORDER THEM !!!!!!!!!!!!!!!!!!!!!!!!!!!!!

 \bibitem{Aamodt:2011mr}
  K.~Aamodt {\it et al.}  [ALICE Collaboration],
  %``Two-pion Bose-Einstein correlations in central Pb-Pb collisions at $sqrt(s_NN)$ = 2.76 TeV,''
  Phys.\ Lett.\ B {\bf 696} (2011) 328
  [arXiv:1012.4035 [nucl-ex]].
  %%CITATION = ARXIV:1012.4035;%%
  %170 citations counted in INSPIRE as of 12 Jun 2015

 \bibitem{Wiedemann:1999qn}
  U.~A.~Wiedemann and U.~W.~Heinz,
  %``Particle interferometry for relativistic heavy ion collisions,''
  Phys.\ Rept.\  {\bf 319} (1999) 145
  [nucl-th/9901094].
  %%CITATION = NUCL-TH/9901094;%%
  %336 citations counted in INSPIRE as of 12 juin 2015

 \bibitem{Scheibl:1998tk}
  R.~Scheibl and U.~W.~Heinz,
  %``Coalescence and flow in ultrarelativistic heavy ion collisions,''
  Phys.\ Rev.\ C {\bf 59} (1999) 1585
  [nucl-th/9809092].
  %%CITATION = NUCL-TH/9809092;%%
  %117 citations counted in INSPIRE as of 12 juin 2015

\end{thebibliography}

\end{document}

%%
%% End of file.

### 2018-05-22 FrascatiPlot/Paper/NucleiB2.tex
adding a lot of text

@@
 For the table: there seems to be a nice summary here (including that the hyper-triton is spin 1/2):
-https://books.google.fr/books?id=utBKDwAAQBAJ&pg=PA56&lpg=PA56&dq=spin+of+hypertriton&source=bl&ots=x-wqVWSIpJ&sig=k2tZUsruf2M5o-slqOp0Q9v-PCI&hl=de&sa=X&ved=0ahUKEwj1-NOo4t3aAhUCU1AKHbjVCAoQ6AEIczAJ#v=onepage&q=spin%20of%20hypertriton&f=false
+%https://books.google.fr/books?id=utBKDwAAQBAJ&pg=PA56&lpg=PA56&dq=spin+of+hypertriton&source=bl&ots=x-wqVWSIpJ&sig=k2tZUsruf2M5o-slqOp0Q9v-PCI&hl=de&sa=X&ved=0ahUKEwj1-NOo4t3aAhUCU1AKHbjVCAoQ6AEIczAJ#v=onepage&q=spin%20of%20hypertriton&f=false
 Properties And Interactions Of Hyperons - Proceedings Of U.s.-japan Seminar
@@
 \subsection{Source volume}
+\label{SecSourceVolume}
 As in \cite{Scheibl:1998tk}, we identify the source volume as the effective sub-volume of the whole system which is governed by the homogeneity length of the interacting nucleons.
@@
 
+- excess binding energy needs to be released to the system to make coalescence work
+
 \section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
 
-Nuclei form at chemical freeze-out and their yields are determined only by mass and chemical freeze-out temperature:  dN/dy ~ exp (-m/Tch)
-pT spectra have been modeled with a Blast-Wave parameterization, with params. fixed by fit to ?,K,p
-
-Normalisation for the spectra is fixed to the d/? (3He/?) ratio from thermal model times the measured ? yield.
-
-Normalisation for 3LH is extracted from the 3He and the S3 predicted by thermal model
+In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
+As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
+In contrast to the coalescence approach, the current implementations~\cite{} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra. 
+In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modeled using a blast-wave~\cite{} parameterization.
+When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{}.
+The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{}.
+This choice is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{}.
+In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio \cite{} and the measured \hethree~yield \cite{}.
+Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/A and compare it with coalescence expectations.
+Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality/multiplicity classes, we use the corresponding \avdNdeta~in the same class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
+In contrast to the coalescence approach which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model, which as a simplified hydrodynamic model treats the system based as a continuum and is not particle based.
+The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg prediction used here).
+We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Volodya} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
 
 \section{Comparison with experimental data}\label{sec:comparison}
-- excess binding energy needs to be released to the system to make coalescence work
+
+Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{}. 
+In Fig. \ref{} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.  
+First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown with \textcolor{red}{empty markers}).
+We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo.
+Therefore, in a second step the radius is tuned such that the data points for (anti-) deuterons fall onto the coalescence prediction (solid markers).
+We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be \textcolor{red}{$a = xxx$ and $b = yyy$}.
+With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree.
+As shown in Fig.~\ref{}, also in the case of \bthree, a tension between the model and the data is found which persists with both parameterisations.
+It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
+
+- discuss sensitivity to the choice of the kT for the radii parameterisation.
+
+- add a plot with different radii for hyper-triton from 10fm to 3fm
+
+- add a plot for A=4
+
+- add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
 

### 2018-05-22 FrascatiPlot/B2vsVolume.C
adapting macro to make plots for papers.

@@ -4,73 +4,99 @@
 #include "TMath.h"
 #include "./generateBWpredictionsB2.C" //ADAPT ME
 
+void convertMultiToRadius(TGraphErrors * graph = 0x0, Int_t paramSet = 0);
+void convertMultiToRadius(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 0);
+
+void getRadiusFromParameterisation(Double_t * multi = 0x0, Double_t * radius = 0x0, Int_t paramSet = 0);
 TF1 * MakeB2TheoryGraphQMfactor(Double_t objSize = 3.2);
 TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 3.2);
 TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 1.75);
 
-TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75);
-TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75);
-TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75);
-TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75);
+TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 
-TGraphErrors      * getB3_PbPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733);
-TGraphErrors      * getB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733);
[…]

### 2018-05-23 FrascatiPlot/B2vsVolume.C
starting paper figures

@@ -1,4 +1,5 @@
-/* akalweit@cern.ch, fbellini@cern.ch
+/*
+   akalweit@cern.ch, fbellini@cern.ch
    17.01.2018 - The Frascati plot
 */
 #include "TMath.h"
@@ -13,13 +14,14 @@ TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize 
 TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 1.75);
 
 TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphErrors * getB2_pp7TeVINEL(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 
 TGraphErrors      * getB3_PbPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
 TGraphErrors      * getB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
-TGraphAsymmErrors * getB3_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3pp = 0.800, Int_t paramSet = 0);
+TGraphAsymmErrors * getB3_pp7TeVINEL(Bool_t plotSys = 0, Double_t pToAb3pp = 0.800, Int_t paramSet = 0);
 TGraphAsymmErrors * getB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1., Int_t paramSet = 0);
 
 TGraphAsymmErrors * getBlastB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
[…]

### 2018-05-23 FrascatiPlot/B2vsVolume.C
Updated plotting macros to include figure for paper: - for pp now using INEL dN/deta and point from 2018 ALICE paper - new figure for comparison of scaling of R with different parameterisations - added eps files

@@ -261,80 +261,92 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
 
   enum EPlotEntries { kPP7, kPPB502, kPBPB276, kPBPB502,
 		      kPP7blast, kPPB502blast, kPBPB276blast, kPBPB502blast,
-		      kB3_PP7, kB3_PPB502, kB3_PBPB276, kB3_PBPB502,
-		      kB3_PP7blast, kB3_PPB502blast, kB3_PBPB276blast, kB3_PBPB502blast};
+		      kB3_PP7, kB3_PPB502, kB3_PBPB276, kB3_PBPB502, kB3L_PBPB276,
+		      kB3_PP7blast, kB3_PPB502blast, kB3_PBPB276blast, kB3_PBPB502blast, kB3L_PBPB276blast};
   
   Color_t color[]      = {kGreen+2, kBlue+2, kRed+1, kRed+2,
 			   kGreen+2, kBlue+2, kRed+1, kRed+2,
-			   kGreen+2, kSpring+4, kRed+1, kRed+2,
-			   kBlue-5, kBlue-7, kRed+1, kRed+2};
+			  kGreen+2, kSpring+4, kRed+1, kRed+2, kAzure-6,
+			  kBlue-5, kBlue-7, kRed+1, kRed+2, kAzure-6};
   
-  Int_t Marker_Style[] = { 23, 22, 21, 20,
-			   23, 22, 21, 20,
-			   23, 22, 21, 20,
-			   23, 22, 21, 20};
+  Int_t Marker_Style[] = { 21, 22, 20, 23,
+			   21, 22, 20, 23,
+			   21, 22, 20, 23, 33,
+			   21, 22, 20, 23, 33};
   
   for (Int_t ip = 0; ip < nParamSet; ip++) {
-    MakeUp(gB2vsR_pp7TeV_sys[ip], color[EPlotEntries::kPP7], color[EPlotEntries::kPP7], Fill_Style, Line_Style, Line_Width, Marker_Style[EPlotEntries::kPP7]+4*ip, Marker_Size);
-    MakeUp(gB2vsR_pp7TeV[ip]    , color[EPlotEntries::kPP7], color[EPlotEntries::kPP7], Fill_Style, Line_Style, Line_Width, Marker_Style[EPlotEntries::kPP7]+4*ip, Marker_Size);
[…]

### 2018-05-23 FrascatiPlot/GetB3inpToA.C

@@ -17,10 +17,14 @@ void GetB3inpToA_pp7TeV()
   if (!gB30100) return;
   if (!gB30100_sys) return;
   
-  //for multi INEL>0 Eur. Phys. J. C 77 (2017) 33, Link: https://link.springer.com/article/10.1140/epjc/s10052-016-4571-1
+  //for multi INEL Eur. Phys. J. C 77 (2017) 33, Link: https://link.springer.com/article/10.1140/epjc/s10052-016-4571-1
   const Int_t nP = 3;
-  Double_t dndeta[nP] = {5.98};
-  Double_t dndetaErr[nP] = {0.09};
+  Double_t dndeta[nP] = {4.60};
+  Double_t dndetaErr[nP] = {0.34};
+
+  //Following are INEL > 0
+  //  Double_t dndeta[nP] = {5.98};
+  // Double_t dndetaErr[nP] = {0.09};
 
   TFile * fout = new TFile("B3pToA_pp7TeV.root","recreate");
 

### 2018-05-23 FrascatiPlot/B2vsVolume.C
save plot into paper folder

@@ -443,7 +443,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   paveB->Draw();
   legC->Draw();
 
-  cr1->Print("radiiParamCompareData.eps");
+  cr1->Print("Paper/radiiParamCompareData.eps");
   
   if (plotPaperFigures) return 0;
 

### 2018-05-23 FrascatiPlot/Paper/NucleiB2.tex

@@
 
+ --> Mention (if true, please check) that this assumes a gaussian wave function of the produced object.
+This might not be true in reality for the hyper-triton, but it allows to show the sensitivity of the wave-function and gives easy analytic expressions.
+
 \subsection{Source volume}
@@
 With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree.
-As shown in Fig.~\ref{}, also in the case of \bthree, a tension between the model and the data is found which persists with both parameterisations.
+As shown in Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found which ameliorates with the parameterisation which is tuned to the (anti-)deuteron data..
 It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
+
+ \begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=\textwidth]{radiiParamCompareData.eps}
+\caption{Comparison of the ALICE data from~\cite{} with the coalescence prediction for two different mappings of the \avdNdeta to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo values in central Pb-Pb collisions.}
+\label{fig:CompareB2B3forDifferentParamWithData}
+\end{center}
+\end{figure}
 

### 2018-05-24 FrascatiPlot/B2vsVolume.C
added figure in png

@@ -264,10 +264,10 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
 		      kB3_PP7, kB3_PPB502, kB3_PBPB276, kB3_PBPB502, kB3L_PBPB276,
 		      kB3_PP7blast, kB3_PPB502blast, kB3_PBPB276blast, kB3_PBPB502blast, kB3L_PBPB276blast};
   
-  Color_t color[]      = {kGreen+2, kBlue+2, kRed+1, kRed+2,
-			   kGreen+2, kBlue+2, kRed+1, kRed+2,
-			  kGreen+2, kSpring+4, kRed+1, kRed+2, kAzure-6,
-			  kBlue-5, kBlue-7, kRed+1, kRed+2, kAzure-6};
+  Color_t color[]      = {kGreen+2, kBlue+2, kRed, kRed+2,
+			  kGreen+2, kBlue+2, kRed, kRed+2,
+			  kGreen+2, kSpring+4, kRed, kRed+2, kAzure-6,
+			  kBlue-5, kBlue-7, kRed, kRed+2, kAzure-6};
   
   Int_t Marker_Style[] = { 21, 22, 20, 23,
 			   21, 22, 20, 23,
@@ -402,48 +402,49 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   cr1->cd(1);
   gPad->SetLogy();
   hframe->Draw();
-  hB2_coalescence->Draw("l");
   gB2vsR_pp7TeVINEL_sys[0]->Draw("samep2");
   gB2vsR_pp7TeVINEL[0]->Draw("samepz");
   gB2vsR_PbPb276TeV_sys[0]->Draw("samep3");
   gB2vsR_PbPb276TeV[0]->Draw("samepz");
+  hB2_coalescence->Draw("l");
   pavept->Draw();
   paveA->Draw();
   
   cr1->cd(2);
   gPad->SetLogy();
   hframe->Draw();
-  hB2_coalescence->Draw("l");
   gB2vsR_pp7TeVINEL_sys[1]->Draw("samep2");
   gB2vsR_pp7TeVINEL[1]->Draw("samepz");
   gB2vsR_PbPb276TeV_sys[1]->Draw("samep3");
   gB2vsR_PbPb276TeV[1]->Draw("samepz");
+  hB2_coalescence->Draw("l");
[…]

### 2018-06-06 FrascatiPlot/Paper/NucleiB2.tex
adding a reminder to mention also the Braaten paper
Alexander starts doing some minor fixes

@@
 
-\section{Coalescence approach} \label{sec:coalescence}
+\section{Coalescence approach} 
+\label{sec:coalescence}
 
@@
 
-\subsection{Full coalescence}{sec:coalescence}
+\subsection{Full coalescence}
+\label{subsec:FullCoalescence}
+
 In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
@@
 - cite Che Ming Ko \cite{Zhang:2018euf}
+
+\subsection{Other exotic QCD objects}
+
+We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature.
+One of them is the X(3872) which might have a wide wave-function as described in http://inspirehep.net/record/861896?ln=de
+
 \section{Projections for the LHC Run 3 and 4}\label{sec:projections}

### 2018-06-06 FrascatiPlot/Paper/NucleiB2.tex
intermediate commit not to loose changes

@@
 
-\usepackage[margin=2.cm]{geometry}
+\usepackage[margin=2.5cm]{geometry}
 \usepackage{multirow}
 \usepackage{tabularx} 
+\usepackage{rotating,graphicx} 
 \usepackage{appendix}
 
-\ifpdf
-  \usepackage[pdftex]{graphicx}
-\else
-  \usepackage[dvips]{graphicx}
-\fi
+%\ifpdf
+%  \usepackage[pdftex]{graphicx}
+%\else
+%  \usepackage[dvips]{graphicx}
+%\fi
 
@@
 \begin{center}
-{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei at LHC energies with recent and future Run 3 and 4 data}}
+{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies with recent and future experimental data}}
 
@@
 
-26th of February 2018
+16th of May 2018
 \end{center}
@@
 At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models.
-While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals largely different predictions between the two approach for the production of 3He and hyper-tritons.
+While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals largely different predictions between the two approach for the production of \hethree\ and hyper-tritons.
 Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions.
 The thermal-statistical model on the other hand is in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system.
-Our finding thus indicate the existence of a novel production mechanism for these objects.
+Our findings thus indicate the existence of a novel production mechanism for these objects.
 \end{abstract}
@@
 %%Table of contents - to be removed for submission%%
+\newpage
 \tableofcontents
@@
 The formation of light anti- and hyper- nuclei in highly energetic proton-proton, proton-nucleus and nucleus-nucleus collisions provides unique observables for the study of the system created in these collisions.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons, because their size is comparable to a fraction or the whole system created in the collision \cite{}.
-The relevant properties of the objects under study are summarised in Table \ref{tab:nucleusradii}
+In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons, because their size (i.e.
+the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
+Halo nuclei as 6He would be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
+It must be noted, that these studies thus do not only shed light on the characteristics of the system created in the collision (if (anti-)nuclei with well known properties are studied), but also on the internal structure of the produced objects if their properties are not well known.
+The relevant known properties of the objects under study are summarised in Table \ref{tab:nucleusradii}.
 As quantum-mechanical objects, their size is typically defined as the rms of their wave function, which ranges from \textcolor{red}{xx fm for the 3He up to yy fm for the hyper-triton}.
-Halo nuclei as 6He would be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
+For simplicity, we approximate the wave-function of the objects under study by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk}.
+This allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
+We encourage future more rigorous studies which address the coalescence probabilities with more precise wave-functions.
 
@@
 
-\begin{table}[b]
+\begin{sidewaystable}[p]
 
 \centering
-\begin{tabularx}{\textwidth}{cccccc}
-\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
-A = 2                           & d                           & pn                              & 2.2                                          & 3.2                                                 &                           \\ \hline
-\multirow{3}{*}{A = 3}  & \tritium 	         & pnn                            &                                                &                                                     &                           \\
-                                   & \hethree                & ppn                            &                                                &                                                     &                           \\
-                                   & \hthreelambda      & p$\Lambda$n       &                                                &                                                     &                           \\ \hline
-\multirow{4}{*}{A = 4}  & \hefour                  & ppnn                                    &                                                &                                                     &                           \\
-                                   & \hfourlambda        & p$\Lambda$nn          &                                              &                                                     &                           \\
-                                   & \hfourtwolambda  &  p$\Lambda\Lambda$n                                   &                                              &                                                     &                           \\
-                                   & \hefourlambda      & pp$\Lambda$n                                    &                                              &                                                     &                           \\ \hline
+\begin{tabularx}{\textwidth}{cccccccc}
+%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
+Mass number             & Nucleus                         & Composition                   & $B_{E}$ (MeV)   & Spin $J$ & rms radius of wavefunction (fm) &  harmonic oscillator width r (fm)   & Refs.
+\\ \hline
+A = 2                           & d                                    & pn                                   &   2.2                    &     1       & 2.1413 $\pm$ 0.0025                 &  3.2                                                &   \cite{Mohr:2015ccw}      \\ \hline
+\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                                &    8.4817986 (20) &      1/2   &  1.755  $\pm$ 0.086                   &                                                     &   \cite{Purcell:2015gtm}           \\
+                                   & \hethree                         & ppn                                &                            &        1/2    &                                                   &                                                       &   \cite{Purcell:2015gtm} \\
+                                   & \hthreelambda               & p$\Lambda$n                &                             &                 &                                                   &                                                      & \\ \hline
+\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &                              &                 &                                                   &                                                       & \\
+                                   & \hfourlambda                & p$\Lambda$nn              &                               &               &                                                    &                                                       &  \\
+                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &                                &               &                                                    &                                                       &\\
+                                   & \hefourlambda              & pp$\Lambda$n              &                               &                &                                                    &                                                      &\\ \hline
 \end{tabularx}
@@
 \label{tab:nucleusradii}
-\end{table}
+\end{sidewaystable}
 
@@
 The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{sside}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
-The ALICE HBT results \cite{Aamodt:2011mr, Adam:2015pwa} are given in the Bertsch-Pratt convention, whereas the coalescence parameter is derived in \cite{Scheibl:1998tk} by expressing the dependence on the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
+The ALICE HBT results \cite{Aamodt:2011mr, Adam:2015vna} are given in the Bertsch-Pratt convention, whereas the coalescence parameter is derived in \cite{Scheibl:1998tk} by expressing the dependence on the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
 The transformation between the two parameterisations is best presented in~\cite{Wiedemann:1999qn} in the equations (W 3.48) to (W 3.52)\footnote{The equations in~\cite{Wiedemann:1999qn} are denoted as (W...) in order to distinguish them from the equations presented in this paper.}:

### 2018-06-06 FrascatiPlot/Paper/NucleiB2.tex
table updated, problem with harmonic oscillator width found

@@
 %\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
-Mass number             & Nucleus                         & Composition                   & $B_{E}$ (MeV)   & Spin $J$ & rms radius of wavefunction (fm) &  harmonic oscillator width r (fm)   & Refs.
-\\ \hline
-A = 2                           & d                                    & pn                                   &   2.2                    &     1       & 2.1413 $\pm$ 0.0025                 &  3.2                                                &   \cite{Mohr:2015ccw}      \\ \hline
+Mass number             & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & charge rms radius (fm) &  harmonic oscillator width r (fm)  & Refs. \\ \hline
+A = 2                           & d                                    & pn                                  &   2.224575 (9)     &     1       & 2.1413 $\pm$ 0.0025                 &  3.2                                 &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
 \multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) &      1/2   &  1.755  $\pm$ 0.086                   &                                                     &   \cite{Purcell:2015gtm}           \\
-                                   & \hethree                         & ppn                                &                            &        1/2    &                                                   &                                                       &   \cite{Purcell:2015gtm} \\
+                                   & \hethree                         & ppn                                &   7.7180428  (23) &        1/2    & 1.959 $\pm$  0.030                  &                                                       &   \cite{Purcell:2015gtm} \\
                                    & \hthreelambda               & p$\Lambda$n                &                             &                 &                                                   &                                                      & \\ \hline
-\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &                              &                 &                                                   &                                                       & \\
+\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0         &  1.6755 $\pm$ 0.0028             &                                                       & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                    & \hfourlambda                & p$\Lambda$nn              &                               &               &                                                    &                                                       &  \\

### 2018-06-07 FrascatiPlot/Paper/NucleiB2.tex
first almost complete version of the master table.

@@
 \centering
-\begin{tabularx}{\textwidth}{cccccccc}
+\begin{tabularx}{\textwidth}{XcccccXc}
 %\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
-Mass number             & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & charge rms radius (fm) &  harmonic oscillator width r (fm)  & Refs. \\ \hline
+Mass \newline number & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & (charge) rms \newline radius (fm) &  harmonic oscillator  \newline width r (fm)  & Refs.
+\\ \hline
 A = 2                           & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
@@
                                    & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &              &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &                             &                 &                                                   &                                                      & \\ \hline
+                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &            & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
 \multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &             & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
-                                   & \hfourlambda                & p$\Lambda$nn              &                               &               &                                                    &                                                       &  \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &                               &               &                                                    &                                                       &\\
-                                   & \hefourlambda              & pp$\Lambda$n              &                               &                &                                                    &                                                      &\\ \hline
+                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
+                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1 (cf text in \cite{Nemura:1999qp})    &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
+                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline
 \end{tabularx}

### 2018-06-08 FrascatiPlot/Paper/NucleiB2.tex
intermediate commit

@@
 \section{Introduction} 
-The formation of light anti- and hyper- nuclei in highly energetic proton-proton, proton-nucleus and nucleus-nucleus collisions provides unique observables for the study of the system created in these collisions.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons, because their size (i.e.
+The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
+In addition, these studies might shed light on the internal structure of the formed objects themselves.
+In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e.
 the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
-Halo nuclei as 6He would be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
-It must be noted, that these studies thus do not only shed light on the characteristics of the system created in the collision (if (anti-)nuclei with well known properties are studied), but also on the internal structure of the produced objects if their properties are not well known.
-The relevant known properties of the objects under study are summarised in Table \ref{tab:nucleusradii}.
-As quantum-mechanical objects, their size is typically defined as the rms of their wave function, which ranges from \textcolor{red}{xx fm for the 3He up to yy fm for the hyper-triton}.
-For simplicity, we approximate the wave-function of the objects under study by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk}.
-This allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-We encourage future more rigorous studies which address the coalescence probabilities with more precise wave-functions.
+The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
+As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
+Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
+Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm which is significantly larger than that of non-strange A=3 nuclei.
+This is driven by the average separation of the Lambda with respect to the two other nucleons which is expected to amount up to 10 fm.
+In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
 
-Surprisingly, thermal-statistical models have been successful at describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem}$ = 156 MeV (near the temperature at the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz}.
+Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
+In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem}$ = 156 MeV (near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz}).
 Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
@@
 %\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
-Mass \newline number & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & (charge) rms \newline radius (fm) &  harmonic oscillator  \newline width r (fm)  & Refs.
+Mass \newline number & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & (charge) rms radius (fm) &  harmonic oscillator  \newline width r (fm)  & Refs.
 \\ \hline
@@
 \end{sidewaystable}
-
-For the table: there seems to be a nice summary here (including that the hyper-triton is spin 1/2):
-%https://books.google.fr/books?id=utBKDwAAQBAJ&pg=PA56&lpg=PA56&dq=spin+of+hypertriton&source=bl&ots=x-wqVWSIpJ&sig=k2tZUsruf2M5o-slqOp0Q9v-PCI&hl=de&sa=X&ved=0ahUKEwj1-NOo4t3aAhUCU1AKHbjVCAoQ6AEIczAJ#v=onepage&q=spin%20of%20hypertriton&f=false
-Properties And Interactions Of Hyperons - Proceedings Of U.s.-japan Seminar
-herausgegeben von Barnes Peter D,Nakai K,Gibson Benjamin F
 
@@
 While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.
-\textcolor{red}{Consider mentioning the approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
+
+\textcolor{red}{In particular, we approximate the wave-function of the objects under study by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk}.
+This allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
+In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter $r$ of the harmonic oscillator potential.
+We encourage future more rigorous studies which address the coalescence probabilities with more realistic wave-functions.
+Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
 In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.

### 2018-06-08 FrascatiPlot/Paper/NucleiB2.tex
mess found everywhere. not sure if we do is all wrong

@@
 \usepackage{appendix} 
+\usepackage{makecell}
 
@@
 Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically.
-This is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV.
+At LHC energies, this is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
 In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects.
-For instance, the binding energy of the deuteron is $E_{B, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
+For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
 As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products (check statement) \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
@@
 
-\begin{sidewaystable}[p]
+\begin{table}[htb]
 
 \centering
-\begin{tabularx}{\textwidth}{XcccccXc}
-%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
-Mass \newline number & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & (charge) rms radius (fm) &  harmonic oscillator  \newline width r (fm)  & Refs.
+\begin{tabularx}{\textwidth}{cccccccc}
+%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.}
+ \hline \hline
+\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J$ & \makecell{(charge) \\rms\\ radius (fm)} &  \makecell{harmonic \\ oscillator \\ width \\r (fm) } & Refs.
 \\ \hline
@@
                                    & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1 (cf text in \cite{Nemura:1999qp})    &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline
+                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
+                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
 \end{tabularx}
 \caption{Properties of nuclei and hyper-nuclei.
-$B_{E}$ is the binding energy per nucleon in MeV and the radius is given in terms of the rms radius of the wavefunction.
-References are given in the last column.}
+$B_{E}$ is the binding energy in MeV.
+The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction.
+The size parameter $r$ of the wave-function of the harmonic oscillator potential is chosen such that the measured/expected rms is approximately reproduced (see text for details).
+References are given in the last column.
+The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
 \label{tab:nucleusradii}
-\end{sidewaystable}
+\end{table}
 
@@
 However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
-In section \ref{sec:projections} we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
+In section \ref{sec:projections}, we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
 As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
@@
 \subsection{Simple coalescence}
-In simple coalescence, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}.
+In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}.
 For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$, which is defined as

### 2018-06-11 FrascatiPlot/Paper/NucleiB2.tex
small changes, next is the big change about the harmonic oscillator potential

@@
 The thermal-statistical model on the other hand is in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system.
-Our findings thus indicate the existence of a novel production mechanism for these objects.
+Our findings thus indicate the existence of a novel production mechanism for these objects and highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects.
 \end{abstract}
@@
 While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
-In addition, the elliptic flow of deuteron cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.
+In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.
 

### 2018-06-18 FrascatiPlot/Paper/NucleiB2.tex
updates to text

@@
  \hline \hline
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J$ & \makecell{(charge) \\rms\\ radius (fm)} &  \makecell{harmonic \\ oscillator \\ width \\r (fm) } & Refs.
+\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J$ & \makecell{(charge) \\rms\\ radius (fm)} &  \makecell{harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
 \\ \hline
@@
 
-\textcolor{red}{In particular, we approximate the wave-function of the objects under study by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk}.
-This allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter $r$ of the harmonic oscillator potential.
+In particular, the wave-function of the objects under study are approximated by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
+For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
+
+\begin{equation}
+ \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
+\end{equation}
+
+\noindent For larger nuclei (A > 2), analogous forms exist (see for instance~\cite{Scheibl:1998tk} for the explicit form of A=3).
+The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
+
+\begin{equation}
+ {\rm rms}_{A}^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
+\end{equation}
+
+\noindent for point-like constituents. In particular, we obtain $r_{d}=\sqrt{4/3}{\rm rms}_{d}$ for A= 2, $r_{3}= {\rm rms}_{3}$ for A = 3, and ???????.
+
+This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
+In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter $r_{A}$ of the harmonic oscillator potential.
 We encourage future more rigorous studies which address the coalescence probabilities with more realistic wave-functions.
-Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
+\textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
+
 In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
@@
 %
-where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lenghts of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
+where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
 The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation

### 2018-06-20 FrascatiPlot/Paper/NucleiB2.tex
updates in appendix to show equivalence with Sato

@@
 In summary, we can consider $R_{\perp} = R_{side}$ and $R_{\parallel}=R_{long}$ for the present study.
+
+\section{Relation to the model proposed by Sato and Yazaki}
+
+As discussed in~\cite{Nagle:1996vp}, the appraoch of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions and thus neglect the collective expansion of the medium as in~\cite{Scheibl:1998tk}.
+
+For the deuteron, they arrive at an expression for the coalescence momentum $p_{0}$ which equals
+
+\begin{equation}
+	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} (\nu_{d}\nu/(\nu_d + \nu))^{3/2}
+\end{equation}
+
+\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$.
+The coalescence process in~\cite{Sato:1981ez} is formulated in terms of the momentum per nucleon $p_{p,n}$ and thus it relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
+
+\begin{equation}
+B_{A} = ({4 \over 3} \pi p_{0}^{3})^{A-1} {M \over m^{A}} {1 \over A^{3}}
+\end{equation}
+
+\noindent where the factor ${1 \over A^{3}}$ results from the transformation of $p_{A} \rightarrow A p_{p,n}$ and $M$ corresponds to the nucleus mass and $m$ to the nucleon mass.
+This expression can be further simplified via the approximation $M \approx A m$ to
+
+\begin{equation}
+B_{A} = ({4 \over 3} \pi p_{0}^{3})^{A-1} {1 \over m^{A-1}} {1 \over A^{2}} \; .
+\end{equation}
+
+\noindent Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
+
+\begin{eqnarray}
+B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{3/2} (\nu_{A}\nu/(\nu_{A}+ \nu))^{3/2} {1 \over m^{A-1}} {1 \over A^{2}}  \\
+           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{3/2} (\nu_{A}\nu/(\nu_{A}+ \nu))^{3/2} \;,
+\end{eqnarray}
+
+\noindent where $\nu_{A}$ corresponds again to the size parameter of the gaussian wave-function of the nucleus.
+
 \end{appendix}

### 2018-06-20 FrascatiPlot/misc/CompareHeinzToSato.C
adding folder for helper macros and studies including the Sato comparison

@@ -1,0 +1,20 @@
+void CompareHeinzToSato() {
+  //
+  // this small macro compares the coalescence models from Heinz and Sato
+  // Phys.Lett. 98B (1981) 153-157
+  //
+  // TF1 * funcB2Sato = new TF1("funcB2Sato","(2*0.938/(0.938*0.938)) * 6.0 * TMath::Power(2*TMath::Pi(),1.5)*TMath::Power(x/0.197*x/0.197 + 3.2/0.197*3.2/0.197/2.0, -1.5)", 0.0, 5.0);
+  //  TF1 * funcB2Sato = new TF1("funcB2Sato","(2./0.938) * 6./8.  * TMath::Power(2*TMath::Pi(),1.5)*TMath::Power((TMath::Sqrt(2./3.)*x/0.197)*(TMath::Sqrt(2./3.)*x/0.197) + (3.2/0.197)*(3.2/0.197)/2.0, -1.5)", 0.0, 5.0);
+  TF1 * funcB2Sato = new TF1("funcB2Sato","(2./0.938) * 6./(2*2*2.)  * TMath::Power(2*TMath::Pi(),1.5)*TMath::Power((x/0.197)*(x/0.197) + (3.2/0.197)*(3.2/0.197)/2.0, -1.5)", 0.0, 5.0);
+
+  TF1 * funcB2Sato2 = new TF1("funcB2Sato2","(1./0.938) * (3./4)  * TMath::Power(2,1.5)*TMath::Power(4*TMath::Pi() * (0.2/(x*x)/(0.2 + 1./(x*x))), 1.5)*0.197*0.197*0.197*0.197", 0.0, 5.0);
+  TF1 * funcB2Heinz = new TF1("funcB2Heinz", " 3./(4*TMath::Sqrt(2)) * TMath::Power(2*TMath::Pi(),1.5) * 1/[0] * TMath::Power(x/0.197*x/0.197 + 3.2/0.197*3.2/0.197/4.0, -1.5)", 0.0, 5.0);
+  funcB2Heinz->SetParName(0, "mT");
+  //funcB2Heinz->SetParameter(0, TMath::Sqrt(0.73*0.73 + 0.938*0.938));
+  funcB2Heinz->SetParameter(0, TMath::Sqrt(0.938*0.938));
+  //
+  funcB2Heinz->Draw();
+  funcB2Sato->SetLineColor(kBlue);
+  funcB2Sato->Draw("SAME");
+
+}

### 2018-06-23 FrascatiPlot/Paper/NucleiB2.tex
bug fix
further updates in the appendix

@@
 \begin{eqnarray}
-B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{3/2} (\nu_{A}\nu/(\nu_{A}+ \nu))^{3/2} {1 \over m^{A-1}} {1 \over A^{2}}  \\
-           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{3/2} (\nu_{A}\nu/(\nu_{A}+ \nu))^{3/2} \;,
+B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{3/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3/2(A-1)} {1 \over m^{A-1}} {1 \over A^{2}}  \\
+           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{3/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3/2(A-1)} \;,
 \end{eqnarray}
 
-\noindent where $\nu_{A}$ corresponds again to the size parameter of the gaussian wave-function of the nucleus.
+\noindent where $\nu_{A}$ corresponds again to the size parameter of the gaussian wave-function of the nucleus which are assumed as gaussians (solutions to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
+
+\begin{equation}
+ \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
+\end{equation}
+
+\noindent with an appropriate normalisation factor $C$.
+The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius $r_{A}^{rms}$ is reproduced.
+The relation between $r_{A}^{rms}$ and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration.
+In particular, one obtains for A < 5:
+
+\begin{eqnarray}
+	(A = 2) \;\;  \nu_{d} = {2 \over r_{d}^2} = {3 \over 4 {r_{d}^{rms}}^2 }  \\
+	(A = 3) \;\;  \nu_{t,{\rm 3He}} = {1 \over r_{t,{\rm 3He}}^2} = {1 \over {r_{t,{\rm 3He}}^{rms}}^2 } \\
+	(A = 4)  \;\; \nu_{\alpha} =  {9 \over 8{r_{\rm 4He}^{rms}}^2 }
+\end{eqnarray}
+
+\noindent Please note that proton rms charge radius ${r_{p}^{rms}}$ is subtracted quadratically from the measured rms charge radius ${r_{A}^{rms,meas}}$ of the nucleus ${r_{A}^{rms}} = \sqrt{{r_{A}^{rms,meas}}^2 - {r_{p}^{rms}}^2}$ to account for the finite extension of the constituents.
 

### 2018-06-28 FrascatiPlot/Paper/NucleiB2.tex
I'm Starting modifications to appendix B. Eq. fixed for missing factors and exponents

@@
 Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm which is significantly larger than that of non-strange A=3 nuclei.
+Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm which is significantly larger than that of non-strange $A$ = 3 nuclei.
 This is driven by the average separation of the Lambda with respect to the two other nucleons which is expected to amount up to 10 fm.
@@
  \hline \hline
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J$ & \makecell{(charge) \\rms\\ radius (fm)} &  \makecell{harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
+\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J_{A}$ & \makecell{(Charge) \\rms radius \\ \rmsradius~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
 \\ \hline
@@
 $B_{E}$ is the binding energy in MeV.
-The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction.
-The size parameter $r$ of the wave-function of the harmonic oscillator potential is chosen such that the measured/expected rms is approximately reproduced (see text for details).
+The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius.
+The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced (see text and Appendix \ref{appendix:Sato} for details).
 References are given in the last column.
@@
 This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter $r_{A}$ of the harmonic oscillator potential.
+In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator potential, $r_{A}$.
 We encourage future more rigorous studies which address the coalescence probabilities with more realistic wave-functions.
@@
 
- --> Mention (if true, please check) that this assumes a gaussian wave function of the produced object.
-This might not be true in reality for the hyper-triton, but it allows to show the sensitivity of the wave-function and gives easy analytic expressions.
+ \textcolor{red}{Mention (if true, please check) that this assumes a gaussian wave function of the produced object.
+This might not be true in reality for the hyper-triton, but it allows to show the sensitivity of the wave-function and gives easy analytic expressions.}
 
@@
 The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-As discussed in Appendix \ref{appendix1}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$, thus $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
+As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$, thus $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
 
@@
 \begin{appendix}
-\section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}
+\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
+As discussed in~\cite{Nagle:1996vp}, the approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium as in~\cite{Scheibl:1998tk}.
+Moreover, the approach of \cite{Sato:1981ez} assumes no correlation between different nucleons and no correlation between coordinates in space and momentum (as those introduced by the presence of hydrodynamical flow).
+
+For the deuteron, the authors propose an expression for the coalescence momentum $p_{0}$ which equals
+
+\begin{equation}
+	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} \left(\frac{\nu_{d}\nu}{\nu_d + \nu}\right)^{3/2}
+\end{equation}
+
+\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$.
+
+The coalescence process in~\cite{Sato:1981ez} is formulated in terms of the momentum per nucleon $p_{p,n}$ and thus it relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
+
+\begin{equation}
+B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {M \over m^{A}} {1 \over A^{3}}{\frac{1}{Z! N!}}
+\end{equation}
+
+\noindent where the factor ${1 \over A^{3}}$ results from the transformation of $p_{A} \rightarrow A p_{p,n}$ and $M$ corresponds to the nucleus mass and $m$ to the nucleon mass.
+This expression can be further simplified via the approximation $M \approx A m$ to
+
+\begin{equation}
+B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {1 \over m^{A-1}} {1 \over A^{2}}{\frac{1}{Z! N!}} \; .
+\end{equation}
+
+\noindent Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
+
+\begin{eqnarray}
+B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{3(A-1)/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3(A-1)/2} {1 \over m^{A-1}} {1 \over A^{2}}  \\
+           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{3(A-1)/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3(A-1)/2} \;,
+\end{eqnarray}
+
+\noindent where $\nu_{A}$ corresponds again to the size parameter of the gaussian wave-function of the nucleus which are assumed as gaussians (solutions to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
+
+\begin{equation}
+ \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
+\end{equation}
+
+\noindent with an appropriate normalisation factor $C$.
+The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius $r_{A}^{rms}$ is reproduced.
+The relation between $r_{A}^{rms}$ and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration.
+In particular, one obtains for A < 5:
+
+\begin{eqnarray}
+	(A = 2) \;\;  \nu_{d} = {2 \over r_{d}^2} = {3 \over 4 {r_{d}^{rms}}^2 }  \\
+	(A = 3) \;\;  \nu_{t,{\rm 3He}} = {1 \over r_{t,{\rm 3He}}^2} = {1 \over {r_{t,{\rm 3He}}^{rms}}^2 } \\
+	(A = 4)  \;\; \nu_{\alpha} =  {9 \over 8{r_{\rm 4He}^{rms}}^2 }
+\end{eqnarray}
+
+\noindent Please note that proton rms charge radius ${r_{p}^{rms}}$ is subtracted quadratically from the measured rms charge radius ${r_{A}^{rms,meas}}$ of the nucleus ${r_{A}^{rms}} = \sqrt{{r_{A}^{rms,meas}}^2 - {r_{p}^{rms}}^2}$ to account for the finite extension of the constituents.
+
+\section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}\label{appendix:YKP}
 The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{sside}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
@@
 
-\section{Relation to the model proposed by Sato and Yazaki}
-
-As discussed in~\cite{Nagle:1996vp}, the appraoch of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions and thus neglect the collective expansion of the medium as in~\cite{Scheibl:1998tk}.
-
-For the deuteron, they arrive at an expression for the coalescence momentum $p_{0}$ which equals
-
-\begin{equation}
-	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} (\nu_{d}\nu/(\nu_d + \nu))^{3/2}
-\end{equation}
-
-\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$.
-The coalescence process in~\cite{Sato:1981ez} is formulated in terms of the momentum per nucleon $p_{p,n}$ and thus it relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
-
-\begin{equation}
-B_{A} = ({4 \over 3} \pi p_{0}^{3})^{A-1} {M \over m^{A}} {1 \over A^{3}}
-\end{equation}
-
-\noindent where the factor ${1 \over A^{3}}$ results from the transformation of $p_{A} \rightarrow A p_{p,n}$ and $M$ corresponds to the nucleus mass and $m$ to the nucleon mass.
-This expression can be further simplified via the approximation $M \approx A m$ to
-
-\begin{equation}
-B_{A} = ({4 \over 3} \pi p_{0}^{3})^{A-1} {1 \over m^{A-1}} {1 \over A^{2}} \; .
-\end{equation}
-
-\noindent Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
-
-\begin{eqnarray}
-B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{3/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3/2(A-1)} {1 \over m^{A-1}} {1 \over A^{2}}  \\
-           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{3/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3/2(A-1)} \;,
-\end{eqnarray}
-
-\noindent where $\nu_{A}$ corresponds again to the size parameter of the gaussian wave-function of the nucleus which are assumed as gaussians (solutions to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
-
-\begin{equation}
- \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
-\end{equation}
-
-\noindent with an appropriate normalisation factor $C$.
-The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius $r_{A}^{rms}$ is reproduced.
-The relation between $r_{A}^{rms}$ and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration.
-In particular, one obtains for A < 5:
-
-\begin{eqnarray}
-	(A = 2) \;\;  \nu_{d} = {2 \over r_{d}^2} = {3 \over 4 {r_{d}^{rms}}^2 }  \\
-	(A = 3) \;\;  \nu_{t,{\rm 3He}} = {1 \over r_{t,{\rm 3He}}^2} = {1 \over {r_{t,{\rm 3He}}^{rms}}^2 } \\
-	(A = 4)  \;\; \nu_{\alpha} =  {9 \over 8{r_{\rm 4He}^{rms}}^2 }
-\end{eqnarray}
-
-\noindent Please note that proton rms charge radius ${r_{p}^{rms}}$ is subtracted quadratically from the measured rms charge radius ${r_{A}^{rms,meas}}$ of the nucleus ${r_{A}^{rms}} = \sqrt{{r_{A}^{rms,meas}}^2 - {r_{p}^{rms}}^2}$ to account for the finite extension of the constituents.
-
 \end{appendix}

### 2018-06-29 FrascatiPlot/Paper/NucleiB2.tex
Appendix B updated, together with text in the coalescence part and table caption. Now breaking for lunch & train

@@
  \hline \hline
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J_{A}$ & \makecell{(Charge) \\rms radius \\ \rmsradius~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
+\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J_{A}$ & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
 \\ \hline
@@
 The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius.
-The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced (see text and Appendix \ref{appendix:Sato} for details).
-References are given in the last column.
-The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
+The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced.
+Details are given in Appendix \ref{appendix:Sato}.
+Please note that proton rms charge radius $\lambda_{p}$ is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+ References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
 \label{tab:nucleusradii}
@@
 In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
-While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.
+While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp, Bergstrom:1979gpv, PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.
 
@@
 
-\begin{equation}
+\begin{equation}\label{eq:WaveHeinz}
  \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
@@
 \begin{equation}
- {\rm rms}_{A}^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
+ \rmsradius^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
 \end{equation}
 
-\noindent for point-like constituents. In particular, we obtain $r_{d}=\sqrt{4/3}{\rm rms}_{d}$ for A= 2, $r_{3}= {\rm rms}_{3}$ for A = 3, and ???????.
+\noindent for point-like constituents.
+In particular, we obtain $r_{d}= \sqrt{4/3}  \rmsd$ for $A = 2$, $r_{3}= {\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{9/8} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).
 
@@
 \section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
-As discussed in~\cite{Nagle:1996vp}, the approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium as in~\cite{Scheibl:1998tk}.
-Moreover, the approach of \cite{Sato:1981ez} assumes no correlation between different nucleons and no correlation between coordinates in space and momentum (as those introduced by the presence of hydrodynamical flow).
-
-For the deuteron, the authors propose an expression for the coalescence momentum $p_{0}$ which equals
-
+%As discussed in~\cite{Nagle:1996vp}, 
+The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium as in~\cite{Scheibl:1998tk}.
+Moreover, it assumes no correlation between different nucleons and no correlation between coordinates in space and momentum (in a heavy ion collisions, such correlations are consequence of hydrodynamical flow).
+%For the deuteron, the authors propose an expression for the coalescence momentum $p_{0}$ which equals
+%\begin{equation}
+%	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} \left(\frac{\nu_{d}\nu}{\nu_d + \nu}\right)^{3/2}
+%\end{equation}
+%\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$.
+\\In~\cite{Sato:1981ez}, the coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
+%
 \begin{equation}
-	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} \left(\frac{\nu_{d}\nu}{\nu_d + \nu}\right)^{3/2}
+\frac{\gamma_{A}}{\sigma_{A,0}} \frac{d^{3}\sigma_{A}}{d^{3}p} =  \left( {4 \over 3} \pi p_{0}^{3}\right)^{A-1}\frac{1}{Z!
+N!} \left(\frac{\gamma_{p}}{\sigma_{p,0}} \frac{d^{3}\sigma_{p}}{d^{3}p_{p}}\right)^{Z} \left(\frac{\gamma_{n}}{\sigma_{n,0}} \frac{d^{3}\sigma_{n}}{d^{3}p_{n}}\right)^{N}
 \end{equation} 
-
-\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$.
-
-The coalescence process in~\cite{Sato:1981ez} is formulated in terms of the momentum per nucleon $p_{p,n}$ and thus it relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
+%
+where $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively. 
+Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
 
@@
 
-\noindent Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
+\noindent For nuclei up to $A = 4$ and the non-relativistic case, Sato and Yazaki derive the following relations for the coalescence momentum $p_{0}$, 
+%
+\begin{align}
+	A& =2&
+	{4 \over 3} \pi p_{0}^{3}& ={3 \over 4}2^{3/2}(4\pi)^{3/2} \left(\frac{\nu_{2}\nu}{\nu_{2} + \nu}\right)^{3/2}\\
+	A& =3&
+	{1 \over 2} \left( {4 \over 3} \pi p_{0}^{3}\right)^{2}& ={1 \over 4} 3^{3/2} (4\pi)^{3} \left(\frac{\nu_{3}\nu}{\nu_{3} + \nu}\right)^{3}\\
+	A& =4&  
+	{1 \over 4} \left({4 \over 3} \pi p_{0}^{3}\right)^{3}& = {1 \over 16} 4^{3/2} (4\pi)^{9/2} \left(\frac{\nu_{4}\nu}{\nu_{4}+ \nu}\right)^{9/2}
+\end{align}
+
+\noindent where the size parameter $\nu$ relates to the rms radius $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$, and $\nu_{A}$ is the size parameter of the nucleus. 
+\\Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
 
 \begin{eqnarray}
-B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{3(A-1)/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3(A-1)/2} {1 \over m^{A-1}} {1 \over A^{2}}  \\
-           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{3(A-1)/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3(A-1)/2} \;,
+B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} {1 \over m^{A-1}} {1 \over A^{2}}  \\
+\label{eq:SatoGeneralised}
+           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} \;,
 \end{eqnarray}
 
-\noindent where $\nu_{A}$ corresponds again to the size parameter of the gaussian wave-function of the nucleus which are assumed as gaussians (solutions to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
+\noindent indicating with $J_{A}$ the spin of the nucleus.
+Once again, the $\nu_{A}$ parameter corresponds to the size parameter of the nucleus wave-function, which is assumed to be gaussian (solution to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
 
-\begin{equation}
+\begin{equation}\label{eq:SatoWave}
  \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
@@
 \noindent with an appropriate normalisation factor $C$. 
-The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius $r_{A}^{rms}$ is reproduced.
-The relation between $r_{A}^{rms}$ and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration.
-In particular, one obtains for A < 5:
+\\We have also verified that our generalisation of Sato-Yazaki provided by Eq.
+\ref{eq:SatoGeneralised} and the expression derived from Heinz in Eq.
+\ref{eq:CA_general} become consistent in the limit $R_{rms} \approx R \rightarrow 0$ (point-like source) and $p_{\mathrm{T}} \rightarrow 0$ (static source), provided that one identifies $\nu_{A} = {2 / r_{A}^{2}}$.
+Incidentally, the same relation between $\nu_{A}$ and $r_{A}$ can be derived by a straightforward comparison of the nucleus wave-functions employed by the same authors \cite{Scheibl:1998tk,Sato:1981ez}.
 
-\begin{eqnarray}
-	(A = 2) \;\;  \nu_{d} = {2 \over r_{d}^2} = {3 \over 4 {r_{d}^{rms}}^2 }  \\
-	(A = 3) \;\;  \nu_{t,{\rm 3He}} = {1 \over r_{t,{\rm 3He}}^2} = {1 \over {r_{t,{\rm 3He}}^{rms}}^2 } \\
-	(A = 4)  \;\; \nu_{\alpha} =  {9 \over 8{r_{\rm 4He}^{rms}}^2 }
-\end{eqnarray}
+The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius \rmsradius~is reproduced.
+The relation between \rmsradius~and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration (see Appendix \ref{appendix:integration}).
+In particular, one obtains for $A < 5$:
 
-\noindent Please note that proton rms charge radius ${r_{p}^{rms}}$ is subtracted quadratically from the measured rms charge radius ${r_{A}^{rms,meas}}$ of the nucleus ${r_{A}^{rms}} = \sqrt{{r_{A}^{rms,meas}}^2 - {r_{p}^{rms}}^2}$ to account for the finite extension of the constituents.
+\begin{align}
+	A& = 2 \qquad \qquad \nu_{2} = {3 \over {4\rmsd^2}}  \\
+	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
+	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}}
+\end{align}
 

### 2018-06-30 FrascatiPlot/Paper/NucleiB2.tex
small fix in formulas

@@
 \begin{equation}
- \rmsradius^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
+ \rmsradius^2 = {3 \over 2}{A - 1 \over A} {r_{A}^2 \over 2}
 \end{equation}
@@
 \noindent for point-like constituents.
-In particular, we obtain $r_{d}= \sqrt{4/3}  \rmsd$ for $A = 2$, $r_{3}= {\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{9/8} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).
+In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).
 

### 2018-07-02 FrascatiPlot/Paper/NucleiB2.tex
finalising the bloody table

@@
       A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
-\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &             &   \cite{Purcell:2015gtm}           \\
-                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &              &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &            & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
-\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &             & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
-                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
+\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
+                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
+                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
+\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
+                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
+                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
+                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
 \end{tabularx}

### 2018-07-03 FrascatiPlot/Paper/NucleiB2.tex
minor updates in appendix structure

@@
 
-%%%%%%%%APPENDIX
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%              APPENDIX                   %%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{appendix}
@@
 
-\noindent with an appropriate normalisation factor $C$. 
-\\We have also verified that our generalisation of Sato-Yazaki provided by Eq.
+\noindent with an appropriate normalisation factor $C$ and the coordinate vector $\vec{X}$ of the centre-of-mass system.
+
+We have also verified that our generalisation of Sato-Yazaki provided by Eq.
 \ref{eq:SatoGeneralised} and the expression derived from Heinz in Eq.
@@
 
+%
+% RMS appendix
+%
+\section{RMS of a gaussian wave-function for A=4 }\label{appendix:integration}
+
+In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of A=4. We thus start from the wave-function
+
+\begin{equation}\label{eq:SatoWave}
+ \phi_{A=4} = C_{4} \exp\Bigl(-{1\over2} \nu_{4} \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \Bigr) \; .
+\end{equation}
+
+\noindent Then we introduce the Jacobi variables which are given by %HERE-I-STOP
+
+%
+% HBT Appendix
+%
 \section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}\label{appendix:YKP}
+
 The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{sside}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.

### 2018-07-04 FrascatiPlot/Paper/NucleiB2.tex
starting to add the new appendix with normalisation constant and rms calculation

@@
 \usepackage{makecell}
+\usepackage{amsmath}% http://ctan.org/pkg/amsmath
 
@@
 
-In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of A=4. We thus start from the wave-function
+In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of A=4. We start from the wave-function
 
@@
 
+\begin{align}
+	\vec{X}    &= {1 \over 4} (\vec{x_1} + \vec{x_2} + \vec{x_3} + \vec{x_4}) \\
+	\vec{r_1} &= \vec{x_2} - \vec{x_1}\\
+	\vec{r_2} &= \vec{x_3} - {1 \over 2}(\vec{x_1} + \vec{x_2})\\
+	\vec{r_3} &= \vec{x_4} - {1 \over 3}(\vec{x_1} + \vec{x_2} + \vec{x_3}) \; .
+\end{align}
+
+\noindent In this parameterisation we can express the squared distance of each nucleon with respect to the centre-of-mass as
+
+\begin{equation}
+ \sum_{i=1}^{4} \bigl(\vec{x_i} - \vec{X} \bigr)^2 = {1\over 4} \bigl(2\vec{r_1} + {8\over 3}\vec{r_2} + 3\vec{r_3}\bigr)  \; .
+\end{equation}
+
+\noindent For the following integral calculations we determine the Jacobian as
+
+\begin{align}
+	{\rm d}R{\rm d}r_{1}{\rm d}r_{2}{\rm d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
+		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
+		{\partial R \over \partial x_{2}} & {\partial r_{1} \over \partial x_{2}} & {\partial r_{2} \over \partial x_{2}}& {\partial r_{3} \over \partial x_{2}} \\ 
+		{\partial R \over \partial x_{3}} & {\partial r_{1} \over \partial x_{3}} & {\partial r_{2} \over \partial x_{3}}& {\partial r_{3} \over \partial x_{3}} \\ 
+		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
+		{\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
+		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
+			{1\over 4} & 1 & -{1\over 2} & -{1\over 3}  \\
+			{1\over 4} & 0 & 1 & -{1\over 3}  \\
+			{1\over 4} & 0 & 0 & 1
+			 \end{vmatrix} {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
+		&= 1 \cdot {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \; .
+\end{align}
+
+\noindent From the requirement $\int|\phi|^2{\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:
+
+\begin{align}
+	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + 3r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}
+\end{align}
+
+\noindent where the integration in spherical coordinates is performed with ${\rm d}\vec{r}_{1} = 4\pi r_{1}^{2}{\rm d}r_{1},  {\rm d}\vec{r}_{2} = \ldots$ which gives
+
+\begin{align}
+	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  {\rm d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
+							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  {\rm d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
+							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  {\rm d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
+		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
+	\Rightarrow C_{4} &= \Bigl({\nu_{A}^{3} \over 4 \pi^{3}}\Bigr)^{3/4} \;.
+\end{align}
+
+\noindent For the rms, we obtain accordingly:
+
 %
@@
 
-The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{sside}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
+The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{side}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
 The ALICE HBT results \cite{Aamodt:2011mr, Adam:2015vna} are given in the Bertsch-Pratt convention, whereas the coalescence parameter is derived in \cite{Scheibl:1998tk} by expressing the dependence on the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.

### 2018-07-05 FrascatiPlot/Paper/NucleiB2.tex
small commit to appendix before I go home
finalised appendix with rms calculation
small changes in coalescence section. Last small change before I start major changes.

@@
 In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator potential, $r_{A}$.
-We encourage future more rigorous studies which address the coalescence probabilities with more realistic wave-functions.
+The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g.
+the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton.
+We encourage future more rigorous numerical studies which address the coalescence probabilities with more realistic wave-functions, but remain with the gaussian ansatz in the following in order to obtain more intuitive analytic solutions which highlight the sensitivity to the source and the (hyper-)nucleus size.
 \textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
@@
 
- \textcolor{red}{Mention (if true, please check) that this assumes a gaussian wave function of the produced object.
-This might not be true in reality for the hyper-triton, but it allows to show the sensitivity of the wave-function and gives easy analytic expressions.}
+In summary, one obtains under the assumption $R_1\approx R_2 \approx R_3 \approx R$ (see details in next section) by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general} the following general expression for the coalescence parameter which can be compared to experimental data:
+
+\begin{equation}
+	\boxed {  B_{A} = {J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%% SOURCE VOLUME
+%%
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In contrast to the coalescence approach, the current implementations~\cite{} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra. 
-In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modeled using a blast-wave~\cite{} parameterization.
+In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{} parameterization.
 When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{}.
@@
 \begin{align}
-	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + 3r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}
+	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}
 \end{align}
@@
 \noindent For the rms, we obtain accordingly:
+
+\begin{align}
+	\lambda_{4}^{2} &= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 {\rm d}\vec{x}_{1}{\rm d}\vec{x}_{2}{\rm d}\vec{x}_{3}{\rm d}\vec{x}_{4} \\
+				 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} \\
+				 &= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm I} \\
+				  &\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm II} \\
+				  &\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm III}
+				 \Bigr)
+\end{align}
+
+\noindent The first summand I can be calculated with ${\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 {\rm d}r_{1}{\rm d}r_{2}{\rm d}r_{3}$ as
+
+\begin{align}
+ {\rm I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr){\rm d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) {\rm d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}r_{3} \\
+ 	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
+\end{align}
+
+\noindent The other two summands II and III are evaluated accordingly and we thus obtain for the rms:
+
+\begin{align}
+	\lambda_{4}^{2} &= {C_4^2 \over 4} ({\rm I} + {\rm II} + {\rm III} ) \\
+	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +
+	{{2\over3} \over ({1\over2})^{3/2}({2\over3})^{5/2}({3\over4})^{3/2} } + {{3\over4} \over ({1\over2})^{3/2}({2\over3})^{3/2}({3\over4})^{5/2} } \Bigr)}_{= 24} \\
+	&= {9 \over 8 \nu_A} \;.
+\end{align}
 

### 2018-07-05 FrascatiPlot/Paper/NucleiB2.tex
added a citation to Che Ming Ko latest papers. Indeed he has a very nice approach, but I think that he is in the end just double counting. In future we might want to use his wave-function for our calculations

@@
 The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g.
-the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton.
-We encourage future more rigorous numerical studies which address the coalescence probabilities with more realistic wave-functions, but remain with the gaussian ansatz in the following in order to obtain more intuitive analytic solutions which highlight the sensitivity to the source and the (hyper-)nucleus size.
+the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
+We encourage future more rigorous numerical studies which address the coalescence probabilities with more realistic wave-functions, but remain with the gaussian ansatz in the following in order to obtain more intuitive analytic solutions which highlight the sensitivity to the source (i.e.
+the centrality dependence) and the (hyper-)nucleus size.
 \textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
@@
 \subsection{(Anti-)nuclei with $A$ = 2, 3, 4}
+
 \subsection{(Anti-)hyper-nuclei}
-- cite Che Ming Ko \cite{Zhang:2018euf}
 

### 2018-07-05 FrascatiPlot/Paper/NucleiB2.tex
read again the Che Ming Ko paper, this could indeed be problematic, added a comment
smaller corrections still related to the rms

@@
 %
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus, (b.) $\dradius = 0.3$ fm as currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the current estimate of the rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
 As can be seen in Fig.
@@
 We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
+
+   % -> http://inspirehep.net/record/1662034 (I think that he is double counting => he should remove the protons and neutrons that have already coalesced into a hyper-triton from the sample.
+He argues that this is one different time scales which might explain it, ie.
+the volume for which hyper-triton coalescence happens is just much larger than the one in which deuteron coalescence happens.
+However, if the two different time-scales are true ?
+in our approach a much larger volume ?
+then they should not show so much radial/elliptic flow as they are then formed after decoupling?
+==> THIS COULD SOMEHOW DESTROY THE WHOLE STORY.)
 

### 2018-07-05 FrascatiPlot/Paper/NucleiB2.tex
B2vsVolume.C
small cosmetic fixes

@@
 \ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a radius of the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
+\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
 \label{fig:radiusDependence}

### 2018-07-05 FrascatiPlot/B2vsVolume.C
small updates in main macro for better bookkepping and comsetics

@@ -199,13 +199,13 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   coalcanv->SetRightMargin(0.02);
   coalcanv->Divide(2,1);
 
-  TH2D * frame_cd = new TH2D("frame_cd", "#LTC_{d}#GT vs radius; R (fm); #LTC_{d}#GT", 1000, 0.01, 6.0, 2e5, 0, 1.2);
+  TH2D * frame_cd = new TH2D("frame_cd", "#LTC_{d}#GT vs radius; #it{R} (fm); #LT#it{C}_{d}#GT", 1000, 0.01, 6.0, 2e5, 0, 1.2);
   frame_cd->GetXaxis()->SetTitleSize(0.05);
   frame_cd->GetYaxis()->SetTitleSize(0.05);
   if (plotLinX) frame_cd->GetXaxis()->SetRangeUser(0.01, 8.5);
   else  frame_cd->GetXaxis()->SetRangeUser(0.1, 10.5);
   
-  TH2D * frame_coal = new TH2D("frame_coal", "B_{2} vs radius; R (fm); #it{B}_{2} (GeV^{2}/#it{c}^{3})", 1000, 0.01, 6.0, 2e5, 1.e-4, 0.1);
+  TH2D * frame_coal = new TH2D("frame_coal", "B_{2} vs radius; #it{R} (fm); #it{B}_{2} (GeV^{2}/#it{c}^{3})", 1000, 0.01, 6.0, 2e5, 1.e-4, 0.1);
   frame_coal->GetXaxis()->SetTitleSize(0.05);
   frame_coal->GetYaxis()->SetTitleSize(0.05);
   if (plotLinX) frame_coal->GetXaxis()->SetRangeUser(0.01, 8.5);
@@ -243,7 +243,8 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   hB2_coalescence_largeradius->Draw("same");
   legB2_coal->Draw();
 
-  coalcanv->Print("theory_coalescence_Cd_B2.eps");
+  coalcanv->Print("Paper/theory_coalescence_Cd_B2.eps");
+  coalcanv->Print("Paper/theory_coalescence_Cd_B2.png");
   if (plotOnlyCoalescence) return 0;
 
   //  if (plotPaperFigures) return 0;

### 2018-07-05 FrascatiPlot/B2vsVolume.C
changing from old 1.75fm for 3He to new value of 2.48fm -- not much changes even though agreement with proton 3He is now better

@@ -11,7 +11,7 @@ void convertMultiToRadius(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 0);
 void getRadiusFromParameterisation(Double_t * multi = 0x0, Double_t * radius = 0x0, Int_t paramSet = 0);
 TF1 * MakeB2TheoryGraphQMfactor(Double_t objSize = 3.2);
 TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 3.2);
-TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 1.75);
+TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 2.48);
 
 TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_pp7TeVINEL(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
@@ -113,7 +113,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   //We use now the mass of the proton and the pT per nucleon
   Double_t mT = TMath::Sqrt(pToA * pToA + 0.938 * 0.938);
   // objSize = 3.2; //fm for the deuteron
-  // objSize = 1.75; //fm for the 3^He
+  // objSize = 2.48; //fm for the 3^He
 
   TF1 * Cd_coalescence = (TF1*) MakeB2TheoryGraphQMfactor();
   Cd_coalescence->SetLineWidth(3);
@@ -369,7 +369,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   legC->SetTextFont(42);
   legC->SetTextSize(0.05);
   legC->SetBorderSize(0);
-  legC->AddEntry(hB3_coalescence, "#it{B}_{3} coalesc., #it{r}(^{3}He) = 1.75 fm", "l");
[…]

### 2018-07-05 FrascatiPlot/Paper/NucleiB2.tex
using png version because of transparency
cosmetic fix

@@
 The coefficients, $a = 0.339$ and $b = 0.128$, have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
-These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.8$ \GeVc~\cite{Adam:2015vna}.
-The highest $k_{\mathrm{T}}$ bin was chosen as it corresponds in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
+These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
+The highest $k_{\mathrm{T}}$ bin was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
 Ideally, one would use the proton femtoscopic radii for such study, but given that these measurements are not  available in all collision systems, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
@@
 \begin{center}
-\includegraphics[width=\textwidth]{radiiParamCompareData.eps}
+\includegraphics[width=\textwidth]{radiiParamCompareData.png}
 \caption{Comparison of the ALICE data from~\cite{} with the coalescence prediction for two different mappings of the \avdNdeta to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo values in central Pb-Pb collisions.}

### 2018-07-05 FrascatiPlot/HbtRadii.C

@@ -25,7 +25,7 @@ void HbtRadii() {
   gStyle->SetPadTopMargin(0.05);
 
   TCanvas * canvHbtPlot = new TCanvas("canvHbtPlot","canvHbtPlot");
-  TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{#it{N}_{ch}}/d#it{#eta}#GT^{1/3}; #it{R} (fm)",200,0.0,13.0,200,0.0,6.0);
+  TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{N}_{ch}/d#it{#eta}#GT^{1/3}; #it{R} (fm)",200,0.0,13.0,200,0.0,6.0);
   histFrame->GetXaxis()->SetTitleSize(0.06);
   histFrame->GetXaxis()->SetLabelSize(0.045);
   histFrame->GetXaxis()->SetTitleOffset(1.1);

### 2018-07-06 FrascatiPlot/Paper/NucleiB2.tex
completing some references

@@
 As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the current implementations~\cite{} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra. 
-In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{} parameterization.
-When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{}.
-The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{}.
-This choice is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{}.
+In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra.
+In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
+When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{Abelev:2013vea}.
+The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
+This choice is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
 In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio \cite{} and the measured \hethree~yield \cite{}.
@@
 The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg prediction used here).
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Volodya} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
+We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
 
@@
 
-Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{}. 
+Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,ALICE:deuteronflow2017,Adam:2015yta}.
 In Fig. \ref{} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.  

### 2018-07-06 FrascatiPlot/Paper/NucleiB2.tex
fixing many references

@@
 This choice is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio \cite{} and the measured \hethree~yield \cite{}.
+In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013xaa,Abelev:2013vea} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
 Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/A and compare it with coalescence expectations.
@@
 Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,ALICE:deuteronflow2017,Adam:2015yta}.
-In Fig. \ref{} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.  
-First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown with \textcolor{red}{empty markers}).
+In Fig.
+\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.
+First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown in the two left panels).
 We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo.
@@
 With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree.
-As shown in Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found which ameliorates with the parameterisation which is tuned to the (anti-)deuteron data..
+As shown in Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found which ameliorates with the parameterisation which is tuned to the (anti-)deuteron data.
+\textcolor{red}{We note that this approach is in contrast to the study of Che Ming Ko which allows different freeze-out times for different particles???}
 It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
@@
 \includegraphics[width=\textwidth]{radiiParamCompareData.png}
-\caption{Comparison of the ALICE data from~\cite{} with the coalescence prediction for two different mappings of the \avdNdeta to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo values in central Pb-Pb collisions.}
+\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the coalescence prediction for two different mappings of the \avdNdeta to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo values in central Pb-Pb collisions.}
 \label{fig:CompareB2B3forDifferentParamWithData}

### 2018-07-06 FrascatiPlot/Paper/NucleiB2.tex
smaller changes

@@
 
-In particular, the wave-function of the objects under study are approximated by the wave-function of a spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
+In particular, the wave-function of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
 For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
@@
 Therefore, in a second step the radius is tuned such that the data points for (anti-) deuterons fall onto the coalescence prediction (solid markers).
-We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be \textcolor{red}{$a = xxx$ and $b = yyy$}.
+We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be \textcolor{red}{$a \approx 0.473$ and $b \approx 0$}.
 With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree.
 As shown in Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found which ameliorates with the parameterisation which is tuned to the (anti-)deuteron data.
-\textcolor{red}{We note that this approach is in contrast to the study of Che Ming Ko which allows different freeze-out times for different particles???}
+The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that it is the same for all fragile anti- and hyper-nuclei.
+%\textcolor{red}{We note that this approach is in contrast to the study of Che Ming Ko which allows different freeze-out times for different particles???}
 It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\newpage
 \begin{appendix}
@@
 %
+\newpage
 \section{RMS of a gaussian wave-function for A=4 }\label{appendix:integration}
@@
 \begin{align}
-	\lambda_{4}^{2} &= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 {\rm d}\vec{x}_{1}{\rm d}\vec{x}_{2}{\rm d}\vec{x}_{3}{\rm d}\vec{x}_{4} \\
+	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
+	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 {\rm d}\vec{x}_{1}{\rm d}\vec{x}_{2}{\rm d}\vec{x}_{3}{\rm d}\vec{x}_{4} \\
 	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} \\
@@
 %
+\newpage
 \section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}\label{appendix:YKP}

### 2018-07-06 FrascatiPlot/Paper/NucleiB2.tex
giving the paper a slightly different structure of sub-sections

@@
 
+\subsection{Constraining the source volume with data}
+
 Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,ALICE:deuteronflow2017,Adam:2015yta}.
@@
 We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo.
-Therefore, in a second step the radius is tuned such that the data points for (anti-) deuterons fall onto the coalescence prediction (solid markers).
-We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be \textcolor{red}{$a \approx 0.473$ and $b \approx 0$}.
-With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree.
-As shown in Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found which ameliorates with the parameterisation which is tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that it is the same for all fragile anti- and hyper-nuclei.
-%\textcolor{red}{We note that this approach is in contrast to the study of Che Ming Ko which allows different freeze-out times for different particles???}
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
 
@@
 
-- discuss sensitivity to the choice of the kT for the radii parameterisation.
+Therefore, in a second step the radius is tuned such that the data points for (anti-) deuterons fall onto the coalescence prediction (solid markers).
+We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be \textcolor{red}{$a \approx 0.473$ and $b \approx 0$}.
+With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree.
+As shown in Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found which ameliorates with the parameterisation which is tuned to the (anti-)deuteron data.
+The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that it is the same for all fragile anti- and hyper-nuclei.
+%\textcolor{red}{We note that this approach is in contrast to the study of Che Ming Ko which allows different freeze-out times for different particles???}
+It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
 
-- add a plot with different radii for hyper-triton from 10fm to 3fm
+ \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}
+ - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm
 
+ \subsection{Predictions for A=4}
  - add a plot for A=4
 
+ \subsection{Other exotic QCD objects}
  - add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
-
-\subsection{(Anti-)nuclei with $A$ = 2, 3, 4}
-
-\subsection{(Anti-)hyper-nuclei}
-
-\subsection{Other exotic QCD objects}
-
 We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature.
@@
 We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
+
+In the following, we summarise our main conclusions:
+\begin{enumerate}
+	\item Thermal and coalescence models give similar predictions for the production of $A$=2 and $A$=3 (anti-)nuclei in heavy-ion collisions for a source volume that is constrained by experimental data on (anti-)deuteron production.
+	\item Thermal and coalescence models give very different predictions for the production of hyper-tritons as a function of source volume in pp, p-Pb, and Pb-Pb collisions.
+In particular, the yield of hyper-tritons appears to be suppressed by a factor of about ????
+in pp collisions with respect ot the production of \hethree.
+\end{enumerate}
 

### 2018-07-06 FrascatiPlot/B2vsVolume.C
adding pt-bin to figure 2 and further cosmetic fixes

@@ -222,6 +222,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   legB2_coal->AddEntry(hB2_coalescence_radius1third, "#it{B}_{2} coalesc., #it{r_{d}} = 0.3 fm", "l");
   legB2_coal->AddEntry(hB2_coalescence, "#it{B}_{2} coalesc., #it{r_{d}} = 3.2 fm", "l");
   legB2_coal->AddEntry(hB2_coalescence_largeradius, "#it{B}_{2} coalesc., #it{r_{d}} = 10 fm", "l");
+  // add pT over A here as well
 
   coalcanv->cd(1);
   gPad->SetTickx();
@@ -242,6 +243,16 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   hB2_coalescence_radius1third->Draw("same");
   hB2_coalescence_largeradius->Draw("same");
   legB2_coal->Draw();
+
+  TPaveText * paveptCoalCanv = new TPaveText(0.5, 0.6, 0.9, 0.7, "NDC");
+  paveptCoalCanv->SetFillStyle(0);
+  paveptCoalCanv->SetTextFont(42);
+  paveptCoalCanv->SetBorderSize(0);
+  paveptCoalCanv->SetTextSize(0.04);
+  paveptCoalCanv->SetTextAlign(12);
+  paveptCoalCanv->AddText(Form("#it{p}_{T}/#it{A} = %3.2f GeV/#it{c}", pToA));
+  paveptCoalCanv->Draw();
+
 
   coalcanv->Print("Paper/theory_coalescence_Cd_B2.eps");
   coalcanv->Print("Paper/theory_coalescence_Cd_B2.png");

### 2018-07-06 FrascatiPlot/Paper/NucleiB2.tex
a few minor changes before starting to outsource each paper plot into a separate function so that the macro becomes more readable

@@
 
-The coefficients, $a = 0.339$ and $b = 0.128$, have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
+The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
 These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.

### 2018-07-06 FrascatiPlot/B2vsVolume.C

@@ -35,10 +35,14 @@ TGraphAsymmErrors * getBlastB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pTo
 void MakeUp(TGraphErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Style, Int_t Line_Style, Int_t Line_Width, Int_t Marker_Style, Float_t Marker_Size);
 void MakeUp(TGraphAsymmErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Style, Int_t Line_Style, Int_t Line_Width, Int_t Marker_Style, Float_t Marker_Size);
 
+void MakePaperFigure2();
   
 Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.733, Double_t pToAb3pp = 0.800, Double_t pToAb3Lambda = 1.,
 		 Bool_t plotOnlyCoalescence = kFALSE, Bool_t plotPaperFigures = kTRUE)
 {
+  //
+  // main function which generates the plots of the Frascati project
+  //
   
   //--------------------
   //data
@@ -764,6 +768,15 @@ void getRadiusFromParameterisation(Double_t * multi, Double_t * radius, Int_t pa
   return; 
 }
 
+
+void MakePaperFigure2() {
+  //
+  // Create the (pure theory) figure which plots <C_d> and B2 vs R
+  // for different radii
+  //
+
+
+}
 
 
 Double_t getB2fromRadius(Double_t homogR, Double_t mT, Double_t objSize)

### 2018-07-06 FrascatiPlot/B2vsVolume.C
adding extra functions for paper figures to make it more readable, not sure if it is better like that; a TLIST to handover all the objects might also be good

@@ -3,6 +3,12 @@
    17.01.2018 - The Frascati plot
 */
 #include "TMath.h"
+#include "TGraphAsymmErrors.h"
+#include "TGraphErrors.h"
+#include "TPaveText.h"
+#include "TLegend.h"
+#include "TH1D.h"
+#include "TH2D.h"
 #include "./generateBWpredictionsB2.C" //ADAPT ME
 
 void convertMultiToRadius(TGraphErrors * graph = 0x0, Int_t paramSet = 0);
@@ -35,8 +41,15 @@ TGraphAsymmErrors * getBlastB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pTo
 void MakeUp(TGraphErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Style, Int_t Line_Style, Int_t Line_Width, Int_t Marker_Style, Float_t Marker_Size);
 void MakeUp(TGraphAsymmErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Style, Int_t Line_Style, Int_t Line_Width, Int_t Marker_Style, Float_t Marker_Size);
 
-void MakePaperFigure2();
-  
+void MakePaperFigure2(Bool_t plotLinX, Double_t pToA,
+		      TF1 *Cd_coalescence, TF1* Cd_coalescence_pointlike, TF1* Cd_coalescence_radius1third,  TF1* Cd_coalescence_largeradius,
+		      TGraphErrors * hB2_coalescence, TGraphErrors * hB2_coalescence_pointlike, TGraphErrors * hB2_coalescence_radius1third, TGraphErrors * hB2_coalescence_largeradius);
+
+void MakePaperFigure3(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,
+		      TGraphErrors * hB2_coalescence, TGraphErrors * hB3_coalescence, 
+		      TGraphErrors ** gB2vsR_PbPb276TeV_sys,  TGraphErrors ** gB2vsR_pp7TeVINEL_sys, TGraphErrors **gB2vsR_PbPb276TeV, TGraphErrors **  gB2vsR_pp7TeVINEL,
[…]

### 2018-07-06 FrascatiPlot/Paper/NucleiB2.tex
small cosmetic changes

@@
  \hline \hline
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J_{A}$ & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
+\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
 \\ \hline
@@
 In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
-While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp, Bergstrom:1979gpv, PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.
+While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp, Bergstrom:1979gpv}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.
 

### 2018-07-08 FrascatiPlot/B2vsVolume.C
adding first version of figure 4 of the paper

@@ -50,6 +50,13 @@ void MakePaperFigure3(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,
 		      TGraphErrors ** gB2vsR_PbPb276TeV_sys,  TGraphErrors ** gB2vsR_pp7TeVINEL_sys, TGraphErrors **gB2vsR_PbPb276TeV, TGraphErrors **  gB2vsR_pp7TeVINEL,
 		      TGraphErrors ** gB3vsR_PbPb276TeV_sys,  TGraphAsymmErrors ** gB3vsR_pp7TeV_sys, TGraphErrors ** gB3vsR_PbPb276TeV, TGraphAsymmErrors **  gB3vsR_pp7TeV);
 
+void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3, Double_t pToAb3Lambda,
+		      TGraphErrors * hB2_coalescence, TGraphErrors * hB3_coalescence, TGraphErrors* hB3L_coalescence,
+		      TGraphErrors ** gB2vsR_PbPb276TeV_sys,  TGraphErrors ** gB2vsR_pp7TeVINEL_sys, TGraphErrors **gB2vsR_PbPb276TeV, TGraphErrors **  gB2vsR_pp7TeVINEL,
+		      TGraphErrors ** gB3vsR_PbPb276TeV_sys,  TGraphAsymmErrors ** gB3vsR_pp7TeV_sys, TGraphErrors ** gB3vsR_PbPb276TeV, TGraphAsymmErrors **  gB3vsR_pp7TeV,
+		      TGraphAsymmErrors** gBlastB2vsR_PbPb276TeV,  TGraphAsymmErrors** gBlastB3vsR_PbPb276TeV,
+		      TGraphAsymmErrors** gB3LambdavsR_PbPb276TeV, TGraphAsymmErrors** gB3LambdavsR_PbPb276TeV_sys, TGraphAsymmErrors** gBlastB3LambdavsR_PbPb276TeV);
+
 Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.733, Double_t pToAb3pp = 0.800, Double_t pToAb3Lambda = 1.,
 		 Bool_t plotOnlyCoalescence = kFALSE, Bool_t plotPaperFigures = kTRUE)
 {
[…]

### 2018-07-08 FrascatiPlot/Paper/NucleiB2.tex
major change: adding figure 4 to the paper and restructuring it for emergency to a first publication which will then be followed up by one explicitly for predictions. Like this the formalism can be kept separate from the studies for the yellow report.

@@
  \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}
- - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm
+ - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm and for the excited state of the hyper-triton!!
 
- \subsection{Predictions for A=4}
- - add a plot for A=4
+\begin{figure}[htbp]
+	\begin{center}
+		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
+		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the thermal model expectations and the coalescence prediction which is tuned to \btwo\ values in central Pb-Pb collisions.}
+		\label{fig:CompareThermalAndCoalescence}
+	\end{center}
+\end{figure}
+ %\subsection{Predictions for A=4}
+ %- add a plot for A=4
 
- \subsection{Other exotic QCD objects}
- - add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
-We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature.
+ %\subsection{Other exotic QCD objects}
+ %- add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
+%We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature.
 One of them is the X(3872) which might have a wide wave-function as described in http://inspirehep.net/record/861896?ln=de
 
-\section{Projections for the LHC Run 3 and 4}\label{sec:projections}
+%\section{Projections for the LHC Run 3 and 4}\label{sec:projections}
 
-\section{Summary and conclusions}
+\section{Summary, conclusions, and outlook}
 
@@
 \end{enumerate}
+
+In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{table} and to more exotic QCD objects like the X(3827).
+These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.
 

### 2018-07-08 FrascatiPlot/B2vsVolume.C

@@ -826,6 +826,7 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
   TH2D * hframe = new TH2D("hframeFig4", "B_{2} vs radius; #it{R} (fm); #it{B}_{2} (GeV^{2}/#it{c}^{3})", 1000, 0.01, 6.0, 2000, 1.e-4, 0.1);
   hframe->GetXaxis()->SetTitleSize(0.06);
   hframe->GetYaxis()->SetTitleSize(0.06);
+  hframe->GetYaxis()->SetTitleOffset(1.25);
   hframe->GetXaxis()->SetTitleOffset(0.8);
   hframe->GetXaxis()->SetLabelSize(0.05);
   hframe->GetYaxis()->SetLabelSize(0.05);
@@ -835,6 +836,7 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
   TH2D * hframe3 = new TH2D("hframe3Fig4", "B_{3} vs radius; #it{R} (fm); #it{B}_{3} (GeV^{4}/#it{c}^{6})", 1000, 0.01, 6.0, 2000, 1.e-9, 1.e-1);
   hframe3->GetXaxis()->SetTitleSize(0.06);
   hframe3->GetYaxis()->SetTitleSize(0.06);
+  hframe3->GetYaxis()->SetTitleOffset(1.25);
   hframe3->GetXaxis()->SetTitleOffset(0.8);
   hframe3->GetXaxis()->SetLabelSize(0.05);
   hframe3->GetYaxis()->SetLabelSize(0.05);
@@ -905,18 +907,23 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
   hframe3->Draw();
   gB3LambdavsR_PbPb276TeV_sys[1]->Draw("samep2");
   gB3LambdavsR_PbPb276TeV[1]->Draw("samep");
-  //  gBlastB3vsR_PbPb276TeV[1]->Draw("samel");
   gBlastB3LambdavsR_PbPb276TeV[1]->Draw("samel");
   hB3L_coalescence->Draw("l");
   paveptB3L->Draw();
+  //
+  Int_t nl = 3;
[…]

### 2018-07-09 FrascatiPlot/B2vsVolume.C
completing legend of figure 4

@@ -885,6 +885,17 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
   gB2vsR_PbPb276TeV_sys[1]->Draw("samep3");
   gB2vsR_PbPb276TeV[1]->Draw("samepz");
   gBlastB2vsR_PbPb276TeV[1]->Draw("samel");
+  //
+  TLegend * legB2 = new TLegend(0.2, 0.95, 0.6, 0.8, "");
+  legB2->SetFillStyle(0);
+  legB2->SetTextSize(0.03);
+  legB2->SetBorderSize(0);
+  legB2->AddEntry(hB2_coalescence, "#it{B}_{2} coalesc., #it{r}(d) = 3.2 fm", "l");
+  legB2->AddEntry(gB2vsR_PbPb276TeV_sys[1], "Pb-Pb #sqrt{#it{s}_{NN}} = 2.76 TeV [PRC 93, 0249717 (2016)]", "pf");
+  legB2->AddEntry(gB2vsR_pp7TeVINEL_sys[1], "pp #sqrt{#it{s}} = 7 TeV, prelim.", "pf");
+  legB2->AddEntry(gBlastB2vsR_PbPb276TeV[1], "Pb-Pb #sqrt{#it{s}_{NN}} = 2.76 TeV, BW + GSI (T = 156 MeV)", "l");
+  legB2->Draw();
+  //
   hB2_coalescence->Draw("l");
 
   pavept->Draw();
@@ -899,6 +910,17 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
   gB3vsR_pp7TeV[1]->Draw("samepz");
   gBlastB3vsR_PbPb276TeV[1]->Draw("samel");
   hB3_coalescence->Draw("l");
+  //
+  TLegend * legB3 = new TLegend(0.2, 0.95, 0.6, 0.8, "");
+  legB3->SetFillStyle(0);
+  legB3->SetTextSize(0.03);
+  legB3->SetBorderSize(0);
+  legB3->AddEntry(hB3_coalescence, "#it{B}_{3} coalesc., #it{r}(^{3}He) = 2.48 fm", "l");
[…]

### 2018-07-09 FrascatiPlot/Paper/NucleiB2.tex
starting to write chapter 4.2

@@
  \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}
+
+In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuteorns, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions.
+For the coalescence predictions, the radius parameterisation tuned to the data is used.
+The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}.
+For deuterons and \hethree\ both approaches lead to similar to similar predictions and give a reasonable description of the experimental data.
+
  - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm and for the excited state of the hyper-triton!!

### 2018-07-09 FrascatiPlot/Paper/NucleiB2.tex
adding first version complete version of chapter 4.2

@@
 The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}.
-For deuterons and \hethree\ both approaches lead to similar to similar predictions and give a reasonable description of the experimental data.
-
- - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm and for the excited state of the hyper-triton!!
+As a first observation, one sees that for deuterons and \hethree\ both approaches lead to similar predictions and give a reasonable description of the experimental data.
+However, both approaches show large differences for the \hthreelambda\ caused by the significantly larger size of  \hthreelambda\ with respect to \hethree.
+As a matter of fact, the only available data point so far shows a better agreement with the thermal+BW model than with the coalescence model.
+However, some authors argue that the difference to the coalescence model might be explained by a later formation through $\Lambda$s and deuterons~\cite{Zhang:2018euf}.
+In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production which is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
+The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from counting the spin states.
 
@@
 \end{figure}
+
+Figure~\ref{fig:CompareThermalAndCoalescence} also shows most importantly that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios.
+This behaviour also highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production.
+
+ - add an estimate for the hyper-triton in pp collisions
+
  %\subsection{Predictions for A=4}
@@
 
-In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{table} and to more exotic QCD objects like the X(3827).
+In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827).
 These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.

### 2018-07-09 FrascatiPlot/Paper/NucleiB2.tex
chapter 4.2 first version completed

@@
 In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production which is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
-The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from counting the spin states.
+The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from only counting the spin states.
 
@@
 Figure~\ref{fig:CompareThermalAndCoalescence} also shows most importantly that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios.
-This behaviour also highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production.
-
- - add an estimate for the hyper-triton in pp collisions
+This behaviour also highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
+The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions.
+As can be seen, its production in pp collisions is expected to be suppressed by about two orders of magnitude with respect to that of \hethree, thus making this measurement a prime candidate for future experimental study.
 
@@
 	\item Thermal and coalescence models give very different predictions for the production of hyper-tritons as a function of source volume in pp, p-Pb, and Pb-Pb collisions.
-In particular, the yield of hyper-tritons appears to be suppressed by a factor of about ????
-in pp collisions with respect ot the production of \hethree.
+In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect ot the production of \hethree.
 \end{enumerate}

### 2018-07-10 FrascatiPlot/Paper/NucleiB2.tex
first version of summary and conclusions

@@
 
-We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
-
+%We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
+While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei, the study presented here shows that large differences are expected for hyper-nuclei with extended wave-functions.
 In the following, we summarise our main conclusions:
@@
 In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect ot the production of \hethree.
+The very limited currently available data on the hyper-triton slightly favors the thermal model prediction.
+	\item Systematic measurement in pp, p-Pb, and Pb-Pb collisions at LHC energies show a unique potential to clarify the production mechanism and also the nature of composite QCD objects as they are sensitive to the extension, i.e.
+the wave-function of the object under study.
 \end{enumerate}
@@
 These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.
+In addition, our study is deliberately based on many simplifying assumptions in order to allow for a completely analytical treatment of the problem highlighting.
+Future studies will be based on more realistic approximations requiring numerical calculations.
 

### 2018-07-10 FrascatiPlot/Paper/NucleiB2.tex
adding a sentence for the X(3872) in the outlook of the current version

@@
 In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827).
+If the X(3872) corresponds to a loosely bound molecule composed of $D^{*0}$ and $D^{0}$ mesons, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm which is very similar to that of the hyper-triton.
+Thus, its production via a possible coalescence mechanism in pp collisions would be subject to similar suppression as the hyper-triton.
 These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.
@@
 	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
-	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}}
+	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}} \;\; .
 \end{align}

### 2018-07-10 FrascatiPlot/Paper/NucleiB2.tex
new, more modest abstract

@@
 \begin{center}
-{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies with recent and future experimental data}}
+%{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies with recent and future experimental data}}
+{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies}}
 
@@
 At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models.
-While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals largely different predictions between the two approach for the production of \hethree\ and hyper-tritons.
-Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions.
-The thermal-statistical model on the other hand is in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system.
-Our findings thus indicate the existence of a novel production mechanism for these objects and highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects.
+While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
+Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they consequently largely differ in their description of (anti-)hyper-triton production.
+%Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions.
+The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system.
+Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a discussion basis for more refined calculations in the future.
 \end{abstract}

### 2018-07-10 FrascatiPlot/Paper/NucleiB2.tex
cosmetic changes to prepare the submission

@@
 %%Table of contents - to be removed for submission%%
-\newpage
-\tableofcontents
+%\newpage
+%\tableofcontents
 \newpage
@@
 Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem}$ = 156 MeV (near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz}).
+In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}.
 Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.

### 2018-07-11 FrascatiPlot/B2vsVolume.C
Updated figure 4: r = 14.1 fm, made 2x2 panels with master legend on the side

@@ -51,7 +51,7 @@ void MakePaperFigure3(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,
 		      TGraphErrors ** gB3vsR_PbPb276TeV_sys,  TGraphAsymmErrors ** gB3vsR_pp7TeV_sys, TGraphErrors ** gB3vsR_PbPb276TeV, TGraphAsymmErrors **  gB3vsR_pp7TeV);
 
 void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3, Double_t pToAb3Lambda,
-		      TGraphErrors * hB2_coalescence, TGraphErrors * hB3_coalescence, TGraphErrors* hB3L_coalescence,
+		      TGraphErrors * hB2_coalescence, TGraphErrors * hB3_coalescence, TGraphErrors* hB3L_coalescence, TGraphErrors* hB3L_coalescence_largeradius,
 		      TGraphErrors ** gB2vsR_PbPb276TeV_sys,  TGraphErrors ** gB2vsR_pp7TeVINEL_sys, TGraphErrors **gB2vsR_PbPb276TeV, TGraphErrors **  gB2vsR_pp7TeVINEL,
 		      TGraphErrors ** gB3vsR_PbPb276TeV_sys,  TGraphAsymmErrors ** gB3vsR_pp7TeV_sys, TGraphErrors ** gB3vsR_PbPb276TeV, TGraphAsymmErrors **  gB3vsR_pp7TeV,
 		      TGraphAsymmErrors** gBlastB2vsR_PbPb276TeV,  TGraphAsymmErrors** gBlastB3vsR_PbPb276TeV,
@@ -201,11 +201,18 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
 
   TGraphErrors* hB3L_coalescence = (TGraphErrors*) MakeB3TheoryGraphCoalescence(mT, 6.8);
   hB3L_coalescence->SetMarkerStyle(20);
-  hB3L_coalescence->SetMarkerColor(kAzure-7);
-  hB3L_coalescence->SetLineColor(kAzure-7);
+  hB3L_coalescence->SetMarkerColor(kBlack);
+  hB3L_coalescence->SetLineColor(kBlack);
[…]

### 2018-07-11 FrascatiPlot/Paper/NucleiB2.tex
Updated figures and minor fixes to caption, just because we are precise...

@@
 		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the coalescence prediction for two different mappings of the \avdNdeta to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo values in central Pb-Pb collisions.}
+		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo~values in central Pb-Pb collisions.}
 		\label{fig:CompareB2B3forDifferentParamWithData}
@@
 \begin{align}
-	{\rm d}R{\rm d}r_{1}{\rm d}r_{2}{\rm d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
+	\mathrm{d}R\mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
 		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
@@
 		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
-		{\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
+		\mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
 		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
@@
 			{1\over 4} & 0 & 0 & 1
-			 \end{vmatrix} {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
-		&= 1 \cdot {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \; .
+			 \end{vmatrix} \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
+		&= 1 \cdot \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \; .
 \end{align}
 
-\noindent From the requirement $\int|\phi|^2{\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:
+\noindent From the requirement $\int|\phi|^2\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:
 
 \begin{align}
-	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}
+	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}
 \end{align}
 
-\noindent where the integration in spherical coordinates is performed with ${\rm d}\vec{r}_{1} = 4\pi r_{1}^{2}{\rm d}r_{1},  {\rm d}\vec{r}_{2} = \ldots$ which gives
+\noindent where the integration in spherical coordinates is performed with $\mathrm{d}\vec{r}_{1} = 4\pi r_{1}^{2}\mathrm{d}r_{1},  \mathrm{d}\vec{r}_{2} = \ldots$ which gives
 
 \begin{align}
-	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  {\rm d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  {\rm d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  {\rm d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
+	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  \mathrm{d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
+							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  \mathrm{d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
+							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  \mathrm{d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
 		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
@@
 	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
-	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 {\rm d}\vec{x}_{1}{\rm d}\vec{x}_{2}{\rm d}\vec{x}_{3}{\rm d}\vec{x}_{4} \\
-	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} \\
-	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm I} \\
-	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm II} \\
-	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm III}
+	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 \mathrm{d}\vec{x}_{1}\mathrm{d}\vec{x}_{2}\mathrm{d}\vec{x}_{3}\mathrm{d}\vec{x}_{4} \\
+	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} \\
+	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{I}} \\
+	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{II}} \\
+	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{III}}
 				 \Bigr)
@@
 
-\noindent The first summand I can be calculated with ${\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 {\rm d}r_{1}{\rm d}r_{2}{\rm d}r_{3}$ as
+\noindent The first summand I can be calculated with $\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 \mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3}$ as
 
 \begin{align}
- {\rm I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr){\rm d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) {\rm d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}r_{3} \\
+ \mathrm{I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr)\mathrm{d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \mathrm{d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}r_{3} \\
  	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
@@
 \begin{align}
-	\lambda_{4}^{2} &= {C_4^2 \over 4} ({\rm I} + {\rm II} + {\rm III} ) \\
+	\lambda_{4}^{2} &= {C_4^2 \over 4} (\mathrm{I} + \mathrm{II} + \mathrm{III} ) \\
 	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +

### 2018-07-11 FrascatiPlot/Paper/NucleiB2.tex
Minor fixes to comments before going  for pizza. Also added a reference to Braaten. We continue tomorrow.

@@
 %Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions.
-The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system.
+The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
 Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a discussion basis for more refined calculations in the future.
@@
 Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm which is significantly larger than that of non-strange $A$ = 3 nuclei.
-This is driven by the average separation of the Lambda with respect to the two other nucleons which is expected to amount up to 10 fm.
+Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm \cite{Nemura:1999qp} which is significantly larger than that of non-strange $A$ = 3 nuclei.
+This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm.
 In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
@@
 Details are given in Appendix \ref{appendix:Sato}.
-Please note that proton rms charge radius $\lambda_{p}$ is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
  References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
@@
 However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
-In section \ref{sec:projections}, we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
+We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
 As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
@@
 
-\subsection{Full coalescence}
+\subsection{Advanced coalescence}
 \label{subsec:FullCoalescence}
@@
 This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator potential, $r_{A}$.
-The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g.
+In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$.
+The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g.
 the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
@@
 %
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo (on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
 As can be seen in Fig.
@@
 The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$, thus $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
+As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$.
+We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
 
@@
 \begin{center}
-\includegraphics[width=0.6\textwidth]{HbtRadiusParam.eps}
+\includegraphics[width=0.7\textwidth]{HbtRadiusParam.eps}
 \caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Abelev:2012sq}.}
@@
 
-- excess binding energy needs to be released to the system to make coalescence work
+%- excess binding energy needs to be released to the system to make coalescence work
 
@@
 The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
-This choice is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
+This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
 In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013xaa,Abelev:2013vea} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
-Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/A and compare it with coalescence expectations.
-Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality/multiplicity classes, we use the corresponding \avdNdeta~in the same class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
-In contrast to the coalescence approach which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model, which as a simplified hydrodynamic model treats the system based as a continuum and is not particle based.
-The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg prediction used here).
+Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
+Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality/multiplicity classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
+In contrast to the coalescence approach which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model, which as a simplified hydrodynamic model treats the system as a continuum and is not particle based.
+The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg model used here).
 We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
@@
 First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown in the two left panels).
-We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo.
+We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
 
@@
 
- \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}
+ \subsection{Thermal and coalescence model for A = 2, 3 anti- and hyper-nuclei}
 
-In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuteorns, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions.
+In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuterons, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions.
 For the coalescence predictions, the radius parameterisation tuned to the data is used.
@@
 
-Figure~\ref{fig:CompareThermalAndCoalescence} also shows most importantly that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios.
-This behaviour also highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
+Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} also shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios.
+This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
 The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions.
@@
 In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827).
-If the X(3872) corresponds to a loosely bound molecule composed of $D^{*0}$ and $D^{0}$ mesons, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm which is very similar to that of the hyper-triton.
+If the X(3872) corresponds to a loosely bound molecule composed of $D^{*0}$ and $D^{0}$ mesons, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu} which is very similar to that of the hyper-triton.
 Thus, its production via a possible coalescence mechanism in pp collisions would be subject to similar suppression as the hyper-triton.

### 2018-07-12 FrascatiPlot/B2vsVolume.C
Moved from INEL to INEL>0 for pp points + minor cosmetics

@@ -20,14 +20,14 @@ TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize 
 TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 2.48);
 
 TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphErrors * getB2_pp7TeVINEL(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphErrors * getB2_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 
 TGraphErrors      * getB3_PbPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
 TGraphErrors      * getB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
-TGraphAsymmErrors * getB3_pp7TeVINEL(Bool_t plotSys = 0, Double_t pToAb3pp = 0.800, Int_t paramSet = 0);
+TGraphAsymmErrors * getB3_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToAb3pp = 0.800, Int_t paramSet = 0);
 TGraphAsymmErrors * getB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1., Int_t paramSet = 0);
 
 TGraphAsymmErrors * getBlastB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
[…]

### 2018-07-12 FrascatiPlot/HbtRadii.C

@@ -62,7 +62,7 @@ void HbtRadii() {
   //
   TGraphErrors * grHbtRadiusPPB = GetPPbHbtRadius0887KT();
   grHbtRadiusPPB->SetMarkerStyle(21);
-  grHbtRadiusPPB->SetMarkerSize(1.);
+  grHbtRadiusPPB->SetMarkerSize(1.2);
   grHbtRadiusPPB->SetLineWidth(1);
   grHbtRadiusPPB->SetLineStyle(1);
   grHbtRadiusPPB->SetLineColor(kBlue);
@@ -71,7 +71,7 @@ void HbtRadii() {
   //
   TGraphErrors * grHbtRadiusPBPB = GetPbPbHbtRadius0887KT();
   grHbtRadiusPBPB->SetMarkerStyle(20);
-  grHbtRadiusPBPB->SetMarkerSize(1.0);
+  grHbtRadiusPBPB->SetMarkerSize(1.2);
   grHbtRadiusPBPB->SetLineWidth(1);
   grHbtRadiusPBPB->SetLineStyle(1);
   grHbtRadiusPBPB->SetLineColor(kRed);
@@ -81,9 +81,11 @@ void HbtRadii() {
   TGraphErrors * grHbtRadiusPP = new TGraphErrors(1);
   grHbtRadiusPP->SetPoint(0, TMath::Power(5.98,1./3.), 0.8);
   grHbtRadiusPP->SetPointError(0, TMath::Power(5.98,-2./3.)*0.09/3., 0.3);
-  grHbtRadiusPP->SetLineColor(kGreen+1);
-  grHbtRadiusPP->SetMarkerColor(kGreen+1);
+  grHbtRadiusPP->SetLineColor(kGreen+2);
+  grHbtRadiusPP->SetMarkerColor(kGreen+2);
   grHbtRadiusPP->SetMarkerStyle(22);
+  grHbtRadiusPP->SetMarkerSize(1.4);
+
 
     //canvHbtPlot->BuildLegend()
   TF1 * poly1 = new TF1("poly1", "[0]*x + [1]", 0., 13.);
@@ -108,19 +110,19 @@ void HbtRadii() {
   leg1->SetBorderSize(0);
   leg1->SetFillStyle(0);
   leg1->SetTextSize(0.04);
[…]

### 2018-07-12 FrascatiPlot/Paper/NucleiB2.tex
Review of the text up to section 2.2 - Added few references for coalescence and p-Pb data, fixed typos in bib.

@@
 \usepackage{amsmath}% http://ctan.org/pkg/amsmath
-
+\usepackage{cite}
 %\ifpdf
@@
 \begin{abstract}
-(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies.
-At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models.
-While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
-Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they consequently largely differ in their description of (anti-)hyper-triton production.
+(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC).
+Their production is typically discussed within the framework of coalescence and thermal-statistical production models.
+While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
+Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
 %Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions.
 The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
-Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a discussion basis for more refined calculations in the future.
+Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
 \end{abstract}
@@
 Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-Theoretical calculations indicate a rms of the wave-function of the hyper-triton of about 5 fm \cite{Nemura:1999qp} which is significantly larger than that of non-strange $A$ = 3 nuclei.
-This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm.
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei.
+This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm \cite{Nemura:1999qp}.
 In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
 
+Since about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
 Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
@@
 For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
-As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products (check statement) \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is \textcolor{red}{smaller than the breakup cross-section} \cite{Schukraft:2017nbn}.
+As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
+Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
 Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-\textcolor{red}{Do similar estimates as Karel in Frascati}.
-In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk}.
+%In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
+Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
 Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
@@
 %\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.}
- \hline \hline
+ \hline \hline \\[-2ex]
 \makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
-\\ \hline
-      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
+\\[1ex]  \hline \\[-2ex]
+      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
 \multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                    & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
+                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
 \multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
@@
                                    & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
+                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
 \end{tabularx}
-\caption{Properties of nuclei and hyper-nuclei.
+\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$.
 $B_{E}$ is the binding energy in MeV.
@@
 
-To this purpose, we compare to models the existing data from the Large Hadron Collider.
+To this purpose, we compare to models the existing data from the LHC.
 For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
@@
 However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
-We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 and 4, in order to rule out or support the aforementioned scenarios.
+We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
 As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
@@
 \begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;,
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
+   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
+,    
 \label{eq:BA}
 \end{equation}
-
+anielski-HQ14
 \noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
-Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
+Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
 \begin{equation}
@@
 Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
+As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
 In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
@@
 If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
-In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.
+While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
+In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
 
@@
 In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
-While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp, Bergstrom:1979gpv}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.
-
-In particular, the wave-function of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
+While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
+The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions.
+They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
+The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
 For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
@@
 
-\noindent For larger nuclei (A > 2), analogous forms exist (see for instance~\cite{Scheibl:1998tk} for the explicit form of A=3).
+\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
 The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
@@
 \noindent for point-like constituents.
-In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).
+In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
 
 This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$.
+In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
 The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g.
-the Hulthen parameterisation for the deuteron or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
-We encourage future more rigorous numerical studies which address the coalescence probabilities with more realistic wave-functions, but remain with the gaussian ansatz in the following in order to obtain more intuitive analytic solutions which highlight the sensitivity to the source (i.e.
-the centrality dependence) and the (hyper-)nucleus size.
-\textcolor{red}{Consider mentioning the further  approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
+the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
+We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions.
+Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
+the centrality dependence) and that of the (hyper-)nucleus.
+In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.
 
-In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
+The quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
 In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
@@
 %
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
 As can be seen in Fig.
@@
 %
-for mass number $A$ and the radii $R_{i}$ which describe the volume of the emitting source.
+for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
 Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised in \cite{Scheibl:1998tk} as
@@
 \end{equation}
-In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes Eq. 9 presented in \cite{Blum:2017qnn}:
+In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes the Eq. 9 presented in \cite{Blum:2017qnn}:
 \begin{equation}
@@
 
- where
+\noindent where
 
@@
 
-In summary, one obtains under the assumption $R_1\approx R_2 \approx R_3 \approx R$ (see details in next section) by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general} the following general expression for the coalescence parameter which can be compared to experimental data:
+In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
 
@@
 \end{equation}
+
+\noindent This formula can be used to compare the predicted $B_{A}$ with experimental data directly.
 
@@
 
-Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,ALICE:deuteronflow2017,Adam:2015yta}.
+Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,Acharya:2017dmc,Adam:2015yta}.
 In Fig.

### 2018-07-12 FrascatiPlot/Paper/NucleiB2.tex
Puh...second half of the comments implemented during the big revision. Only acknowledgments are missing now before we send it to Andreas and ALICE.

@@
 \usepackage{amsmath}% http://ctan.org/pkg/amsmath
+\usepackage{amssymb}
 \usepackage{cite}
@@
 This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm \cite{Nemura:1999qp}.
-In principle, halo nuclei as $^{6}$He would therefore be ideal for such studies, but they remain out of the experimental reach in high-energy experiments in the near future.
+Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
 
@@
 \label{SecSourceVolume}
-As in \cite{Scheibl:1998tk}, we identify the source volume as the effective sub-volume of the whole system which is governed by the homogeneity length of the interacting nucleons.
+We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}.
 In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
@@
 The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
-These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
+The values we obtain by interpolating the geometric mean of the measured radii are consistent with the radii from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radii from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
 The highest $k_{\mathrm{T}}$ bin was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii for such study, but given that these measurements are not  available in all collision systems, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
+Ideally, one would use the proton femtoscopic radii for such a study, but given that these measurements are not  available in all collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
 
@@
 \includegraphics[width=0.7\textwidth]{HbtRadiusParam.eps}
-\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Abelev:2012sq}.}
+\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.}
 \label{fig:radiiparam}
@@
 As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra.
+In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the \pt-differential hadron spectra.
 In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
-When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{Abelev:2013vea}.
+When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}.
 The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
 This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013xaa,Abelev:2013vea} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
-Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
-Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality/multiplicity classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
-In contrast to the coalescence approach which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model, which as a simplified hydrodynamic model treats the system as a continuum and is not particle based.
-The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg model used here).
+In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
+Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
+Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
+In contrast to the coalescence approach, which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
+Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based.
+The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg model used here).
 We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
@@
 
-\subsection{Constraining the source volume with data}
+\subsection{Constraining the source volume with data}\label{sec:radiiParamet}
 
-Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017,Acharya:2017dmc,Adam:2015yta}.
+Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
 In Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.
-First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown in the two left panels).
-We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
+\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
+For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions.
+In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>0$ class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
+First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
+\ref{fig:CompareB2B3forDifferentParamWithData}).
+We notice already at this point that the coalescence volume from parameterisation A radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
+
+In a second step the radius is tuned such that the data points for (anti-)deuterons fall onto the coalescence prediction (top right panel of Fig.
+\ref{fig:CompareB2B3forDifferentParamWithData}).
+We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
+With this second parameterisation (labeled as "B" in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree,  \bthree.
+As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
+The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the latter is the same for all anti- and hyper-nuclei.
+It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
 
@@
 		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo~values in central Pb-Pb collisions.}
+		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.}
 		\label{fig:CompareB2B3forDifferentParamWithData}
@@
 
-Therefore, in a second step the radius is tuned such that the data points for (anti-) deuterons fall onto the coalescence prediction (solid markers).
-We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be \textcolor{red}{$a \approx 0.473$ and $b \approx 0$}.
-With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree.
-As shown in Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found which ameliorates with the parameterisation which is tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that it is the same for all fragile anti- and hyper-nuclei.
-%\textcolor{red}{We note that this approach is in contrast to the study of Che Ming Ko which allows different freeze-out times for different particles???}
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
+\newpage
+ \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
 
- \subsection{Thermal and coalescence model for A = 2, 3 anti- and hyper-nuclei}
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and \hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
+For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}.
+The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}.
 
-In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuterons, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions.
-For the coalescence predictions, the radius parameterisation tuned to the data is used.
-The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}.
-As a first observation, one sees that for deuterons and \hethree\ both approaches lead to similar predictions and give a reasonable description of the experimental data.
-However, both approaches show large differences for the \hthreelambda\ caused by the significantly larger size of  \hthreelambda\ with respect to \hethree.
-As a matter of fact, the only available data point so far shows a better agreement with the thermal+BW model than with the coalescence model.
-However, some authors argue that the difference to the coalescence model might be explained by a later formation through $\Lambda$s and deuterons~\cite{Zhang:2018euf}.
-In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production which is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
-The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from only counting the spin states.
-
-\begin{figure}[htbp]
+\begin{figure}[ht]
 	\begin{center}
-		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the thermal model expectations and the coalescence prediction which is tuned to \btwo\ values in central Pb-Pb collisions.}
+		\includegraphics[width=0.8\textwidth]{compareThermalAndCoalescence.png}
+		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
+Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
+The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
 		\label{fig:CompareThermalAndCoalescence}
@@
 
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} also shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios.
+As a first observation, one sees that for deuterons both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
+For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 2.
+The the limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
+Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor of about 30 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
+As a matter of fact, the only datapoint available so far in Pb--Pb collisions is in agreement with the thermal+BW model but not with coalescence.
+The difference between data and the coalescence model is about 6$\sigma$.
+However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
+Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
+In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production.
+This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
+According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
+%The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from only counting the spin states.
+
+Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity or centrality in order to distinguish between the two production scenarios.
+In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.
+\ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities.
 This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
 The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions.
-As can be seen, its production in pp collisions is expected to be suppressed by about two orders of magnitude with respect to that of \hethree, thus making this measurement a prime candidate for future experimental study.
+As it can be seen, the latter is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
 
@@
 %- add a plot for A=4
-
 %\subsection{Other exotic QCD objects}
@@
 One of them is the X(3872) which might have a wide wave-function as described in http://inspirehep.net/record/861896?ln=de
-
 %\section{Projections for the LHC Run 3 and 4}\label{sec:projections}
@@
 %We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
-While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei, the study presented here shows that large differences are expected for hyper-nuclei with extended wave-functions.
+While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
 In the following, we summarise our main conclusions:
 \begin{enumerate}
-	\item Thermal and coalescence models give similar predictions for the production of $A$=2 and $A$=3 (anti-)nuclei in heavy-ion collisions for a source volume that is constrained by experimental data on (anti-)deuteron production.
-	\item Thermal and coalescence models give very different predictions for the production of hyper-tritons as a function of source volume in pp, p-Pb, and Pb-Pb collisions.
-In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect ot the production of \hethree.
-The very limited currently available data on the hyper-triton slightly favors the thermal model prediction.
-	\item Systematic measurement in pp, p-Pb, and Pb-Pb collisions at LHC energies show a unique potential to clarify the production mechanism and also the nature of composite QCD objects as they are sensitive to the extension, i.e.
-the wave-function of the object under study.
+	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on (anti-)deuteron production in central Pb--Pb collisions at the LHC.
+	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume.
+In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
+The very limited amount of data currently available favours the thermal model prediction within our assumptions.
+	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects. 
 \end{enumerate}
 
-In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827).
-If the X(3872) corresponds to a loosely bound molecule composed of $D^{*0}$ and $D^{0}$ mesons, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu} which is very similar to that of the hyper-triton.
-Thus, its production via a possible coalescence mechanism in pp collisions would be subject to similar suppression as the hyper-triton.
-These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.
-In addition, our study is deliberately based on many simplifying assumptions in order to allow for a completely analytical treatment of the problem highlighting.
-Future studies will be based on more realistic approximations requiring numerical calculations.
+We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
+Future studies should be based on more realistic approximations, which requires numerical calculations.
+Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
+
+In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872).
+In fact, if the X(3872) corresponds to a loosely bound $D^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
+Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
+Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.
 
@@
 %As discussed in~\cite{Nagle:1996vp}, 
-The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium as in~\cite{Scheibl:1998tk}.
-Moreover, it assumes no correlation between different nucleons and no correlation between coordinates in space and momentum (in a heavy ion collisions, such correlations are consequence of hydrodynamical flow).
-%For the deuteron, the authors propose an expression for the coalescence momentum $p_{0}$ which equals
-%\begin{equation}
-%	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} \left(\frac{\nu_{d}\nu}{\nu_d + \nu}\right)^{3/2}
-%\end{equation}
-%\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$.
-\\In~\cite{Sato:1981ez}, the coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
+The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}.
+It assumes no correlation between different nucleons and no correlation between coordinates in space and momentum.
+In a heavy ion collisions, such correlations are consequence of hydrodynamical flow.
+The coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
 %
@@
 %
-where $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively. 
+where $p_{0}$ corresponds to the coalescence momentum, $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively.
+The reaction cross sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
 Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
@@
 \noindent indicating with $J_{A}$ the spin of the nucleus.
-Once again, the $\nu_{A}$ parameter corresponds to the size parameter of the nucleus wave-function, which is assumed to be gaussian (solution to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
+Once again, the $\nu_{A}$ parameter corresponds to the size parameter of the nucleus wave-function, which is assumed to be gaussian (solution to the isotropic spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
 
@@
 First, we notice that the cross term $R_{ol}$ vanishes if the measured fireball is longitudinally boost-invariant, which is a valid approximation for the rapidity ranges studied here.
-The remaining terms are all proportional to $\beta_l$, which is also $\beta_l = 0$ by definition of the rest frame for a longitudinally-boosted invariant system.
+The remaining terms are all proportional to $\beta_l$.
+By definition of the rest frame for a longitudinally-boosted invariant system, $\beta_l = 0$.
 In summary, we can consider $R_{\perp} = R_{side}$ and $R_{\parallel}=R_{long}$ for the present study.

### 2018-07-12 FrascatiPlot/B2vsVolume.C

@@ -815,8 +815,8 @@ void MakePaperFigure3(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,
   paveB->Draw();
   legC->Draw();
 
-  cr1->SaveAs("Paper/radiiParamCompareData.eps");
-  cr1->SaveAs("Paper/radiiParamCompareData.png");
+  // cr1->SaveAs("Paper/radiiParamCompareData.eps");
+  // cr1->SaveAs("Paper/radiiParamCompareData.png");
   
 
 }
@@ -1013,8 +1013,8 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
   cr4->cd(2);
   masterLeg->Draw();
   
-  cr4->SaveAs("Paper/compareThermalAndCoalescence.eps");
-  cr4->SaveAs("Paper/compareThermalAndCoalescence.png");
+  // cr4->SaveAs("Paper/compareThermalAndCoalescence.eps");
+  // cr4->SaveAs("Paper/compareThermalAndCoalescence.png");
 
 }
 

### 2018-07-12 FrascatiPlot/Paper/NucleiB2.tex
We are very grateful

@@
 
+%%%%% acknowledgements
+\newenvironment{acknowledgement}{\relax}{\relax}
+\begin{acknowledgement}
+\section*{Acknowledgements}
+We thank U.
+Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
+We further acknowledge discussions with Benjamin Doenigus about the production of \hthreelambda\ in pp collisions.
+In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Roman Lietava, Kfir Blum and the colleagues from the ALICE Collaboration for their valuable input.
+
+\end{acknowledgement}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
 \begin{appendix}
@@
 
-%%%%% acknowledgements
-\newenvironment{acknowledgement}{\relax}{\relax}
-\begin{acknowledgement}
-\section*{Acknowledgements}
-We thank U. Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
-The authors would like to thank themselves for the auto-critics.
-
-\end{acknowledgement}
-
 \bibliographystyle{utphys} 	

### 2018-07-12 FrascatiPlot/Paper/NucleiB2.tex
Minor fixes. Version sent to Phys. Coord. and LF.
Added affiliation to CERN
Fixed missing bar in the D0*-bar D0 for the X(3872)

@@
 
-F. Bellini and A. Kalweit
-
+F. Bellini$^{1}$ and A. Kalweit$^{1}$
+\\$^{1}$CERN, Switzerland
 \medskip
 
-16th of May 2018
+12th July 2018
 \end{center}
@@
 \end{equation}
-anielski-HQ14
+
 \noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
@@
 In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872).
-In fact, if the X(3872) corresponds to a loosely bound $D^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
+In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
 Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.

### 2018-07-13 FrascatiPlot/Paper/NucleiB2.tex
Correcting typos spotted by Andreas

@@
 For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei.
-This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount up to 10 fm \cite{Nemura:1999qp}.
+This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
 Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
@@
 We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
-As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity to for the final understanding of (anti-)(hyper-)nuclei production.
+As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
 Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments.
@@
 
-\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
+\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
 Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
@@
 This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but we also list the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
+In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
 The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g.

### 2018-07-16 FrascatiPlot/Paper/NucleiB2.tex
Fixed a couple of bib items, including Jonas as spotted by Benjamin

@@
 \RequirePackage{ifpdf}
-
-%\documentclass[a4paper,11pt]{scrartcl} % scrartcl scrreprt
-\documentclass[a4paper,11pt]{scrartcl} % scrartcl scrreprt
-
+\documentclass[a4paper,11pt]{scrartcl} 
 \usepackage[margin=2.5cm]{geometry}
@@
 \usepackage{makecell}
-\usepackage{amsmath}% http://ctan.org/pkg/amsmath
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
 %\fi
-
 %\usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-
 \usepackage{amsmath}
@@
 
-%
-% DOCUMENT STARTS HERE
-%
 \input{./commands.tex}
@@
 \begin{center}
-%{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies with recent and future experimental data}}
+
 {\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies}}
@@
 
-12th July 2018
+15th July 2018
 \end{center}
@@
 \bigskip
-
-%
-% Introduction 
-%
-%\listoffigures
-%\listoftables
-%\newpage
 
@@
 Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
-%Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions.
 The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
@@
 
-%%Table of contents - to be removed for submission%%
-%\newpage
-%\tableofcontents
 \newpage
@@
 Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-%In addition, it was recently shown that the assumption of realistic eigenvolumina for light nuclei would lead to instabilities of the statistical/thermal model predictions \cite{Vovchenko:2016mwg}.
 Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
@@
 \begin{tabularx}{\textwidth}{cccccccc}
-%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.}
 \hline \hline \\[-2ex]
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% SOURCE VOLUME
-%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Source volume}
@@
 \includegraphics[width=0.7\textwidth]{HbtRadiusParam.eps}
-\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.}
+\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
+The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
 \label{fig:radiiparam}
@@
 \end{figure}
-
-%- excess binding energy needs to be released to the system to make coalescence work
 
@@
 		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.}
+		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
+The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
 		\label{fig:CompareB2B3forDifferentParamWithData}
@@
 According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
-%The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from only counting the spin states.
 
@@
 
-%\subsection{Predictions for A=4}
-%- add a plot for A=4
-%\subsection{Other exotic QCD objects}
-%- add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
-%We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature.
-One of them is the X(3872) which might have a wide wave-function as described in http://inspirehep.net/record/861896?ln=de
-%\section{Projections for the LHC Run 3 and 4}\label{sec:projections}
-
 \section{Summary, conclusions, and outlook}
 
-%We conclude that (c.) appears unlikely, thus leaving (b.) as a viable option, at least with our present knowledge of the hypertriton size.
 While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
@@
 
-   % -> http://inspirehep.net/record/1662034 (I think that he is double counting => he should remove the protons and neutrons that have already coalesced into a hyper-triton from the sample.
-He argues that this is one different time scales which might explain it, ie.
-the volume for which hyper-triton coalescence happens is just much larger than the one in which deuteron coalescence happens.
-However, if the two different time-scales are true ?
-in our approach a much larger volume ?
-then they should not show so much radial/elliptic flow as they are then formed after decoupling?
-==> THIS COULD SOMEHOW DESTROY THE WHOLE STORY.)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% acknowledgments
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%% acknowledgements
 \newenvironment{acknowledgement}{\relax}{\relax}
@@
 Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
-We further acknowledge discussions with Benjamin Doenigus about the production of \hthreelambda\ in pp collisions.
+We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions.
 In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Roman Lietava, Kfir Blum and the colleagues from the ALICE Collaboration for their valuable input.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%              APPENDIX                   %%%%%%%%%%%
+%   APPENDIX                   
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
-%As discussed in~\cite{Nagle:1996vp}, 
 The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}.
@@
 
-%
-% RMS appendix
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% A = 4 Appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 
-\noindent Then we introduce the Jacobi variables which are given by %HERE-I-STOP
-
+\noindent Then we introduce the Jacobi variables which are given by 
 \begin{align}
@@
 
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % HBT Appendix
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 \end{document}
-
-%%
-%% End of file.

### 2018-07-16 FrascatiPlot/Paper/NucleiB2.tex
Version for submission to the arXiv: all figures in png format, comments removed -- it compiles properly on arXiv! :)
Fixed last couple of issues, added emails, removed reference to r = 0.3 fm from thermal model, .... and finally we are good to go

@@
 \usepackage{lineno}
-\linenumbers
+%\linenumbers
 
@@
 
-F. Bellini$^{1}$ and A. Kalweit$^{1}$
-\\$^{1}$CERN, Switzerland
+F. Bellini and A. Kalweit \footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch}
+\\CERN, EP Department, Geneva (Switzerland)
+
 \medskip
 
-15th July 2018
+16$^{th}$ July 2018
 \end{center}
@@
 %
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, similar to the value currently assumed in thermal model calculations \cite{Andronic:2016nof}, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
 As can be seen in Fig.
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.eps}
+\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.png}
 \caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{HbtRadiusParam.eps}
+\includegraphics[width=0.7\textwidth]{HbtRadiusParam.png}
 \caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
@@
 Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based.
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg model used here).
+The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
 We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
@@
 For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions.
-In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>0$ class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
+In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
 First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
@@
 	\begin{center}
-		\includegraphics[width=0.8\textwidth]{compareThermalAndCoalescence.png}
+		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
 		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
@@
 \section*{Acknowledgements}
+We would like to thank Kfir Blum for inspiring this work.
 We thank U.
 Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
-We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions.
-In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Roman Lietava, Kfir Blum and the colleagues from the ALICE Collaboration for their valuable input.
-
+We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
+In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava and the colleagues from the ALICE Collaboration for their valuable input.
 \end{acknowledgement}
@@
 \newpage
-\section{RMS of a gaussian wave-function for A=4 }\label{appendix:integration}
+\section{RMS of a gaussian wave-function for $\mathbf{A=4}$}\label{appendix:integration}
 
-In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of A=4. We start from the wave-function
+In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of $A=4$. We start from the wave-function
 

### 2018-08-21 FrascatiPlot/B2vsVolume.C
Minor changes to plotting macros for YR

@@ -178,7 +178,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   // objSize = 2.48; //fm for the 3^He
 
   TF1 * Cd_coalescence = (TF1*) MakeB2TheoryGraphQMfactor();
-  Cd_coalescence->SetLineWidth(3);
+  Cd_coalescence->SetLineWidth(2);
   Cd_coalescence->SetLineStyle(1);
   Cd_coalescence->SetLineColor(kBlack);
 
@@ -188,18 +188,18 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   Cd_coalescence_pointlike->SetLineColor(kBlue);
 
   TF1 * Cd_coalescence_radius1third = (TF1*) MakeB2TheoryGraphQMfactor(0.3);
-  Cd_coalescence_radius1third->SetLineWidth(3);
+  Cd_coalescence_radius1third->SetLineWidth(2);
   Cd_coalescence_radius1third->SetLineStyle(7);
   Cd_coalescence_radius1third->SetLineColor(kRed);
 
   TF1 * Cd_coalescence_largeradius = (TF1*) MakeB2TheoryGraphQMfactor(10.0);
-  Cd_coalescence_largeradius->SetLineWidth(3);
+  Cd_coalescence_largeradius->SetLineWidth(2);
   Cd_coalescence_largeradius->SetLineStyle(9);
   Cd_coalescence_largeradius->SetLineColor(kGreen+1);
   
   TGraphErrors* hB2_coalescence = (TGraphErrors*) MakeB2TheoryGraphCoalescence(mT);
   hB2_coalescence->SetMarkerStyle(20);
-  hB2_coalescence->SetLineWidth(3);
+  hB2_coalescence->SetLineWidth(2);
   hB2_coalescence->SetLineStyle(1);
 
   TGraphErrors* hB2_coalescence_pointlike = (TGraphErrors*) MakeB2TheoryGraphCoalescence(mT, 0.0);
@@ -212,14 +212,14 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
[…]

### 2018-08-21 FrascatiPlot/CoalescenceBA.C

@@ -115,7 +115,7 @@ Double_t getBAfromRadius(Short_t A, Double_t JA, Double_t mT, Double_t homogR,  
 {
   // formula 13 of the Frascati paper arXiv:1807.05894
   Double_t convFactor_fm2InvGeV = 0.197;
-  Double_t spinFactor = (JA+1) / TMath::Power(2., A);
+  Double_t spinFactor = (2*JA+1) / TMath::Power(2., A);
   Double_t expo = 3.*(A-1)/2.;
   Double_t mtfactor = TMath::Power(mT, -(A-1));
   Double_t BA =  spinFactor * 1./TMath::Sqrt(A) * mtfactor *

### 2018-08-21 FrascatiPlot/generateBWpredictionsB2.C

@@ -395,9 +395,9 @@ TGraphAsymmErrors * generateBWpredictionsB2(TString system = "PbPb276TeV",  TStr
   //output graph
   TGraphAsymmErrors * gB2 = new TGraphAsymmErrors(binCounter, multi, B2blastW, 0x0, 0x0, 0x0, 0x0);
 
-  TCanvas * model = new TCanvas("model","model", 800, 800);
-  model->cd();
-  gB2->Draw("apz");
+  // TCanvas * model = new TCanvas("model","model", 800, 800);
+  // model->cd();
+  // gB2->Draw("apz");
   
   return gB2;
 }

### 2018-08-21 FrascatiPlot/Paper/NucleiB2.tex
typo fix in formula 13 (the one with the box) in the spin factor
Mrowczynski's addressed

@@
 \usepackage{lineno}
-%\linenumbers
+\linenumbers
 
@@
 We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches.
-A comparison of the production rates of nuclei with similar mass but very different internal structure has already been suggested for the case of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
+
+A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
 However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
@@
 \begin{equation}
-	\boxed {  B_{A} = {J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
+	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
 \end{equation}

### 2018-08-21 FrascatiPlot/Paper/NucleiB2.tex
Starting implementing Marco's comments

@@
 They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
+The fact that the coalescence probability is anti-proportional to the source volume can already be understood in the classical phase-space picture as due simply to the separation in configuration space.
+Because coalescence is a quantum-mechanical process, however, the classical definition of phase space does not apply and it is replaced by the Wigner formalism.
+Therefore, most coalescence models, including \cite{Scheibl:1998tk}, determine the production probability of a nucleon cluster as by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
+
 The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
@@
 
+We understand the relation between $B_A$ and the radii as follows: for small radii of the source, as $R \rightarrow 0$, the coalescence probability appears to be anti-proportional to the harmonic oscillator size parameter $r_A$, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
+Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
+For large source volume, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, and thus decreases for large differences in configuration space.
+
 \subsection{Source volume}
@@
 We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}. 
-In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
+The latter is much smaller that the entire fireball which is created in heavy-ion collisions. 
+This is not only caused by the limitations ascribed to the causally-connected volume, but also to the presence of a common radial expansion, which causes the particles inside the fireball to be sorted according to their velocities.
+As pointed out by the same authors, this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
 The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$.
-We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
+As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$. We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
 
@@
 We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
-In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava and the colleagues from the ALICE Collaboration for their valuable input.
+In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava, Natasha Sharma and the colleagues from the ALICE Collaboration for their valuable input.
 \end{acknowledgement}

### 2018-09-05 FrascatiPlot/Paper/NucleiB2.tex
We are done with the comments from the friendly reviewwers + some changes to the macros to make plots for the YR

@@
 \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
+As a matter of fact, the inflection point of $\langle C_{d} \rangle$ is situated at $R = \dradius/\sqrt{6}$, as indicated in the left panel of Fig.
+\ref{fig:radiusDependence} by the vertical dotted line for $\dradius = 3.2$ fm.
 
-\begin{figure}[htbp]
+\begin{figure}[ht]
 \begin{center}
-\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.png}
+\includegraphics[width=.9\textwidth]{theory_coalescence_Cd_B2.png}
 \caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
 \ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
+\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
+The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
 \label{fig:radiusDependence}
@@
 Ideally, one would use the proton femtoscopic radii for such a study, but given that these measurements are not  available in all collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
+We acknowledge that a model-based scaling factor is proposed by \cite{Kisiel:2014upa}, which alternatively could be considered.
 
@@
 As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the \pt-differential hadron spectra.
+In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provide only \pt-integrated yields and not the \pt-differential hadron spectra.
 In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
@@
 The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
-This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
+This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
 In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
@@
 
+The necessity of introducing a second parameterisation for the radius could point to the fact that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered here, but by a slightly larger system.
+
 \begin{figure}[htbp]
@@
 
-\newpage
 \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-
 In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and \hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
@@
 
-\begin{figure}[ht]
-	\begin{center}
-		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
-Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
-The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
-		\label{fig:CompareThermalAndCoalescence}
-	\end{center}
-\end{figure}
-
 As a first observation, one sees that for deuterons both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
-For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 2.
+For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2.
 The the limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
-Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor of about 30 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
+Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
 As a matter of fact, the only datapoint available so far in Pb--Pb collisions is in agreement with the thermal+BW model but not with coalescence.
@@
 
+\begin{figure}[htbp]
+	\begin{center}
+		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
+		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
+Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
+The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
+		\label{fig:CompareThermalAndCoalescence}
+	\end{center}
+\end{figure}
+
 \section{Summary, conclusions, and outlook}
-
 While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
@@
 	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects.
+Ideally, such measurements are accompanied by systematic measurements of the HBT radii in the same multiplicity/centrality classes and collision systems.
 \end{enumerate}
@@
 We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
-Future studies should be based on more realistic approximations, which requires numerical calculations.
+As mentioned earlier, future studies should be based on more realistic approximations (in particular the wave function), which requires numerical calculations.
+The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
 Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.

### 2018-09-05 FrascatiPlot/B2vsVolume.C

@@ -206,7 +206,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   // objSize = 2.48; //fm for the 3^He
 
   TF1 * Cd_coalescence = (TF1*) MakeB2TheoryGraphQMfactor();
-  Cd_coalescence->SetLineWidth(2);
+  Cd_coalescence->SetLineWidth(3);
   Cd_coalescence->SetLineStyle(1);
   Cd_coalescence->SetLineColor(kBlack);
 
@@ -227,7 +227,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   
   TGraphErrors* hB2_coalescence = (TGraphErrors*) MakeB2TheoryGraphCoalescence(mT);
   hB2_coalescence->SetMarkerStyle(20);
-  hB2_coalescence->SetLineWidth(2);
+  hB2_coalescence->SetLineWidth(3);
   hB2_coalescence->SetLineStyle(1);
 
   TGraphErrors* hB2_coalescence_pointlike = (TGraphErrors*) MakeB2TheoryGraphCoalescence(mT, 0.0);
@@ -255,7 +255,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   hB3_coalescence->SetMarkerStyle(20);
   hB3_coalescence->SetMarkerColor(kBlack);
   hB3_coalescence->SetLineColor(kBlack);
-  hB3_coalescence->SetLineWidth(2);
+  hB3_coalescence->SetLineWidth(3);
 
   TGraphErrors* hB3_coalescence_pointlike = (TGraphErrors*) MakeB3TheoryGraphCoalescence(mT3, 0.0);
   hB3_coalescence_pointlike->SetMarkerStyle(24);
@@ -268,7 +268,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   hB3L_coalescence->SetMarkerStyle(20);
   hB3L_coalescence->SetMarkerColor(kBlack);
   hB3L_coalescence->SetLineColor(kBlack);
-  hB3L_coalescence->SetLineWidth(2);
[…]

### 2018-09-05 FrascatiPlot/CoalescenceBA.C

@@ -7,30 +7,81 @@
 #include "TH2D.h"
 
 
-Double_t getBAfromRadius(Short_t A, Double_t JA, Double_t mT, Double_t homogR,  Double_t objSize);
-TGraphErrors * MakeBATheoryGraphCoalescence(Short_t A, Double_t JA, Double_t mT, Double_t objSize);
-TGraphErrors * MakeBAcoalRelSize(Short_t A, Double_t JA, Double_t pToA, Bool_t isHyper);
+void CoalescenceBA(Double_t pToA = 0.75);
+void CoalescenceYields();
+Double_t getBAfromCoalescence(Double_t A, Double_t JA, Double_t mT, Double_t homogR,  Double_t objSize);
+TGraphErrors * MakeBATheoryGraphCoalescence(Double_t A, Double_t JA, Double_t mT, Double_t objSize);
+TGraphErrors * MakeBAcoalRelSize(Double_t A, Double_t JA, Double_t pToA, Bool_t isHyper);
+TH2D * CreateFrameBA();
+TH1D * GetProtonIn010CentBin();
 
+//make coalescence prediction
+Double_t nucleiA[8] = {2, 3, 3, 3, 4, 4, 4, 4};
+Double_t spin[8] = {1., 0.5, 0.5, 0.5, 0., 0., 1., 0};
+Double_t objRadius[8] = {3.2, 2.15, 2.48, 6.8, 1.9, 2.4, 5.5, 2.4};
+Color_t color[8] = {kBlack, kBlue+1, kAzure+8, kGreen+2, kRed+1, kOrange+8, kPink-3, kOrange};
+Int_t line[8] = {1, 1, 1, 2, 1, 2, 5, 3};
+
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+//Extract yields for different (hyper-)nuclear species from predictions of BA from coalescence
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+void CoalescenceYields()
+{
+  Double_t radiusCent = 1.;
+
+  //GetProton Spectrum
+  TH1D * hProSpectrum = (TH1D *) GetProtonIn010CentBin();
+  const Int_t nBinsIn = hProSpectrum->GetBinsX();
+  Double_t ptBinsOut[nBinsIn];
+  
[…]

### 2018-09-18 FrascatiPlot/generateBWpredictionsB2.C
Included 5.02 TeV Lambda yields (from paper draft, David priv. comm. 13.09.18)

@@ -3,7 +3,9 @@
 #include "TMath.h"
 #include "TCanvas.h"
 
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
 //AK implementation of the blast-wave function
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
 Double_t blast_integrand(const Double_t *x,const Double_t *par){
   Double_t x0=x[0];
   Double_t m=par[0];
@@ -43,6 +45,12 @@ void get_average(Double_t &bt, Double_t &bn, Double_t &bb)
   bb = (0.547*5 + 0.531*5 + 0.511*10) / 20.0;
   return;
 }
+
+
+
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+// Blast-wave parameters from ALICE fits to π,K,p
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
 
 void GetParams_pp7TeV(Double_t *parT, Double_t *parTerr, Double_t *parN, Double_t *parNerr, Double_t *parB, Double_t *parBerr, Double_t *dNdeta, Double_t *dNdetaerr, Double_t *protdNdy, Double_t *protdNdyErr, Double_t *piondNdy, Double_t *piondNdyErr)
 {    
@@ -171,9 +179,11 @@ void GetParams_PbPb276TeV(Double_t *parT, Double_t *parTerr, Double_t *parN, Dou
   Double_t dNdyPion[10]     = {733., 606., 455., 307., 201., 124., 71., 37., 17.1, 6.6};
   Double_t dNdyErrPion[10]  = { 54.,  42.,  31.,  20.,  13.,   8.,  5.,  2.,  1.1, 0.4};
 
-  // table 23 of http://hepdata.cedar.ac.uk/view/ins1243863 --> TODO: deal with different binning by interpolation
-  Double_t dNdyLambda[10]    = {25.61, 21.58, 16.89, 0., 0., 0., 0., 0., 0., 0.};
-  Double_t dNdyErrLambda[10] = { 0.72,  0.62,  0.50, 0., 0., 0., 0., 0., 0., 0.};
+  // Lambda only -- table 23 of http://hepdata.cedar.ac.uk/view/ins1243863
+  // --> TODO: deal with different binning by interpolation
[…]

### 2018-09-18 FrascatiPlot/CoalescenceBA.C
Added here figure with comparison of thermal and coalescence, relative stat uncert on BA from pseudodata and separation.

@@ -7,14 +7,28 @@
 #include "TH2D.h"
 #include "./B2vsVolume.C"
 
-void CoalescenceBA(Double_t pToA = 0.75);
-TH1D * CoalescenceYields010(Int_t iN = 0, Bool_t useBlastWave = kFALSE);
+//coalescence
+void    CoalescenceBA(Double_t pToA = 0.75);
+Double_t getBAfunc(Double_t *x, Double_t *par);
 Double_t getBAfromCoalescence(Double_t A, Double_t JA, Double_t mT, Double_t homogR,  Double_t objSize);
 TGraphErrors * MakeBATheoryGraphCoalescence(Double_t A, Double_t JA, Double_t mT, Double_t objSize);
 TGraphErrors * MakeBAcoalRelSize(Double_t A, Double_t JA, Double_t pToA, Bool_t isHyper);
-TH2D * CreateFrameBA();
+
+//thermal 2 coalescence comparison
+void           Thermal2Coalescence(Bool_t draw = 0);
+TGraphErrors * Thermal2CoalescenceSeparation(Int_t particle = 0, Double_t relSysUnc = 0.10);
+
+//pseudodata
+TH1D * CoalescenceYields010(Int_t iN = 0, Bool_t useBlastWave = kFALSE);
 TH1D * GetProtonIn010CentBin(TString file = "~/alice/pwglf-piKp5teV/SpectraAnalysisRun2/results/spectra/spectra-pag/Preliminaries/QM2017/Spectra_PbPbLHC15o_Combined_Histograms.root");
 TH1D * GetProtonIn010CentBinBlast();
+
+
+//frames and plotting
+TH1D * CreateFrameBA();
+TH1D * CreateFrameSeparation();
+TH1D * CreateFrameUncertainty();
+void   SetCanvasStyle();
 
 //make coalescence prediction
 Double_t nucleiA[8] = {2, 3, 3, 3, 4, 4, 4, 4};
@@ -22,6 +36,271 @@ Double_t spin[8] = {1., 0.5, 0.5, 0.5, 0., 0., 1., 0};
 Double_t objRadius[8] = {3.2, 2.15, 2.48, 6.8, 1.9, 2.4, 5.5, 2.4};
 Color_t color[8] = {kBlack, kBlue+1, kAzure+8, kGreen+2, kRed+1, kOrange+8, kPink-3, kOrange};
 Int_t line[8] = {1, 1, 1, 2, 1, 2, 5, 3};
+
[…]

### 2018-09-18 FrascatiPlot/Thermal2Coalescence.C
remove this macro --> moved to CoalescenceBA.C

@@ -1,238 +1,0 @@
-#include "CoalescenceBA.C"
-#include "B2vsVolume.C"
-
-TH1D * CreateFrameSeparation();
-TH1D * CreateFrameUncertainty();
-void SetCanvasStyle();
-TLegend * BuildLegendSpecies();
-TLegend * BuildLegendModels();
-
-
-Double_t getBAfunc(Double_t *x, Double_t *par);
-TGraphAsymmErrors * getBAthermalBlast(TString particle, Double_t pToA, Color_t color);
-
-void Thermal2Coalescence()
-{
-
-  // d, 3H, 3He, 3LH, 4He, 4LH 
-  Char_t particle[6][15] = {"deuteron", "triton", "He3", "hyper-triton", "He4", "4LH"};
-  Double_t nucleiA[]     = {   2,   3,     3,    3,    4,    4};
-  Double_t spin[]        = { 1.0, 0.5,   0.5,  0.5,  0.0,  0.0};
-  Double_t objRadius[]   = { 3.2, 2.15, 2.48,  6.8,  1.9,  2.4};
-  Double_t pToA[]        = {0.75, 0.77, 0.77, 1.17, 0.75, 0.62};
-  Color_t color[]        = {kBlack, kBlue+1, kAzure+8, kGreen+2, kRed+1, kOrange+8};
-  
-  TCanvas * cr4 = new TCanvas("cr4", "compare thermal with coalescence", 900, 2000);
-  SetCanvasStyle();
-  TH2D * frame = CreateFrameBA();
-  frame->GetYaxis()->SetTitleOffset(0.8);
-  frame->GetYaxis()->SetRangeUser(1e-12, 1);
-  TH1D * frameSep = CreateFrameSeparation();
-  TH1D * frameUnc = CreateFrameUncertainty();
-  cr4->Divide(1,3);
-  cr4->cd(1); gPad->SetLogy(); gPad->SetTicky();  gPad->SetTickx();
-  frame->Draw();
-  cr4->cd(3); gPad->SetLogy(); gPad->SetTicky();  gPad->SetTickx();
-  frameSep->Draw();
-  cr4->cd(2); gPad->SetLogy(); gPad->SetTicky();  gPad->SetTickx();
-  frameUnc->Draw();
-
-  TF1 * fBAcoalescence[6];
-  TGraphAsymmErrors * gThermalBlast[6];
-  TGraphErrors * gSeparation[6];
[…]

### 2018-09-18 FrascatiPlot/B2vsVolume.C
Moved figure for the YR in a new macro and fixed some dependencies. All that is from the old version and is commented will have to be cleaned up later

@@ -9,7 +9,7 @@
 #include "TLegend.h"
 #include "TH1D.h"
 #include "TH2D.h"
-#include "./generateBWpredictionsB2.C" //ADAPT ME
+#include "./generateBWpredictionsB2.C" 
 
 //mapping multiplicity into radius
 void convertMultiToRadius(TGraphErrors * graph = 0x0, Int_t paramSet = 0);
@@ -40,6 +40,8 @@ TGraphAsymmErrors * getBlastB4_pp7TeV(Bool_t plotSys = 0, Double_t pToAb4 = 0.75
 TGraphAsymmErrors * getBlastB4Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.75, Int_t paramSet = 0);
 TGraphAsymmErrors * getBlastB4Lambda_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.75, Int_t paramSet = 0);
 
+TGraphAsymmErrors * getBAthermalBlast(TString system = "PbPb276TeV", TString particle = "deuteron", Double_t pToA = 0.75, Color_t color = kBlack, Int_t paramSet = 1);
+
 //ALICE data on nuclei BA
 //deuteron
 TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
@@ -57,12 +59,15 @@ TGraphAsymmErrors * getB3_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToAb3pp = 0
 TGraphAsymmErrors * getB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1., Int_t paramSet = 0);
 
 //pseudodata
-TGraphErrors * GetPseudoBAvsMulti(TString particle = "deuteron",  Int_t paramSet = 0);
+//TGraphErrors * GetPseudoBAvsMulti(TString particle = "deuteron",  Int_t paramSet = 1);
+//TGraphErrors * GetPseudoBAvsMultiUnc(TString particle = "deuteron",  Int_t paramSet = 1);
 
   
 // beautification of plots
[…]

### 2018-09-18 FrascatiPlot/MakeYRfigure.C
New macro for figure for the YR

@@ -1,0 +1,704 @@
+/*
+   fbellini@cern.ch
+   17.09.2018 - Yellow Report plot
+*/
+
+#include "./CoalescenceBA.C"
+
+void ConfigTwoPanelsPad(TPad* pad1, TPad* pad2, Float_t leftmargin, Float_t rightmargin);
+void ConfigThreePanelsPad(TPad* pad1, TPad* pad2, TPad* pad3, Float_t leftmargin = 0.15, Float_t rightmargin = 0.001);
+
+//pseudodata
+TGraphErrors * GetPseudoBAvsMulti(TString particle = "deuteron",  Int_t paramSet = 1);
+TGraphErrors * GetPseudoBAvsMultiUnc(TString particle = "deuteron",  Int_t paramSet = 1);
+
+//main
+void MakeYRfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t pToAb4 = 0.75, Double_t pToAb4Lambda = 0.62, Bool_t plotPseudoData = 1)
+{
+  //
+  // main function which generates Figure 1 for the LF chapter of the yellow report
+  //
+  gStyle->SetOptStat(0);
+  gStyle->SetOptTitle(0);
+  gStyle->SetPadTopMargin(0.02);
+  gStyle->SetPadBottomMargin(0.1);
+  gStyle->SetPadLeftMargin(0.15);
+  gStyle->SetPadRightMargin(0.02); 
+
+  Double_t Rmin = 0.01; Double_t Rmax = 6.5;
+  //------------------------------
+  // Pseudodata
+  //------------------------------
+  TGraphErrors * gPseudo3He = (TGraphErrors *) GetPseudoBAvsMulti("he3", 1);
+  TGraphErrors * gPseudo3LambdaH = (TGraphErrors *) GetPseudoBAvsMulti("hyperH3", 1);
+  TGraphErrors * gPseudo4He = (TGraphErrors *) GetPseudoBAvsMulti("he4", 1);
+  TGraphErrors * gPseudo4LambdaH = (TGraphErrors *) GetPseudoBAvsMulti("hyperH4", 1);
+  
+  //-----------------------------
+  //theory - Blast Wave + thermal
+  //-----------------------------
+  // pToAb3 = 0.77;
[…]

### 2018-09-18 FrascatiPlot/generateBWpredictionsB2.C
Now using centrality dependent lambda yields for hyper-triton BW normalisation. Left to do: for wider bins of centrality from the 2.76 TeV measurement we still have to interpolate. Now I am using the same yield in the wider bin for the 10%-wide bins.

@@ -181,9 +181,9 @@ void GetParams_PbPb276TeV(Double_t *parT, Double_t *parTerr, Double_t *parN, Dou
 
   // Lambda only -- table 23 of http://hepdata.cedar.ac.uk/view/ins1243863
   // --> TODO: deal with different binning by interpolation
-  // published bins are (0-5, 5-10, 10-20, 20-40, 40-60, 60-80, 80-90)%
-  Double_t dNdyLambda[10]    = {25.61, 21.58, 16.89, 9.79, 3.79, 0.99, 0.214, -1., -1., -1.};
-  Double_t dNdyErrLambda[10] = { 2.91,  1.9,   1.9,  0.947,0.378,0.0937, 0.0166, 0., 0., 0.};
+  // published bins are          (0-5,  5-10, 10-20, 20-40, fixme, 40-60, fixme, 60-80, fixme,  80-90)%
+  Double_t dNdyLambda[10]    = {25.61, 21.58, 16.89, 9.79,  9.79,  3.79, 3.79,  0.99,   0.99,   0.214};
+  Double_t dNdyErrLambda[10] = { 2.91,  1.9,   1.9,  0.947, 0.947, 0.378,0.378, 0.0937, 0.0937, 0.0166};
 
 
 
@@ -216,7 +216,6 @@ void GetParams_PbPb502TeV(Double_t *parT, Double_t *parTerr, Double_t *parN, Dou
   //BW Results from Livio (email 27/01/2017): fit of the spectra from 24.01.2017 (approval forum, iteration 1)
   //Parameters and proton yield can be found at:
   //https://gitlab.cern.ch/njacazio/SpectraAnalysisRun2/tree/master/results/spectra/spectra-pag/Preliminaries/QM2017
-  
 
   Double_t bt[10]    = {0.086, 0.088, 0.091, 0.094, 0.099, 0.106, 0.104, 0.127, 0.147, 0.163};
   Double_t bterr[10] = {0.004, 0.004, 0.004, 0.004, 0.004, 0.005, 0.005, 0.006, 0.007, 0.008};
@@ -367,9 +366,8 @@ TGraphAsymmErrors * generateBWpredictionsB2(TString system = "PbPb276TeV",  TStr
     fLambda->SetParameters(mLambda, 1., bt[j], bn[j], bb[j]);//m is mass, yield is yield in min bias
     fLambda->SetLineColor(color[j]);
     Double_t Ilambda = fLambda->Integral(0.,30.);
[…]

### 2018-09-18 FrascatiPlot/generateBWpredictionsB2.C
Using pdg values for proton and Lambda mass (with all significant digits, even if it does  not change anything)

@@ -434,8 +434,9 @@ TH1D * generateBWpredictionSpectra(Int_t selcent = 0, TString system = "PbPb276T
   //
   // Get the blast-wave for proton, based on the pi/K/p parameters.
   // The normalisation is such that the pT-integrated yield of protons corresponds to the measured yield
-  const Double_t mProton = 0.938;
-  const Double_t mLambda = 1.115; // FIXME: use proper mass value
+  //masses of p and Lambda from PDG 2018
+  const Double_t mProton = 0.938272081;
+  const Double_t mLambda = 1.115683; 
   //Set mass
   Double_t m = 0.0;
   

### 2018-09-18 FrascatiPlot/generateBWpredictionsB2.C
New methos to return the mass of the nucleus (keep all values in one place)

@@ -3,6 +3,23 @@
 #include "TMath.h"
 #include "TCanvas.h"
 
+
+//masses of p and Lambda from PDG 2018
+const Double_t mProton = 0.938272081;
+const Double_t mLambda = 1.115683; 
+
+Double_t Mass(TString particle)
+{
+  Double_t m = 0.0;
+  if (particle.Contains("deuteron")) m = 1.875612928; //CODATA, https://physics.nist.gov/cgi-bin/cuu/Value?mdc2mev
+  if (particle.Contains("triton")) m = 2.808921112; //triton mass 
+  if (particle.Contains("He3")) m = 2.808921112 - 0.018592017; //using mass difference (m3H - m3He) from CODATA
+  if (particle.Contains("hyper-triton")) m = 2.991; //FIXME: use a proper values, but this is correct within two permille 2*0.938+1.115
+  if (particle.Contains("He4")) m = 3.72737937823; //using value from CODATA for alpha particle
+  if (particle.Contains("4LH")) m = 3.931; //Ramona uses the same, from STEER/STEERBase/AliPDG.cxx
+  return m;
+}
+
 /////////////////////////////////////////////////////////////////////////////////////////////////////////
 //AK implementation of the blast-wave function
 /////////////////////////////////////////////////////////////////////////////////////////////////////////
@@ -278,21 +295,15 @@ TGraphAsymmErrors * generateBWpredictionsB2(TString system = "PbPb276TeV",  TStr
   const Double_t dOverPiThermal = 0.0001817; // GSI-Heidelberg at 156 MeV
   const Double_t He3OverPiThermal = 5.354e-07; // GSI-Heidelberg at 156 MeV
   const Double_t He3OverPthermal =  8.68733e-06; // GSI-Heidelberg at 156 MeV --- (only 4% difference wrt to old value of 0.00294824/330.)
-  const Double_t s3thermal = 0.55; // TODO: this is just read off figure 7 og hyper-triton paper.
-  const Double_t mProton = 0.938;
-  const Double_t mLambda = 1.115; // FIXME: use proper mass value
+  const Double_t s3thermal = 0.55; // FIXME: this is just read off figure 7 of hyper-triton paper.
+  const Double_t mProton = 0.938272081;
+  const Double_t mLambda = 1.115683; 
   const Double_t He4thermal = 7.e-7; //read off plot 
[…]

### 2018-09-20 FrascatiPlot/MakeYRfigure.C
Minor cosmetic fixes

@@ -10,7 +10,7 @@ void ConfigThreePanelsPad(TPad* pad1, TPad* pad2, TPad* pad3, Float_t leftmargin
 
 //pseudodata
 TGraphErrors * GetPseudoBAvsMulti(TString particle = "deuteron",  Int_t paramSet = 1);
-TGraphErrors * GetPseudoBAvsMultiUnc(TString particle = "deuteron",  Int_t paramSet = 1);
+TGraphErrors * GetPseudoBAvsMultiUnc(TString particle = "deuteron",  Int_t paramSet = 1, Color_t color = 0);
 
 //main
 void MakeYRfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t pToAb4 = 0.75, Double_t pToAb4Lambda = 0.62, Bool_t plotPseudoData = 1)
@@ -25,6 +25,8 @@ void MakeYRfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t
   gStyle->SetPadLeftMargin(0.15);
   gStyle->SetPadRightMargin(0.02); 
 
+
+  Color_t projCol = kRed+1;
   Double_t Rmin = 0.01; Double_t Rmax = 6.5;
   //------------------------------
   // Pseudodata
@@ -33,7 +35,47 @@ void MakeYRfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t
   TGraphErrors * gPseudo3LambdaH = (TGraphErrors *) GetPseudoBAvsMulti("hyperH3", 1);
   TGraphErrors * gPseudo4He = (TGraphErrors *) GetPseudoBAvsMulti("he4", 1);
   TGraphErrors * gPseudo4LambdaH = (TGraphErrors *) GetPseudoBAvsMulti("hyperH4", 1);
+
+   //TGraphErrors * gPseudoDeuteronUnc = (TGraphErrors *) GetPseudoBAvsMultiUnc("deuteron", 1);
+  TGraphErrors * gPseudo3HeUnc = (TGraphErrors *) GetPseudoBAvsMultiUnc("he3", 1, projCol);
+  TGraphErrors * gPseudo3LambdaHUnc = (TGraphErrors *) GetPseudoBAvsMultiUnc("hyperH3", 1, projCol);
+  TGraphErrors * gPseudo4HeUnc = (TGraphErrors *) GetPseudoBAvsMultiUnc("he4", 1, projCol);
[…]

### 2018-09-20 FrascatiPlot/B2vsVolume.C
Added option to plot figure 2 vertically for aps papers

@@ -72,7 +72,7 @@ void MakeUp(TGraphAsymmErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fil
 //figure making
 void MakePaperFigure2(Bool_t plotLinX, Double_t pToA,
 		      TF1 *Cd_coalescence, TF1* Cd_coalescence_pointlike, TF1* Cd_coalescence_radius1third,  TF1* Cd_coalescence_largeradius,
-		      TGraphErrors * hB2_coalescence, TGraphErrors * hB2_coalescence_pointlike, TGraphErrors * hB2_coalescence_radius1third, TGraphErrors * hB2_coalescence_largeradius);
+		      TGraphErrors * hB2_coalescence, TGraphErrors * hB2_coalescence_pointlike, TGraphErrors * hB2_coalescence_radius1third, TGraphErrors * hB2_coalescence_largeradius, Bool_t plotvert = 1);
 
 void MakePaperFigure3(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,
 		      TGraphErrors * hB2_coalescence, TGraphErrors * hB3_coalescence, 
@@ -307,8 +307,8 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   gStyle->SetOptStat(0);
   gStyle->SetOptTitle(0);
   gStyle->SetPadTopMargin(0.02);
-  gStyle->SetPadBottomMargin(0.1);
-  gStyle->SetPadLeftMargin(0.15);
+  gStyle->SetPadBottomMargin(0.15);
+  gStyle->SetPadLeftMargin(0.17);
   gStyle->SetPadRightMargin(0.02); 
 
   // ------------------
@@ -316,7 +316,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   // ------------------
   MakePaperFigure2(plotLinX, pToA,
 		   Cd_coalescence, Cd_coalescence_pointlike, Cd_coalescence_radius1third, Cd_coalescence_largeradius,
-		   hB2_coalescence, hB2_coalescence_pointlike, hB2_coalescence_radius1third, hB2_coalescence_largeradius);
[…]

### 2018-09-20 FrascatiPlot/Paper/aps/abstract.tex
First version of the paper into aps paper format - sub-files created, table modified - everything else is the same as for the arXiv version

--- 2018-08-21 FrascatiPlot/Paper/NucleiB2.tex
@@
-\RequirePackage{ifpdf}
-\documentclass[a4paper,11pt]{scrartcl} 
-\usepackage[margin=2.5cm]{geometry}
-\usepackage{multirow}
-\usepackage{tabularx} 
-\usepackage{rotating,graphicx} 
-\usepackage{appendix} 
-\usepackage{makecell}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{cite}
-%\ifpdf
-%  \usepackage[pdftex]{graphicx}
-%\else
-%  \usepackage[dvips]{graphicx}
-%\fi
-%\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{amsmath}
-\usepackage[amssymb]{SIunits}
-\usepackage{hyperref}
-
-\usepackage{lineno}
-\linenumbers
-
-\usepackage{xcolor}
-
-\input{./commands.tex}
-
-\begin{document}
-\begin{center}
-
-{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies}}
-
-\medskip
-
-F. Bellini and A. Kalweit \footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch}
-\\CERN, EP Department, Geneva (Switzerland)
-
-\medskip
-
-16$^{th}$ July 2018
-\end{center}
-
-\bigskip
-
-\begin{abstract}
 (Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC).
@@
 While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
+We propose for the first time a study which is experimentally feasible with the current and upgraded LHC experiments to distinguish between the two production scenarios.
 Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
@@
 Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
-\end{abstract}
-
-\newpage
-
-\section{Introduction} 
-The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
-In addition, these studies might shed light on the internal structure of the formed objects themselves.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e.
-the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
-The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
-As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
-Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei.
-This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
-Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
-
-Since about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
-Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}.
-Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
-Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
-Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically.
-At LHC energies, this is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
-In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects.
-For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
-As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
-Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
-While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
-
-\begin{table}[htb]
-
-\centering
-\begin{tabularx}{\textwidth}{cccccccc}
-\hline \hline \\[-2ex]
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
-\\[1ex]  \hline \\[-2ex]
-      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
-\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
-                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
-\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
-                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
-\end{tabularx}
-\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$.
-$B_{E}$ is the binding energy in MeV.
-The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius.
-The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced.
-Details are given in Appendix \ref{appendix:Sato}.
-Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
-Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
- References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
-\label{tab:nucleusradii}
-\end{table}
-
-To this purpose, we compare to models the existing data from the LHC.
-For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
-In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.
-The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}.
-In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach.
-The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
-We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches.
-
-A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
-We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
-As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
-Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments.
-In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
-
-\section{Coalescence approach} 
-\label{sec:coalescence}
-
-\subsection{Simple coalescence}
-In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}.
-For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$, which is defined as
-
-\begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
-   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
-,    
-\label{eq:BA}
-\end{equation}
-
-\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
-Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
-\begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
-\label{eq:BA}
-\end{equation}
-%
-Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
-As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
-In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
-In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision.
-If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
-In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
-
-\subsection{Advanced coalescence}
-\label{subsec:FullCoalescence}
-
-In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
-While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
-The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions.
-They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
-The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
-For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
-
-\begin{equation}\label{eq:WaveHeinz}
- \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
-\end{equation}
-
-\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
-
-\begin{equation}
- \rmsradius^2 = {3 \over 2}{A - 1 \over A} {r_{A}^2 \over 2}
-\end{equation}
-
-\noindent for point-like constituents.
-In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-
-This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
-The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g.
-the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
-We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions.
-Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
-the centrality dependence) and that of the (hyper-)nucleus.
-In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.
-
-The quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
-In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
-
-\begin{equation}
-\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
-\label{eq:Cd}
-\end{equation}
-%
-where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
-The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
-%
-\begin{equation}
-\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
-\label{eq:B2cd}
-\end{equation}
-%
-which is the main result of \cite{Scheibl:1998tk}.
-It is interesting to note that the coalescence parameter decreases with increasing volume, as expected.
-In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability.
-If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
-\begin{equation}
-\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
-\label{eq:Cdapprox}
-\end{equation}
-%
-and
-%
-\begin{equation}
-\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
-\label{eq:B2approx}
-\end{equation}
-%
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
-As can be seen in Fig.
-\ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.png}
-\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
-\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
-\label{fig:radiusDependence}
-\end{center}
-\end{figure}
-
-Following the approach and discussion presented in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as
-
-\begin{equation}
-\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
-\label{eq:CA_general}
-\end{equation}
-%
-for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
-Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised in \cite{Scheibl:1998tk} as
-\begin{equation}
-\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1}.
-\label{eq:BA_general}
-\end{equation}
-In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes the Eq. 9 presented in \cite{Blum:2017qnn}:
-\begin{equation}
-\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
-\label{eq:B3}
-\end{equation}
-
-\noindent where
-
- \begin{equation}
-\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1}.
-\label{eq:C3}
-\end{equation}
-
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
-
-\begin{equation}
-	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
-\end{equation}
-
-\noindent This formula can be used to compare the predicted $B_{A}$ with experimental data directly.
-
-\subsection{Source volume}
-\label{SecSourceVolume}
-We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}.
-In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
-The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$.
-We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
-
-Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e.
-different centrality classes \cite{Abelev:2013qoq}.
-In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
-In the following, we make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we therefore do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
-
-\begin{equation}
-R = a \avdNdeta^{1/3} + b
-\label{eq:radiusParameterisation}
-\end{equation}
-
-The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
-The values we obtain by interpolating the geometric mean of the measured radii are consistent with the radii from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radii from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
-The highest $k_{\mathrm{T}}$ bin was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii for such a study, but given that these measurements are not  available in all collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{HbtRadiusParam.png}
-\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-\label{fig:radiiparam}
-\end{center}
-\end{figure}
-
-\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
-
-In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the \pt-differential hadron spectra.
-In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
-When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}.
-The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
-This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
-Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
-Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
-In contrast to the coalescence approach, which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
-Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based.
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
-
-\section{Comparison with experimental data}\label{sec:comparison}
-
-\subsection{Constraining the source volume with data}\label{sec:radiiParamet}
-
-Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
-In Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
-For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions.
-In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
-First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We notice already at this point that the coalescence volume from parameterisation A radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
-
-In a second step the radius is tuned such that the data points for (anti-)deuterons fall onto the coalescence prediction (top right panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
-With this second parameterisation (labeled as "B" in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree,  \bthree.
-As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the latter is the same for all anti- and hyper-nuclei.
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
-
-\begin{figure}[htbp]
-	\begin{center}
-		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-		\label{fig:CompareB2B3forDifferentParamWithData}
-	\end{center}
-\end{figure}
-
-\newpage
- \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and \hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
-For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}.
-The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}.
-
-\begin{figure}[ht]
-	\begin{center}
-		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
-Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
-The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
-		\label{fig:CompareThermalAndCoalescence}
-	\end{center}
-\end{figure}
-
-As a first observation, one sees that for deuterons both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
-For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 2.
-The the limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
-Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor of about 30 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-As a matter of fact, the only datapoint available so far in Pb--Pb collisions is in agreement with the thermal+BW model but not with coalescence.
-The difference between data and the coalescence model is about 6$\sigma$.
-However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
-Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
-In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production.
-This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
-According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
-
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity or centrality in order to distinguish between the two production scenarios.
-In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.
-\ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities.
-This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
-The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions.
-As it can be seen, the latter is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
-
-\section{Summary, conclusions, and outlook}
-
-While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
-In the following, we summarise our main conclusions:
-\begin{enumerate}
-	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on (anti-)deuteron production in central Pb--Pb collisions at the LHC.
-	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume.
-In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
-The very limited amount of data currently available favours the thermal model prediction within our assumptions.
-	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects. 
-\end{enumerate}
-
-We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
-Future studies should be based on more realistic approximations, which requires numerical calculations.
-Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
-
-In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872).
-In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
-Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% acknowledgments
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newenvironment{acknowledgement}{\relax}{\relax}
-\begin{acknowledgement}
-\section*{Acknowledgements}
-We would like to thank Kfir Blum for inspiring this work.
-We thank U.
-Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
-We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
-In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava and the colleagues from the ALICE Collaboration for their valuable input.
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%   APPENDIX                   
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{appendix}
-\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
-The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}.
-It assumes no correlation between different nucleons and no correlation between coordinates in space and momentum.
-In a heavy ion collisions, such correlations are consequence of hydrodynamical flow.
-The coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
-%
-\begin{equation}
-\frac{\gamma_{A}}{\sigma_{A,0}} \frac{d^{3}\sigma_{A}}{d^{3}p} =  \left( {4 \over 3} \pi p_{0}^{3}\right)^{A-1}\frac{1}{Z!
-N!} \left(\frac{\gamma_{p}}{\sigma_{p,0}} \frac{d^{3}\sigma_{p}}{d^{3}p_{p}}\right)^{Z} \left(\frac{\gamma_{n}}{\sigma_{n,0}} \frac{d^{3}\sigma_{n}}{d^{3}p_{n}}\right)^{N}
-\end{equation} 
-%
-where $p_{0}$ corresponds to the coalescence momentum, $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively.
-The reaction cross sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
-Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
-
-\begin{equation}
-B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {M \over m^{A}} {1 \over A^{3}}{\frac{1}{Z! N!}}
-\end{equation}
-
-\noindent where the factor ${1 \over A^{3}}$ results from the transformation of $p_{A} \rightarrow A p_{p,n}$ and $M$ corresponds to the nucleus mass and $m$ to the nucleon mass.
-This expression can be further simplified via the approximation $M \approx A m$ to
-
-\begin{equation}
-B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {1 \over m^{A-1}} {1 \over A^{2}}{\frac{1}{Z! N!}} \; .
-\end{equation}
-
-\noindent For nuclei up to $A = 4$ and the non-relativistic case, Sato and Yazaki derive the following relations for the coalescence momentum $p_{0}$, 
-%
-\begin{align}
-	A& =2&
-	{4 \over 3} \pi p_{0}^{3}& ={3 \over 4}2^{3/2}(4\pi)^{3/2} \left(\frac{\nu_{2}\nu}{\nu_{2} + \nu}\right)^{3/2}\\
-	A& =3&
-	{1 \over 2} \left( {4 \over 3} \pi p_{0}^{3}\right)^{2}& ={1 \over 4} 3^{3/2} (4\pi)^{3} \left(\frac{\nu_{3}\nu}{\nu_{3} + \nu}\right)^{3}\\
-	A& =4&  
-	{1 \over 4} \left({4 \over 3} \pi p_{0}^{3}\right)^{3}& = {1 \over 16} 4^{3/2} (4\pi)^{9/2} \left(\frac{\nu_{4}\nu}{\nu_{4}+ \nu}\right)^{9/2}
-\end{align}
-
-\noindent where the size parameter $\nu$ relates to the rms radius $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$, and $\nu_{A}$ is the size parameter of the nucleus. 
-\\Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
-
-\begin{eqnarray}
-B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} {1 \over m^{A-1}} {1 \over A^{2}}  \\
-\label{eq:SatoGeneralised}
-           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} \;,
-\end{eqnarray}
-
-\noindent indicating with $J_{A}$ the spin of the nucleus.
-Once again, the $\nu_{A}$ parameter corresponds to the size parameter of the nucleus wave-function, which is assumed to be gaussian (solution to the isotropic spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
-
-\begin{equation}\label{eq:SatoWave}
- \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
-\end{equation}
-
-\noindent with an appropriate normalisation factor $C$ and the coordinate vector $\vec{X}$ of the centre-of-mass system.
-
-We have also verified that our generalisation of Sato-Yazaki provided by Eq.
-\ref{eq:SatoGeneralised} and the expression derived from Heinz in Eq.
-\ref{eq:CA_general} become consistent in the limit $R_{rms} \approx R \rightarrow 0$ (point-like source) and $p_{\mathrm{T}} \rightarrow 0$ (static source), provided that one identifies $\nu_{A} = {2 / r_{A}^{2}}$.
-Incidentally, the same relation between $\nu_{A}$ and $r_{A}$ can be derived by a straightforward comparison of the nucleus wave-functions employed by the same authors \cite{Scheibl:1998tk,Sato:1981ez}.
-
-The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius \rmsradius~is reproduced.
-The relation between \rmsradius~and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration (see Appendix \ref{appendix:integration}).
-In particular, one obtains for $A < 5$:
-
-\begin{align}
-	A& = 2 \qquad \qquad \nu_{2} = {3 \over {4\rmsd^2}}  \\
-	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
-	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}} \;\; .
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% A = 4 Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{RMS of a gaussian wave-function for $\mathbf{A=4}$}\label{appendix:integration}
-
-In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of $A=4$. We start from the wave-function
-
-\begin{equation}\label{eq:SatoWave}
- \phi_{A=4} = C_{4} \exp\Bigl(-{1\over2} \nu_{4} \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \Bigr) \; .
-\end{equation}
-
-\noindent Then we introduce the Jacobi variables which are given by 
-\begin{align}
-	\vec{X}    &= {1 \over 4} (\vec{x_1} + \vec{x_2} + \vec{x_3} + \vec{x_4}) \\
-	\vec{r_1} &= \vec{x_2} - \vec{x_1}\\
-	\vec{r_2} &= \vec{x_3} - {1 \over 2}(\vec{x_1} + \vec{x_2})\\
-	\vec{r_3} &= \vec{x_4} - {1 \over 3}(\vec{x_1} + \vec{x_2} + \vec{x_3}) \; .
-\end{align}
-
-\noindent In this parameterisation we can express the squared distance of each nucleon with respect to the centre-of-mass as
-
-\begin{equation}
- \sum_{i=1}^{4} \bigl(\vec{x_i} - \vec{X} \bigr)^2 = {1\over 4} \bigl(2\vec{r_1} + {8\over 3}\vec{r_2} + 3\vec{r_3}\bigr)  \; .
-\end{equation}
-
-\noindent For the following integral calculations we determine the Jacobian as
-
-\begin{align}
-	\mathrm{d}R\mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
-		{\partial R \over \partial x_{2}} & {\partial r_{1} \over \partial x_{2}} & {\partial r_{2} \over \partial x_{2}}& {\partial r_{3} \over \partial x_{2}} \\ 
-		{\partial R \over \partial x_{3}} & {\partial r_{1} \over \partial x_{3}} & {\partial r_{2} \over \partial x_{3}}& {\partial r_{3} \over \partial x_{3}} \\ 
-		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
-		\mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 0 & 1 & -{1\over 3}  \\
-			{1\over 4} & 0 & 0 & 1
-			 \end{vmatrix} \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= 1 \cdot \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \; .
-\end{align}
-
-\noindent From the requirement $\int|\phi|^2\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:
-
-\begin{align}
-	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}
-\end{align}
-
-\noindent where the integration in spherical coordinates is performed with $\mathrm{d}\vec{r}_{1} = 4\pi r_{1}^{2}\mathrm{d}r_{1},  \mathrm{d}\vec{r}_{2} = \ldots$ which gives
-
-\begin{align}
-	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  \mathrm{d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  \mathrm{d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  \mathrm{d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
-		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
-	\Rightarrow C_{4} &= \Bigl({\nu_{A}^{3} \over 4 \pi^{3}}\Bigr)^{3/4} \;.
-\end{align}
-
-\noindent For the rms, we obtain accordingly:
-
-\begin{align}
-	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
-	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 \mathrm{d}\vec{x}_{1}\mathrm{d}\vec{x}_{2}\mathrm{d}\vec{x}_{3}\mathrm{d}\vec{x}_{4} \\
-	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} \\
-	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{I}} \\
-	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{II}} \\
-	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{III}}
-				 \Bigr)
-\end{align}
-
-\noindent The first summand I can be calculated with $\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 \mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3}$ as
-
-\begin{align}
- \mathrm{I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr)\mathrm{d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \mathrm{d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}r_{3} \\
- 	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
-\end{align}
-
-\noindent The other two summands II and III are evaluated accordingly and we thus obtain for the rms:
-
-\begin{align}
-	\lambda_{4}^{2} &= {C_4^2 \over 4} (\mathrm{I} + \mathrm{II} + \mathrm{III} ) \\
-	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +
-	{{2\over3} \over ({1\over2})^{3/2}({2\over3})^{5/2}({3\over4})^{3/2} } + {{3\over4} \over ({1\over2})^{3/2}({2\over3})^{3/2}({3\over4})^{5/2} } \Bigr)}_{= 24} \\
-	&= {9 \over 8 \nu_A} \;.
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% HBT Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}\label{appendix:YKP}
-
-The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{side}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
-The ALICE HBT results \cite{Aamodt:2011mr, Adam:2015vna} are given in the Bertsch-Pratt convention, whereas the coalescence parameter is derived in \cite{Scheibl:1998tk} by expressing the dependence on the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-The transformation between the two parameterisations is best presented in~\cite{Wiedemann:1999qn} in the equations (W 3.48) to (W 3.52)\footnote{The equations in~\cite{Wiedemann:1999qn} are denoted as (W...) in order to distinguish them from the equations presented in this paper.}:
-
-\begin{eqnarray}
-R_{side}^{2}    &=& R_{\perp}^{2}  \;, \\
-R_{diff}^{2} &=& R_{out}^{2} -  R_{side}^{2} = \beta_{\perp}^2 \gamma^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
-R_{long}^{2}     &=& (1 - \beta_l^2) R_{\parallel}^2 + \gamma^2 (\beta_l - v)^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
-R_{ol}^{2}   &=& \beta_{\perp} (-\beta_l R_{\parallel}^{2} +  \gamma^2 (\beta_l - v)(R_{0}^2 + v^2R_{\parallel}^2)) \,.
-\end{eqnarray}
-%
-We immediately identify that $R_{\perp}^2$ can be identified with $R_{side}^{2}$.
-Following the reasoning and the nomenclature in~\cite{Wiedemann:1999qn} (W 3.52-3.53), the above equations can be inverted and $R_{\parallel}^{2}$ can be expressed as
-%
-\begin{eqnarray}
-R_{\parallel}^{2} &=& B  - v \cdot C \;, \\
-                          &=& R_{long}^2 - 2{\beta_l \over \beta_\perp}  R_{ol}^2 + {\beta_l^2 \over \beta_\perp^2} R_{diff}^2 
-                          - v \cdot \Bigl(-{1 \over \beta_\perp } R_{ol}^2 + {\beta_l \over \beta_\perp^2} R_{diff}^2  \Bigr) \; .
-\end{eqnarray}
-%
-As it turns out all corrections which are subtracted from $R_{long}^{2}$ can be neglected.
-First, we notice that the cross term $R_{ol}$ vanishes if the measured fireball is longitudinally boost-invariant, which is a valid approximation for the rapidity ranges studied here.
-The remaining terms are all proportional to $\beta_l$.
-By definition of the rest frame for a longitudinally-boosted invariant system, $\beta_l = 0$.
-In summary, we can consider $R_{\perp} = R_{side}$ and $R_{\parallel}=R_{long}$ for the present study.
-
-\end{appendix}
-
-\bibliographystyle{utphys} 	
-\bibliography{NucleiB2}
-
-\end{document}

### 2018-09-20 FrascatiPlot/Paper/aps/appendixA.tex
First version of the paper into aps paper format - sub-files created, table modified - everything else is the same as for the arXiv version

--- 2018-08-21 FrascatiPlot/Paper/NucleiB2.tex
@@
-\RequirePackage{ifpdf}
-\documentclass[a4paper,11pt]{scrartcl} 
-\usepackage[margin=2.5cm]{geometry}
-\usepackage{multirow}
-\usepackage{tabularx} 
-\usepackage{rotating,graphicx} 
-\usepackage{appendix} 
-\usepackage{makecell}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{cite}
-%\ifpdf
-%  \usepackage[pdftex]{graphicx}
-%\else
-%  \usepackage[dvips]{graphicx}
-%\fi
-%\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{amsmath}
-\usepackage[amssymb]{SIunits}
-\usepackage{hyperref}
-
-\usepackage{lineno}
-\linenumbers
-
-\usepackage{xcolor}
-
-\input{./commands.tex}
-
-\begin{document}
-\begin{center}
-
-{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies}}
-
-\medskip
-
-F. Bellini and A. Kalweit \footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch}
-\\CERN, EP Department, Geneva (Switzerland)
-
-\medskip
-
-16$^{th}$ July 2018
-\end{center}
-
-\bigskip
-
-\begin{abstract}
-(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC).
-Their production is typically discussed within the framework of coalescence and thermal-statistical production models.
-While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
-Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
-The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
-Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
-\end{abstract}
-
-\newpage
-
-\section{Introduction} 
-The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
-In addition, these studies might shed light on the internal structure of the formed objects themselves.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e.
-the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
-The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
-As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
-Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei.
-This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
-Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
-
-Since about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
-Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}.
-Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
-Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
-Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically.
-At LHC energies, this is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
-In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects.
-For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
-As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
-Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
-While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
-
-\begin{table}[htb]
-
-\centering
-\begin{tabularx}{\textwidth}{cccccccc}
-\hline \hline \\[-2ex]
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
-\\[1ex]  \hline \\[-2ex]
-      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
-\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
-                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
-\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
-                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
-\end{tabularx}
-\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$.
-$B_{E}$ is the binding energy in MeV.
-The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius.
-The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced.
-Details are given in Appendix \ref{appendix:Sato}.
-Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
-Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
- References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
-\label{tab:nucleusradii}
-\end{table}
-
-To this purpose, we compare to models the existing data from the LHC.
-For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
-In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.
-The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}.
-In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach.
-The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
-We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches.
-
-A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
-We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
-As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
-Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments.
-In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
-
-\section{Coalescence approach} 
-\label{sec:coalescence}
-
-\subsection{Simple coalescence}
-In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}.
-For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$, which is defined as
-
-\begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
-   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
-,    
-\label{eq:BA}
-\end{equation}
-
-\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
-Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
-\begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
-\label{eq:BA}
-\end{equation}
-%
-Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
-As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
-In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
-In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision.
-If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
-In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
-
-\subsection{Advanced coalescence}
-\label{subsec:FullCoalescence}
-
-In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
-While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
-The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions.
-They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
-The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
-For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
-
-\begin{equation}\label{eq:WaveHeinz}
- \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
-\end{equation}
-
-\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
-
-\begin{equation}
- \rmsradius^2 = {3 \over 2}{A - 1 \over A} {r_{A}^2 \over 2}
-\end{equation}
-
-\noindent for point-like constituents.
-In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-
-This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
-The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g.
-the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
-We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions.
-Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
-the centrality dependence) and that of the (hyper-)nucleus.
-In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.
-
-The quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
-In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
-
-\begin{equation}
-\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
-\label{eq:Cd}
-\end{equation}
-%
-where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
-The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
-%
-\begin{equation}
-\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
-\label{eq:B2cd}
-\end{equation}
-%
-which is the main result of \cite{Scheibl:1998tk}.
-It is interesting to note that the coalescence parameter decreases with increasing volume, as expected.
-In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability.
-If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
-\begin{equation}
-\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
-\label{eq:Cdapprox}
-\end{equation}
-%
-and
-%
-\begin{equation}
-\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
-\label{eq:B2approx}
-\end{equation}
-%
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
-As can be seen in Fig.
-\ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.png}
-\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
-\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
-\label{fig:radiusDependence}
-\end{center}
-\end{figure}
-
-Following the approach and discussion presented in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as
-
-\begin{equation}
-\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
-\label{eq:CA_general}
-\end{equation}
-%
-for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
-Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised in \cite{Scheibl:1998tk} as
-\begin{equation}
-\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1}.
-\label{eq:BA_general}
-\end{equation}
-In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes the Eq. 9 presented in \cite{Blum:2017qnn}:
-\begin{equation}
-\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
-\label{eq:B3}
-\end{equation}
-
-\noindent where
-
- \begin{equation}
-\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1}.
-\label{eq:C3}
-\end{equation}
-
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
-
-\begin{equation}
-	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
-\end{equation}
-
-\noindent This formula can be used to compare the predicted $B_{A}$ with experimental data directly.
-
-\subsection{Source volume}
-\label{SecSourceVolume}
-We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}.
-In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
-The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$.
-We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
-
-Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e.
-different centrality classes \cite{Abelev:2013qoq}.
-In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
-In the following, we make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we therefore do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
-
-\begin{equation}
-R = a \avdNdeta^{1/3} + b
-\label{eq:radiusParameterisation}
-\end{equation}
-
-The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
-The values we obtain by interpolating the geometric mean of the measured radii are consistent with the radii from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radii from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
-The highest $k_{\mathrm{T}}$ bin was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii for such a study, but given that these measurements are not  available in all collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{HbtRadiusParam.png}
-\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-\label{fig:radiiparam}
-\end{center}
-\end{figure}
-
-\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
-
-In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the \pt-differential hadron spectra.
-In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
-When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}.
-The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
-This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
-Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
-Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
-In contrast to the coalescence approach, which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
-Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based.
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
-
-\section{Comparison with experimental data}\label{sec:comparison}
-
-\subsection{Constraining the source volume with data}\label{sec:radiiParamet}
-
-Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
-In Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
-For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions.
-In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
-First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We notice already at this point that the coalescence volume from parameterisation A radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
-
-In a second step the radius is tuned such that the data points for (anti-)deuterons fall onto the coalescence prediction (top right panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
-With this second parameterisation (labeled as "B" in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree,  \bthree.
-As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the latter is the same for all anti- and hyper-nuclei.
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
-
-\begin{figure}[htbp]
-	\begin{center}
-		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-		\label{fig:CompareB2B3forDifferentParamWithData}
-	\end{center}
-\end{figure}
-
-\newpage
- \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and \hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
-For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}.
-The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}.
-
-\begin{figure}[ht]
-	\begin{center}
-		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
-Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
-The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
-		\label{fig:CompareThermalAndCoalescence}
-	\end{center}
-\end{figure}
-
-As a first observation, one sees that for deuterons both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
-For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 2.
-The the limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
-Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor of about 30 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-As a matter of fact, the only datapoint available so far in Pb--Pb collisions is in agreement with the thermal+BW model but not with coalescence.
-The difference between data and the coalescence model is about 6$\sigma$.
-However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
-Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
-In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production.
-This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
-According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
-
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity or centrality in order to distinguish between the two production scenarios.
-In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.
-\ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities.
-This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
-The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions.
-As it can be seen, the latter is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
-
-\section{Summary, conclusions, and outlook}
-
-While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
-In the following, we summarise our main conclusions:
-\begin{enumerate}
-	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on (anti-)deuteron production in central Pb--Pb collisions at the LHC.
-	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume.
-In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
-The very limited amount of data currently available favours the thermal model prediction within our assumptions.
-	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects. 
-\end{enumerate}
-
-We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
-Future studies should be based on more realistic approximations, which requires numerical calculations.
-Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
-
-In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872).
-In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
-Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% acknowledgments
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newenvironment{acknowledgement}{\relax}{\relax}
-\begin{acknowledgement}
-\section*{Acknowledgements}
-We would like to thank Kfir Blum for inspiring this work.
-We thank U.
-Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
-We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
-In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava and the colleagues from the ALICE Collaboration for their valuable input.
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%   APPENDIX                   
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{appendix}
-\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
+\label{appendix:Sato}
 The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}.
@@
 where $p_{0}$ corresponds to the coalescence momentum, $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively.
-The reaction cross sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
+The reaction cross-sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
 Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
@@
 \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% A = 4 Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{RMS of a gaussian wave-function for $\mathbf{A=4}$}\label{appendix:integration}
-
-In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of $A=4$. We start from the wave-function
-
-\begin{equation}\label{eq:SatoWave}
- \phi_{A=4} = C_{4} \exp\Bigl(-{1\over2} \nu_{4} \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \Bigr) \; .
-\end{equation}
-
-\noindent Then we introduce the Jacobi variables which are given by 
-\begin{align}
-	\vec{X}    &= {1 \over 4} (\vec{x_1} + \vec{x_2} + \vec{x_3} + \vec{x_4}) \\
-	\vec{r_1} &= \vec{x_2} - \vec{x_1}\\
-	\vec{r_2} &= \vec{x_3} - {1 \over 2}(\vec{x_1} + \vec{x_2})\\
-	\vec{r_3} &= \vec{x_4} - {1 \over 3}(\vec{x_1} + \vec{x_2} + \vec{x_3}) \; .
-\end{align}
-
-\noindent In this parameterisation we can express the squared distance of each nucleon with respect to the centre-of-mass as
-
-\begin{equation}
- \sum_{i=1}^{4} \bigl(\vec{x_i} - \vec{X} \bigr)^2 = {1\over 4} \bigl(2\vec{r_1} + {8\over 3}\vec{r_2} + 3\vec{r_3}\bigr)  \; .
-\end{equation}
-
-\noindent For the following integral calculations we determine the Jacobian as
-
-\begin{align}
-	\mathrm{d}R\mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
-		{\partial R \over \partial x_{2}} & {\partial r_{1} \over \partial x_{2}} & {\partial r_{2} \over \partial x_{2}}& {\partial r_{3} \over \partial x_{2}} \\ 
-		{\partial R \over \partial x_{3}} & {\partial r_{1} \over \partial x_{3}} & {\partial r_{2} \over \partial x_{3}}& {\partial r_{3} \over \partial x_{3}} \\ 
-		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
-		\mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 0 & 1 & -{1\over 3}  \\
-			{1\over 4} & 0 & 0 & 1
-			 \end{vmatrix} \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= 1 \cdot \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \; .
-\end{align}
-
-\noindent From the requirement $\int|\phi|^2\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:
-
-\begin{align}
-	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}
-\end{align}
-
-\noindent where the integration in spherical coordinates is performed with $\mathrm{d}\vec{r}_{1} = 4\pi r_{1}^{2}\mathrm{d}r_{1},  \mathrm{d}\vec{r}_{2} = \ldots$ which gives
-
-\begin{align}
-	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  \mathrm{d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  \mathrm{d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  \mathrm{d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
-		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
-	\Rightarrow C_{4} &= \Bigl({\nu_{A}^{3} \over 4 \pi^{3}}\Bigr)^{3/4} \;.
-\end{align}
-
-\noindent For the rms, we obtain accordingly:
-
-\begin{align}
-	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
-	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 \mathrm{d}\vec{x}_{1}\mathrm{d}\vec{x}_{2}\mathrm{d}\vec{x}_{3}\mathrm{d}\vec{x}_{4} \\
-	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} \\
-	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{I}} \\
-	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{II}} \\
-	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{III}}
-				 \Bigr)
-\end{align}
-
-\noindent The first summand I can be calculated with $\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 \mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3}$ as
-
-\begin{align}
- \mathrm{I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr)\mathrm{d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \mathrm{d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}r_{3} \\
- 	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
-\end{align}
-
-\noindent The other two summands II and III are evaluated accordingly and we thus obtain for the rms:
-
-\begin{align}
-	\lambda_{4}^{2} &= {C_4^2 \over 4} (\mathrm{I} + \mathrm{II} + \mathrm{III} ) \\
-	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +
-	{{2\over3} \over ({1\over2})^{3/2}({2\over3})^{5/2}({3\over4})^{3/2} } + {{3\over4} \over ({1\over2})^{3/2}({2\over3})^{3/2}({3\over4})^{5/2} } \Bigr)}_{= 24} \\
-	&= {9 \over 8 \nu_A} \;.
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% HBT Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}\label{appendix:YKP}
-
-The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{side}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
-The ALICE HBT results \cite{Aamodt:2011mr, Adam:2015vna} are given in the Bertsch-Pratt convention, whereas the coalescence parameter is derived in \cite{Scheibl:1998tk} by expressing the dependence on the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-The transformation between the two parameterisations is best presented in~\cite{Wiedemann:1999qn} in the equations (W 3.48) to (W 3.52)\footnote{The equations in~\cite{Wiedemann:1999qn} are denoted as (W...) in order to distinguish them from the equations presented in this paper.}:
-
-\begin{eqnarray}
-R_{side}^{2}    &=& R_{\perp}^{2}  \;, \\
-R_{diff}^{2} &=& R_{out}^{2} -  R_{side}^{2} = \beta_{\perp}^2 \gamma^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
-R_{long}^{2}     &=& (1 - \beta_l^2) R_{\parallel}^2 + \gamma^2 (\beta_l - v)^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
-R_{ol}^{2}   &=& \beta_{\perp} (-\beta_l R_{\parallel}^{2} +  \gamma^2 (\beta_l - v)(R_{0}^2 + v^2R_{\parallel}^2)) \,.
-\end{eqnarray}
-%
-We immediately identify that $R_{\perp}^2$ can be identified with $R_{side}^{2}$.
-Following the reasoning and the nomenclature in~\cite{Wiedemann:1999qn} (W 3.52-3.53), the above equations can be inverted and $R_{\parallel}^{2}$ can be expressed as
-%
-\begin{eqnarray}
-R_{\parallel}^{2} &=& B  - v \cdot C \;, \\
-                          &=& R_{long}^2 - 2{\beta_l \over \beta_\perp}  R_{ol}^2 + {\beta_l^2 \over \beta_\perp^2} R_{diff}^2 
-                          - v \cdot \Bigl(-{1 \over \beta_\perp } R_{ol}^2 + {\beta_l \over \beta_\perp^2} R_{diff}^2  \Bigr) \; .
-\end{eqnarray}
-%
-As it turns out all corrections which are subtracted from $R_{long}^{2}$ can be neglected.
-First, we notice that the cross term $R_{ol}$ vanishes if the measured fireball is longitudinally boost-invariant, which is a valid approximation for the rapidity ranges studied here.
-The remaining terms are all proportional to $\beta_l$.
-By definition of the rest frame for a longitudinally-boosted invariant system, $\beta_l = 0$.
-In summary, we can consider $R_{\perp} = R_{side}$ and $R_{\parallel}=R_{long}$ for the present study.
-
-\end{appendix}
-
-\bibliographystyle{utphys} 	
-\bibliography{NucleiB2}
-
-\end{document}

### 2018-09-20 FrascatiPlot/Paper/aps/appendixC.tex
First version of the paper into aps paper format - sub-files created, table modified - everything else is the same as for the arXiv version

--- 2018-08-21 FrascatiPlot/Paper/NucleiB2.tex
@@
-\RequirePackage{ifpdf}
-\documentclass[a4paper,11pt]{scrartcl} 
-\usepackage[margin=2.5cm]{geometry}
-\usepackage{multirow}
-\usepackage{tabularx} 
-\usepackage{rotating,graphicx} 
-\usepackage{appendix} 
-\usepackage{makecell}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{cite}
-%\ifpdf
-%  \usepackage[pdftex]{graphicx}
-%\else
-%  \usepackage[dvips]{graphicx}
-%\fi
-%\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{amsmath}
-\usepackage[amssymb]{SIunits}
-\usepackage{hyperref}
-
-\usepackage{lineno}
-\linenumbers
-
-\usepackage{xcolor}
-
-\input{./commands.tex}
-
-\begin{document}
-\begin{center}
-
-{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies}}
-
-\medskip
-
-F. Bellini and A. Kalweit \footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch}
-\\CERN, EP Department, Geneva (Switzerland)
-
-\medskip
-
-16$^{th}$ July 2018
-\end{center}
-
-\bigskip
-
-\begin{abstract}
-(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC).
-Their production is typically discussed within the framework of coalescence and thermal-statistical production models.
-While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
-Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
-The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
-Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
-\end{abstract}
-
-\newpage
-
-\section{Introduction} 
-The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
-In addition, these studies might shed light on the internal structure of the formed objects themselves.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e.
-the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
-The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
-As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
-Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei.
-This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
-Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
-
-Since about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
-Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}.
-Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
-Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
-Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically.
-At LHC energies, this is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
-In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects.
-For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
-As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
-Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
-While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
-
-\begin{table}[htb]
-
-\centering
-\begin{tabularx}{\textwidth}{cccccccc}
-\hline \hline \\[-2ex]
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
-\\[1ex]  \hline \\[-2ex]
-      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
-\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
-                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
-\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
-                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
-\end{tabularx}
-\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$.
-$B_{E}$ is the binding energy in MeV.
-The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius.
-The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced.
-Details are given in Appendix \ref{appendix:Sato}.
-Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
-Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
- References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
-\label{tab:nucleusradii}
-\end{table}
-
-To this purpose, we compare to models the existing data from the LHC.
-For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
-In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.
-The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}.
-In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach.
-The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
-We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches.
-
-A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
-We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
-As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
-Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments.
-In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
-
-\section{Coalescence approach} 
-\label{sec:coalescence}
-
-\subsection{Simple coalescence}
-In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}.
-For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$, which is defined as
-
-\begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
-   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
-,    
-\label{eq:BA}
-\end{equation}
-
-\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
-Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
-\begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
-\label{eq:BA}
-\end{equation}
-%
-Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
-As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
-In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
-In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision.
-If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
-In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
-
-\subsection{Advanced coalescence}
-\label{subsec:FullCoalescence}
-
-In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
-While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
-The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions.
-They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
-The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
-For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
-
-\begin{equation}\label{eq:WaveHeinz}
- \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
-\end{equation}
-
-\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
-
-\begin{equation}
- \rmsradius^2 = {3 \over 2}{A - 1 \over A} {r_{A}^2 \over 2}
-\end{equation}
-
-\noindent for point-like constituents.
-In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-
-This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
-The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g.
-the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
-We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions.
-Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
-the centrality dependence) and that of the (hyper-)nucleus.
-In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.
-
-The quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
-In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
-
-\begin{equation}
-\langle C_{d} \rangle \approx \frac{1}{\left[1+ \left(\frac{\dradius}{2R_{\perp}(m_{T})}\right)^{2}\right] \sqrt{1+ \left(\frac{\dradius}{2R_{\|}(m_{T})}\right)^{2}}}
-\label{eq:Cd}
-\end{equation}
-%
-where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
-The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
-%
-\begin{equation}
-\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
-\label{eq:B2cd}
-\end{equation}
-%
-which is the main result of \cite{Scheibl:1998tk}.
-It is interesting to note that the coalescence parameter decreases with increasing volume, as expected.
-In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability.
-If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
-\begin{equation}
-\langle C_{d} \rangle \approx \left[1+ \left(\frac{\dradius}{2R(m_{T})}\right)^{2}\right]^{-3/2}
-\label{eq:Cdapprox}
-\end{equation}
-%
-and
-%
-\begin{equation}
-\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}R^{3}(m_{T})}.
-\label{eq:B2approx}
-\end{equation}
-%
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
-As can be seen in Fig.
-\ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.0\textwidth]{theory_coalescence_Cd_B2.png}
-\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
-\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.}}
-\label{fig:radiusDependence}
-\end{center}
-\end{figure}
-
-Following the approach and discussion presented in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as
-
-\begin{equation}
-\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
-\label{eq:CA_general}
-\end{equation}
-%
-for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
-Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised in \cite{Scheibl:1998tk} as
-\begin{equation}
-\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1}.
-\label{eq:BA_general}
-\end{equation}
-In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes the Eq. 9 presented in \cite{Blum:2017qnn}:
-\begin{equation}
-\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
-\label{eq:B3}
-\end{equation}
-
-\noindent where
-
- \begin{equation}
-\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1}.
-\label{eq:C3}
-\end{equation}
-
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
-
-\begin{equation}
-	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
-\end{equation}
-
-\noindent This formula can be used to compare the predicted $B_{A}$ with experimental data directly.
-
-\subsection{Source volume}
-\label{SecSourceVolume}
-We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}.
-In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
-The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$.
-We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
-
-Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e.
-different centrality classes \cite{Abelev:2013qoq}.
-In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
-In the following, we make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we therefore do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
-
-\begin{equation}
-R = a \avdNdeta^{1/3} + b
-\label{eq:radiusParameterisation}
-\end{equation}
-
-The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
-The values we obtain by interpolating the geometric mean of the measured radii are consistent with the radii from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radii from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
-The highest $k_{\mathrm{T}}$ bin was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii for such a study, but given that these measurements are not  available in all collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{HbtRadiusParam.png}
-\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-\label{fig:radiiparam}
-\end{center}
-\end{figure}
-
-\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
-
-In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the current implementations~\cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} of the statistical-thermal model provide only \pt-integrated yields and not the \pt-differential hadron spectra.
-In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
-When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}.
-The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
-This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
-Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
-Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
-In contrast to the coalescence approach, which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
-Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based.
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
-
-\section{Comparison with experimental data}\label{sec:comparison}
-
-\subsection{Constraining the source volume with data}\label{sec:radiiParamet}
-
-Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
-In Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
-For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions.
-In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
-First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We notice already at this point that the coalescence volume from parameterisation A radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
-
-In a second step the radius is tuned such that the data points for (anti-)deuterons fall onto the coalescence prediction (top right panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
-With this second parameterisation (labeled as "B" in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree,  \bthree.
-As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the latter is the same for all anti- and hyper-nuclei.
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
-
-\begin{figure}[htbp]
-	\begin{center}
-		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-		\label{fig:CompareB2B3forDifferentParamWithData}
-	\end{center}
-\end{figure}
-
-\newpage
- \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and \hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
-For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}.
-The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}.
-
-\begin{figure}[ht]
-	\begin{center}
-		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
-Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
-The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
-		\label{fig:CompareThermalAndCoalescence}
-	\end{center}
-\end{figure}
-
-As a first observation, one sees that for deuterons both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
-For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 2.
-The the limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
-Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor of about 30 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-As a matter of fact, the only datapoint available so far in Pb--Pb collisions is in agreement with the thermal+BW model but not with coalescence.
-The difference between data and the coalescence model is about 6$\sigma$.
-However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
-Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
-In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production.
-This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
-According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
-
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity or centrality in order to distinguish between the two production scenarios.
-In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.
-\ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities.
-This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
-The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions.
-As it can be seen, the latter is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
-
-\section{Summary, conclusions, and outlook}
-
-While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
-In the following, we summarise our main conclusions:
-\begin{enumerate}
-	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on (anti-)deuteron production in central Pb--Pb collisions at the LHC.
-	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume.
-In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
-The very limited amount of data currently available favours the thermal model prediction within our assumptions.
-	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects. 
-\end{enumerate}
-
-We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
-Future studies should be based on more realistic approximations, which requires numerical calculations.
-Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
-
-In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872).
-In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
-Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% acknowledgments
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newenvironment{acknowledgement}{\relax}{\relax}
-\begin{acknowledgement}
-\section*{Acknowledgements}
-We would like to thank Kfir Blum for inspiring this work.
-We thank U.
-Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
-We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
-In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava and the colleagues from the ALICE Collaboration for their valuable input.
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%   APPENDIX                   
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{appendix}
-\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
-The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}.
-It assumes no correlation between different nucleons and no correlation between coordinates in space and momentum.
-In a heavy ion collisions, such correlations are consequence of hydrodynamical flow.
-The coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
-%
-\begin{equation}
-\frac{\gamma_{A}}{\sigma_{A,0}} \frac{d^{3}\sigma_{A}}{d^{3}p} =  \left( {4 \over 3} \pi p_{0}^{3}\right)^{A-1}\frac{1}{Z!
-N!} \left(\frac{\gamma_{p}}{\sigma_{p,0}} \frac{d^{3}\sigma_{p}}{d^{3}p_{p}}\right)^{Z} \left(\frac{\gamma_{n}}{\sigma_{n,0}} \frac{d^{3}\sigma_{n}}{d^{3}p_{n}}\right)^{N}
-\end{equation} 
-%
-where $p_{0}$ corresponds to the coalescence momentum, $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively.
-The reaction cross sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
-Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
-
-\begin{equation}
-B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {M \over m^{A}} {1 \over A^{3}}{\frac{1}{Z! N!}}
-\end{equation}
-
-\noindent where the factor ${1 \over A^{3}}$ results from the transformation of $p_{A} \rightarrow A p_{p,n}$ and $M$ corresponds to the nucleus mass and $m$ to the nucleon mass.
-This expression can be further simplified via the approximation $M \approx A m$ to
-
-\begin{equation}
-B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {1 \over m^{A-1}} {1 \over A^{2}}{\frac{1}{Z! N!}} \; .
-\end{equation}
-
-\noindent For nuclei up to $A = 4$ and the non-relativistic case, Sato and Yazaki derive the following relations for the coalescence momentum $p_{0}$, 
-%
-\begin{align}
-	A& =2&
-	{4 \over 3} \pi p_{0}^{3}& ={3 \over 4}2^{3/2}(4\pi)^{3/2} \left(\frac{\nu_{2}\nu}{\nu_{2} + \nu}\right)^{3/2}\\
-	A& =3&
-	{1 \over 2} \left( {4 \over 3} \pi p_{0}^{3}\right)^{2}& ={1 \over 4} 3^{3/2} (4\pi)^{3} \left(\frac{\nu_{3}\nu}{\nu_{3} + \nu}\right)^{3}\\
-	A& =4&  
-	{1 \over 4} \left({4 \over 3} \pi p_{0}^{3}\right)^{3}& = {1 \over 16} 4^{3/2} (4\pi)^{9/2} \left(\frac{\nu_{4}\nu}{\nu_{4}+ \nu}\right)^{9/2}
-\end{align}
-
-\noindent where the size parameter $\nu$ relates to the rms radius $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$, and $\nu_{A}$ is the size parameter of the nucleus. 
-\\Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
-
-\begin{eqnarray}
-B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} {1 \over m^{A-1}} {1 \over A^{2}}  \\
-\label{eq:SatoGeneralised}
-           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} \;,
-\end{eqnarray}
-
-\noindent indicating with $J_{A}$ the spin of the nucleus.
-Once again, the $\nu_{A}$ parameter corresponds to the size parameter of the nucleus wave-function, which is assumed to be gaussian (solution to the isotropic spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
-
-\begin{equation}\label{eq:SatoWave}
- \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
-\end{equation}
-
-\noindent with an appropriate normalisation factor $C$ and the coordinate vector $\vec{X}$ of the centre-of-mass system.
-
-We have also verified that our generalisation of Sato-Yazaki provided by Eq.
-\ref{eq:SatoGeneralised} and the expression derived from Heinz in Eq.
-\ref{eq:CA_general} become consistent in the limit $R_{rms} \approx R \rightarrow 0$ (point-like source) and $p_{\mathrm{T}} \rightarrow 0$ (static source), provided that one identifies $\nu_{A} = {2 / r_{A}^{2}}$.
-Incidentally, the same relation between $\nu_{A}$ and $r_{A}$ can be derived by a straightforward comparison of the nucleus wave-functions employed by the same authors \cite{Scheibl:1998tk,Sato:1981ez}.
-
-The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius \rmsradius~is reproduced.
-The relation between \rmsradius~and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration (see Appendix \ref{appendix:integration}).
-In particular, one obtains for $A < 5$:
-
-\begin{align}
-	A& = 2 \qquad \qquad \nu_{2} = {3 \over {4\rmsd^2}}  \\
-	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
-	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}} \;\; .
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% A = 4 Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{RMS of a gaussian wave-function for $\mathbf{A=4}$}\label{appendix:integration}
-
-In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of $A=4$. We start from the wave-function
-
-\begin{equation}\label{eq:SatoWave}
- \phi_{A=4} = C_{4} \exp\Bigl(-{1\over2} \nu_{4} \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \Bigr) \; .
-\end{equation}
-
-\noindent Then we introduce the Jacobi variables which are given by 
-\begin{align}
-	\vec{X}    &= {1 \over 4} (\vec{x_1} + \vec{x_2} + \vec{x_3} + \vec{x_4}) \\
-	\vec{r_1} &= \vec{x_2} - \vec{x_1}\\
-	\vec{r_2} &= \vec{x_3} - {1 \over 2}(\vec{x_1} + \vec{x_2})\\
-	\vec{r_3} &= \vec{x_4} - {1 \over 3}(\vec{x_1} + \vec{x_2} + \vec{x_3}) \; .
-\end{align}
-
-\noindent In this parameterisation we can express the squared distance of each nucleon with respect to the centre-of-mass as
-
-\begin{equation}
- \sum_{i=1}^{4} \bigl(\vec{x_i} - \vec{X} \bigr)^2 = {1\over 4} \bigl(2\vec{r_1} + {8\over 3}\vec{r_2} + 3\vec{r_3}\bigr)  \; .
-\end{equation}
-
-\noindent For the following integral calculations we determine the Jacobian as
-
-\begin{align}
-	\mathrm{d}R\mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
-		{\partial R \over \partial x_{2}} & {\partial r_{1} \over \partial x_{2}} & {\partial r_{2} \over \partial x_{2}}& {\partial r_{3} \over \partial x_{2}} \\ 
-		{\partial R \over \partial x_{3}} & {\partial r_{1} \over \partial x_{3}} & {\partial r_{2} \over \partial x_{3}}& {\partial r_{3} \over \partial x_{3}} \\ 
-		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
-		\mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 0 & 1 & -{1\over 3}  \\
-			{1\over 4} & 0 & 0 & 1
-			 \end{vmatrix} \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= 1 \cdot \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \; .
-\end{align}
-
-\noindent From the requirement $\int|\phi|^2\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:
-
-\begin{align}
-	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}
-\end{align}
-
-\noindent where the integration in spherical coordinates is performed with $\mathrm{d}\vec{r}_{1} = 4\pi r_{1}^{2}\mathrm{d}r_{1},  \mathrm{d}\vec{r}_{2} = \ldots$ which gives
-
-\begin{align}
-	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  \mathrm{d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  \mathrm{d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  \mathrm{d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
-		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
-	\Rightarrow C_{4} &= \Bigl({\nu_{A}^{3} \over 4 \pi^{3}}\Bigr)^{3/4} \;.
-\end{align}
-
-\noindent For the rms, we obtain accordingly:
-
-\begin{align}
-	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
-	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 \mathrm{d}\vec{x}_{1}\mathrm{d}\vec{x}_{2}\mathrm{d}\vec{x}_{3}\mathrm{d}\vec{x}_{4} \\
-	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} \\
-	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{I}} \\
-	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{II}} \\
-	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{III}}
-				 \Bigr)
-\end{align}
-
-\noindent The first summand I can be calculated with $\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 \mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3}$ as
-
-\begin{align}
- \mathrm{I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr)\mathrm{d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \mathrm{d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}r_{3} \\
- 	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
-\end{align}
-
-\noindent The other two summands II and III are evaluated accordingly and we thus obtain for the rms:
-
-\begin{align}
-	\lambda_{4}^{2} &= {C_4^2 \over 4} (\mathrm{I} + \mathrm{II} + \mathrm{III} ) \\
-	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +
-	{{2\over3} \over ({1\over2})^{3/2}({2\over3})^{5/2}({3\over4})^{3/2} } + {{3\over4} \over ({1\over2})^{3/2}({2\over3})^{3/2}({3\over4})^{5/2} } \Bigr)}_{= 24} \\
-	&= {9 \over 8 \nu_A} \;.
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% HBT Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}\label{appendix:YKP}
+\label{appendix:YKP}
 
@@
 In summary, we can consider $R_{\perp} = R_{side}$ and $R_{\parallel}=R_{long}$ for the present study.
-
-\end{appendix}
-
-\bibliographystyle{utphys} 	
-\bibliography{NucleiB2}
-
-\end{document}

### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
First version of the paper into aps paper format - sub-files created, table modified - everything else is the same as for the arXiv version

--- 2018-09-05 FrascatiPlot/Paper/NucleiB2.tex
@@
-\RequirePackage{ifpdf}
-\documentclass[a4paper,11pt]{scrartcl} 
-\usepackage[margin=2.5cm]{geometry}
-\usepackage{multirow}
-\usepackage{tabularx} 
-\usepackage{rotating,graphicx} 
-\usepackage{appendix} 
-\usepackage{makecell}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{cite}
-%\ifpdf
-%  \usepackage[pdftex]{graphicx}
-%\else
-%  \usepackage[dvips]{graphicx}
-%\fi
-%\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{amsmath}
-\usepackage[amssymb]{SIunits}
-\usepackage{hyperref}
-
-\usepackage{lineno}
-\linenumbers
-
-\usepackage{xcolor}
-
-\input{./commands.tex}
-
-\begin{document}
-\begin{center}
-
-{\Large \textbf{Testing coalescence and statistical-thermal production scenarios for (anti-)(hyper-)nuclei and exotic QCD objects at LHC energies}}
-
-\medskip
-
-F. Bellini and A. Kalweit \footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch}
-\\CERN, EP Department, Geneva (Switzerland)
-
-\medskip
-
-16$^{th}$ July 2018
-\end{center}
-
-\bigskip
-
-\begin{abstract}
-(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC).
-Their production is typically discussed within the framework of coalescence and thermal-statistical production models.
-While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
-Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
-The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
-Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
-\end{abstract}
-
-\newpage
-
 \section{Introduction} 
@@
 In addition, these studies might shed light on the internal structure of the formed objects themselves.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e.
+In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size (i.e.
 the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
-The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
-As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
+The relevant known properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
+As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave-function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
 Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei.
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$.
 This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
 Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
+
+\input{table1}
 
@@
 Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of the coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
 Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
 While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
-
-\begin{table}[htb]
-
-\centering
-\begin{tabularx}{\textwidth}{cccccccc}
-\hline \hline \\[-2ex]
-\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs.
-\\[1ex]  \hline \\[-2ex]
-      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
-\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
-                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
-\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
-                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
-\end{tabularx}
-\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$.
-$B_{E}$ is the binding energy in MeV.
-The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius.
-The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced.
-Details are given in Appendix \ref{appendix:Sato}.
-Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
-Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
- References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
-\label{tab:nucleusradii}
-\end{table}
 
@@
 The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}.
-In section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach.
-The direct comparison of the two approaches and the comparison with data are discussed in section \ref{sec:comparison}.
+In Section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach.
+The direct comparison of the two approaches and the comparison with data are discussed in Section \ref{sec:comparison}.
 We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches.
@@
 A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with hyper-nuclei proposed here.
+However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with the hyper-nuclei proposed here.
 We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
 As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
-Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss} and future \cite{AMS100, Aramaki:2015laa} experiments.
+Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
 In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
@@
 If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}.
+While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
 In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
@@
 
-This ansatz allows to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wavefunction, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
-The approximation of the wave-function with a gaussian form can be further refined with these more realistic parameterisations, e.g.
+This ansatz allows one to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
+In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wave-function, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
+The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g.
 the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
 We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. 
+The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
 Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
-the centrality dependence) and that of the (hyper-)nucleus.
+the centrality dependence) and to the size of the (hyper-)nucleus.
 In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.
 
-The quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$.
-In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
+The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum-mechanical correction factor, $\langle C_{A} \rangle$.
+In the case of the deuteron, the quantum-mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
 
@@
 where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
-The size of the nucleus enters in the determination of the coalescence parameter \btwo~via the quantum-mechanical correction factor $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
+The size of the nucleus enters in the determination of the coalescence parameter \btwo~via $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
 %
@@
 It is interesting to note that the coalescence parameter decreases with increasing volume, as expected.
-In addition to this, the quantum mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability.
+In addition to this, the quantum-mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability.
 If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
@@
 \begin{center}
-\includegraphics[width=.9\textwidth]{theory_coalescence_Cd_B2.png}
-\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
+\includegraphics[width=1\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
+\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
 \ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
+\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
 The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
@@
 \begin{equation}
-\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1}.
+\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1} \;\;.
 \label{eq:BA_general}
@@
  \begin{equation}
-\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1}.
+\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1} \;\;.
 \label{eq:C3}
@@
 \begin{equation}
-R = a \avdNdeta^{1/3} + b
+R = a \avdNdeta^{1/3} + b \;\;.
 \label{eq:radiusParameterisation}
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{HbtRadiusParam.png}
+\includegraphics[width=1\columnwidth]{../HbtRadiusParam.png}
 \caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
+The radius $R$ and the parameters $a$ and $b$ are in units of fm.
+Parameterisation A is shown here, see text for details.}
 \label{fig:radiiparam}
@@
 As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provide only \pt-integrated yields and not the \pt-differential hadron spectra.
-In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
+In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields and not the \pt-differential hadron spectra.
+In order to fill this gap, and for the purpose of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
 When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}.
 The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
-This choice, as opposed to using ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
+This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
+In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}H / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
 Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
@@
 In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
-First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as "parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
+First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as ``parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
 \ref{fig:CompareB2B3forDifferentParamWithData}).
-We notice already at this point that the coalescence volume from parameterisation A radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
+We notice already at this point that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
 
@@
 We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
-With this second parameterisation (labeled as "B" in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree, \bthree.
+With this second parameterisation (labeled as``B'' in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree, \bthree.
 As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the latter is the same for all anti- and hyper-nuclei.
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
+The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the coalescence volume is the same for all anti- and hyper-nuclei.
+It is also noteworthy that any change of the radii parameterisation would result in a shift along the x-axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
 
-The necessity of introducing a second parameterisation for the radius could point to the fact that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered here, but by a slightly larger system.
+The necessity of introducing a second parameterisation for the radius could point to the fact that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered in parameterisation A, but by a slightly larger system as given by parameterisation B.
 
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 	\begin{center}
-		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
+		\includegraphics[width=\textwidth]{../radiiParamCompareData.png}
 		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
@@
 	\end{center}
-\end{figure}
+\end{figure*}
 
 \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and \hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
 For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}.
@@
 For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2.
-The the limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
+The limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
 Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-As a matter of fact, the only datapoint available so far in Pb--Pb collisions is in agreement with the thermal+BW model but not with coalescence.
+As a matter of fact, the only data point available so far in Pb--Pb collisions is in agreement with the thermal+blast-wave model but not with coalescence.
 The difference between data and the coalescence model is about 6$\sigma$.
@@
 
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 	\begin{center}
-		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
+		\includegraphics[width=\textwidth]{../compareThermalAndCoalescence.png}
+		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
 Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
@@
 	\end{center}
-\end{figure}
+\end{figure*}
 
@@
 	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume.
-In particular, the yield of hyper-tritons appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
-The very limited amount of data currently available favours the thermal model prediction within our assumptions.
+In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
+The very limited amount of currently available data favours the thermal model prediction within our assumptions.
 	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects.
@@
 We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
-As mentioned earlier, future studies should be based on more realistic approximations (in particular the wave function), which requires numerical calculations.
-The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
+As mentioned earlier, future studies should be based on more realistic approximations (in particular the wave-function), which requires numerical calculations.
 Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
@@
 Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% acknowledgments
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newenvironment{acknowledgement}{\relax}{\relax}
-\begin{acknowledgement}
-\section*{Acknowledgements}
-We would like to thank Kfir Blum for inspiring this work.
-We thank U.
-Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
-We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
-In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Maximiliano Puccio, Roman Lietava, Natasha Sharma and the colleagues from the ALICE Collaboration for their valuable input.
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%   APPENDIX                   
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{appendix}
-\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
-The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}.
-It assumes no correlation between different nucleons and no correlation between coordinates in space and momentum.
-In a heavy ion collisions, such correlations are consequence of hydrodynamical flow.
-The coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
-%
-\begin{equation}
-\frac{\gamma_{A}}{\sigma_{A,0}} \frac{d^{3}\sigma_{A}}{d^{3}p} =  \left( {4 \over 3} \pi p_{0}^{3}\right)^{A-1}\frac{1}{Z!
-N!} \left(\frac{\gamma_{p}}{\sigma_{p,0}} \frac{d^{3}\sigma_{p}}{d^{3}p_{p}}\right)^{Z} \left(\frac{\gamma_{n}}{\sigma_{n,0}} \frac{d^{3}\sigma_{n}}{d^{3}p_{n}}\right)^{N}
-\end{equation} 
-%
-where $p_{0}$ corresponds to the coalescence momentum, $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively.
-The reaction cross sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
-Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as
-
-\begin{equation}
-B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {M \over m^{A}} {1 \over A^{3}}{\frac{1}{Z! N!}}
-\end{equation}
-
-\noindent where the factor ${1 \over A^{3}}$ results from the transformation of $p_{A} \rightarrow A p_{p,n}$ and $M$ corresponds to the nucleus mass and $m$ to the nucleon mass.
-This expression can be further simplified via the approximation $M \approx A m$ to
-
-\begin{equation}
-B_{A} = \left({4 \over 3} \pi p_{0}^{3}\right)^{A-1} {1 \over m^{A-1}} {1 \over A^{2}}{\frac{1}{Z! N!}} \; .
-\end{equation}
-
-\noindent For nuclei up to $A = 4$ and the non-relativistic case, Sato and Yazaki derive the following relations for the coalescence momentum $p_{0}$, 
-%
-\begin{align}
-	A& =2&
-	{4 \over 3} \pi p_{0}^{3}& ={3 \over 4}2^{3/2}(4\pi)^{3/2} \left(\frac{\nu_{2}\nu}{\nu_{2} + \nu}\right)^{3/2}\\
-	A& =3&
-	{1 \over 2} \left( {4 \over 3} \pi p_{0}^{3}\right)^{2}& ={1 \over 4} 3^{3/2} (4\pi)^{3} \left(\frac{\nu_{3}\nu}{\nu_{3} + \nu}\right)^{3}\\
-	A& =4&  
-	{1 \over 4} \left({4 \over 3} \pi p_{0}^{3}\right)^{3}& = {1 \over 16} 4^{3/2} (4\pi)^{9/2} \left(\frac{\nu_{4}\nu}{\nu_{4}+ \nu}\right)^{9/2}
-\end{align}
-
-\noindent where the size parameter $\nu$ relates to the rms radius $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$, and $\nu_{A}$ is the size parameter of the nucleus. 
-\\Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter
-
-\begin{eqnarray}
-B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} {1 \over m^{A-1}} {1 \over A^{2}}  \\
-\label{eq:SatoGeneralised}
-           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} \;,
-\end{eqnarray}
-
-\noindent indicating with $J_{A}$ the spin of the nucleus.
-Once again, the $\nu_{A}$ parameter corresponds to the size parameter of the nucleus wave-function, which is assumed to be gaussian (solution to the isotropic spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:
-
-\begin{equation}\label{eq:SatoWave}
- \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
-\end{equation}
-
-\noindent with an appropriate normalisation factor $C$ and the coordinate vector $\vec{X}$ of the centre-of-mass system.
-
-We have also verified that our generalisation of Sato-Yazaki provided by Eq.
-\ref{eq:SatoGeneralised} and the expression derived from Heinz in Eq.
-\ref{eq:CA_general} become consistent in the limit $R_{rms} \approx R \rightarrow 0$ (point-like source) and $p_{\mathrm{T}} \rightarrow 0$ (static source), provided that one identifies $\nu_{A} = {2 / r_{A}^{2}}$.
-Incidentally, the same relation between $\nu_{A}$ and $r_{A}$ can be derived by a straightforward comparison of the nucleus wave-functions employed by the same authors \cite{Scheibl:1998tk,Sato:1981ez}.
-
-The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius \rmsradius~is reproduced.
-The relation between \rmsradius~and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration (see Appendix \ref{appendix:integration}).
-In particular, one obtains for $A < 5$:
-
-\begin{align}
-	A& = 2 \qquad \qquad \nu_{2} = {3 \over {4\rmsd^2}}  \\
-	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
-	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}} \;\; .
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% A = 4 Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{RMS of a gaussian wave-function for $\mathbf{A=4}$}\label{appendix:integration}
-
-In this appendix, we show the calculation of the RMS of a gaussian wave-function with the example of $A=4$. We start from the wave-function
-
-\begin{equation}\label{eq:SatoWave}
- \phi_{A=4} = C_{4} \exp\Bigl(-{1\over2} \nu_{4} \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \Bigr) \; .
-\end{equation}
-
-\noindent Then we introduce the Jacobi variables which are given by 
-\begin{align}
-	\vec{X}    &= {1 \over 4} (\vec{x_1} + \vec{x_2} + \vec{x_3} + \vec{x_4}) \\
-	\vec{r_1} &= \vec{x_2} - \vec{x_1}\\
-	\vec{r_2} &= \vec{x_3} - {1 \over 2}(\vec{x_1} + \vec{x_2})\\
-	\vec{r_3} &= \vec{x_4} - {1 \over 3}(\vec{x_1} + \vec{x_2} + \vec{x_3}) \; .
-\end{align}
-
-\noindent In this parameterisation we can express the squared distance of each nucleon with respect to the centre-of-mass as
-
-\begin{equation}
- \sum_{i=1}^{4} \bigl(\vec{x_i} - \vec{X} \bigr)^2 = {1\over 4} \bigl(2\vec{r_1} + {8\over 3}\vec{r_2} + 3\vec{r_3}\bigr)  \; .
-\end{equation}
-
-\noindent For the following integral calculations we determine the Jacobian as
-
-\begin{align}
-	\mathrm{d}R\mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
-		{\partial R \over \partial x_{2}} & {\partial r_{1} \over \partial x_{2}} & {\partial r_{2} \over \partial x_{2}}& {\partial r_{3} \over \partial x_{2}} \\ 
-		{\partial R \over \partial x_{3}} & {\partial r_{1} \over \partial x_{3}} & {\partial r_{2} \over \partial x_{3}}& {\partial r_{3} \over \partial x_{3}} \\ 
-		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
-		\mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 1 & -{1\over 2} & -{1\over 3}  \\
-			{1\over 4} & 0 & 1 & -{1\over 3}  \\
-			{1\over 4} & 0 & 0 & 1
-			 \end{vmatrix} \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
-		&= 1 \cdot \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \; .
-\end{align}
-
-\noindent From the requirement $\int|\phi|^2\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:
-
-\begin{align}
-	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}
-\end{align}
-
-\noindent where the integration in spherical coordinates is performed with $\mathrm{d}\vec{r}_{1} = 4\pi r_{1}^{2}\mathrm{d}r_{1},  \mathrm{d}\vec{r}_{2} = \ldots$ which gives
-
-\begin{align}
-	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  \mathrm{d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  \mathrm{d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
-							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  \mathrm{d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
-		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
-	\Rightarrow C_{4} &= \Bigl({\nu_{A}^{3} \over 4 \pi^{3}}\Bigr)^{3/4} \;.
-\end{align}
-
-\noindent For the rms, we obtain accordingly:
-
-\begin{align}
-	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
-	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 \mathrm{d}\vec{x}_{1}\mathrm{d}\vec{x}_{2}\mathrm{d}\vec{x}_{3}\mathrm{d}\vec{x}_{4} \\
-	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} \\
-	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{I}} \\
-	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{II}} \\
-	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{III}}
-				 \Bigr)
-\end{align}
-
-\noindent The first summand I can be calculated with $\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 \mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3}$ as
-
-\begin{align}
- \mathrm{I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr)\mathrm{d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \mathrm{d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}r_{3} \\
- 	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
-\end{align}
-
-\noindent The other two summands II and III are evaluated accordingly and we thus obtain for the rms:
-
-\begin{align}
-	\lambda_{4}^{2} &= {C_4^2 \over 4} (\mathrm{I} + \mathrm{II} + \mathrm{III} ) \\
-	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +
-	{{2\over3} \over ({1\over2})^{3/2}({2\over3})^{5/2}({3\over4})^{3/2} } + {{3\over4} \over ({1\over2})^{3/2}({2\over3})^{3/2}({3\over4})^{5/2} } \Bigr)}_{= 24} \\
-	&= {9 \over 8 \nu_A} \;.
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% HBT Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{HBT radii in Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisation for comparison with coalescence models}\label{appendix:YKP}
-
-The results of HBT analyses are typically presented in either the Bertsch-Pratt ($R_{out}$, $R_{side}$, $R_{long}$) or the Yano-Koonin-Podgoretskii ($R_{\perp}$, $R_{0}$, $R_{\parallel}$) parameterization.
-The ALICE HBT results \cite{Aamodt:2011mr, Adam:2015vna} are given in the Bertsch-Pratt convention, whereas the coalescence parameter is derived in \cite{Scheibl:1998tk} by expressing the dependence on the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-The transformation between the two parameterisations is best presented in~\cite{Wiedemann:1999qn} in the equations (W 3.48) to (W 3.52)\footnote{The equations in~\cite{Wiedemann:1999qn} are denoted as (W...) in order to distinguish them from the equations presented in this paper.}:
-
-\begin{eqnarray}
-R_{side}^{2}    &=& R_{\perp}^{2}  \;, \\
-R_{diff}^{2} &=& R_{out}^{2} -  R_{side}^{2} = \beta_{\perp}^2 \gamma^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
-R_{long}^{2}     &=& (1 - \beta_l^2) R_{\parallel}^2 + \gamma^2 (\beta_l - v)^2 (R_{0}^2 + v^2R_{\parallel}^2) \;, \\
-R_{ol}^{2}   &=& \beta_{\perp} (-\beta_l R_{\parallel}^{2} +  \gamma^2 (\beta_l - v)(R_{0}^2 + v^2R_{\parallel}^2)) \,.
-\end{eqnarray}
-%
-We immediately identify that $R_{\perp}^2$ can be identified with $R_{side}^{2}$.
-Following the reasoning and the nomenclature in~\cite{Wiedemann:1999qn} (W 3.52-3.53), the above equations can be inverted and $R_{\parallel}^{2}$ can be expressed as
-%
-\begin{eqnarray}
-R_{\parallel}^{2} &=& B  - v \cdot C \;, \\
-                          &=& R_{long}^2 - 2{\beta_l \over \beta_\perp}  R_{ol}^2 + {\beta_l^2 \over \beta_\perp^2} R_{diff}^2 
-                          - v \cdot \Bigl(-{1 \over \beta_\perp } R_{ol}^2 + {\beta_l \over \beta_\perp^2} R_{diff}^2  \Bigr) \; .
-\end{eqnarray}
-%
-As it turns out all corrections which are subtracted from $R_{long}^{2}$ can be neglected.
-First, we notice that the cross term $R_{ol}$ vanishes if the measured fireball is longitudinally boost-invariant, which is a valid approximation for the rapidity ranges studied here.
-The remaining terms are all proportional to $\beta_l$.
-By definition of the rest frame for a longitudinally-boosted invariant system, $\beta_l = 0$.
-In summary, we can consider $R_{\perp} = R_{side}$ and $R_{\parallel}=R_{long}$ for the present study.
-
-\end{appendix}
-
-\bibliographystyle{utphys} 	
-\bibliography{NucleiB2}
-
-\end{document}
+Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.

### 2018-09-20 FrascatiPlot/Paper/aps/table1.tex
First version of the paper into aps paper format - sub-files created, table modified - everything else is the same as for the arXiv version

\begin{table*}[htb]

\centering

\begin{ruledtabular}
\begin{tabular}{cccccccc}\\[-2ex]
Mass number & Nucleus &  Composition  & $B_{E}$ (MeV)   &  $J_{A}$ & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
\\[0.5ex] \hline \\[-2ex]
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
      A = 3  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
                                   A = 4  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]

\end{tabular}
\end{ruledtabular}

\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV, $J_{A}$ is the spin. The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced. Details are given in Appendix \ref{appendix:Sato}. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table*}

### 2018-09-20 FrascatiPlot/Paper/aps/abstract.tex
Start modifying draft for journal submission: abstract shortened

@@
-(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC).
-Their production is typically discussed within the framework of coalescence and thermal-statistical production models.
-While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.
-We propose for the first time a study which is experimentally feasible with the current and upgraded LHC experiments to distinguish between the two production scenarios.
-Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
-The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
+The production of (anti-)(hyper-)nuclei in high-energy collisions is typically described within the framework of
+the coalescence and thermal-statistical production models. 
+We present a detailed comparison of the two production scenarios carried out for the first time as a function of the size of the object relative to the size of the particle emitting source. 
+While both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei,  they largely differ in their description of (anti-)hyper-triton production.
+Our study reveals large differences between the two scenarios for the production of objects with extended wave-functions. 
+We propose to address experimentally the comparison of the production models by measuring the coalescence parameter systematically for different (anti-)(hyper-)nuclei in different collision systems and differentially in multiplicity.
+Such measurements are feasible with the current and upgraded LHC experiments. 
+%(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at the energies available at the Large Hadron Collider (LHC). 
+%Their production is typically discussed within the framework of coalescence and thermal-statistical production models. 
+%While it is often argued that these two approaches are not distinguishable, we present a detailed study of both theories which reveals large differences between the two scenarios for the production of objects with extended wave-functions.}
+%We propose for the first time a study which is experimentally feasible with the current and upgraded LHC experiments to distinguish between the two production scenarios. 
+%Both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, but they largely differ in their description of (anti-)hyper-triton production.
+%The thermal-statistical model is found to be in agreement with results in central Pb--Pb collisions even though fragile objects such as light (anti-)(hyper-)nuclei should be destroyed in hadronic interactions after the chemical freeze-out of the system.
 Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.

### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: modified intro (rm halo nuclei part and rm outlook from intro)

@@
 This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
-Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
+%Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
 
@@
 We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
-As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
-Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
-In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
+%As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
+%Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
+%In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
 

### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: rm coalescence subsection and first equation

@@
 
-\section{Coalescence approach} 
-\label{sec:coalescence}
+\section{Coalescence approach} \label{sec:coalescence}
 
-\subsection{Simple coalescence}
+%\subsection{Simple coalescence}
 In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
-For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$, which is defined as
+For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$.
+%that is defined as 
+%\begin{equation}
+%E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
+%   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
+%,    
+%\label{eq:BA}
+%\end{equation}
+%\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
+%Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
+Considering that in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as
 
 \begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
-   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
-,    
-\label{eq:BA}
-\end{equation}
-
-\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
-Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
-\begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right..
 \label{eq:BA}
@@
 %
+where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
+
 Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
@@
 
-\subsection{Advanced coalescence}
-\label{subsec:FullCoalescence}
-
+%\subsection{Advanced coalescence} 
 In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.

### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: shortened some text in the advanced coalescence section

@@
 While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
-The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions.
+%The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions.
 They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
-The fact that the coalescence probability is anti-proportional to the source volume can already be understood in the classical phase-space picture as due simply to the separation in configuration space.
+The authors use a density matrix approach to calculate the coalescence probability of nucleons within a source that is rapidly expanding under collective flow in heavy-ion collisions.
+%The fact that the coalescence probability is anti-proportional to the source volume can already be understood in the classical phase-space picture as due simply to the separation in configuration space.
 Because coalescence is a quantum-mechanical process, however, the classical definition of phase space does not apply and it is replaced by the Wigner formalism.
 Therefore, most coalescence models, including \cite{Scheibl:1998tk}, determine the production probability of a nucleon cluster as by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
+As coalescence is a quantum-mechanical process, the classical definition of phase space is replaced by the Wigner formalism.
+Therefore, the production probability of a nucleon cluster is given by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
 
-The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
+%The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
+The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with one single characteristic-size parameter, $r_{A}$.
 For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
@@
 
-This ansatz allows one to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
+In this work, we follow the gaussian ansatz in order to obtain fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
+the centrality dependence) and to the size of the (hyper-)nucleus.
+In Tab.~\ref{tab:nucleusradii}, we list the measured rms of the wave-function, $\rmsradius^{meas}$, as well as the $r_{A}$ parameter derived according to these relations. 
+We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with more realistic wave-functions, e.g.
+the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
+The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model.
+%This ansatz allows one to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
 In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wave-function, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
@@
 the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
-We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. 
-The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
-Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
+%We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. 
+%The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
+%Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
 the centrality dependence) and to the size of the (hyper-)nucleus.
@@
 for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
-Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised in \cite{Scheibl:1998tk} as
-\begin{equation}
-\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1} \;\;.
-\label{eq:BA_general}
-\end{equation}
-In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes the Eq. 9 presented in \cite{Blum:2017qnn}:
-\begin{equation}
-\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
-\label{eq:B3}
-\end{equation}
-
-\noindent where
-
- \begin{equation}
-\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1} \;\;.
-\label{eq:C3}
-\end{equation}
+Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 in \cite{Scheibl:1998tk}.
+%as
+%\begin{equation}
+%\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1} \;\;.
+%\label{eq:BA_general}
+%\end{equation}
+In particular, for the case of \hethree~with $A=3$ and $J=1/2$, 
+%Eq. \ref{eq:BA_general} 
+the latter becomes the Eq. 9 presented in \cite{Blum:2017qnn}.
+%\begin{equation}
+%\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
+%\label{eq:B3}
+%\end{equation}
+% 
+%\noindent where
+%
+% \begin{equation}
+%\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1} \;\;.
+%\label{eq:C3}
+%\end{equation}
 

### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: revised conclusions and outlook

@@
 We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
-%As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
-%Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
-%In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
 
@@
 
-\section{Summary, conclusions, and outlook}
-While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
+\section{Conclusions and outlook}
+%While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
 In the following, we summarise our main conclusions:
+We summarise our main conclusions as follows:
 \begin{enumerate}
-	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on (anti-)deuteron production in central Pb--Pb collisions at the LHC.
+	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on d, $\bar{\mathrm{d}}$~production in central Pb--Pb collisions at the LHC.
 	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume.
@@
 
-We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
+%We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
 As mentioned earlier, future studies should be based on more realistic approximations (in particular the wave-function), which requires numerical calculations.
-Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
+%Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
+As our study is deliberately based on simplified assumptions that allow for a completely analytical treatment of the problem, future studies should be based on more realistic approximations (in particular the wave-function), which require numerical calculations.
+Moreover, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
 
-In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872).
+In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872), which has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
 In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
 Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.
+%Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.
+The upcoming high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
+Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
+%In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: revised section 3 - it can be shortened more perhaps

@@
 As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields and not the \pt-differential hadron spectra.
-In order to fill this gap, and for the purpose of this exercise, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
+In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields. 
+%and not the \pt-differential hadron spectra. 
+%In order to fill this gap, and for the purpose of this exercise, 
+Therefore, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
 When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}.
@@
 Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
-In contrast to the coalescence approach, which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
-Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based.
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
+%In contrast to 
+Whereas the coalescence approach
+%, which 
+explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
+%Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based. 
+The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter %(0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
+(0.3 fm for baryons in the GSI-Heidelberg model \cite{Andronic:2017}).
+ We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
 

### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: yet another minor revision to the text of difference between data and models - it can be shortened more perhaps

@@
 
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
+In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining %Eq.~\ref{eq:BA_general} 
+Eq. 6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
 
@@
 \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
-For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}.
-The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}.
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
+%both coalescence and thermal model predictions. 
+%For the coalescence predictions, 
+For the latter and for data, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}. 
+%The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}. 
+%As a first observation, one sees that
 
-As a first observation, one sees that for deuterons both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
+For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
 For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2.
@@
 Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-As a matter of fact, the only data point available so far in Pb--Pb collisions is in agreement with the thermal+blast-wave model but not with coalescence.
-The difference between data and the coalescence model is about 6$\sigma$.
-However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
-Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
-In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production.
+%As a matter of fact, 
+The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
+The difference between data and the coalescence model is about 6$\sigma$,
+%However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
+albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
+%
+%Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
+%In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production.
 This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
 According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
+%
+In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons. 
+A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
 

### 2018-09-21 FrascatiPlot/B2vsVolume.C
Added pPb points for B3 from S. Hornung analysis (not prelim) to Frascati plot

@@ -53,6 +53,7 @@ TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t 
 //helium-3
 TGraphErrors      * getB3_PbPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
 TGraphErrors      * getB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
+TGraphErrors      * getB3_pPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
 TGraphAsymmErrors * getB3_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToAb3pp = 0.800, Int_t paramSet = 0);
 
 //hypertriton
@@ -134,6 +135,8 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   TGraphErrors* gB3vsR_PbPb5TeV_sys[nParamSet];
   TGraphErrors* gB3vsR_PbPb276TeV[nParamSet];
   TGraphErrors* gB3vsR_PbPb276TeV_sys[nParamSet];
+  TGraphErrors* gB3vsR_pPb5TeV[nParamSet];
+  TGraphErrors* gB3vsR_pPb5TeV_sys[nParamSet];
   TGraphAsymmErrors* gB3vsR_pp7TeV[nParamSet];
   TGraphAsymmErrors* gB3vsR_pp7TeV_sys[nParamSet];
   TGraphAsymmErrors* gB3LambdavsR_PbPb276TeV[nParamSet];
@@ -157,9 +160,9 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
     gB2vsR_pp7TeVINELg0[ip] = (TGraphErrors *) getB2_pp7TeVINELg0(kFALSE, pToA, ip);
     gB2vsR_pp7TeVINELg0_sys[ip] = (TGraphErrors *) getB2_pp7TeVINELg0(kTRUE, pToA, ip);
 
-    gB2vsR_pp7TeV[ip] = (TGraphErrors *) getB2_pp7TeVINELg0(kFALSE, pToA, ip);
[…]

### 2018-09-21 FrascatiPlot/GetB3inpToA.C

@@ -2,6 +2,7 @@ void GetB3inpToA_PbPb5TeV();
 void GetB3inpToA_PbPb276TeV();
 void GetB3inpToA_pp7TeV();
 void GetB3LambdainpToA_PbPb276TeV();
+void GetB3inpToA_pPb5TeV(Double_t pToA = 0.733);
 
 void GetB3inpToA_pp7TeV()
 {
@@ -175,7 +176,48 @@ void GetB3inpToA_PbPb5TeV()
   return;
 
 }
+
+
+void GetB3inpToA_pPb5TeV(Double_t pToA = 0.733)
+{
+  TFile * fin = TFile::Open("B3_pPb_5TeV_21092018.root");
+  if (!fin) return;
+
+  Int_t cent[5] = {0, 10, 20, 40, 100}; 
+  TH1D * hin[4];
+  TH1D * hin_syst[4];
+  //                       0-10    10-20     20-40    40-100
+  Double_t dndeta[4] =    {40.6,    30.5,     23.2,     10.1}; 
+  Double_t dndetaErr[4] = {0.9,     0.7,     0.5,        0.16};
   
+  for (int i = 0; i < 4; i++){
+    hin[i] = (TH1D *) fin->Get(Form("B3_3He_%i_%i", cent[i], cent[i+1]));
+    hin_syst[i] = (TH1D *) fin->Get(Form("B3_3He_%i_%i_Syst", cent[i], cent[i+1]));
+  }
+
+  //selected pt bin  
+  TFile * fout = new TFile("B3pToA_pPb502TeV.root","recreate");
+  TGraphErrors * gout = new TGraphErrors(4);
+  gout->SetName(Form("B3_pPb15_pToA=%4.3f", pToA));
+  
+  TGraphErrors * gout_sys = new TGraphErrors(4);
+  gout_sys->SetName(Form("B3_pPb15_pToA=%4.3f_sys", pToA));
+  
+  for (Int_t ip = 0; ip<4; ip++){
+    Int_t sb = hin[ip]->GetXaxis()->FindBin(pToA);
+    
+    gout->SetPoint(ip, dndeta[ip], hin[ip]->GetBinContent(sb));
+    gout->SetPointError(ip, dndetaErr[ip], hin[ip]->GetBinError(sb));
+    
+    gout_sys->SetPoint(ip, dndeta[ip], hin_syst[ip]->GetBinContent(sb));
[…]

### 2018-09-24 FrascatiPlot/Paper/aps/abstract.tex
start of shortening campaign

@@
-The production of (anti-)(hyper-)nuclei in high-energy collisions is typically described within the framework of
-the coalescence and thermal-statistical production models. 
-We present a detailed comparison of the two production scenarios carried out for the first time as a function of the size of the object relative to the size of the particle emitting source. 
+We present a detailed comparison of coalescence and thermal-statistical models for the production of (anti-)(hyper-)nuclei in high-energy collisions.
+For the first time, such a study is carried out as a function of the size of the object relative to the size of the particle emitting source.
+Our study reveals large differences between the two scenarios for the production of objects with extended wave-functions.
 While both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei,  they largely differ in their description of (anti-)hyper-triton production.
-Our study reveals large differences between the two scenarios for the production of objects with extended wave-functions. 
 We propose to address experimentally the comparison of the production models by measuring the coalescence parameter systematically for different (anti-)(hyper-)nuclei in different collision systems and differentially in multiplicity.

### 2018-09-24 FrascatiPlot/Paper/aps/main.tex
start of shortening campaign

@@
 In addition, these studies might shed light on the internal structure of the formed objects themselves.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size (i.e.
+Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size (i.e.
 the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
@@
 As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave-function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
-Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
+%Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. 
 For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$.
@@
 Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
-Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically.
-At LHC energies, this is seen to occur when the system has reached temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
+Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically at temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
 In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects.
@@
 %\subsection{Advanced coalescence} 
-In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
+More advanced coalescence models take into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
 While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
@@
 They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
-The authors use a density matrix approach to calculate the coalescence probability of nucleons within a source that is rapidly expanding under collective flow in heavy-ion collisions.
+%The authors use a density matrix approach to calculate the coalescence probability of nucleons within a source that is rapidly expanding under collective flow in heavy-ion collisions.
 %The fact that the coalescence probability is anti-proportional to the source volume can already be understood in the classical phase-space picture as due simply to the separation in configuration space.

### 2018-09-25 FrascatiPlot/Paper/aps/main.tex
end of AK shortening the text

@@
 
-\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
+%\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details). 
+\noindent For nuclei with $A > 2$, analogous forms exist. The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
 
@@
 \noindent for point-like constituents.
-In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
+In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$.% (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
 
@@
 which is the main result of \cite{Scheibl:1998tk}.
-It is interesting to note that the coalescence parameter decreases with increasing volume, as expected.
-In addition to this, the quantum-mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size in the calculation of \btwo, which reflects the coalescence probability.
+The coalescence parameter decreases with increasing volume, as expected.
+In addition to this, the quantum-mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size.
 If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to
+
 \begin{equation}
@@
 %
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm \cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
 As can be seen in Fig.
 \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
-As a matter of fact, the inflection point of $\langle C_{d} \rangle$ is situated at $R = \dradius/\sqrt{6}$, as indicated in the left panel of Fig.
+%As a matter of fact, the inflection point of $\langle C_{d} \rangle$ is situated at $R = \dradius/\sqrt{6}$, as indicated in the left panel of Fig.
 \ref{fig:radiusDependence} by the vertical dotted line for $\dradius = 3.2$ fm.
@@
 \includegraphics[width=1\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
-\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
-\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
+\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
 The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
@@
 for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
-Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 in \cite{Scheibl:1998tk}.
+Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 in~\cite{Scheibl:1998tk}.
 %as
@@
 %Eq. \ref{eq:BA_general} 
-the latter becomes the Eq. 9 presented in \cite{Blum:2017qnn}.
+the latter becomes the Eq. 9 presented in~\cite{Blum:2017qnn}.
 %\begin{equation}
@@
 Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
-For large source volume, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, and thus decreases for large differences in configuration space.
+For a large source volume, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, and thus decreases for large distances in configuration space.
 
@@
 We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}. 
-The latter is much smaller that the entire fireball which is created in heavy-ion collisions. 
-This is not only caused by the limitations ascribed to the causally-connected volume, but also to the presence of a common radial expansion, which causes the particles inside the fireball to be sorted according to their velocities.
+%The latter is much smaller that the entire fireball which is created in heavy-ion collisions. 
+%This is not only caused by the limitations ascribed to the causally-connected volume, but also to the presence of a common radial expansion, which causes the particles inside the fireball to be sorted according to their velocities.
 As pointed out by the same authors, this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
 The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-As discussed in Appendix \ref{appendix:YKP}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$. We then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
+%As discussed in Appendix \ref{appendix:YKP},
+We identify $\rperp = R_{side}$ as well as $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
 
@@
 In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
-In the following, we make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
+We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
 In contrast to \cite{Blum:2017qnn}, we therefore do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
@@
 In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
+%As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since 
+At the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
 In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields. 
@@
 This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}H / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
+In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
 Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
-Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, we use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}.
+%Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, 
+We use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
 %In contrast to 
@@
 We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
-With this second parameterisation (labeled as``B'' in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree, \bthree.
+With this second parameterisation (labeled as ``B'' in the following), we investigate the agreement of the model with the measured coalescence parameter \bthree\ for \hethree.
 As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
@@
 \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
 %both coalescence and thermal model predictions. 
@@
 %As a first observation, one sees that 
-
 For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
@@
 
-In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872), which has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
-In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton.
+In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872)~\cite{Esposito:2015fsa, Cho:2017dcy}.
+In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}.
 Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.

### 2018-09-25 FrascatiPlot/Paper/aps/main.tex
one more superfluous sentence removed

@@
 \ref{fig:CompareB2B3forDifferentParamWithData}).
-We notice already at this point that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
+We notice that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
 
@@
 We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
-With this second parameterisation (labeled as ``B'' in the following), we investigate the agreement of the model with the measured coalescence parameter \bthree\ for \hethree.
+With this second parameterisation (labeled as ``B''), we investigate the agreement of the model with the measured coalescence parameter \bthree\ for \hethree.
 As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
 The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the coalescence volume is the same for all anti- and hyper-nuclei.
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x-axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
+%It is also noteworthy that any change of the radii parameterisation would result in a shift along the x-axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
 

### 2018-09-25 FrascatiPlot/Paper/aps/main.tex
almost there in shortening, now fine-tuning

@@
 In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons. 
-A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
+A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
 
@@
 As our study is deliberately based on simplified assumptions that allow for a completely analytical treatment of the problem, future studies should be based on more realistic approximations (in particular the wave-function), which require numerical calculations.
-Moreover, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
+Moreover, it will be interesting to explore further the \pt~dependence of the observations made here.% in comparison to future and currently available data.
 

### 2018-09-25 FrascatiPlot/Paper/aps/main.tex
3749

@@
 This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
-The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions.
-As it can be seen, the latter is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
+The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
 
@@
 %Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.
-The upcoming high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
-Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
+The upcoming high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of \mbox{(anti-)}(hyper-)nuclei production.
+Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
 %In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

### 2018-09-25 FrascatiPlot/B2vsVolume.C
Added options to plot w 13teV data vs multi

@@ -9,7 +9,8 @@
 #include "TLegend.h"
 #include "TH1D.h"
 #include "TH2D.h"
-#include "./generateBWpredictionsB2.C" 
+#include "./generateBWpredictionsB2.C"
+#include "./Make13TeVPaperFigure.C"
 
 //mapping multiplicity into radius
 void convertMultiToRadius(TGraphErrors * graph = 0x0, Int_t paramSet = 0);
@@ -45,6 +46,7 @@ TGraphAsymmErrors * getBAthermalBlast(TString system = "PbPb276TeV", TString par
 //ALICE data on nuclei BA
 //deuteron
 TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphErrors * getB2_pp13TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
@@ -87,35 +89,16 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3, Double_t 
 		      TGraphAsymmErrors** gBlastB2vsR_PbPb276TeV,  TGraphAsymmErrors** gBlastB3vsR_PbPb276TeV,
 		      TGraphAsymmErrors** gB3LambdavsR_PbPb276TeV, TGraphAsymmErrors** gB3LambdavsR_PbPb276TeV_sys, TGraphAsymmErrors** gBlastB3LambdavsR_PbPb276TeV);
 
-// void MakeYRfigure(Bool_t plotLinX, Double_t pToA, Double_t pToAb3, Double_t pToAb3Lambda, Double_t pToAb4Lambda,
[…]

### 2018-09-25 FrascatiPlot/Make13TeVPaperFigure.C
Macro to plot w 13teV data vs multi

@@ -1,0 +1,76 @@
+
+void Make13TeVPaperFigure(Bool_t plotLinX, Double_t pToA, Int_t RmappingParam,
+			  TGraphErrors * hB2_coalescence, 
+			  TGraphErrors ** gB2vsR_PbPb276TeV_sys,  TGraphErrors ** gB2vsR_pp7TeV_sys, TGraphErrors **gB2vsR_PbPb276TeV, TGraphErrors **  gB2vsR_pp7TeV,
+			  TGraphErrors ** gB2vsR_pPb502TeV_sys,  TGraphErrors ** gB2vsR_pp13TeV_sys, TGraphErrors ** gB2vsR_pPb502TeV, TGraphErrors **  gB2vsR_pp13TeV)
+{
+
+  Int_t ip = RmappingParam;
+  
+  TH2D * hframe = new TH2D("hframe", "B_{2} vs radius; #it{R} (fm); #it{B}_{2} (GeV^{2}/#it{c}^{3})", 1000, 0.01, 6.0, 2000, 1.e-4, 0.1);
+  hframe->GetXaxis()->SetTitleSize(0.06);
+  hframe->GetYaxis()->SetTitleSize(0.06);
+  hframe->GetXaxis()->SetTitleOffset(0.8);
+  hframe->GetXaxis()->SetLabelSize(0.05);
+  hframe->GetYaxis()->SetLabelSize(0.05);
+  if (plotLinX) hframe->GetXaxis()->SetRangeUser(0.01, 8.5);
+  else  hframe->GetXaxis()->SetRangeUser(0.1, 10.5);
+  
+  //Define pT/A labels only once
+  TPaveText * pavept = new TPaveText(0.17, 0.17, 0.7, 0.23, "NDC");
+  pavept->SetFillStyle(0);
+  pavept->SetTextFont(42);
+  pavept->SetBorderSize(0);
+  pavept->SetTextSize(0.05);
+  pavept->SetTextAlign(12);
+  pavept->AddText(Form("#it{p}_{T}/#it{A} = %3.2f GeV/#it{c}", pToA));
+
+  Int_t nl = 6;
+  TLegend * legB2data = new TLegend(0.45, 0.9-nl*0.04, 0.85, 0.9);
+  legB2data->SetFillStyle(0);
+  legB2data->SetTextSize(0.035);
+  legB2data->SetBorderSize(0);
[…]

### 2018-09-25 FrascatiPlot/GetB3inpToA.C
Changes to add p-Pb 5.02 TeV

@@ -3,6 +3,7 @@ void GetB3inpToA_PbPb276TeV();
 void GetB3inpToA_pp7TeV();
 void GetB3LambdainpToA_PbPb276TeV();
 void GetB3inpToA_pPb5TeV(Double_t pToA = 0.733);
+void GetB3inpToA_pPb5TeV_inelg0(Double_t pToA = 0.733);
 
 void GetB3inpToA_pp7TeV()
 {
@@ -194,7 +195,7 @@ void GetB3inpToA_pPb5TeV(Double_t pToA = 0.733)
     hin[i] = (TH1D *) fin->Get(Form("B3_3He_%i_%i", cent[i], cent[i+1]));
     hin_syst[i] = (TH1D *) fin->Get(Form("B3_3He_%i_%i_Syst", cent[i], cent[i+1]));
   }
-
+  
   //selected pt bin  
   TFile * fout = new TFile("B3pToA_pPb502TeV.root","recreate");
   TGraphErrors * gout = new TGraphErrors(4);
@@ -215,10 +216,50 @@ void GetB3inpToA_pPb5TeV(Double_t pToA = 0.733)
   fout->cd();
   gout->Write();
   gout_sys->Write();
+  fout->Close();
   return;
   
 }
+
+
+void GetB3inpToA_pPb5TeV_inelg0(Double_t pToA = 0.733)
+{
+  TFile * fin = TFile::Open("B3_pPb_5TeV_21092018.root");
+  if (!fin) return;
+
+  Int_t cent[2] = {0, 100}; 
+  TH1D * hin;
+  TH1D * hin_syst;
+  Double_t dndeta =  10.6; //fixme
+  Double_t dndetaErr = 0.1; //fixme
   
+  hin = (TH1D *) fin->Get("B3_3He_MultiplicityIntegrated");
+  hin_syst = (TH1D *) fin->Get("B3_3He_MultiplicityIntegrated_Syst");
+  
+  //selected pt bin  
+  TFile * fout = new TFile("B3pToA_pPb502TeV_inelg0.root","recreate");
+  TGraphErrors * gout = new TGraphErrors(1);
+  gout->SetName(Form("B3_pPb15_pToA=%4.3f", pToA));
+  
+  TGraphErrors * gout_sys = new TGraphErrors(4);
+  gout_sys->SetName(Form("B3_pPb15_pToA=%4.3f_sys", pToA));
+
+  
+  Int_t sb = hin->GetXaxis()->FindBin(pToA);
[…]

### 2018-09-26 FrascatiPlot/B2vsVolume.C
Modified figure for 13 TeV Paper - separated macro and coal vs dN/deta

@@ -10,7 +10,6 @@
 #include "TH1D.h"
 #include "TH2D.h"
 #include "./generateBWpredictionsB2.C"
-#include "./Make13TeVPaperFigure.C"
 
 //mapping multiplicity into radius
 void convertMultiToRadius(TGraphErrors * graph = 0x0, Int_t paramSet = 0);
@@ -45,12 +44,12 @@ TGraphAsymmErrors * getBAthermalBlast(TString system = "PbPb276TeV", TString par
 
 //ALICE data on nuclei BA
 //deuteron
-TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphErrors * getB2_pp13TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphErrors * getB2_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_pp13TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
[…]

### 2018-09-26 FrascatiPlot/Make13TeVPaperFigure.C

@@ -1,11 +1,67 @@
+#include "./B2vsVolume.C"
 
-void Make13TeVPaperFigure(Bool_t plotLinX, Double_t pToA, Int_t RmappingParam,
-			  TGraphErrors * hB2_coalescence, 
-			  TGraphErrors ** gB2vsR_PbPb276TeV_sys,  TGraphErrors ** gB2vsR_pp7TeV_sys, TGraphErrors **gB2vsR_PbPb276TeV, TGraphErrors **  gB2vsR_pp7TeV,
-			  TGraphErrors ** gB2vsR_pPb502TeV_sys,  TGraphErrors ** gB2vsR_pp13TeV_sys, TGraphErrors ** gB2vsR_pPb502TeV, TGraphErrors **  gB2vsR_pp13TeV)
+void convertRadiusToMulti(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 1);
+void convertRadiusToMulti(TGraphErrors * graph = 0x0, Int_t paramSet = 1);
+void getMultiFromR(Double_t * multi = NULL, Double_t * radius = NULL, Int_t paramSet = 1);
+void Make13TeVPaperFigure(Bool_t plotLinX = 0, Double_t pToA = 0.75, Int_t RmappingParam = 1);
+
+  
+void Make13TeVPaperFigure(Bool_t plotLinX, Double_t pToA, Int_t RmappingParam)
 {
 
   Int_t ip = RmappingParam;
+
+  //----------------------------
+  //Get data
+  //----------------------------
+  const Int_t nParamSet = 2;
+  TGraphErrors* gB2vsR_pp7TeV[nParamSet];
+  TGraphErrors* gB2vsR_pp7TeV_sys[nParamSet];
+  TGraphErrors* gB2vsR_pp13TeV[nParamSet];
+  TGraphErrors* gB2vsR_pp13TeV_sys[nParamSet];
+  TGraphErrors* gB2vsR_pPb502TeV[nParamSet];
+  TGraphErrors* gB2vsR_pPb502TeV_sys[nParamSet];
+  TGraphErrors* gB2vsR_PbPb276TeV[nParamSet];
+  TGraphErrors* gB2vsR_PbPb276TeV_sys[nParamSet];
+
+  for (Int_t jj = 0; jj < nParamSet; jj++){
+    gB2vsR_pp7TeV[jj] = (TGraphErrors *) getB2_pp7TeV(kFALSE, pToA, jj, kFALSE);
[…]

### 2018-09-26 FrascatiPlot/Paper/aps/main.tex
Another small review to reduce some text here and there. Also, removed appendices and references to them

@@
 %Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
-Considering that in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as
+Considering that at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as
 
@@
 Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
-As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
+As a consequence, the anti-particle to particle ratio for the (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
 In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
@@
 If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
+While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
 In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
@@
 
-The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum-mechanical correction factor, $\langle C_{A} \rangle$.
+The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average correction factor, $\langle C_{A} \rangle$.
 In the case of the deuteron, the quantum-mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
@@
 We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we therefore do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
 
@@
 \includegraphics[width=1\columnwidth]{../HbtRadiusParam.png}
-\caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.
-Parameterisation A is shown here, see text for details.}
+\caption{Parameterisation A (details in text) of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
+The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
 \label{fig:radiiparam}
@@
 Therefore, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
-When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}.
+When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave
+%(average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$)
+are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}. 
 The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
 This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and the measured \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
+In the case of hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
 Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
@@
 Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
-In Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
+In Fig.~\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
 For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions.
@@
 %For the coalescence predictions, 
-For the latter and for data, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}. 
+For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
 %The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}. 
@@
 
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity or centrality in order to distinguish between the two production scenarios.
+Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity in order to distinguish between the two production scenarios.
 In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.

### 2018-09-26 FrascatiPlot/Paper/aps/table1.tex
Another small review to reduce some text here and there. Also, removed appendices and references to them

@@
                                    & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
+                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1 \cite{Nemura:1999qp}    &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                    & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]
@@
 The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced.
-Details are given in Appendix \ref{appendix:Sato}.
-Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
-Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
- References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
+Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
+ %References are given in the last column.}
+%. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.
 \label{tab:nucleusradii}

### 2018-09-26 FrascatiPlot/Paper/aps/main.tex
Removed all commented text for submission

@@
 As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave-function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
-%Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects. 
 For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$.
 This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
-%Halo nuclei as $^{6}$He would therefore be an ideal complement to this study, but they remain out of the experimental reach in high-energy experiments in the near future.
 
@@
 
-%\subsection{Simple coalescence}
 In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
 For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$.
-%that is defined as 
-%\begin{equation}
-%E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
-%   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
-%,    
-%\label{eq:BA}
-%\end{equation}
-%\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
-%Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
 Considering that at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as
@@
 
-%\subsection{Advanced coalescence} 
 More advanced coalescence models take into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
 While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
-%The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions.
-They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
-%The authors use a density matrix approach to calculate the coalescence probability of nucleons within a source that is rapidly expanding under collective flow in heavy-ion collisions.
-%The fact that the coalescence probability is anti-proportional to the source volume can already be understood in the classical phase-space picture as due simply to the separation in configuration space.
-Because coalescence is a quantum-mechanical process, however, the classical definition of phase space does not apply and it is replaced by the Wigner formalism.
-Therefore, most coalescence models, including \cite{Scheibl:1998tk}, determine the production probability of a nucleon cluster as by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
 As coalescence is a quantum-mechanical process, the classical definition of phase space is replaced by the Wigner formalism.
 Therefore, the production probability of a nucleon cluster is given by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
-
-%The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$.
 The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with one single characteristic-size parameter, $r_{A}$.
@@
 
-%\noindent For nuclei with $A > 2$, analogous forms exist (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details). 
 \noindent For nuclei with $A > 2$, analogous forms exist. The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
@@
 
-\noindent for point-like constituents.
-In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$.% (see Appendix \ref{appendix:Sato} and \ref{appendix:integration} for details).
-
+\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$.
 In this work, we follow the gaussian ansatz in order to obtain fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
@@
 The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model.
-%This ansatz allows one to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions.
-In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wave-function, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations.
-The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g.
-the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
-%We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. 
-%The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
-%Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
-the centrality dependence) and to the size of the (hyper-)nucleus.
-In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.
 
@@
 \ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
-%As a matter of fact, the inflection point of $\langle C_{d} \rangle$ is situated at $R = \dradius/\sqrt{6}$, as indicated in the left panel of Fig.
-\ref{fig:radiusDependence} by the vertical dotted line for $\dradius = 3.2$ fm.
 
@@
 Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 in~\cite{Scheibl:1998tk}.
-%as
-%\begin{equation}
-%\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1} \;\;.
-%\label{eq:BA_general}
-%\end{equation}
-In particular, for the case of \hethree~with $A=3$ and $J=1/2$, 
-%Eq. \ref{eq:BA_general} 
-the latter becomes the Eq. 9 presented in~\cite{Blum:2017qnn}.
-%\begin{equation}
-%\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
-%\label{eq:B3}
-%\end{equation}
-% 
-%\noindent where
-%
-% \begin{equation}
-%\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1} \;\;.
-%\label{eq:C3}
-%\end{equation}
+In particular, for the case of \hethree~with $A=3$ and $J=1/2$, the latter becomes the Eq. 9 presented in~\cite{Blum:2017qnn}.
 
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining %Eq.~\ref{eq:BA_general} 
-Eq. 6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
+In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.
+6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
 
@@
 We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}. 
-%The latter is much smaller that the entire fireball which is created in heavy-ion collisions. 
-%This is not only caused by the limitations ascribed to the causally-connected volume, but also to the presence of a common radial expansion, which causes the particles inside the fireball to be sorted according to their velocities.
 As pointed out by the same authors, this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
 The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-%As discussed in Appendix \ref{appendix:YKP},
 We identify $\rperp = R_{side}$ as well as $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
@@
 In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-%As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since 
 At the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
 In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields. 
-%and not the \pt-differential hadron spectra. 
-%In order to fill this gap, and for the purpose of this exercise, 
 Therefore, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
 When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave
-%(average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$)
 are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}. 
@@
 Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
-%Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality classes, 
 We use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
-%In contrast to 
 Whereas the coalescence approach
-%, which 
 explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
-%Being a simplified hydrodynamic model, the latter treats the system as a continuum and is not particle based. 
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter %(0.3 fm in the case of baryons for the GSI-Heidelberg model used here).
-(0.3 fm for baryons in the GSI-Heidelberg model \cite{Andronic:2017}).
+The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm for baryons in the GSI-Heidelberg model \cite{Andronic:2017}).
  We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
@@
 The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the coalescence volume is the same for all anti- and hyper-nuclei.
-%It is also noteworthy that any change of the radii parameterisation would result in a shift along the x-axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
-
 The necessity of introducing a second parameterisation for the radius could point to the fact that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered in parameterisation A, but by a slightly larger system as given by parameterisation B.
@@
 In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
-%both coalescence and thermal model predictions. 
-%For the coalescence predictions, 
 For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
-%The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}. 
-%As a first observation, one sees that 
 For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
@@
 Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-%As a matter of fact, 
 The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
 The difference between data and the coalescence model is about 6$\sigma$,
-%However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
 albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
-%
-%Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
-%In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production.
-This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
-According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
-%
 In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons. 
@@
 \section{Conclusions and outlook}
-%While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions.
-In the following, we summarise our main conclusions:
 We summarise our main conclusions as follows:
@@
 
-%We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem.
-As mentioned earlier, future studies should be based on more realistic approximations (in particular the wave-function), which requires numerical calculations.
-%Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
 As our study is deliberately based on simplified assumptions that allow for a completely analytical treatment of the problem, future studies should be based on more realistic approximations (in particular the wave-function), which require numerical calculations.
-Moreover, it will be interesting to explore further the \pt~dependence of the observations made here.% in comparison to future and currently available data.
+Moreover, it will be interesting to explore further the \pt~dependence of the observations made here.
 
@@
 Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-%Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.
 The upcoming high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of \mbox{(anti-)}(hyper-)nuclei production.
 Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
-%In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

### 2018-09-26 FrascatiPlot/B2vsVolume.C
Ädding Lambda yields vs centrality for Pbpb 2.76 TeV with finer bins wrt to measured ones (interpolation)

@@ -1,6 +1,7 @@
 /*
    akalweit@cern.ch, fbellini@cern.ch
    17.01.2018 - The Frascati plot
+   last update: 26.09.2018
 */
 #include "TMath.h"
 #include "TGraphAsymmErrors.h"
@@ -60,16 +61,9 @@ TGraphAsymmErrors * getB3_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToAb3pp = 0
 //hypertriton
 TGraphAsymmErrors * getB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1., Int_t paramSet = 0);
 
-//pseudodata
-//TGraphErrors * GetPseudoBAvsMulti(TString particle = "deuteron",  Int_t paramSet = 1);
-//TGraphErrors * GetPseudoBAvsMultiUnc(TString particle = "deuteron",  Int_t paramSet = 1);
-
-  
 // beautification of plots
 void MakeUp(TGraphErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Style, Int_t Line_Style, Int_t Line_Width, Int_t Marker_Style, Float_t Marker_Size);
 void MakeUp(TGraphAsymmErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Style, Int_t Line_Style, Int_t Line_Width, Int_t Marker_Style, Float_t Marker_Size);
-//void ConfigTwoPanelsPad(TPad* pad1, TPad* pad2, Float_t leftmargin, Float_t rightmargin);
-//void ConfigThreePanelsPad(TPad* pad1, TPad* pad2, TPad* pad3, Float_t leftmargin = 0.15, Float_t rightmargin = 0.001);
 
 //figure making
 void MakePaperFigure2(Bool_t plotLinX, Double_t pToA,
@@ -88,11 +82,10 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3, Double_t 
 		      TGraphAsymmErrors** gBlastB2vsR_PbPb276TeV,  TGraphAsymmErrors** gBlastB3vsR_PbPb276TeV,
 		      TGraphAsymmErrors** gB3LambdavsR_PbPb276TeV, TGraphAsymmErrors** gB3LambdavsR_PbPb276TeV_sys, TGraphAsymmErrors** gBlastB3LambdavsR_PbPb276TeV);
 
-
[…]

### 2018-09-26 FrascatiPlot/generateBWpredictionsB2.C

@@ -197,13 +197,12 @@ void GetParams_PbPb276TeV(Double_t *parT, Double_t *parTerr, Double_t *parN, Dou
   Double_t dNdyErrPion[10]  = { 54.,  42.,  31.,  20.,  13.,   8.,  5.,  2.,  1.1, 0.4};
 
   // Lambda only -- table 23 of http://hepdata.cedar.ac.uk/view/ins1243863
-  // --> TODO: deal with different binning by interpolation
-  // published bins are          (0-5,  5-10, 10-20, 20-40, fixme, 40-60, fixme, 60-80, fixme,  80-90)%
-  Double_t dNdyLambda[10]    = {25.61, 21.58, 16.89, 9.79,  9.79,  3.79, 3.79,  0.99,   0.99,   0.214};
+  // We dealt with different binning by interpolation
+  // published bins are          (0-5,  5-10, 10-20,                       20-30,                       30-40,                      40-50,                      50-60,                     60-70,                      70-80, 80-90)%
+  Double_t dNdyLambda[10]    = {25.61, 21.58, 16.89, 649.*2./(649.+ 426.) * 9.79, 426.*2./(649.+ 426.) * 9.79, 261.*2*3.79 / (261.+ 149.), 149.*2*3.79 / (261.+ 149.), 76. *2.* 0.99 / (76.+ 35),  35. *2.* 0.99 / (76.+ 35),   0.214}; 
   Double_t dNdyErrLambda[10] = { 2.91,  1.9,   1.9,  0.947, 0.947, 0.378,0.378, 0.0937, 0.0937, 0.0166};
-
-
-
+  // 20-40% L dN/dy = 9.79 ± 0.947
+  
   for (Int_t j=0; j<10; j++){
     parT[j] = bt[j];
     parTerr[j] = bterr[j];

### 2018-09-27 FrascatiPlot/Paper/aps/main.tex
Updated paper for PRL submission
Starting hard cut on n. of words - figure 3 removed

@@
-\section{Introduction} 
+%\section{Introduction} 
 The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
@@
 While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
-
-To this purpose, we compare to models the existing data from the LHC.
+\\To this purpose, we compare to models the existing data from the LHC.
 For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
@@
 We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
-
-A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
+\\A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
 However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with the hyper-nuclei proposed here.
@@
 
-Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
-In Fig.~\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
-For pp collisions, data in  \cite{ALICE:nucleipp2017} are given for inelastic (INEL) collisions.
-In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of the charged particle multiplicity density in these two event classes \cite{Adam:2015gka}.
-First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} (labeled in the following as ``parameterisation A") is used to map the \avdNdeta~to the source size (top left panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We notice that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo~for Pb-Pb collisions.
+Data on anti- and hyper-nuclei production at the LHC in different collision systems have been released by the ALICE Collaboration in centrality/multiplicity classes \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
+Data in \cite{ALICE:nucleipp2017} are given for inelastic (INEL) pp collisions.
+In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of \avdNdeta~in these two event classes \cite{Adam:2015gka}.
+In order to map the \avdNdeta~to the source size we followed two approaches. 
+First, we used the parameterisation (labeled as ``A'') from the fit to the HBT data shown in Fig.~\ref{fig:radiiparam}. 
+We found that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation.
+In particular, the model would require a larger radius for a given value of \btwo~for Pb--Pb collisions.
+%In Fig.~\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
+In a second step the radius is tuned such that the data points for (anti-)deuterons fall onto the coalescence prediction, finding the values $a = 0.473$ and $b = 0$ for the parameters of Eq.~\ref{eq:radiusParameterisation}.
 
-In a second step the radius is tuned such that the data points for (anti-)deuterons fall onto the coalescence prediction (top right panel of Fig.
-\ref{fig:CompareB2B3forDifferentParamWithData}).
-We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
 With this second parameterisation (labeled as ``B''), we investigate the agreement of the model with the measured coalescence parameter \bthree\ for \hethree. 
@@
 
+%\begin{figure*}[htbp]
+%	\begin{center}
+%		\includegraphics[width=\textwidth]{../radiiParamCompareData.png}
+%		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
+The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
+%		\label{fig:CompareB2B3forDifferentParamWithData}
+%	\end{center}
+%\end{figure*}
+
+\subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
 \begin{figure*}[htbp]
 	\begin{center}
-		\includegraphics[width=\textwidth]{../radiiParamCompareData.png}
-		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-		\label{fig:CompareB2B3forDifferentParamWithData}
+		\includegraphics[width=\textwidth]{../compareThermalAndCoalescence.png}
+		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
+Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
+The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
+		\label{fig:CompareThermalAndCoalescence}
 	\end{center}
 \end{figure*}
-
-\subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
 In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
@@
 The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
-
-\begin{figure*}[htbp]
-	\begin{center}
-		\includegraphics[width=\textwidth]{../compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
-Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
-The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
-		\label{fig:CompareThermalAndCoalescence}
-	\end{center}
-\end{figure*}
 

### 2018-09-27 FrascatiPlot/B2vsVolume.C
Figure 4 with vertically arranges panels for PRL

@@ -380,10 +380,10 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   //---------------------------------------  
   if (plotPaperFigures) {
 
-    MakePaperFigure3(plotLinX, pToA, pToAb3,
-		     hB2_coalescence, hB3_coalescence, 
-		     gB2vsR_PbPb276TeV_sys,  gB2vsR_pp7TeVINELg0_sys, gB2vsR_PbPb276TeV,  gB2vsR_pp7TeVINELg0,
-		     gB3vsR_PbPb276TeV_sys,  gB3vsR_pp7TeV_sys, gB3vsR_PbPb276TeV,  gB3vsR_pp7TeV);
+    // MakePaperFigure3(plotLinX, pToA, pToAb3,
+    // 		     hB2_coalescence, hB3_coalescence, 
+    // 		     gB2vsR_PbPb276TeV_sys,  gB2vsR_pp7TeVINELg0_sys, gB2vsR_PbPb276TeV,  gB2vsR_pp7TeVINELg0,
+    // 		     gB3vsR_PbPb276TeV_sys,  gB3vsR_pp7TeV_sys, gB3vsR_PbPb276TeV,  gB3vsR_pp7TeV);
 
     MakePaperFigure4(plotLinX, pToA, pToAb3, pToAb3Lambda,
 		     hB2_coalescence, hB3_coalescence, hB3L_coalescence, hB3L_coalescence_largeradius,
@@ -947,55 +947,54 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
   //
   // make figure 4 of the current paper
   //
-  TH2D * hframe = new TH2D("hframeFig4", "B_{2} vs radius; #it{R} (fm); #it{B}_{2} (GeV^{2}/#it{c}^{3})", 1000, 0.01, 6.0, 2000, 1.e-4, 0.1);
-  hframe->GetXaxis()->SetTitleSize(0.06);
-  hframe->GetYaxis()->SetTitleSize(0.06);
-  hframe->GetYaxis()->SetTitleOffset(1.3);
[…]

### 2018-09-27 FrascatiPlot/Paper/aps/main.tex
Let the axe fall...

@@
-%\section{Introduction} 
+\section{Introduction} 
 The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
-In addition, these studies might shed light on the internal structure of the formed objects themselves.
-Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size (i.e.
-the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
+Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, kaons, protons, etc.), because their size is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
 The relevant known properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
 As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave-function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$.
-This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$, driven by the average separation of the $\Lambda$ with respect to the two other nucleons.
 
@@
 
-Since about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
-Surprisingly, thermal-statistical models have been successful in describing not only light-flavour particle production, but also that of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2017, Andronic:2010qu}.
+For about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
+Surprisingly, thermal-statistical models have been successful in describing also the production of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2010qu,Andronic:2017}.
 In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}.
@@
 While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
-\\To this purpose, we compare to models the existing data from the LHC.
+
+To this purpose, we compare to models the existing data from the LHC.
 For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
 In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.
-The coalescence model is reviewed in Section \ref{sec:coalescence}, starting from its simplest form (uncorrelated nucleon emission from a point-like source) to the full space-time evolution picture as discussed in \cite{Scheibl:1998tk}.
-In Section \ref{sec:thermal}, a blast-wave parameterisation for particle transverse momentum spectra in combination with predictions from the statistical-thermal model for the yields is used as an alternative approach.
-The direct comparison of the two approaches and the comparison with data are discussed in Section \ref{sec:comparison}.
-We find that a systematic study of the coalescence parameter \bA~provides an important discrimination power between the two approaches. 
-\\A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
+
+A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
 However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with the hyper-nuclei proposed here.
-We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.
+Based on our findings, we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the LHC Run 3 \& 4, in order to discriminate the aforementioned scenarios.
 
@@
 where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
-
-Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
-As a consequence, the anti-particle to particle ratio for the (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
+%
+The LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
+As a consequence, the anti-particle to particle ratio for (hyper-)nuclei is measured to be consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
 In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
@@
 the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
-The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model.
 
@@
 %
-which is the main result of \cite{Scheibl:1998tk}.
-The coalescence parameter decreases with increasing volume, as expected.
-In addition to this, the quantum-mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size.
+which is the main result of \cite{Scheibl:1998tk}. The coalescence parameter decreases with increasing volume, as expected. 
+The quantum-mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size. 
 If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to
@@
 We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}. 
-As pointed out by the same authors, this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
+This volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
 The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
@@
 different centrality classes \cite{Abelev:2013qoq}.
-In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
+In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged-particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
 We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{../HbtRadiusParam.png}
-\caption{Parameterisation A (details in text) of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
+\includegraphics[width=.8\columnwidth]{../HbtRadiusParam.png}
+\caption{Parameterisation A of the dependence of the source radius on multiplicity compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
 The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
@@
 We use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
-Whereas the coalescence approach
-explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model.
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter (0.3 fm for baryons in the GSI-Heidelberg model \cite{Andronic:2017}).
+In contrast to the coalescence approach, the object size does not enter in the formulation of the blast-wave model.
+The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter.
 We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
 
-\section{Comparison with experimental data}\label{sec:comparison}
-
-\subsection{Constraining the source volume with data}\label{sec:radiiParamet}
+\section{Constraining the source volume with data}\label{sec:radiiParamet}
 
 Data on anti- and hyper-nuclei production at the LHC in different collision systems have been released by the ALICE Collaboration in centrality/multiplicity classes \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
-Data in \cite{ALICE:nucleipp2017} are given for inelastic (INEL) pp collisions.
-In order to facilitate the comparison with future multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the \btwo~and \bthree~by the ratio of \avdNdeta~in these two event classes \cite{Adam:2015gka}.
-In order to map the \avdNdeta~to the source size we followed two approaches. 
-First, we used the parameterisation (labeled as ``A'') from the fit to the HBT data shown in Fig.~\ref{fig:radiiparam}. 
-We found that the coalescence volume from parameterisation A leads to discrepancies with respect to the curve from the coalescence calculation.
-In particular, the model would require a larger radius for a given value of \btwo~for Pb--Pb collisions.
-%In Fig.~\ref{fig:CompareB2B3forDifferentParamWithData} we compare the coalescence parameter for deuteron (\btwo) from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) to the ALICE data for Pb-Pb collisions at $\sqrt{s_{\mathrm{NN}}} = 2.76$ TeV and pp collisions at $\sqrt{s} = 7$ TeV.
-In a second step the radius is tuned such that the data points for (anti-)deuterons fall onto the coalescence prediction, finding the values $a = 0.473$ and $b = 0$ for the parameters of Eq.~\ref{eq:radiusParameterisation}.
+To facilitate the comparison with multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the data in \cite{ALICE:nucleipp2017}, given for inelastic pp collisions, by the ratio of \avdNdeta~in these two event classes \cite{Adam:2015gka}.
+In order to map the \avdNdeta~to the source size we first used the parameterisation (labeled as ``A'') from the fit to the HBT data shown in Fig.~\ref{fig:radiiparam}. 
+We found a discrepancy between the coalescence volume from parameterisation A and the curve from the coalescence calculation.
+In particular, the model would require a larger radius for a given value of \btwo~in Pb--Pb collisions.
+In a second step we tuned the parameterisation (labeled as ``B'') such that the data points for (anti-)deuterons fall onto the coalescence prediction, finding the values $a = 0.473$ and $b = 0$ for the parameters of Eq.~\ref{eq:radiusParameterisation}.
 
-With this second parameterisation (labeled as ``B''), we investigate the agreement of the model with the measured coalescence parameter \bthree\ for \hethree. 
-As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the coalescence volume is the same for all anti- and hyper-nuclei.
-The necessity of introducing a second parameterisation for the radius could point to the fact that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered in parameterisation A, but by a slightly larger system as given by parameterisation B.
+With parameterisation B, we investigate the agreement of the model with the measured \bthree\ for \hethree.
+Thus the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the coalescence volume is the same for all anti- and hyper-nuclei.
+The necessity of introducing a second parameterisation for the radius might suggest that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered in parameterisation A, but by a slightly larger system as from parameterisation B.
 
@@
 
-\subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-\begin{figure*}[htbp]
-	\begin{center}
-		\includegraphics[width=\textwidth]{../compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
-Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
-The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
-		\label{fig:CompareThermalAndCoalescence}
-	\end{center}
-\end{figure*}
+\section{Comparison with data}
+
 In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
@@
 The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
+ \begin{figure}[ht]
+	\begin{center}
+		\includegraphics[width=.95\columnwidth]{../compareThermalAndCoalescence.png}
+		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper panel), \hethree\ (middle panel) and \hthreelambda\ (lower panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
+Parameterisation B has been used to map \avdNdeta~into the radius $R$ of the source.
+The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
+		\label{fig:CompareThermalAndCoalescence}
+	\end{center}
+\end{figure}
 

### 2018-09-27 FrascatiPlot/Paper/aps/main.tex
Axe keeps falling...

@@
 \section{Introduction} 
-The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these collisions.
-Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, kaons, protons, etc.), because their size is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
-The relevant known properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
-As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave-function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$, driven by the average separation of the $\Lambda$ with respect to the two other nucleons.
+Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, protons, etc.), because their size is comparable to a fraction or the whole system created in high-energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions~\cite{Adam:2015vna}.
+Their size is typically defined as the rms of their (charge) wave-function, corresponding to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ with respect to the two other nucleons.
+The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
 
@@
 
-For about sixty years, coalescence models have been used to describe the formation of composite objects (see for instance \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf} and references therein).
-Surprisingly, thermal-statistical models have been successful in describing also the production of light (anti-)(hyper-)nuclei across a wide range of energies in nucleus-nucleus collisions \cite{Andronic:2010qu,Andronic:2017}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV that are near the temperature of the QCD phase transition boundary, as predicted by lattice QCD calculations \cite{Bazavov:2014pvz,Bellwied:2013cta}.
+For about sixty years, coalescence models have been used to describe the formation of composite objects \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf}.
+Surprisingly, thermal-statistical models have been successful in describing also the production of light (anti-)(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}.
+In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV.
 Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
 Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
-Once the particle density of the system is so low that the mean free path for elastic collisions is larger than the size of the system, the fireball freezes-out kinetically at temperatures of the order of $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
-In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile'' objects.
+Once the mean free path for elastic collisions is larger than the system size, the fireball freezes-out kinetically at $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
+In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile''. 
 For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
-As a matter of fact, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Similarly, the elastic cross-section which drives the deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of the coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
-Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
-While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei production yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in the present work.
+The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
+Similarly, the elastic cross-section driving deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
+The deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase, yet their production is measured to be consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc}.
+Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+Data from rescattering of short-lived hadronic resonances suggest a long-lasting hadronic phase \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
+While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in this letter.
 
-To this purpose, we compare to models the existing data from the LHC.
-For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system and object size.
-In the nucleon-coalescence approach, nuclei are formed at kinetic freeze-out by coalescence of nucleons that are nearby in space and have similar velocities.
-
-A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with the hyper-nuclei proposed here.
-Based on our findings, we propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the LHC Run 3 \& 4, in order to discriminate the aforementioned scenarios.
+To this purpose, we compare LHC data to models. 
+For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system- and object-size. 
+A quantitative comparison of the two scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
+However, as ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the comparison with the hyper-nuclei proposed here.
+We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the LHC Run 3 \& 4, in order to discriminate the aforementioned scenarios.
 
@@
 In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
-For a nucleus with mass number $A = Z + N$, the coalescence probability is typically quantified in terms of the coalescence parameter $B_{A}$.
+For a nucleus with mass number $A = Z + N$, the coalescence probability is quantified by the coalescence parameter $B_{A}$.
 Considering that at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as
@@
 The LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
-As a consequence, the anti-particle to particle ratio for (hyper-)nuclei is measured to be consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
-In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
-In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision.
-If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei.
+Consequently, the anti-particle to particle ratio for (hyper-)nuclei is consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
+
+In a simple coalescence approach, \bA~is expected to be independent of momentum and of the object size relative to the volume of particle emission (hereafter referred to as ``source volume'' or ``size'').
 While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
-In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
+The elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
 
-More advanced coalescence models take into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space.
-While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
+More advanced coalescence models \cite{Sato:1981ez, Nagle:1996vp, Scheibl:1998tk} take into account the source size, as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space.
+We rely on the formalism proposed in~\cite{Scheibl:1998tk}.
 As coalescence is a quantum-mechanical process, the classical definition of phase space is replaced by the Wigner formalism.
-Therefore, the production probability of a nucleon cluster is given by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
-The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with one single characteristic-size parameter, $r_{A}$.
-For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains
+The production probability of a nucleon cluster is given by the overlap of the Wigner function with the phase-space distributions of the constituents.
+The wave-functions of the (hyper-)nuclei are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with one single characteristic-size parameter, $r_{A}$.
+For the deuteron wave-function $\varphi_{d}(\vec{r}) $, one obtains
 
@@
 
-\noindent For nuclei with $A > 2$, analogous forms exist. The relation between the characteristic size parameter $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
+\noindent For nuclei with $A > 2$, analogous forms exist. The relation between $r_{A}$ and the rms of the wave-function was derived in~\cite{Shebeko:2006ud} as
 
@@
 
-\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$.
-In this work, we follow the gaussian ansatz in order to obtain fully analytic solutions that highlight the sensitivity to the size of the source (i.e.
-the centrality dependence) and to the size of the (hyper-)nucleus.
-In Tab.~\ref{tab:nucleusradii}, we list the measured rms of the wave-function, $\rmsradius^{meas}$, as well as the $r_{A}$ parameter derived according to these relations. 
+\noindent for point-like constituents. 
+We follow the gaussian ansatz to obtain fully analytic solutions.
+In Tab.~\ref{tab:nucleusradii}, we list the measured rms of the wave-function, $\rmsradius^{meas}$, and the $r_{A}$ parameter derived from these relations. 
 We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with more realistic wave-functions, e.g.
-the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}.
+the Hulthen parameterisation for deuterons \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for hyper-tritons as done only for central collisions in~\cite{Zhang:2018euf}.
 
 The quantum-mechanical nature of the coalescence products is explicitly accounted for by means of an average correction factor, $\langle C_{A} \rangle$.
-In the case of the deuteron, the quantum-mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
+For deuterons, $\langle C_{d} \rangle$ has been approximated as
 
@@
 %
-where \dradius~is the radius of the deuteron, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
-The size of the nucleus enters in the determination of the coalescence parameter \btwo~via $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation
+where \dradius~is the size parameter, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
+The nucleus size enters in the  calculation of \btwo~via $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation~\cite{Scheibl:1998tk}
 %
 \begin{equation}
-\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})}
+\btwo = \frac{3\pi^{3/2} \langle C_{d} \rangle}{2m_{T}\rperp^{2}(m_{T})\rpar(m_{T})} \;\; .
 \label{eq:B2cd}
@@
 %
-which is the main result of \cite{Scheibl:1998tk}. The coalescence parameter decreases with increasing volume, as expected. 
-The quantum-mechanical correction factor introduces a length scale defined by the deuteron size relative to the source size. 
+The coalescence parameter decreases with increasing volume, as expected. 
+$\langle C_{d} \rangle$ introduces a length scale defined by the deuteron size relative to the source size. 
 If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to
@@
 %
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of the quantum-mechanical correction factor (on the left) and the coalescence parameter \btwo~(on the right), calculated assuming (a.) a point-like nucleus $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value which reproduces the measured rms radius of the deuteron $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, irrealistic value of  $\dradius = 10$ fm.
-As can be seen in Fig.
-\ref{fig:radiusDependence}, the quantum-mechanical correction factor leads to a significant suppression in the production of those objects whose radius is large compared to that of the source.
+
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of $\langle C_{d} \rangle$ and \btwo, calculated assuming (a.) $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, irrealistic $\dradius = 10$ fm.
+As shown in Fig. \ref{fig:radiusDependence}, $\langle C_{d} \rangle$ suppresses significantly the production of objects with radius larger than the source.
 
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
+\includegraphics[width=.8\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
 \caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
@@
 
-Following the approach and discussion presented in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as
+Following the discussion in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as
 
 \begin{equation}
-\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
+\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)} \;\; .
 \label{eq:CA_general}
@@
 %
-for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
-Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 in~\cite{Scheibl:1998tk}.
-In particular, for the case of \hethree~with $A=3$ and $J=1/2$, the latter becomes the Eq. 9 presented in~\cite{Blum:2017qnn}.
+Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 of~\cite{Scheibl:1998tk}.
+For the case of \hethree, the latter becomes Eq. 9 of~\cite{Blum:2017qnn}.
 
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.
-6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:
+In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see next section) and by combining Eq.
+6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain:
 
 \begin{equation}
-	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;\; .
+	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;.
 \end{equation}
 
-\noindent This formula can be used to compare the predicted $B_{A}$ with experimental data directly.
+\noindent This general formula can be used to compare the predicted $B_{A}$ with data directly.
 
- We understand the relation between $B_A$ and the radii as follows: for small radii of the source, as $R \rightarrow 0$, the coalescence probability appears to be anti-proportional to the harmonic oscillator size parameter $r_A$, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
+For small sources, as $R \rightarrow 0$, the coalescence probability is anti-proportional to the harmonic oscillator size parameter, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
 Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
-For a large source volume, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, and thus decreases for large distances in configuration space.
+For a large source, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space.
 
@@
 \begin{center}
-\includegraphics[width=.8\columnwidth]{../HbtRadiusParam.png}
+\includegraphics[width=\columnwidth]{../HbtRadiusParam.png}
 \caption{Parameterisation A of the dependence of the source radius on multiplicity compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
@@
 The necessity of introducing a second parameterisation for the radius might suggest that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered in parameterisation A, but by a slightly larger system as from parameterisation B.
-
-%\begin{figure*}[htbp]
-%	\begin{center}
-%		\includegraphics[width=\textwidth]{../radiiParamCompareData.png}
-%		\caption{Comparison of the ALICE data from~\cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation A, fitted to the HBT radii, (right panels) the parameterisation B, tuned to the \btwo~values in central Pb-Pb collisions.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-%		\label{fig:CompareB2B3forDifferentParamWithData}
-%	\end{center}
-%\end{figure*}
 

### 2018-09-27 FrascatiPlot/Paper/aps/table1.tex
Axe keeps falling...

@@
                                    & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
-                                   A = 4  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
-                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
-                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1    &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
-                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]
-
+                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]
 \end{tabular}
@@
 
-\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$.
+\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 3$.
 $B_{E}$ is the binding energy in MeV, $J_{A}$ is the spin.

### 2018-09-27 FrascatiPlot/Paper/aps/main.tex
Axe keeps falling...before pizza

@@
 \label{SecSourceVolume}
-We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}. 
-This volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
-The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-We identify $\rperp = R_{side}$ as well as $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
+We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}, and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
+Experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
+We identify $\rperp = R_{side}$, $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
 
-Experimentally, the size of the effective volume can be controlled by selecting different collision geometries, i.e.
-different centrality classes \cite{Abelev:2013qoq}.
-In heavy-ion collisions the HBT radii are known to scale with the cubic root of the average charged-particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and to depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
+Experimentally, $R$ can be controlled by selecting different collision geometries, i.e. different centrality classes \cite{Abelev:2013qoq}. 
+The HBT radii scale with the cubic root of the average charged-particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
 We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study, but we derive the radii from the measured \avdNdeta~according to the following relation:
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study, but we derive$R$ from the measured \avdNdeta~according to the following:
 
@@
 
-The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
+The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, as shown in Fig. \ref{fig:radiiparam}. 
 The values we obtain by interpolating the geometric mean of the measured radii are consistent with the radii from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radii from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
-The highest $k_{\mathrm{T}}$ bin was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii for such a study, but given that these measurements are not  available in all collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.
-We acknowledge that a model-based scaling factor is proposed by \cite{Kisiel:2014upa}, which alternatively could be considered.
+The highest $k_{\mathrm{T}}$ was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
+Ideally, one would use the proton femtoscopic radii, but given the unavailability of these measurements in every collision system and centrality, we assume that $m_{\mathrm{T}}$-scaling holds\cite{Adam:2015vja}.
 
@@
 
-In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-At the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
-In contrast to the coalescence approach, the statistical-thermal model \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp} provides only \pt-integrated yields. 
-Therefore, \pt~spectra have been modelled using a blast-wave~\cite{Schnedermann:1993ws} parameterization.
-When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave
-are fixed to the values obtained from the simultaneous fit to the pion, kaon and proton spectra measured in Pb--Pb collisions as a function of centrality by ALICE~\cite{Abelev:2013vea}. 
-The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{Abelev:2013vea}.
-This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model predictions at the LHC~\cite{Abelev:2012wca}.
-In the case of hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
-Based on the spectra obtained in this way, we calculate the corresponding coalescence parameters for a given \pt/$A$ and compare it with coalescence expectations.
+In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
+At the LHC, the chemical potentials which ensure the conservation of baryon number, strangeness, and electric charge are negligible.
+In contrast to coalescence, the statistical-thermal models provide only \pt-integrated yields. 
+We use a blast-wave~\cite{Schnedermann:1993ws} parameterization to model the \pt-dependence, with parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in Pb--Pb collisions by ALICE~\cite{Abelev:2013vea}.
+The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the measured pion yield~\cite{Abelev:2013vea}.
+This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model~\cite{Abelev:2012wca}.
+For hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
+With the resulting spectra, we calculate \bA~for a given \pt/$A$ and compare it with coalescence expectations. 
 We use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
@@
 The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter.
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.
+We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production as compact quark bags~\cite{Andronic:2017}.
 
@@
 
-Data on anti- and hyper-nuclei production at the LHC in different collision systems have been released by the ALICE Collaboration in centrality/multiplicity classes \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}.
-To facilitate the comparison with multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the data in \cite{ALICE:nucleipp2017}, given for inelastic pp collisions, by the ratio of \avdNdeta~in these two event classes \cite{Adam:2015gka}.
-In order to map the \avdNdeta~to the source size we first used the parameterisation (labeled as ``A'') from the fit to the HBT data shown in Fig.~\ref{fig:radiiparam}. 
-We found a discrepancy between the coalescence volume from parameterisation A and the curve from the coalescence calculation.
+Multiplicity-differential data on anti- and hyper-nuclei production at the LHC have been released by ALICE \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}. 
+To facilitate the comparison with multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the inelastic pp collision data in \cite{ALICE:nucleipp2017} by the ratio of \avdNdeta~in these two event classes \cite{Adam:2015gka}.
+In order to map \avdNdeta~to the source size we first used the parameterisation (labeled as ``A'') from the fit to the HBT data shown in Fig.~\ref{fig:radiiparam}. 
+When comparing to data, we found a discrepancy between the coalescence volume from parameterisation A and the coalescence curve. 
 In particular, the model would require a larger radius for a given value of \btwo~in Pb--Pb collisions.
-In a second step we tuned the parameterisation (labeled as ``B'') such that the data points for (anti-)deuterons fall onto the coalescence prediction, finding the values $a = 0.473$ and $b = 0$ for the parameters of Eq.~\ref{eq:radiusParameterisation}.
+In a second step we tuned the parameterisation (labeled as ``B'') such that the data points for (anti-)deuterons fall onto the coalescence prediction, finding the values $a = 0.473$ and $b = 0$ for Eq.~\ref{eq:radiusParameterisation}.
 
-With parameterisation B, we investigate the agreement of the model with the measured \bthree\ for \hethree.
-Thus the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the coalescence volume is the same for all anti- and hyper-nuclei.
-The necessity of introducing a second parameterisation for the radius might suggest that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered in parameterisation A, but by a slightly larger system as from parameterisation B.
+With parameterisation B, we compare models to data, thus constraining the coalescence volume with the more differential (anti-)deuteron data and assuming that it is the same for all anti- and hyper-nuclei.
+The necessity of introducing a second parameterisation might suggest that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT radius considered in parameterisation A, but by a slightly larger system as from parameterisation B.
 

### 2018-09-27 FrascatiPlot/Paper/aps/table1.tex
Axe keeps falling...before pizza

@@
 \begin{tabular}{cccccccc}\\[-2ex]
-Mass number & Nucleus &  Composition  & $B_{E}$ (MeV)   &  $J_{A}$ & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
+Mass number & Nucleus &  Composition  & Binding energy (MeV)   &  Spin & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
 \\[0.5ex] \hline \\[-2ex]
@@
 \caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 3$.
-$B_{E}$ is the binding energy in MeV, $J_{A}$ is the spin.
-The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius.
+The nucleus size is given in terms of the (charge) rms radius of the wave-function, \rmsradius.
 The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced.
-Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
-Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
- %References are given in the last column.}
-%. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.
+The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted from $\rmsradius^{meas}$  according to $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+We assume $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
 \label{tab:nucleusradii}

### 2018-09-27 FrascatiPlot/B2vsVolume.C
change aspect ratio of figures

@@ -1,7 +1,7 @@
 /*
    akalweit@cern.ch, fbellini@cern.ch
    17.01.2018 - The Frascati plot
-   last update: 26.09.2018
+   last update: 27.09.2018
 */
 #include "TMath.h"
 #include "TGraphAsymmErrors.h"
@@ -291,10 +291,10 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   
   gStyle->SetOptStat(0);
   gStyle->SetOptTitle(0);
-  gStyle->SetPadTopMargin(0.02);
+  gStyle->SetPadTopMargin(0.03);
   gStyle->SetPadBottomMargin(0.15);
-  gStyle->SetPadLeftMargin(0.17);
-  gStyle->SetPadRightMargin(0.02); 
+  gStyle->SetPadLeftMargin(0.15);
+  gStyle->SetPadRightMargin(0.05); 
 
   // ------------------
   // make the figure with coalescence only
@@ -713,30 +713,33 @@ void MakePaperFigure2(Bool_t plotLinX, Double_t pToA,
   //
   TCanvas * coalcanv;
   if (plotvert) {
-    coalcanv = new TCanvas("coalcanv", "coalescence", 500, 1000);
+    coalcanv = new TCanvas("coalcanv", "coalescence", 800, 800);
     coalcanv->Divide(1,2);
   } else {
     coalcanv = new TCanvas("coalcanv", "coalescence", 1600, 700);
     coalcanv->Divide(2,1);
   }
   coalcanv->SetBottomMargin(0.1);
-  coalcanv->SetTopMargin(0.02);
-  coalcanv->SetLeftMargin(0.17);
+  coalcanv->SetTopMargin(0.03);
+  coalcanv->SetLeftMargin(0.15);
   coalcanv->SetRightMargin(0.02);
 
   TH2D * frame_cd = new TH2D("frame_cd", "#LTC_{d}#GT vs radius; #it{R} (fm); #LT#it{C}_{d}#GT", 1000, 0.01, 6.0, 2e5, 0, 1.2);
-  frame_cd->GetXaxis()->SetTitleSize(0.06);
-  frame_cd->GetYaxis()->SetTitleSize(0.06);
[…]

### 2018-09-27 FrascatiPlot/HbtRadii.C

@@ -24,7 +24,7 @@ void HbtRadii() {
   gStyle->SetPadBottomMargin(0.15);
   gStyle->SetPadTopMargin(0.05);
 
-  TCanvas * canvHbtPlot = new TCanvas("canvHbtPlot","canvHbtPlot");
+  TCanvas * canvHbtPlot = new TCanvas("canvHbtPlot","canvHbtPlot", 800, 600);
   TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{N}_{ch}/d#it{#eta}#GT^{1/3}; #it{R} (fm)",200,0.0,13.0,200,0.0,6.0);
   histFrame->GetXaxis()->SetTitleSize(0.06);
   histFrame->GetXaxis()->SetLabelSize(0.045);

### 2018-09-28 FrascatiPlot/B2vsVolume.C
Updated figure 1 to acocunt for new aspect ratio for PRL

@@ -66,7 +66,7 @@ void MakeUp(TGraphErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Sty
 void MakeUp(TGraphAsymmErrors* obj, Color_t color, Color_t Fill_Color, Int_t Fill_Style, Int_t Line_Style, Int_t Line_Width, Int_t Marker_Style, Float_t Marker_Size);
 
 //figure making
-void MakePaperFigure2(Bool_t plotLinX, Double_t pToA,
+void MakePaperFigure1(Bool_t plotLinX, Double_t pToA,
 		      TF1 *Cd_coalescence, TF1* Cd_coalescence_pointlike, TF1* Cd_coalescence_radius1third,  TF1* Cd_coalescence_largeradius,
 		      TGraphErrors * hB2_coalescence, TGraphErrors * hB2_coalescence_pointlike, TGraphErrors * hB2_coalescence_radius1third, TGraphErrors * hB2_coalescence_largeradius, Bool_t plotvert = 1);
 
@@ -299,7 +299,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   // ------------------
   // make the figure with coalescence only
   // ------------------
-  MakePaperFigure2(plotLinX, pToA,
+  MakePaperFigure1(plotLinX, pToA,
 		   Cd_coalescence, Cd_coalescence_pointlike, Cd_coalescence_radius1third, Cd_coalescence_largeradius,
 		   hB2_coalescence, hB2_coalescence_pointlike, hB2_coalescence_radius1third, hB2_coalescence_largeradius, kTRUE);
   if (plotOnlyCoalescence) return 0;
@@ -704,92 +704,86 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
 
 
 
-void MakePaperFigure2(Bool_t plotLinX, Double_t pToA,
+void MakePaperFigure1(Bool_t plotLinX, Double_t pToA,
 		      TF1 *Cd_coalescence, TF1* Cd_coalescence_pointlike, TF1* Cd_coalescence_radius1third,  TF1* Cd_coalescence_largeradius,
[…]

### 2018-09-28 FrascatiPlot/Paper/aps/main.tex
3737
Last minor fixes before submission

@@
 
-\input{table1}
-
 For about sixty years, coalescence models have been used to describe the formation of composite objects \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf}.
-Surprisingly, thermal-statistical models have been successful in describing also the production of light (anti-)(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}.
+Surprisingly, thermal-statistical models have been successful in describing also the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}.
 In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV.
@@
 In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile''. 
-For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2 MeV $\ll T_{chem}, T_{kin}$.
+For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2~MeV~$\ll~T_{chem},~T_{kin}$.
 The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
@@
 While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in this letter.
+%
+\begin{table*}[htb]
+\centering
+\begin{ruledtabular}
+\begin{tabular}{cccccccc}\\[-2ex]
+Mass number & Nucleus &  Composition  & Binding energy (MeV)   &  Spin & \rmsradius$^{meas}$~(fm) &  $r_{A}$ (fm) & Refs. 
+\\[0.5ex] \hline \\[-2ex]
+      A = 2  & d                                    & pn                   &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
+      A = 3  & \tritium 	                  & pnn                       &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
+                & \hethree                         & ppn                 &   7.7180428  (23) & 1/2   & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
+                & \hthreelambda               & p$\Lambda$n &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                     &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]
+\end{tabular}
+\end{ruledtabular}
+\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 3$.
+The nucleus size is given in terms of the (charge) rms radius of the wave-function, \rmsradius.
+The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced.
+The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted from $\rmsradius^{meas}$  according to $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+We assume $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
+\label{tab:nucleusradii}
+\end{table*}%
 
-To this purpose, we compare LHC data to models. 
+\indent To this purpose, we compare LHC data to models. 
 For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system- and object-size. 
@@
 However, as ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the comparison with the hyper-nuclei proposed here.
-We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the LHC Run 3 \& 4, in order to discriminate the aforementioned scenarios.
+We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the High-Luminosity LHC, in order to discriminate the aforementioned scenarios.
 
 \section{Coalescence approach} \label{sec:coalescence}
-
 In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963,Kapusta:1980}. 
@@
 \begin{equation}
-E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right..
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.,
 \label{eq:BA}
@@
 Consequently, the anti-particle to particle ratio for (hyper-)nuclei is consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
-
 In a simple coalescence approach, \bA~is expected to be independent of momentum and of the object size relative to the volume of particle emission (hereafter referred to as ``source volume'' or ``size'').
@@
 For deuterons, $\langle C_{d} \rangle$ has been approximated as
-
+%
 \begin{equation}
@@
 If we assume that  $\rperp \approx \rpar \approx R$, Eqs. \ref{eq:Cd} and \ref{eq:B2cd} simplify to 
-
+%
 \begin{equation}
@@
 %
-
 Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of $\langle C_{d} \rangle$ and \btwo, calculated assuming (a.) $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, irrealistic $\dradius = 10$ fm.
@@
 
-\begin{figure}[ht]
+\begin{figure}[hb]
 \begin{center}
-\includegraphics[width=.8\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
-\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
+\includegraphics[width=\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
+\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (top, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (bottom, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
 The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
@@
 Following the discussion in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as 
-
+%
 \begin{equation}
@@
 In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see next section) and by combining Eq.
-6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain:
-
+6.2 in \cite{Scheibl:1998tk} and our Eq.~\ref{eq:CA_general}, we obtain:
+%
 \begin{equation}
@@
 \end{equation}
-
-\noindent This general formula can be used to compare the predicted $B_{A}$ with data directly.
+%
+This general formula can be used to compare the predicted $B_{A}$ with data directly.
 
@@
 For a large source, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space. 
+%
 
-\subsection{Source volume}
-\label{SecSourceVolume}
+\section{Source volume} \label{SecSourceVolume}
 We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}, and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
@@
 We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study, but we derive$R$ from the measured \avdNdeta~according to the following:
-
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study, but we derive $R$ from the measured \avdNdeta~according to the following:
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, as shown in Fig. \ref{fig:radiiparam}. 
@@
 The highest $k_{\mathrm{T}}$ was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii, but given the unavailability of these measurements in every collision system and centrality, we assume that $m_{\mathrm{T}}$-scaling holds\cite{Adam:2015vja}.
+Ideally, one would use the proton femtoscopic radii, but given the unavailability of these measurements in every collision system and centrality, we assume that $m_{\mathrm{T}}$-scaling holds~\cite{Adam:2015vja}.
 
@@
 \section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
-
 In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
@@
 The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter.
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light (anti-)(hyper-)nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production as compact quark bags~\cite{Andronic:2017}.
+We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light \mbox{(anti-)(hyper-)}nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production as compact quark bags~\cite{Andronic:2017}.
 
@@
 
-\section{Comparison with data}
-
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
-For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
-For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
-For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2.
-The limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
-Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
-The difference between data and the coalescence model is about 6$\sigma$,
-albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
-In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons. 
-A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
-
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity in order to distinguish between the two production scenarios.
-In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.
-\ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities.
-This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
-The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
  \begin{figure}[ht]
@@
 
+\section{Comparison with data}
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
+For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
+For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
+For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2.
+The limited amount of data currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
+Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
+The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
+The difference between data and the coalescence model is about 6$\sigma$,
+albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
+In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through coalescence of $\Lambda$s and deuterons. 
+A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
+
+Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity in order to distinguish between the two production scenarios.
+In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.
+\ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities.
+This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
+The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
+
 \section{Conclusions and outlook}
@@
 In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
-The very limited amount of currently available data favours the thermal model prediction within our assumptions.
+The very limited amount of data available favours the thermal model prediction within our assumptions.
 	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects.
@@
 \end{enumerate}
-
 As our study is deliberately based on simplified assumptions that allow for a completely analytical treatment of the problem, future studies should be based on more realistic approximations (in particular the wave-function), which require numerical calculations.
@@
 
-In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872)~\cite{Esposito:2015fsa, Cho:2017dcy}.
-In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}.
-Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-The upcoming high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of \mbox{(anti-)}(hyper-)nuclei production.
+In a follow-up publication, we plan to extend our study to $A=4$ systems and to more exotic QCD objects like the X(3872)~\cite{Esposito:2015fsa, Cho:2017dcy}. 
+If the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}.
+Thus, its possible production via coalescence in pp collisions would be subject to a similar suppression as the hyper-triton.
+The upcoming high-luminosity phase of the LHC, where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of \mbox{(anti-)}(hyper-)nuclei production.
 Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.

### 2018-12-10 FrascatiPlot/Paper/aps/main.tex
Changes for first submission to PRL

@@
 Their size is typically defined as the rms of their (charge) wave-function, corresponding to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ with respect to the two other nucleons.
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ relative to the two other nucleons.
 The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
@@
 Surprisingly, thermal-statistical models have been successful in describing also the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}.
-In this approach, particles are produced from a fireball in thermal and kinetic equilibrium with temperatures of the order of $T_{chem} \approx$ 156 MeV.
+In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV.
 Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
-Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that can affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
+Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
 Once the mean free path for elastic collisions is larger than the system size, the fireball freezes-out kinetically at $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}.
@@
 Similarly, the elastic cross-section driving deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-The deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase, yet their production is measured to be consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+Deuterons produced at chemical freeze-out are not expected to survive the hadronic phase, yet their measured production is consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc}.
+Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
 Data from rescattering of short-lived hadronic resonances suggest a long-lasting hadronic phase \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
@@
 The nucleus size is given in terms of the (charge) rms radius of the wave-function, \rmsradius.
-The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms,  \rmsradius$^{meas}$~(fm), is approximately reproduced.
+The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen to approximately reproduce the measured/expected rms,  \rmsradius$^{meas}$~(fm).
 The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted from $\rmsradius^{meas}$  according to $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
@@
 \indent To this purpose, we compare LHC data to models. 
-For the first time, these data allow for the systematic study of the light (anti-)(hyper-)nuclei production as a function of the system- and object-size. 
+For the first time, these data allow for the study of \mbox{(anti-)(hyper-)nuclei} production as a function of the system- and object-size. 
 A quantitative comparison of the two scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-However, as ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the comparison with the hyper-nuclei proposed here.
-We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample foreseen at the High-Luminosity LHC, in order to discriminate the aforementioned scenarios.
+As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the comparison with hyper-nuclei proposed here.
+In order to discriminate the aforementioned scenarios, we propose a systematic measurement of the coalescence parameter in all collision systems at the High-Luminosity LHC.
 
@@
 %
-where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energies.
+where $p_{\mathrm{p,n}}$ are the proton and neutron momenta and $E_{p,n}$ their energies.
 %
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{../theory_coalescence_Cd_B2_vert.png}
+\includegraphics[width=\columnwidth]{theory_coalescence_Cd_B2_vert.png}
 \caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (top, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (bottom, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
@@
 \section{Source volume} \label{SecSourceVolume}
-We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons, as in \cite{Scheibl:1998tk}, and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
-Experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation.
-We identify $\rperp = R_{side}$, $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
-
-Experimentally, $R$ can be controlled by selecting different collision geometries, i.e. different centrality classes \cite{Abelev:2013qoq}. 
+We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons (as in \cite{Scheibl:1998tk}) and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
+To match the Bertsch-Pratt parameterisation ($R_{out}, R_{side}, R_{long}$) employed by experiments, with the Yano-Koonin-Podgoretskii (\rperp, \rpar, $R_{0}$) parameterisation used in the coalescence model,  we identify $\rperp = R_{side}$, $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
+%
+Experimentally, $R$ can be controlled by selecting different collision geometries, i.e. different centralities \cite{Abelev:2013qoq}. 
 The HBT radii scale with the cubic root of the average charged-particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
 We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study, but we derive $R$ from the measured \avdNdeta~according to the following:
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study. We derive $R$ from the measured \avdNdeta~according to
 %
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{../HbtRadiusParam.png}
+\includegraphics[width=\columnwidth]{HbtRadiusParam.png}
 \caption{Parameterisation A of the dependence of the source radius on multiplicity compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
@@
 	\begin{center}
-		\includegraphics[width=.95\columnwidth]{../compareThermalAndCoalescence.png}
+		\includegraphics[width=.95\columnwidth]{compareThermalAndCoalescence.png}
 		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper panel), \hethree\ (middle panel) and \hthreelambda\ (lower panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
@@
 \section{Comparison with data}
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available LHC data for (anti-)(hyper-)nuclei \cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015, Adam:2015yta}
+%(anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} 
+are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
 For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
-For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
-For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2.
-The limited amount of data currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data.
-Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
-The difference between data and the coalescence model is about 6$\sigma$,
-albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
-In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through coalescence of $\Lambda$s and deuterons. 
-A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
+For deuterons, both approaches lead to similar predictions and describe reasonably the data for $R \gtrsim 1.6$ fm. 
+For \hethree, the models exhibit a qualitatively similar $R$-dependence but differ by a factor of about 1.5 to 2. 
+The currently available data are consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on data. 
+Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
+The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but differs by 6$\sigma$ from coalescence, albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
+In \cite{Zhang:2018euf} it is argued that the difference between data and coalescence might be explained by a later formation through coalescence of $\Lambda$s and deuterons. 
+A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda
+%which would significantly enhance the phase space for its production, 
+is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
 
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity in order to distinguish between the two production scenarios.
-In the case of \hthreelambda~we have considered also a prediction from coalescence for a wider wave-function (dashed line in bottom right panel of Fig.
+Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing $R$, underlining the need for additional multiplicity-differential data to distinguish between the two production scenarios.
+For \hthreelambda~we considered also a prediction from coalescence for a wider wave-function (see Fig.
 \ref{fig:CompareThermalAndCoalescence}), which results in even lower production probabilities.
-This behaviour highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production via precise measurements of the coalescence parameter as a function of the source volume.
-The curves presented here also explicitly allow for an estimate of the expected hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to the production of \hethree, thus making this measurement a prime candidate for future experimental studies.
+This behaviour highlights the unique potential to constrain the wave-function of (hyper-)nuclei via precise measurements of the $R$-dependent coalescence parameter.
+The curves presented here explicitly allow for an estimate of the hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to that of \hethree, making this measurement a prime candidate for future experimental studies.
 
@@
 \begin{enumerate}
-	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on d, $\bar{\mathrm{d}}$~production in central Pb--Pb collisions at the LHC.
-	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume.
-In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree.
+	\item For the production of $A=2$ and $A=3$ \mbox{(anti-)nuclei} in heavy-ion collisions, thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on d, $\bar{\mathrm{d}}$~production in central Pb--Pb collisions.
+	\item For the production of hyper-triton, thermal and coalescence models give very different predictions as a function of source volume.
+In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to \hethree.
 The very limited amount of data available favours the thermal model prediction within our assumptions.
@@
 As our study is deliberately based on simplified assumptions that allow for a completely analytical treatment of the problem, future studies should be based on more realistic approximations (in particular the wave-function), which require numerical calculations.
-Moreover, it will be interesting to explore further the \pt~dependence of the observations made here.
-
-In a follow-up publication, we plan to extend our study to $A=4$ systems and to more exotic QCD objects like the X(3872)~\cite{Esposito:2015fsa, Cho:2017dcy}. 
+We plan to extend our study to explore further the \pt~dependence as well as to investigate $A=4$ systems and more exotic QCD objects like the X(3872)~\cite{Esposito:2015fsa, Cho:2017dcy}. 
 If the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}.
 Thus, its possible production via coalescence in pp collisions would be subject to a similar suppression as the hyper-triton.
-The upcoming high-luminosity phase of the LHC, where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of \mbox{(anti-)}(hyper-)nuclei production.
+The upcoming high-luminosity phase of the LHC
+%, where $A = 4$ (hyper-)nuclei and other rare composite objects will become experimentally accessible, 
+will provide a unique opportunity for the final understanding of \mbox{(anti-)(hyper-)nuclei} production.
 Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.

### 2018-12-11 FrascatiPlot/B2vsVolume.C
Update to macros

@@ -29,8 +29,8 @@ TGraphAsymmErrors * getBlastB2_PbPb502TeV(Bool_t plotSys = 0, Double_t pToA = 0.
 TGraphAsymmErrors * getBlastB2_pPb502TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 TGraphAsymmErrors * getBlastB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
 
-TGraphAsymmErrors * getBlastB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
-TGraphAsymmErrors * getBlastB3_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
+TGraphAsymmErrors * getBlastB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphAsymmErrors * getBlastB3_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
 
 TGraphAsymmErrors * getBlastB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1.0, Int_t paramSet = 0);
 TGraphAsymmErrors * getBlastB3Lambda_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1.0, Int_t paramSet = 0);
@@ -53,10 +53,10 @@ TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t pa
 TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
 
 //helium-3
-TGraphErrors      * getB3_PbPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
-TGraphErrors      * getB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0);
[…]

### 2018-12-11 FrascatiPlot/GetB3inpToA.C

@@ -2,7 +2,7 @@ void GetB3inpToA_PbPb5TeV();
 void GetB3inpToA_PbPb276TeV();
 void GetB3inpToA_pp7TeV();
 void GetB3LambdainpToA_PbPb276TeV();
-void GetB3inpToA_pPb5TeV(Double_t pToA = 0.733);
+void GetB3inpToA_pPb5TeV(Double_t pToA = 0.900);
 void GetB3inpToA_pPb5TeV_inelg0(Double_t pToA = 0.733);
 
 void GetB3inpToA_pp7TeV()

### 2018-12-11 FrascatiPlot/MakeYRfigure.C

@@ -11,6 +11,7 @@ void ConfigThreePanelsPad(TPad* pad1, TPad* pad2, TPad* pad3, Float_t leftmargin
 //pseudodata
 TGraphErrors * GetPseudoBAvsMulti(TString particle = "deuteron",  Int_t paramSet = 1);
 TGraphErrors * GetPseudoBAvsMultiUnc(TString particle = "deuteron",  Int_t paramSet = 1, Color_t color = 0);
+TGraphErrors * GetMeasBAvsMultiUnc(TString particle = "he3",  Int_t paramSet = 1, Color_t color = kGreen+2);
 
 //main
 void MakeYRfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t pToAb4 = 0.75, Double_t pToAb4Lambda = 0.62, Bool_t plotPseudoData = 1)
@@ -28,6 +29,7 @@ void MakeYRfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t
 
   Color_t projCol = kRed+1;
   Double_t Rmin = 0.01; Double_t Rmax = 6.5;
+  
   //------------------------------
   // Pseudodata
   //------------------------------
@@ -41,10 +43,18 @@ void MakeYRfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t
   TGraphErrors * gPseudo3LambdaHUnc = (TGraphErrors *) GetPseudoBAvsMultiUnc("hyperH3", 1, projCol);
   TGraphErrors * gPseudo4HeUnc = (TGraphErrors *) GetPseudoBAvsMultiUnc("he4", 1, projCol);
   TGraphErrors * gPseudo4LambdaHUnc = (TGraphErrors *) GetPseudoBAvsMultiUnc("hyperH4", 1, projCol);
-  gPseudo3HeUnc->SetFillStyle(0);
-  gPseudo3LambdaHUnc->SetFillStyle(0);
-  gPseudo4HeUnc->SetFillStyle(0);
-  gPseudo4LambdaHUnc->SetFillStyle(0);
+  gPseudo3HeUnc->SetFillStyle(1001);
+  gPseudo3LambdaHUnc->SetFillStyle(1001);
+  gPseudo4HeUnc->SetFillStyle(1001);
[…]

### 2018-12-11 FrascatiPlot/Make3HepPbPaperFigure.C
Adding macros for pp 13 teV and p-Pb paper with BA vs multi

@@ -1,0 +1,294 @@
+#include "./B2vsVolume.C"
+
+void convertRadiusToMulti(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 1);
+void convertRadiusToMulti(TGraphErrors * graph = 0x0, Int_t paramSet = 1);
+void getMultiFromR(Double_t * multi = NULL, Double_t * radius = NULL, Int_t paramSet = 1);
+void Make3HepPbPaperFigure(Bool_t plotLinX = 0, Double_t pToA = 0.90, Int_t RmappingParam = 1);
+
+  
+void Make3HepPbPaperFigure(Bool_t plotLinX, Double_t pToA, Int_t RmappingParam)
+{
+
+  Int_t ip = RmappingParam;
+
+  //----------------------------
+  //Get data
+  //----------------------------
+  const Int_t nParamSet = 2;
+  TGraphErrors* gB3vsR_pp7TeV[nParamSet];
+  TGraphErrors* gB3vsR_pp7TeV_sys[nParamSet];
+  // TGraphErrors* gB3vsR_pp13TeV[nParamSet];
+  // TGraphErrors* gB3vsR_pp13TeV_sys[nParamSet];
+  TGraphErrors* gB3vsR_pPb502TeV[nParamSet];
+  TGraphErrors* gB3vsR_pPb502TeV_sys[nParamSet];
+  TGraphErrors* gB3vsR_PbPb276TeV[nParamSet];
+  TGraphErrors* gB3vsR_PbPb276TeV_sys[nParamSet];
+  TGraphErrors* gB3vsR_PbPb502TeV[nParamSet];
+  TGraphErrors* gB3vsR_PbPb502TeV_sys[nParamSet];
+
+  //Thermal + blast-wave
+  TGraphErrors* gB3blastvsR_PbPb276TeV[nParamSet];
+  TGraphErrors* gB3blastvsR_PbPb276TeV_sys[nParamSet];
+  
+  for (Int_t jj = 0; jj < nParamSet; jj++){
+    gB3vsR_pp7TeV[jj] = (TGraphErrors *) getB3_pp7TeVINELg0(kFALSE, 0.8, jj, kFALSE);
+    gB3vsR_pp7TeV_sys[jj] = (TGraphErrors *) getB3_pp7TeVINELg0(kTRUE, 0.8, jj, kFALSE);
[…]

### 2019-02-20 FrascatiPlot/Paper/aps/submit_20022019/replies_to_referee.txt
New version for PRL

Dear Editor and referees,

    we are gratefult for having considered and reviewed our manuscript.
In the following we hope to address your concerns and we provide replies 
to the main issues as well as an updated version of the manuscript.
We do hope that based on our replies, the two referees will reconsider their judgement 
regarding the suitability for publication in PRL. 
At the same time we tried to improve the readability of the paper, which was one of the 
main criticisms of the first referee.
In addition, we shortened the text in order to fit within the word limit.

With kind regards,

     A. Kalweit and F. Bellini

------------------------------------------------------------------------
Replies to referees
------------------------------------------------------------------------
Re: LW16156
    Testing production scenarios for (anti-)(hyper-)nuclei and exotica at
    LHC energies
    by Francesca Bellini and Alexander P. Kalweit

----------------------------------------------------------------------
Report of Referee A -- LW16156/Bellini
----------------------------------------------------------------------

R: I recommend against publication of the manuscript in PRL. The topic is
certainly of interest, although to a small community.

A: We do believe that the paper is of interest for a large community that spans several 
fields of physics: 
- nuclear physics (it addresses special nature of hypertriton and uses state-of the art knowledge 
of nuclear properties)
- heavy-ion physics (it addresses the "anti-nuclei puzzle" as described in the manuscript) 
- hadron spectroscopy (the hypertriton could serve as a test case for new studies on X(3872) and 
hadron-molecule states in general) 
- dark matter searches and astroparticle physics (production mechanisms of anti-nuclei need to be 
understood for the determination of the secondary cosmic ray background for space-based experiments 
like AMS-02, GAPS, ...) 
- nuclear astrophysics (understanding hypernuclei production and properties adds to the study of the 
hyperon-nucleon interactions that are relevant to understand and model the equation of state of 
neutron stars)

R: The techniques are rather standard, and the ideas have been discussed previously.
Non-zero-extent wave functions have been applied to deuteron production, but to my knowledge this is 
the first time I've seen it applied to A>2 coalescence.

R: Unfortunately, the paper is not well written. I had to re-read several
sections numerous times to understand what was meant by the various
formalisms. The model descriptions "thermal", "blast-wave" and
"thermal+blast-wave" seemed to be applied to the same line in Figure 3
depending on what was being read in the manuscript. The ordering of
the various subsections made it hard to follow where the authors were
going, or to discern the main point of the paper.

R: The conclusions were insufficiently compelling to warrant publication
in PRL, even if the paper was rewritten. Stating that one model fit
the data better than another is publishable, but not as a PRL.

R: If the paper was rewritten and submitted to PRC, it would benefit from
a more physical comparison between models. Foregoing the
finite-extent-wave-function corrections, coalescence and thermal
models should provide identical answers apart from a modest Boltzmann
correction, exp(-B/T). Additionally, in this paper, the coalescence
prescription used a Gaussian assumption for the spatial shape of the
phase space density. By comparing the phase space distributions (for a
given momentum) in the blast-wave to that assumed in the coalescence
prescription, one should be able to understand why the two models
differed so greatly in the lower panel of Figure 3. Was the problem
that the shape of the phase space distribution was non-Gaussian, or
was the Gaussian radii incorrect? Aside, I assumed both models used
the same non-zero-extent wave function corrections.

Finally, I list two physics questions the authors should consider
should they rewrite the paper for PRC.

1. Many of the hadrons come from longer-lived decays. How does this
affect the various B_A parameters?

2. For coalescence, the HBT radii used should be those that
characterize the phase space distribution in the pair frame, not the
lab frame. In the pair frame, Rout is larger than Rside by an
additional gamma factor. This could increase the product of the three
radii by nearly a factor of 2.

----------------------------------------------------------------------
Report of Referee B -- LW16156/Bellini
----------------------------------------------------------------------

In this paper the authors study the coalescence model for the
production of light (anti)-nuclei in heavy ion collisions. The authors
emphasize the special role of the hyper triton since, due to it every
small separation energy and associated large size, it provides the
most sensitivity for testing the coalescence model. The authors imply
a simple model for the nuclei and use the quantum improved formulas of
Ref. 7 to calculate the coalescence parameter B2 for various system.
They argue, more or less correctly, that a measurement of the
hyper-triton for smaller colliding systems would be very helpful in
testing the coalescence model and/or the structure of the hyper
triton.

In principle this paper would potentially be suitable for PRL is the
following comments are properly addressed:

1) The authors admit that they use a simple (oscillator) model for the
nuclear "wave function" i.e. rms. While this is probably fine for d
and He, it is by no means clear if it will not be misleading for the
hyper-triton. As shown in Ref. 2 the hyper-triton is closer to a
"deuteron"+ weakly bound Lambda than the simple three baryon
oscillator state the authors assume. This is also demonstrated in Ref.
33, where the authors of that paper are able to reproduce the measured
hyper-triton yield by talking into account, in addition to three
baryon coalescence, the deuteron - Lambda coalescence. Incidentally,
the authors of Ref. 33 state that by using p+n+Lambda coalescence only
they get about 50% of the measured hyper-triton yield. The present
paper, on the other hand, seems to be almost a factor of ten below the
data (see Fig. 3). This obvious discrepancy needs to be addressed. In
addition the authors also need to provide an estimate how the
dependence of the source size R changes if one were to include the
aforementioned "deuteron"-Lambda coalescence.

2) The authors concentrate on the system size and argue for
measurements with smaller systems. However, coalescence being a
phasespace effect can equally be tested by looking at the momentum
dependence of B_2. Or in other words, it is known from HBT
measurements the the effective source size (region of homogeneity)
drops with increasing momentum. Thus one would expect that a similar
effect as shown in Fig. 3 should also be seen if one looks at the
momentum dependence of the coalescence parameter B2. The authors need
to discuss this and give credible arguments why the momentum
dependence is less suitable (if this is the case) (Incidentally the
measured pt dependence of the the B2 parameter shows already this
effect)

3) The authors use a blast wave model for to calculate the spectrum
for the thermal model. What are the blast wave parameters used? They
should be provided.

4) In the introduction the authors list three approaches, (a)-(c), to
address the production of light (anti)-nuclei. They miss a fourth, and
likely most realistic one, which has recently been developed by
Oliinychenko et al. (arXiv:1809.03071) In this approach, which was
restricted to deuteron, the destruction and production of deuteron
after chemical freeze out was studied in kinetic theory and the
measured B2 parameters were well reproduced.

5) Section V needs to be rewritten. After reading this several times I
still have no idea what these models A and B are supposed to be. Also,
the average reader will not necessarily know what INEL>0 is supposed
to mean.

### 2019-02-20 FrascatiPlot/Paper/aps/submit_20022019/main_aps.tex
New version for PRL

--- 2018-12-10 FrascatiPlot/Paper/aps/main.tex
@@
+% ****** Start of file apssamp.tex ******
+%
+%   This file is part of the APS files in the REVTeX 4.1 distribution.
+%   Version 4.1r of REVTeX, August 2010
+%
+%   Copyright (c) 2009, 2010 The American Physical Society.
+%
+%   See the REVTeX 4 README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.1
+%
+% See the REVTeX 4 README file
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex apssamp.tex
+%  2)  bibtex apssamp
+%  3)  latex apssamp.tex
+%  4)  latex apssamp.tex
+%
+\documentclass[%
+ reprint,
+%superscriptaddress,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%showpacs,preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+ amsmath,amssymb,
+ aps,
+%pra,
+%prb,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-1}
+
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+
+\input{./commands.tex}
+
+\begin{document}
+
+\preprint{APS/123-QED}
+
+\title{Testing production scenarios for (anti-)(hyper-)nuclei and exotica at LHC energies}
+
+\author{Francesca Bellini}
+\email{francesca.bellini@cern.ch}
+\author{Alexander P. Kalweit}
+\email{alexander.kalweit@cern.ch}
+\affiliation{European Organisation for Nuclear Research (CERN) \\Geneva, Switzerland}
+
+\date{\today}
+
+\begin{abstract}
+We present a detailed comparison of coalescence and thermal-statistical models for the production of (anti-)(hyper-)nuclei in high-energy collisions.
+For the first time, such a study is carried out as a function of the size of the object relative to the size of the particle emitting source.
+Our study reveals large differences between the two scenarios for the production of objects with extended wave-functions.
+While both models give similar predictions and show similar agreement with experimental data for (anti-)deuterons and (anti-)\hethree\ nuclei, they largely differ in their description of (anti-)hyper-triton production.
+We propose to address experimentally the comparison of the production models by measuring the coalescence parameter systematically for different (anti-)(hyper-)nuclei in different collision systems and differentially in multiplicity.
+Such measurements are feasible with the current and upgraded LHC experiments. 
+Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
+\end{abstract}
+
+%\pacs{Valid PACS appear here}
+%\keywords{(Anti-)nuclei, hyper-triton, coalescence, thermal model}
+
+\maketitle
+
 \section{Introduction} 
@@
 For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ relative to the two other nucleons.
+This difference in the wave-functions results in dramatic consequences for the production scenarios, as discussed in the following.
 The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
@@
 For about sixty years, coalescence models have been used to describe the formation of composite objects \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf}.
-Surprisingly, thermal-statistical models have been successful in describing also the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}.
+Surprisingly, thermal-statistical models have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}.
 In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV.
@@
 For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2~MeV~$\ll~T_{chem},~T_{kin}$.
-The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Similarly, the elastic cross-section driving deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn}.
-Deuterons produced at chemical freeze-out are not expected to survive the hadronic phase, yet their measured production is consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}.
+Similarly, the elastic cross-section driving deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}
+(Anti-)nuclei produced at chemical freeze-out are not expected to survive the hadronic phase, yet their measured production is consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc, Puccio:2019oyd}.
+Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, (c.) the continuous interplay of breakup and formation reactions resulting in the coincidence of thermal and kinetic equilibration \cite{Oliinychenko:2018ugs, Xu:2018jff}, (d.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
 Data from rescattering of short-lived hadronic resonances suggest a long-lasting hadronic phase \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
-While hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei yields with statistical-thermal model predictions, hypothesis (c.) is scrutinised in this letter.
+Hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei yields with statistical-thermal model predictions.
+Calculations for (c.) are currently available only for deuterons.
+Hypothesis (d.) is scrutinised in this letter.
+To this purpose, we propose a new method to compare models that also allows for a direct comparison with LHC data. 
 %
@@
                 & \hethree                         & ppn                 &   7.7180428  (23) & 1/2   & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                & \hthreelambda               & p$\Lambda$n &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                     &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]
+                & \hthreelambda               & p$\Lambda$n &    0.13 $\pm$ 0.05  \footnote{For hypertriton, we report here the separation energy of the $\Lambda$ from the two other nucleons.} & 1/2  &  4.9 --  10.0                     &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]
 \end{tabular}
@@
 \label{tab:nucleusradii}
-\end{table*}%
+\end{table*}
 
-\indent To this purpose, we compare LHC data to models. 
-For the first time, these data allow for the study of \mbox{(anti-)(hyper-)nuclei} production as a function of the system- and object-size. 
-A quantitative comparison of the two scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the comparison with hyper-nuclei proposed here.
-In order to discriminate the aforementioned scenarios, we propose a systematic measurement of the coalescence parameter in all collision systems at the High-Luminosity LHC.
+\indent For the first time, LHC data allow for the study of \mbox{(anti-)(hyper-)nuclei} production as a function of the system- and object-size. 
+A quantitative comparison of the production scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
+As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters proposed here.
 
@@
 %
-The LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
-Consequently, the anti-particle to particle ratio for (hyper-)nuclei is consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
-In a simple coalescence approach, \bA~is expected to be independent of momentum and of the object size relative to the volume of particle emission (hereafter referred to as ``source volume'' or ``size'').
+The LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is equal at midrapidity \cite{Abbas:2013rua}.
+Consequently, the anti-particle to particle ratio for \mbox{(hyper-)nuclei} is consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
+In a simple coalescence approach, \bA~is expected to be independent of momentum and of the object size relative to the volume of particle emission (hereafter referred to as ``source size'').
 While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
@@
 We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with more realistic wave-functions, e.g.
-the Hulthen parameterisation for deuterons \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for hyper-tritons as done only for central collisions in~\cite{Zhang:2018euf}.
+the Hulthen parameterisation for deuterons \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for hyper-tritons as done in~\cite{Zhang:2018euf, Sun:2018mqq}.
 
@@
 \section{Comparison with data}
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available LHC data for (anti-)(hyper-)nuclei \cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015, Adam:2015yta}
-%(anti-)deuterons, \mbox{(anti-)}\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} 
-are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available LHC data for (anti-)(hyper-)nuclei \cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015, Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
 For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
@@
 In \cite{Zhang:2018euf} it is argued that the difference between data and coalescence might be explained by a later formation through coalescence of $\Lambda$s and deuterons. 
-A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda
-%which would significantly enhance the phase space for its production, 
-is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
+A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda~is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
 
@@
 Ideally, such measurements are accompanied by systematic measurements of the HBT radii in the same multiplicity/centrality classes and collision systems.
+	\item Our findings suggest a clear experimental path to be pursued with high-precision measurements at the upcoming phase of the LHC in the next ten years, which will finally provide sufficient integrated luminosity for the studies proposed here \cite{Citron:2018lsq}.
+% will provide a unique opportunity for the final understanding of \mbox{(anti-)(hyper-)nuclei} production.
+
 \end{enumerate}
@@
 Thus, its possible production via coalescence in pp collisions would be subject to a similar suppression as the hyper-triton.
-The upcoming high-luminosity phase of the LHC
-%, where $A = 4$ (hyper-)nuclei and other rare composite objects will become experimentally accessible, 
-will provide a unique opportunity for the final understanding of \mbox{(anti-)(hyper-)nuclei} production.
 Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
+
+\begin{acknowledgments}
+We would like to thank Kfir Blum for inspiring this work.
+We thank U.
+Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
+We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
+In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Marco Van Leuween, Maximiliano Puccio, Roman Lietava, Natasha Sharma and the colleagues from the ALICE Collaboration for their valuable input.
+\end{acknowledgments}
+
+\bibliography{main_aps}
+\end{document}

### 2019-02-20 FrascatiPlot/Paper/aps/submit_20022019/main_aps.tex
Üpdate

@@
 A quantitative comparison of the production scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters proposed here.
+As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters propose d here.
 
@@
 
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see next section) and by combining Eq.
-6.2 in \cite{Scheibl:1998tk} and our Eq.~\ref{eq:CA_general}, we obtain:
+In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} and by combining Eq. 6.2 in \cite{Scheibl:1998tk} with our Eq.~\ref{eq:CA_general}, we obtain:
 %
@@
 Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
-For a large source, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space. 
+For a large source where $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space. 
 %

### 2019-02-21 FrascatiPlot/Paper/aps/submit_20022019/main_aps.tex
Üpdate

@@
 
-\section{Source volume} \label{SecSourceVolume}
-We identify the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons (as in \cite{Scheibl:1998tk}) and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry.
-To match the Bertsch-Pratt parameterisation ($R_{out}, R_{side}, R_{long}$) employed by experiments, with the Yano-Koonin-Podgoretskii (\rperp, \rpar, $R_{0}$) parameterisation used in the coalescence model,  we identify $\rperp = R_{side}$, $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.
-%
-Experimentally, $R$ can be controlled by selecting different collision geometries, i.e. different centralities \cite{Abelev:2013qoq}. 
-The HBT radii scale with the cubic root of the average charged-particle multiplicity density \avdNdeta$^{1/3}$ \cite{Adam:2015vna}, and depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$ \cite{Aamodt:2011mr}.
-We make the simplifying assumption that the scaling with \avdNdeta$^{1/3}$ holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015pya}.
-In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study. We derive $R$ from the measured \avdNdeta~according to
+\section{Statistical-thermal approach combined with blast-wave}\label{sec:thermal}
+In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
+At the LHC, the chemical potentials which ensure the conservation of baryon number, strangeness, and electric charge are negligible.
+The thermal model implements eigenvolume corrections by fixing the object radius as an external parameter.
+We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light \mbox{(anti-)(hyper-)}nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production as compact quark bags~\cite{Andronic:2017}.
+
+In contrast to coalescence, the statistical-thermal models provide only \pt-integrated yields. 
+Therefore, we use in addition a blast-wave~\cite{Schnedermann:1993ws} parameterization to model the \pt-dependence, with parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in Pb--Pb collisions by ALICE for several centralities~\cite{Abelev:2013vea}.
+ As discussed in the following section, centrality-dependent parameters allow one to extract spectral distributions for a given source size. 
+The object size does not enter in the formulation of the blast-wave model.
+
+The normalisation of the resulting spectra is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg implementation of the statistical-thermal model with $T_{chem} = 156$ MeV, multiplied by the measured pion yield~\cite{Abelev:2013vea}.
+This choice, as opposed to using the ratio to protons, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model~\cite{Abelev:2012wca}.
+For hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
+With the resulting spectra, we calculate \bA~for a given \pt/$A$ and compare it with coalescence expectations. 
+In the following, we label this model as ``thermal+blast-wave''.
+
+\section{Mapping event multiplicity into source size} \label{sec:radiiParamet}
+In order to compare the source radius-dependent predictions from coalescence with the centrality-dependent data and with predictions from the thermal+blast-wave model, we map the average charged particle multiplicity density (\avdNdeta) in each centrality (or multiplicity) event class into the system size.
+Experimentally, the source size can be controlled by selecting different collision geometries, i.e. different centralities \cite{Abelev:2013qoq}. 
+This mapping is based on the following parameterisation:
 %
 \begin{equation}
-R = a \avdNdeta^{1/3} + b \;\;.
+R = a \avdNdeta^{1/3}\;\;
 \label{eq:radiusParameterisation}
@@
 %
-The coefficients, $a = 0.339$ and $b = 0.128$ (in units of fm), have been determined by fitting linearly the ALICE data, as shown in Fig. \ref{fig:radiiparam}. 
-The values we obtain by interpolating the geometric mean of the measured radii are consistent with the radii from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radii from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.9$ \GeVc~\cite{Adam:2015vna}.
-The highest $k_{\mathrm{T}}$ was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii, but given the unavailability of these measurements in every collision system and centrality, we assume that $m_{\mathrm{T}}$-scaling holds~\cite{Adam:2015vja}.
+\noindent where $R$ is the source radius and $a = 0.473$ fm.
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=\columnwidth]{HbtRadiusParam.png}
-\caption{Parameterisation A of the dependence of the source radius on multiplicity compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
-\label{fig:radiiparam}
-\end{center}
-\end{figure}
+The value of the empirical parameter $a$ is obtained by tuning the parameterisation such that the measured (anti-)deuteron \btwo~in the most central \PbPb~class falls onto the coalescence prediction. 
+In this way, we constrain the coalescence volume with the more differential (anti-)deuteron data and assume that it is the same for all anti- and hyper-nuclei. 
+We justify the choice of Eq.~\ref{eq:radiusParameterisation} by identifying the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons (as in \cite{Scheibl:1998tk}) and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry~\footnote{To match the Bertsch-Pratt parameterisation ($R_{out}, R_{side}, R_{long}$) employed by experiments, with the Yano-Koonin-Podgoretskii (\rperp, \rpar, $R_{0}$) parameterisation used in the coalescence model,  we identify $\rperp = R_{side}$, $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.}.
+The HBT radii scale with \avdNdeta$^{1/3}$ and we make the simplifying assumption that this scaling holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015vna,Adam:2015pya}.
+We also note that the HBT radii, and thus also the source size, depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$~\cite{Aamodt:2011mr}. 
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT-data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($\approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($\approx$~5.5~fm)~
+\footnote{For this comparison, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nuclei production.
+Ideally, one would use the proton femtoscopic radii, but given the availability of these measurements in only some of the collision systems and centralities, 
+we assume that $m_{\mathrm{T}}$-scaling holds.}.
 
-\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
-In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-At the LHC, the chemical potentials which ensure the conservation of baryon number, strangeness, and electric charge are negligible.
-In contrast to coalescence, the statistical-thermal models provide only \pt-integrated yields. 
-We use a blast-wave~\cite{Schnedermann:1993ws} parameterization to model the \pt-dependence, with parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in Pb--Pb collisions by ALICE~\cite{Abelev:2013vea}.
-The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the measured pion yield~\cite{Abelev:2013vea}.
-This choice, as opposed to using the ratio to proton, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model~\cite{Abelev:2012wca}.
-For hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
-With the resulting spectra, we calculate \bA~for a given \pt/$A$ and compare it with coalescence expectations. 
-We use the corresponding \avdNdeta~in each class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
-In contrast to the coalescence approach, the object size does not enter in the formulation of the blast-wave model.
-The thermal model on the other hand, implements eigenvolume corrections by fixing the object radius as an external parameter.
-We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light \mbox{(anti-)(hyper-)}nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production as compact quark bags~\cite{Andronic:2017}.
+\section{Comparison with data}
 
-\section{Constraining the source volume with data}\label{sec:radiiParamet}
-
-Multiplicity-differential data on anti- and hyper-nuclei production at the LHC have been released by ALICE \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Acharya:2017dmc, Adam:2015yta}. 
-To facilitate the comparison with multiplicity-dependent data given in the INEL$>$0 class, we have rescaled the inelastic pp collision data in \cite{ALICE:nucleipp2017} by the ratio of \avdNdeta~in these two event classes \cite{Adam:2015gka}.
-In order to map \avdNdeta~to the source size we first used the parameterisation (labeled as ``A'') from the fit to the HBT data shown in Fig.~\ref{fig:radiiparam}. 
-When comparing to data, we found a discrepancy between the coalescence volume from parameterisation A and the coalescence curve. 
-In particular, the model would require a larger radius for a given value of \btwo~in Pb--Pb collisions.
-In a second step we tuned the parameterisation (labeled as ``B'') such that the data points for (anti-)deuterons fall onto the coalescence prediction, finding the values $a = 0.473$ and $b = 0$ for Eq.~\ref{eq:radiusParameterisation}.
-
-With parameterisation B, we compare models to data, thus constraining the coalescence volume with the more differential (anti-)deuteron data and assuming that it is the same for all anti- and hyper-nuclei.
-The necessity of introducing a second parameterisation might suggest that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT radius considered in parameterisation A, but by a slightly larger system as from parameterisation B.
-
- \begin{figure}[ht]
+\begin{figure}[!h]
 	\begin{center}
@@
 		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper panel), \hethree\ (middle panel) and \hthreelambda\ (lower panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
-Parameterisation B has been used to map \avdNdeta~into the radius $R$ of the source.
-The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.}
+The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.
+We have rescaled the inelastic pp collision data in \cite{ALICE:nucleipp2017} to match the so-called INEL$>$0 class by the ratio of \avdNdeta~in these two event classes, see~\cite{Adam:2015gka} for details.
+		}
 		\label{fig:CompareThermalAndCoalescence}
@@
 
-\section{Comparison with data}
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available LHC data for (anti-)(hyper-)nuclei \cite{ALICE:nucleipp2017, ALICE:deuteronppPbPb2015, Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
-For the latter and for data, the radius parameterisation B is used, see Sec.~\ref{sec:radiiParamet}. 
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available LHC data for \mbox{(anti-)(hyper-)nuclei} \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
+For the latter and for data, the radius parameterisation given by Eq.~\ref{eq:radiusParameterisation} is used.
 For deuterons, both approaches lead to similar predictions and describe reasonably the data for $R \gtrsim 1.6$ fm. 

### 2019-02-21 FrascatiPlot/Make3HepPbPaperFigure.C

@@ -3,7 +3,7 @@
 void convertRadiusToMulti(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 1);
 void convertRadiusToMulti(TGraphErrors * graph = 0x0, Int_t paramSet = 1);
 void getMultiFromR(Double_t * multi = NULL, Double_t * radius = NULL, Int_t paramSet = 1);
-void Make3HepPbPaperFigure(Double_t pToA = 0.9, Bool_t plotLinX = 0, Int_t RmappingParam = 1, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0);
+void Make3HepPbPaperFigure(Double_t pToA = 0.9, Bool_t plotLinX = 0, Int_t RmappingParam = 3, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0);
 
   
 void Make3HepPbPaperFigure(Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, 
@@ -216,7 +216,7 @@ void Make3HepPbPaperFigure(Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, 
 
   hB3_coalescenceParam0->Draw("l");
   hB3_coalescenceParam1->Draw("l");
-  //hB3_coalescenceParam3->Draw("l"); 
+  if (RmappingParam==3) hB3_coalescenceParam3->Draw("l"); 
   gB3blastvsR_PbPb276TeV[0]->Draw("lsame");
   
   if (plotPbPb5TeV) {

### 2019-03-12 FrascatiPlot/Paper/aps/submit_12032019/main_aps.tex
New folder and draft for resubmission to PRC

--- 2019-02-21 FrascatiPlot/Paper/aps/submit_20022019/main_aps.tex
@@
 The LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is equal at midrapidity \cite{Abbas:2013rua}.
-Consequently, the anti-particle to particle ratio for \mbox{(hyper-)nuclei} is consistent with unity \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
+Consequently, the anti-particle to particle ratio for \mbox{(hyper-)nuclei} is consistent with unity \cite{ALICE:nucleipp2017, Acharya:2019rgc, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
 In a simple coalescence approach, \bA~is expected to be independent of momentum and of the object size relative to the volume of particle emission (hereafter referred to as ``source size'').
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
+While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, Acharya:2019rgc, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
 The elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
@@
 
-Following the discussion in~\cite{Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as 
+Following the discussion in~\cite{Scheibl:1998tk, Blum:2017qnn}, Eq.~\ref{eq:Cd} may be generalised as 
 %
@@
 %
-Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 of~\cite{Scheibl:1998tk}.
-For the case of \hethree, the latter becomes Eq. 9 of~\cite{Blum:2017qnn}.
-
-In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} and by combining Eq. 6.2 in \cite{Scheibl:1998tk} with our Eq.~\ref{eq:CA_general}, we obtain:
+%Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 of~\cite{Scheibl:1998tk}.
+%For the case of \hethree, the latter becomes Eq. 9 of~\cite{Blum:2017qnn}.
+Under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} and by combining Eq. 6.2 in \cite{Scheibl:1998tk} with our Eq.~\ref{eq:CA_general}, 
+we obtain:
 %
@@
 This general formula can be used to compare the predicted $B_{A}$ with data directly.
-
 For small sources, as $R \rightarrow 0$, the coalescence probability is anti-proportional to the harmonic oscillator size parameter, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
@@
 In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
-At the LHC, the chemical potentials which ensure the conservation of baryon number, strangeness, and electric charge are negligible.
 The thermal model implements eigenvolume corrections by fixing the object radius as an external parameter.
 We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light \mbox{(anti-)(hyper-)}nuclei~\cite{Vovchenko:2016mwg} and the relation with the possible production as compact quark bags~\cite{Andronic:2017}.
-
 In contrast to coalescence, the statistical-thermal models provide only \pt-integrated yields. 
@@
 
-The normalisation of the resulting spectra is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg implementation of the statistical-thermal model with $T_{chem} = 156$ MeV, multiplied by the measured pion yield~\cite{Abelev:2013vea}.
+The normalisation of the predicted blast-wave spectra for nuclei is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg implementation of the statistical-thermal model with $T_{chem} = 156$ MeV, multiplied by the measured pion yield~\cite{Abelev:2013vea}.
 This choice, as opposed to using the ratio to protons, is motivated by the fact that the measured proton yield is seen to be slightly overestimated by the thermal model~\cite{Abelev:2012wca}.
-For hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$ multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
+For hyper-triton, the normalisation is extracted from the statistical-thermal model prediction of the strangeness population factor \mbox{$S_{3} = { _{\Lambda}^{3}\mathrm{H} / ^{3}{\mathrm{He}} \over \Lambda/p}$} multiplied by the measured $\Lambda/p$ ratio~\cite{Abelev:2013vea,Abelev:2013xaa} and \hethree~yield~\cite{ALICE:deuteronppPbPb2015}.
 With the resulting spectra, we calculate \bA~for a given \pt/$A$ and compare it with coalescence expectations. 
@@
 We also note that the HBT radii, and thus also the source size, depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$~\cite{Aamodt:2011mr}. 
-In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT-data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($\approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($\approx$~5.5~fm)~
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT-data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($\approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($\approx$~5.5~fm).
+We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence on the source volume, in contrast to a similar coalescence study shown in \cite{Sun:2018mqq}. 
+As a matter of fact, the momentum dependence is a crucial element in the discussion presented here, because one might argue that the effects shown here, can equally be studied by looking at the transverse momentum dependence of the coalescence parameter.
+However, a study as a function of centrality/multiplicity based on different collision systems turns out to be more sensitive due to the larger lever arm in system size: for a fixed \pt/$A$, e.g.
+0.75 GeV/$c$ as in Fig.~\ref{fig:CompareThermalAndCoalescence}, \btwo~changes by about a factor 50 going from pp to central \PbPb~collisions.
+
+Considering the \pt/$A$ dependence as measured by ALICE, \btwo~changes by a factor two going from \pt/$A$~=~0.4~GeV/$c$ to \pt/$A$~=~2.2~GeV/$c$  in most central \PbPb~collisions \cite{ALICE:deuteronppPbPb2015}, and by less than a factor two in the measured \pt/$A$ range in pp collisions \cite{ALICE:nucleipp2017, Acharya:2019rgc}.
+one might argue that the effects shown here, can equally be studied by looking at the transverse momentum dependence of the coalescence parameter.
+However, a study as a function of centrality/multiplicity based on different collision systems turns out to be more sensitive due to the larger lever arm in system size: for a fixed \pt/$A$, e.g.
+0.75 GeV/$c$ as in Fig.~\ref{fig:CompareThermalAndCoalescence}, \btwo~changes by about a factor 50 going from pp to central \PbPb~collisions.
+
 \footnote{For this comparison, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nuclei production.
@@
 
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available LHC data for \mbox{(anti-)(hyper-)nuclei} \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available LHC data for \mbox{(anti-)(hyper-)nuclei} \cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Adam:2015yta} are compared to coalescence and to the thermal+blast-wave predictions.
 For the latter and for data, the radius parameterisation given by Eq.~\ref{eq:radiusParameterisation} is used.
@@
 Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but differs by 6$\sigma$ from coalescence, albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
+The only data point available so far in Pb--Pb collisions is in agreement with the thermal+blast-wave model but differs by 6$\sigma$ from coalescence, albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
 In \cite{Zhang:2018euf} it is argued that the difference between data and coalescence might be explained by a later formation through coalescence of $\Lambda$s and deuterons. 
@@
 \begin{enumerate}
-	\item For the production of $A=2$ and $A=3$ \mbox{(anti-)nuclei} in heavy-ion collisions, thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on d, $\bar{\mathrm{d}}$~production in central Pb--Pb collisions.
-	\item For the production of hyper-triton, thermal and coalescence models give very different predictions as a function of source volume.
-In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to \hethree.
-The very limited amount of data available favours the thermal model prediction within our assumptions.
+	\item For the production of $A=2$ and $A=3$ \mbox{(anti-)nuclei} in heavy-ion collisions, thermal+blast-wave and coalescence models give similar predictions for a source volume that is constrained by experimental data on d, $\bar{\mathrm{d}}$~production in central Pb--Pb collisions.
+	\item For hyper-triton, the two models give very different predictions as a function of source volume.
+In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to \hethree~due to its wider wave-function.
+	\item In \PbPb~collisions, the very limited amount of data available favours the thermal+blast-wave model prediction within our assumptions.
 	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects.
 Ideally, such measurements are accompanied by systematic measurements of the HBT radii in the same multiplicity/centrality classes and collision systems.
-	\item Our findings suggest a clear experimental path to be pursued with high-precision measurements at the upcoming phase of the LHC in the next ten years, which will finally provide sufficient integrated luminosity for the studies proposed here \cite{Citron:2018lsq}.
+	\item Our findings suggest a clear experimental path to be pursued with high-precision measurements at the upcoming phase of the LHC in the next ten years, which will finally provide sufficient integrated luminosity for the studies proposed here~\cite{Citron:2018lsq}.
 % will provide a unique opportunity for the final understanding of \mbox{(anti-)(hyper-)nuclei} production.

### 2019-03-13 FrascatiPlot/Paper/aps/submit_12032019/main_aps.tex
Üpdated draft for PRC submission: plot with 3 radius parameterisations added to appendinx

@@
 \begin{equation}
-R = a \avdNdeta^{1/3}\;\;
+R = a \avdNdeta^{1/3} + b\;\;
 \label{eq:radiusParameterisation}
@@
 %
-\noindent where $R$ is the source radius and $a = 0.473$ fm.
+\noindent where $R$ is the source radius, $a = 0.473$ fm and $b$ = 0.
 
@@
 We also note that the HBT radii, and thus also the source size, depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$~\cite{Aamodt:2011mr}. 
-In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT-data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($\approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($\approx$~5.5~fm).
-We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence on the source volume, in contrast to a similar coalescence study shown in \cite{Sun:2018mqq}. 
-As a matter of fact, the momentum dependence is a crucial element in the discussion presented here, because one might argue that the effects shown here, can equally be studied by looking at the transverse momentum dependence of the coalescence parameter.
-However, a study as a function of centrality/multiplicity based on different collision systems turns out to be more sensitive due to the larger lever arm in system size: for a fixed \pt/$A$, e.g.
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT-data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($\approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($\approx$~5.5~fm) in central \PbPb~collisions.
+We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence on the source volume, in contrast to a similar coalescence study shown in \cite{Sun:2018mqq} (for a detailed discussion on possible alternative source volume parameterisations, see Appendix \ref{appendixA}).
+%
+Production via coalescence could also be investigated by looking at the transverse momentum dependence of the coalescence parameter. However, 
+the advantage of studying these effects as a function of multiplicity/centrality is that system size offers a larger lever arm. 
+For a fixed \pt/$A$, \btwo~changes by about a factor 50 going from pp to central \PbPb~collisions, whereas \btwo~changes by a factor two going from \pt/$A$~=~0.4~GeV/$c$ to \pt/$A$~=~2.2~GeV/$c$  in most central \PbPb~collisions \cite{ALICE:deuteronppPbPb2015}, and by less than a factor two in the measured \pt/$A$ range in pp collisions \cite{ALICE:nucleipp2017, Acharya:2019rgc}.
+
+%As a matter of fact, the momentum dependence is a crucial element in the discussion presented here, because one might argue that However, a study as a function of centrality/multiplicity based on different collision systems turns out to be more sensitive due to the larger lever arm in system size: for a fixed \pt/$A$, e.g.
 0.75 GeV/$c$ as in Fig.~\ref{fig:CompareThermalAndCoalescence}, \btwo~changes by about a factor 50 going from pp to central \PbPb~collisions.
-
-Considering the \pt/$A$ dependence as measured by ALICE, \btwo~changes by a factor two going from \pt/$A$~=~0.4~GeV/$c$ to \pt/$A$~=~2.2~GeV/$c$  in most central \PbPb~collisions \cite{ALICE:deuteronppPbPb2015}, and by less than a factor two in the measured \pt/$A$ range in pp collisions \cite{ALICE:nucleipp2017, Acharya:2019rgc}.
-one might argue that the effects shown here, can equally be studied by looking at the transverse momentum dependence of the coalescence parameter.
-However, a study as a function of centrality/multiplicity based on different collision systems turns out to be more sensitive due to the larger lever arm in system size: for a fixed \pt/$A$, e.g.
-0.75 GeV/$c$ as in Fig.~\ref{fig:CompareThermalAndCoalescence}, \btwo~changes by about a factor 50 going from pp to central \PbPb~collisions.
-
-\footnote{For this comparison, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii, but given the availability of these measurements in only some of the collision systems and centralities, 
-we assume that $m_{\mathrm{T}}$-scaling holds.}.
 
@@
 
+\appendix
+\section{Comparison of alternative source volume parameterisations} \label{appendixA}
+For this comparison, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nuclei production.
+Ideally, one would use the proton femtoscopic radii, but given the availability of these measurements in only some of the collision systems and centralities, 
+we assume that $m_{\mathrm{T}}$-scaling holds.
+
+\begin{figure}[!h]
+	\begin{center}
+		\includegraphics[width=\columnwidth]{HbtRadiusParam.png}
+		\caption{Comparison of different source volume parameterisations.
+The dotted gray line is the result of a linear fit to the ALICE HBT data~\cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}, according to Eq.~\ref{eq:radiusParameterisation} with $a$~=~0.339~fm and $b$~=~0.128~fm.
+		The blue dashed line represents the parameterisation used in \cite{Sun:2018mqq}, corresponding to $a$~=~0.83~fm and $b$~=~0.
+		The continuous black line represents the parameterisation used in our study ($a$~=~0.473~fm and $b$~=~0) and obtained by a constraint from the \btwo~measured in central (0-10$\%$) \PbPb~collisions.}
+		\label{fig:sourceVolume}
+	\end{center}
+\end{figure}
+
 \begin{acknowledgments}

### 2019-03-13 FrascatiPlot/B2vsVolume.C

@@ -323,7 +323,7 @@ Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.
   Color_t color[]      = {kGreen+2, kOrange-3, kBlue+2, kRed, kRed+2,
 			  kGreen+2, kBlue+2, kBlue+1, kRed+2,
 			  kGreen+2, kBlue+2, kRed, kRed+2, kRed,
-			  kBlue-5, kBlue-7, kBlue+1, kRed+2, kBlue+1};
+			  kBlue-5, kBlue-7, kBlue+1, kRed+2, kAzure+1};
   
   Int_t Marker_Style[] = { 21, 33, 22, 20, 23,
 			   21, 22, 20, 23,

### 2019-03-13 FrascatiPlot/HbtRadii.C

@@ -25,7 +25,7 @@ void HbtRadii() {
   gStyle->SetPadTopMargin(0.05);
 
   TCanvas * canvHbtPlot = new TCanvas("canvHbtPlot","canvHbtPlot", 800, 600);
-  TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{N}_{ch}/d#it{#eta}#GT^{1/3}; #it{R} (fm)",200,0.0,13.0,200,0.0,6.0);
+  TH2D * histFrame = new TH2D("histFrame","radius vs mult; #LTd#it{N}_{ch}/d#it{#eta}#GT^{1/3}; #it{R} (fm)",200,0.0,13.0,200,0.0,12.0);
   histFrame->GetXaxis()->SetTitleSize(0.06);
   histFrame->GetXaxis()->SetLabelSize(0.045);
   histFrame->GetXaxis()->SetTitleOffset(1.1);
@@ -38,26 +38,34 @@ void HbtRadii() {
   histFrame->Draw();
   //
   const Long_t nPoints = 500;
-  Double_t xP[nPoints];
-  Double_t yP[nPoints];
-  for (int i = 0; i<nPoints; i++){
-    xP[i] = 15.0 * i / nPoints; 
-    Double_t multi[2] = {xP[i]*xP[i]*xP[i], 0.0};
-    Double_t radius[2] = {0.0, 0.0};
-    getRadiusFromParameterisation(multi, radius);
-    yP[i] = radius[0];
-    //
+  const Int_t nPrmtz = 4;
+  Double_t xP[nPrmtz][nPoints];
+  Double_t yP[nPrmtz][nPoints];
+  
+  
+  for (int j = 0; j<nPrmtz; j++){
+    for (int i = 0; i<nPoints; i++){
+      xP[j][i] = 15.0 * i / nPoints; 
+      Double_t multi[2] = {xP[j][i]*xP[j][i]*xP[j][i], 0.0};
+      Double_t radius[2] = {0.0, 0.0};
+      getRadiusFromParameterisation(multi, radius, j);
+      yP[j][i] = radius[0];
+    }
   }
   //
-  // TGraph * grRadiusVsMult = new TGraph(nPoints, xP, yP);
-  // grRadiusVsMult->SetMarkerColor(kBlack);
-  // grRadiusVsMult->SetLineColor(kBlack);
[…]

### 2019-03-13 FrascatiPlot/Make3HepPbPaperFigure.C

@@ -6,8 +6,7 @@ void getMultiFromR(Double_t * multi = NULL, Double_t * radius = NULL, Int_t para
 void Make3HepPbPaperFigure(Double_t pToA = 0.9, Bool_t plotLinX = 0, Int_t RmappingParam = 3, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0);
 
   
-void Make3HepPbPaperFigure(Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, 
-                          Bool_t plotPbPb5TeV)
+void Make3HepPbPaperFigure(Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, Bool_t plotPbPb5TeV)
 {
 
   Int_t ip = RmappingParam;

### 2019-03-20 FrascatiPlot/Paper/aps/submit_12032019/main_aps.tex
Draft updated for submission for PRC - all reuqests from PRL referees implemented, t/3He ratio added

@@
 %
-\begin{equation}
-	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;.
+\begin{equation}\label{eq:master}
+	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} } \;.
 \end{equation}
@@
 In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT-data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($\approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($\approx$~5.5~fm) in central \PbPb~collisions.
-We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence on the source volume, in contrast to a similar coalescence study shown in \cite{Sun:2018mqq} (for a detailed discussion on possible alternative source volume parameterisations, see Appendix \ref{appendixA}).
+We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence of the source volume, in contrast to a similar coalescence study shown in \cite{Sun:2018mqq} (for a detailed discussion on possible alternative source volume parameterisations, see Appendix \ref{appendixA}).
 %
@@
 
-%As a matter of fact, the momentum dependence is a crucial element in the discussion presented here, because one might argue that However, a study as a function of centrality/multiplicity based on different collision systems turns out to be more sensitive due to the larger lever arm in system size: for a fixed \pt/$A$, e.g.
-0.75 GeV/$c$ as in Fig.~\ref{fig:CompareThermalAndCoalescence}, \btwo~changes by about a factor 50 going from pp to central \PbPb~collisions.
-
-\section{Comparison with data}
+\section{Comparison with data}\label{sec:results}
 
@@
 Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
-The only data point available so far in Pb--Pb collisions is in agreement with the thermal+blast-wave model but differs by 6$\sigma$ from coalescence, albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
+The only data point available so far in Pb--Pb collisions is in agreement with the thermal+blast-wave model but differs by 6$\sigma$ from our coalescence calculation.
+This discrepancy might differ for calculations that use a more realistic (non-gaussian) wave-function.
 In \cite{Zhang:2018euf} it is argued that the difference between data and coalescence might be explained by a later formation through coalescence of $\Lambda$s and deuterons. 
@@
 The curves presented here explicitly allow for an estimate of the hyper-triton production in pp collisions, which is expected to be suppressed by about two orders of magnitude with respect to that of \hethree, making this measurement a prime candidate for future experimental studies.
+
+\section{(Anti-)triton production}
+For isobars with same spin but different wave-function, like \tritium~(\antitritium)~and \hethree~(\antihethree), Eq.~\ref{eq:master} provides as corollary a relation between the relative coalescence probabilities:
+
+\begin{equation} \label{eq:rho}
+\rho (\pt) \equiv \frac{B_{A}(\tritium)}{B_{A}(\hethree)}(\pt) = \bigg( \frac{R(\pt)^{2} + \frac{r_{\hethree}^{2}}{4}} {R(\pt)^{2} + \frac{r_{\tritium}^{2}}{4}} \bigg)^{3}
+\end{equation}
+
+\noindent Under the assumption that the distributions of protons and neutrons are identical, this is equivalent to the ratio of \tritium~yield relative to that of \hethree~(or \antitritium/\antihethree) at a given transverse momentum.
+It is to be noted that the transverse momentum dependence of this ratio originates solely from the \pt-dependence of the source volume.
+The ratio $\rho$ is reported in Fig.~\ref{fig:sourceVolume} for \pt/$A$~=~0.75 \GeVc~of the two isobars and as a function of the average charged particle multiplicity.
+Multiplicity is obtained from the system radius by inverting Eq.~\ref{eq:radiusParameterisation} in the aforementioned parameterisation constrained to \btwo.
+The coalescence model predicts a dependence of $\rho$ on the system size and thus on the charged particle multiplicity.
+In particular, the production of \tritium~(\antitritium) is expected to be up to a factor two more abundant than the production of \hethree~(\antihethree) in small systems.
+Such an excess of (anti-)tritons is not expected in thermal-statistical hadronisation.
+Since the two isobars have the same mass, spin and baryon number, the Grand Canonical thermal model~\cite{Andronic:2010qu,Andronic:2017} predicts a \tritium/\hethree~ratio equal to unity.
+The same holds true when taking into account the potential suppression of \mbox{(anti-)nuclei} yields due to explicit conservation of baryon number, as in Canonical Statistical Model calculations~\cite{Vovchenko:2018fiy}.
+Existing (anti-)triton measurements in pp collisions~\cite{ALICE:nucleipp2017} are limited by statistical precision and thus do not allow yet for a distinction between the two scenarios.
+
+\begin{figure}[!h]
+	\begin{center}
+		\includegraphics[width=\columnwidth]{RhoTritiumOver3HeliumVsMulti.png}
+		\caption{Yield of \tritium~relative to \hethree~for \pt/$A$~=~0.75~\GeVc~as defined by Eq.~\ref{eq:rho} in the coalescence picture (black line).
+The source radius has been mapped into average charged particle multiplicity by using the parameterisation constrained to the ALICE \btwo~measurement described in Sec.~\ref{sec:radiiParamet}.
+The orange dashed line represents the expectation from statistical hadronisation models.
+Colored arrows highlight the multiplicity range spanned by ALICE measurements in different collision systems.}
+		\label{fig:sourceVolume}
+	\end{center}
+\end{figure}
 
@@
 \section{Comparison of alternative source volume parameterisations} \label{appendixA} 
-For this comparison, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) was chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nuclei production.
-Ideally, one would use the proton femtoscopic radii, but given the availability of these measurements in only some of the collision systems and centralities, 
-we assume that $m_{\mathrm{T}}$-scaling holds.
-
+For the considerations discussed in this work and in similar ones, one crucial aspect has to be taken into account, namely how the source radius is parameterised as a function of multiplicity and transverse momentum.
+As discussed in Sec.~\ref{sec:radiiParamet}, for our main result we rely on the parameterisation given by Eq.~\ref{eq:radiusParameterisation}, which assumes a linear dependence between the cubic root of the measured average charged particle multiplicity density and the radius of the source.
+In order to extract the $a$ and $b$ coefficients of Eq.~\ref{eq:radiusParameterisation}, several solutions can be adopted. 
+One possibility is to fix the coefficients by fitting the available HBT data from ALICE~\cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq} with Eq.~\ref{eq:radiusParameterisation}, as shown in Fig.~\ref{fig:sourceVolume} by the data points fitted with the gray dotted line.
+%
 \begin{figure}[!h]
@@
 \end{figure}
+%
+In order to preserve the momentum dependence of the source volume, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) from pion HBT is chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nuclei production.
+Ideally, one would use the proton femtoscopic radii, but given the availability of these measurements in only some of the collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds.
+The fit to the ALICE data results in $a$~=~0.339~fm and $b$~=~0.128~fm.
+However, this approach does not describe the deuteron \btwo~data: we observe that in order for the measured \btwo~to agree with the coalescence prediction in most central \PbPb~collisions, a larger source radius of $R \approx 5.5$ fm is required instead of $R \approx 4$ fm as resulting from the HBT fit.
+This might also indicate that the volume relevant for the coalescence process is slightly larger than the homogeneity volume that can be extracted from HBT studies.
+Because of this, we chose to constrain the parameterisation to the measured \btwo~in central \PbPb~collisions for \pt~=~0.75 \GeVc~as well as to the origin ($b = 0$). 
+The resulting parameterisation, with $a = 0.473$ fm, is reported in Fig.~\ref{fig:sourceVolume} with a continuous black line, and it is used for the results of our study discussed in Sec.~\ref{sec:results}.
+
+The authors of \cite{Sun:2018mqq} assume the same functional dependence as we do in Eq.~\ref{eq:radiusParameterisation}. 
+However, their approach deviates from ours as they neglect the momentum dependence of the source volume and constrain it with HBT data at low momentum ($k_{\rm T} = 0.25$ \GeVc). 
+The parameterisation from \cite{Sun:2018mqq} ($a$~=~0.83~fm and $b$~=~0) is shown for comparison in Fig.~\ref{fig:sourceVolume} as the blue dashed line.
+While this choice allows for a good description of \pt-integrated yield ratios (e.g.
+d/p, \hethree/p, \hthreelambda/$\Lambda$)~\cite{Sun:2018mqq}, using this parameterisation for the \pt-differential study would lead to a significantly lower coalescence probability than measured caused by a much larger source volume (e.g.
+a \btwo~lower by a factor 5.6 for \pt~=~0.75~\GeVc, corresponding to a a factor two larger radius).
+In other words, by integrating over transverse momentum, one looses sensitivity to the \pt-dependence of the coalescence probability as the object radius becomes dominated by the large source volumina for small $k_{\rm T}$ (see Eq.~\ref{eq:master}).
+
+\bigskip
 
@@
 We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
-In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Marco Van Leuween, Maximiliano Puccio, Roman Lietava, Natasha Sharma and the colleagues from the ALICE Collaboration for their valuable input.
+In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Marco Van Leuween, Maximiliano Puccio, Roman Lietava, Natasha Sharma, Sebastian Hornung and the colleagues from the ALICE Collaboration for their valuable input.
 \end{acknowledgments}

### 2019-03-20 FrascatiPlot/Triton2heliumRatio.C
Added macro to produce t/3He ratio

@@ -1,0 +1,145 @@
+#include "./Make3HepPbPaperFigure.C"
+Float_t getRho(Float_t radius, Float_t errt, Float_t err3He);
+TGraphErrors * MakeRhoGraph();
+
+void Triton2heliumRatio()
+{
+  //set style
+  gStyle->SetOptStat(0);
+  gStyle->SetOptTitle(0);
+  gStyle->SetPadTopMargin(0.02);
+  gStyle->SetPadBottomMargin(0.2);
+  gStyle->SetPadLeftMargin(0.17);
+  gStyle->SetPadRightMargin(0.02);
+   
+  TH2D * hframeMult = new TH2D("hframeMult", "#rho vs mult; #LTd#it{N}_{ch}/d#it{#eta_{lab}}#GT; #rho", 3000, 0., 3000.0, 180, 0.0, 2.2);
+  hframeMult->GetXaxis()->SetTitleSize(0.06);
+  hframeMult->GetYaxis()->SetTitleSize(0.06);
+  hframeMult->GetXaxis()->SetTitleOffset(1.2);
+  hframeMult->GetXaxis()->SetLabelSize(0.05);
+  hframeMult->GetYaxis()->SetLabelSize(0.05);
+  hframeMult->GetYaxis()->SetNdivisions(505);
+  hframeMult->GetXaxis()->SetRangeUser(1., 3.E3);
+
+  //Define pT/A labels only once
+  TPaveText * pavept = new TPaveText(0.67, 0.85, 0.87, 0.9, "NDC");
+  pavept->SetFillStyle(0);
+  pavept->SetTextFont(42);
+  pavept->SetBorderSize(0);
+  pavept->SetTextSize(0.04);
+  pavept->SetTextAlign(12);
+  pavept->AddText(Form("#it{p}_{T}/#it{A} = 0.75 GeV/#it{c}"));
+
+TGraphErrors * gRhoVsR = (TGraphErrors*) MakeRhoGraph();
+gRhoVsR->SetLineStyle(1);
+gRhoVsR->SetLineColor(kBlack);
+gRhoVsR->SetLineWidth(4);
+convertRadiusToMulti(gRhoVsR, 1);
+
+Float_t arrowsize = 0.02;
+TArrow * arrpp = new TArrow(2.0, 0.8, 22.0, 0.8, arrowsize, "<|>");
+arrpp->SetLineColor(kGreen+2);
+arrpp->SetFillColor(kGreen+2);
[…]

### 2019-03-21 FrascatiPlot/Paper/aps/submit_12032019/main_aps.tex
Minor corrections to draft prior to submission to PRC. Slightly improvedaspect ratio for figure 1.

@@
 (Anti-)nuclei produced at chemical freeze-out are not expected to survive the hadronic phase, yet their measured production is consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc, Puccio:2019oyd}.
-Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, (c.) the continuous interplay of breakup and formation reactions resulting in the coincidence of thermal and kinetic equilibration \cite{Oliinychenko:2018ugs, Xu:2018jff}, (d.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary \cite{Castorina:2019pnb}, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, (c.) the continuous interplay of breakup and formation reactions resulting in the coincidence of thermal and kinetic equilibration \cite{Oliinychenko:2018ugs, Xu:2018jff}, (d.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
 Data from rescattering of short-lived hadronic resonances suggest a long-lasting hadronic phase \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
@@
 A quantitative comparison of the production scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
-As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters propose d here.
+As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters proposed here.
 
@@
 For a nucleus with mass number $A = Z + N$, the coalescence probability is quantified by the coalescence parameter $B_{A}$.
-Considering that at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal,  $B_{A}$ is defined as
+Considering that at LHC energies the number of produced protons and neutrons at midrapidity as well as their momentum distributions are expected to be equal, $B_{A}$ is defined as
 
@@
 \section{Statistical-thermal approach combined with blast-wave}\label{sec:thermal}
-In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$.
+In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto (2J_{A} + 1)\exp(-m/T_{chem})$.
 The thermal model implements eigenvolume corrections by fixing the object radius as an external parameter.
@@
 We also note that the HBT radii, and thus also the source size, depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$~\cite{Aamodt:2011mr}. 
-In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT-data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($\approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($\approx$~5.5~fm) in central \PbPb~collisions.
-We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence of the source volume, in contrast to a similar coalescence study shown in \cite{Sun:2018mqq} (for a detailed discussion on possible alternative source volume parameterisations, see Appendix \ref{appendixA}).
+In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($R \approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($R \approx$~5.5~fm) in central \PbPb~collisions.
+We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence of the source size, in contrast to a similar coalescence study reported in \cite{Sun:2018mqq} (for a detailed discussion on possible alternative source volume parameterisations, see Appendix \ref{appendixA}).
 %
-Production via coalescence could also be investigated by looking at the transverse momentum dependence of the coalescence parameter. However, 
+Production via coalescence could also be investigated by looking at the transverse momentum dependence of $B_{A}$. However, 
 the advantage of studying these effects as a function of multiplicity/centrality is that system size offers a larger lever arm. 
@@
 \section{(Anti-)triton production}
-For isobars with same spin but different wave-function, like \tritium~(\antitritium)~and \hethree~(\antihethree), Eq.~\ref{eq:master} provides as corollary a relation between the relative coalescence probabilities:
+For isobars with same spin but different wave-function, like \tritium~(\antitritium)~and \hethree~(\antihethree), Eq.~\ref{eq:master} provides a relation between the relative coalescence probabilities as corollary:
 
 \begin{equation} \label{eq:rho}
-\rho (\pt) \equiv \frac{B_{A}(\tritium)}{B_{A}(\hethree)}(\pt) = \bigg( \frac{R(\pt)^{2} + \frac{r_{\hethree}^{2}}{4}} {R(\pt)^{2} + \frac{r_{\tritium}^{2}}{4}} \bigg)^{3}
+\rho (\pt) \equiv \frac{B_{A}(\tritium)}{B_{A}(\hethree)}(\pt) = \bigg( \frac{R(\pt)^{2} + \frac{r_{\hethree}^{2}}{4}} {R(\pt)^{2} + \frac{r_{\tritium}^{2}}{4}} \bigg)^{3} \;\; .
 \end{equation}
@@
 The ratio $\rho$ is reported in Fig.~\ref{fig:sourceVolume} for \pt/$A$~=~0.75 \GeVc~of the two isobars and as a function of the average charged particle multiplicity.
-Multiplicity is obtained from the system radius by inverting Eq.~\ref{eq:radiusParameterisation} in the aforementioned parameterisation constrained to \btwo.
+Multiplicity is obtained from the system radius by inverting Eq.~\ref{eq:radiusParameterisation}.
 The coalescence model predicts a dependence of $\rho$ on the system size and thus on the charged particle multiplicity.
-In particular, the production of \tritium~(\antitritium) is expected to be up to a factor two more abundant than the production of \hethree~(\antihethree) in small systems.
+In particular, the production of \tritium~(\antitritium) is predicted by our model to be up to a factor two more abundant than the production of \hethree~(\antihethree) in small systems.
 Such an excess of (anti-)tritons is not expected in thermal-statistical hadronisation.

### 2019-03-21 FrascatiPlot/B2vsVolume.C

@@ -85,7 +85,7 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3, Double_t 
 
 //main plotting for Frascati plot
 Int_t B2vsVolume(Bool_t plotLinX = 1, Double_t pToA = 0.75, Double_t pToAb3 = 0.733, Double_t pToAb3pp = 0.800, Double_t pToAb3Lambda = 1., Double_t pToAb4 = 0.75,
-		 Double_t pToAb4Lambda = 0.75, Bool_t plotOnlyCoalescence = kFALSE, Bool_t plotPaperFigures = 0, Bool_t plotYRFigure = 0, Bool_t plotPseudoData = 0)
+		 Double_t pToAb4Lambda = 0.75, Bool_t plotOnlyCoalescence = kFALSE, Bool_t plotPaperFigures = 1, Bool_t plotYRFigure = 0, Bool_t plotPseudoData = 0)
 {
   //
   // main function which generates the plots of the Frascati project
@@ -749,14 +749,14 @@ void MakePaperFigure1(Bool_t plotLinX, Double_t pToA,
   TLegend * legB2_coal;
   legB2_coal = new TLegend(0.52, 0.93-5*0.06, 0.85, 0.93, Form("#it{p}_{T}/#it{A} = %3.2f GeV/#it{c}", pToA));
   legB2_coal->SetFillStyle(0);
-  legB2_coal->SetTextSize(0.06);
+  legB2_coal->SetTextSize(0.05);
   legB2_coal->SetBorderSize(0);
   legB2_coal->AddEntry(hB2_coalescence_pointlike, "#it{B}_{2} coalesc., #it{r_{d}} = 0 (point-like)", "l");
   legB2_coal->AddEntry(hB2_coalescence_radius1third, "#it{B}_{2} coalesc., #it{r_{d}} = 0.3 fm", "l");
   legB2_coal->AddEntry(hB2_coalescence, "#it{B}_{2} coalesc., #it{r_{d}} = 3.2 fm", "l");
   legB2_coal->AddEntry(hB2_coalescence_largeradius, "#it{B}_{2} coalesc., #it{r_{d}} = 10 fm", "l");
   
-  TCanvas * coalcanv = new TCanvas("coalcanv", "coalescence", 1000, 800);
+  TCanvas * coalcanv = new TCanvas("coalcanv", "coalescence", 800, 1800);
   //top pad
[…]

### 2019-03-30 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Add folder for EPIPHANY's proceedings

\documentclass{appolb}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tabularx} 
\usepackage{rotating,graphicx} 
\usepackage{appendix} 
\usepackage{makecell}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage[amssymb]{SIunits}
\usepackage{hyperref}

\usepackage{lineno}
\linenumbers

% graphicx package included for placing figures in the text
%------------------------------------------------------
\input{./commands.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                %
%    BEGINNING OF TEXT                           %
%                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \eqsec  % uncomment this line to get equations numbered by (sec.num)
\title{Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC}
\author{F. Bellini (CERN, Geneva) \\and A. P. Kalweit (CERN, Geneva)}
\thanks{Proceedings of the XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}%
\address{Contact: francesca.bellini@cern.ch}

\maketitle
\begin{abstract}
The production of light anti- and hyper-nuclei provides unique observables to characterise the system created in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions. In particular, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size is comparable to a fraction or the whole system created in the collision. Their formation is typically described within the framework of coalescence and thermal-statistical production models. 
In order to distinguish between the two production scenarios, we propose to measure the coalescence parameter $B_A$ for different anti- and hyper-nuclei (that differ by mass, size and internal wave-function) as a function of the size of the particle emitting source. 
The latter can be controlled by performing systematic measurements of light anti- hyper- nuclei in different collision systems (pp, pA, AA) and as a function of the multiplicity of particles created in the collision. 
While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light nuclei in heavy-ion collisions, our study shows that large differences can be expected for hyper-nuclei with extended wave-functions, as the hyper-triton. We compare the model predictions with data from the ALICE experiment and we discuss perspectives for future measurements with the upgraded detectors during the High-Luminosity LHC phase in the next decade. 
\end{abstract}

%\PACS{PACS numbers come here}

\section{Introduction}
In the last few years A Large Ion Collider Experiment (ALICE) Collaboration has reported on the measurement of the production of light nuclei in pp, p--Pb and Pb--Pb collisions at TeV centre-of-mass energies \cite{}, based on data collected during the first ten years of operations of the CERN Large Hadron Collider (LHC). 
The measurements of deuteron, ,

\begin{table}[htb]
\resizebox{\textwidth}{!}{%
\centering
\begin{tabularx}{1.25\textwidth}{cccccccc}
\hline \hline \\[-2ex]
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\[1ex]  \hline \\[-2ex] 
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
\end{tabularx}
}
\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced. Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

\section{The coalescence approach}

Starting from the model described in~\cite{Scheibl:1998tk, Blum:2017qnn}, we have obtained in \cite{Bellini:2018epz} a generalised expression for the coalescence parameter $B_A$

\begin{equation}\label{eq:master}
	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} } \;\;,
\end{equation}

\noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\rm T}$, its size parameter $r_A$ and the source radius $R$.
Figure \ref{Fig:BA} shows the source radius dependence of $B_A$ for different composite objects, including the nuclei and hyper-nuclei with $A = 2, 3$ and 4 whose properties are reported in Tab.~\ref{tab:nucleusradii}.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{coalescenceBA075.eps}
\caption{(Color online) Coalescence parameter $B_A$ as a function of the source radius $R$ as predicted from the coalescence model (Eq.~\ref{eq:master}) for various composite objects with \pt$/A$~=~0.75~\GeVc. For each (hyper-)nucleus, the radius $r$ used for the calculation is reported in the legend.}
\label{Fig:BA}
\end{center}
\end{figure}

\subsection{Comparison with data}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\textwidth]{coal2Thermal2alice.png}
\caption{(Color online) Coalescence parameter $B_A$ as a function of the average charged particle multiplicity density for various (hyper-)nuclei, up to $A = 4$. The coalescence calculations (continuous or dashed-dotted black lines) are compared to the thermal+blast-wave predictions (dashed blue line), as well as to pp (green square) and \PbPb~(red circles) collision data from ALICE~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Adam:2015yta}. }
\label{Fig:BA}
\end{center}
\end{figure}

\bibliographystyle{utphys} 	
\bibliography{biblio}
\end{document}

### 2019-03-30 FrascatiPlot/B2vsVolume.C
Updated macros for coalescnece and added macro to prepared EPIPHANY's proceedings figures. Also, new macro to map multi into R and viceversa

@@ -11,12 +11,7 @@
 #include "TH1D.h"
 #include "TH2D.h"
 #include "./generateBWpredictionsB2.C"
-
-//mapping multiplicity into radius
-void convertMultiToRadius(TGraphErrors * graph = 0x0, Int_t paramSet = 0);
-void convertMultiToRadius(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 0);
-void getRadiusFromParameterisation(Double_t * multi = 0x0, Double_t * radius = 0x0, Int_t paramSet = 0);
-
+#include "./MapMulti2R.C"
 //coalescence predictions up to A=4
 TF1 *          MakeB2TheoryGraphQMfactor(Double_t objSize = 3.2);
 TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 3.2);
@@ -42,7 +37,7 @@ TGraphAsymmErrors * getBlastB4_pp7TeV(Bool_t plotSys = 0, Double_t pToAb4 = 0.75
 TGraphAsymmErrors * getBlastB4Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.75, Int_t paramSet = 0);
 TGraphAsymmErrors * getBlastB4Lambda_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.75, Int_t paramSet = 0);
 
-TGraphAsymmErrors * getBAthermalBlast(TString system = "PbPb276TeV", TString particle = "deuteron", Double_t pToA = 0.75, Color_t color = kBlack, Int_t paramSet = 1);
+TGraphAsymmErrors * getBAthermalBlast(TString system = "PbPb276TeV", TString particle = "deuteron", Double_t pToA = 0.75, Color_t color = kBlack, Int_t paramSet = 1, Bool_t convertToR = kTRUE);
 
 //ALICE data on nuclei BA
 //deuteron
@@ -1186,61 +1181,6 @@ void MakePaperFigure4(Bool_t plotLinX, Double_t pToA, Double_t pToAb3,  Double_t
 
 }
 
-
-void getRadiusFromParameterisation(Double_t * multi, Double_t * radius, Int_t paramSet)
-{
-  // parameterisation to convert multiplicity into Rside
-  // this is the parameterisation for the pion radius
-  //
-  if (!multi || !radius) return;
-  Double_t  multi3 = TMath::Power(multi[0], 1./3.);  
-  //
[…]

### 2019-03-30 FrascatiPlot/CoalescenceBA.C

@@ -8,7 +8,7 @@
 #include "./B2vsVolume.C"
 
 //coalescence
-void    CoalescenceBA(Double_t pToA = 0.75);
+void    CoalescenceBA(Double_t pToA = 0.75, TString figPath = ".");
 Double_t getBAfunc(Double_t *x, Double_t *par);
 Double_t getBAfromCoalescence(Double_t A, Double_t JA, Double_t mT, Double_t homogR,  Double_t objSize);
 TGraphErrors * MakeBATheoryGraphCoalescence(Double_t A, Double_t JA, Double_t mT, Double_t objSize);
@@ -489,7 +489,7 @@ TH1D * GetProtonIn010CentBinBlast()
 /////////////////////////////////////////////////////////////////////////////////////////////////////////
 // Make plot with coalescence BA predictions for different (hyper-)nuclear species
 /////////////////////////////////////////////////////////////////////////////////////////////////////////
-void CoalescenceBA(Double_t pToA = 0.75)
+void CoalescenceBA(Double_t pToA, TString figPath)
 {
   //set style
   gStyle->SetOptStat(0);
@@ -510,26 +510,39 @@ void CoalescenceBA(Double_t pToA = 0.75)
   for(Int_t j=0; j<8; j++) {
     hBA_coalescence[j] = (TGraphErrors*) MakeBATheoryGraphCoalescence(nucleiA[j], spin[j], pToA, objRadius[j]);
     hBA_coalescence[j]->SetMarkerStyle(1);
-    hBA_coalescence[j]->SetLineWidth(2);
+    hBA_coalescence[j]->SetLineWidth(3);
     hBA_coalescence[j]->SetLineStyle(line[j]);
     hBA_coalescence[j]->SetLineColor(color[j]);
   }
 
   TH1D * hframe4 = CreateFrameBA();
-  
+  hframe4->GetYaxis()->SetTitleOffset(1.4);
+  hframe4->GetYaxis()->SetTitleSize(0.06);
+  hframe4->GetYaxis()->SetRangeUser(1e-13, .1);
   //Define pT/A labels only once
[…]

### 2019-03-30 FrascatiPlot/Make3HepPbPaperFigure.C

@@ -1,12 +1,9 @@
 #include "./B2vsVolume.C"
 
-void convertRadiusToMulti(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 1);
-void convertRadiusToMulti(TGraphErrors * graph = 0x0, Int_t paramSet = 1);
-void getMultiFromR(Double_t * multi = NULL, Double_t * radius = NULL, Int_t paramSet = 1);
-void Make3HepPbPaperFigure(Double_t pToA = 0.9, Bool_t plotLinX = 0, Int_t RmappingParam = 3, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0);
+TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA = 0.733, Bool_t plotLinX = 0, Int_t RmappingParam = 1, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0, Bool_t plotpPb = 0);
 
   
-void Make3HepPbPaperFigure(Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, Bool_t plotPbPb5TeV)
+TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, Bool_t plotPbPb5TeV, Bool_t plotpPb)
 {
 
   Int_t ip = RmappingParam;
@@ -38,7 +35,6 @@ void Make3HepPbPaperFigure(Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, 
     gB3vsR_pPb502TeV_sys[jj] = (TGraphErrors *) getB3_pPb5TeV(kTRUE, pToA, jj, kFALSE);
     gB3vsR_pPb502TeV_sys[jj]->SetFillStyle(1001);
     gB3vsR_pPb502TeV_sys[jj]->SetFillColor(kBlue-10);
-    
 
     gB3vsR_PbPb276TeV[jj] = (TGraphErrors *) getB3_PbPb276TeV(kFALSE, pToA, jj, kFALSE);
     gB3vsR_PbPb276TeV_sys[jj] = (TGraphErrors *) getB3_PbPb276TeV(kTRUE, pToA, jj, kFALSE);
@@ -128,7 +124,7 @@ void Make3HepPbPaperFigure(Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, 
[…]

### 2019-03-30 FrascatiPlot/MakeFiguresEpiphany.C

@@ -1,0 +1,514 @@
+#include "./CoalescenceBA.C"
+#include "./MapMulti2R.C"
+
+void MakeFiguresEpiphany()
+{
+    TString figPath = "../EPIPHANY2019proceedings";
+
+    //Figure 1: BA from coalescence
+    CoalescenceBA(0.75, figPath.Data());
+    Make3HepPbPaperFigure(figPath.Data(), 0.733, 0, Int_t 1, 1, 0, 0);
+
+    gStyle->SetOptStat(0);
+    gStyle->SetOptTitle(0);
+    gStyle->SetPadTopMargin(0.03);
+    gStyle->SetPadBottomMargin(0.17);
+    gStyle->SetPadLeftMargin(0.17);
+    gStyle->SetPadRightMargin(0.02); 
+
+    Bool_t convertToR = kFALSE;    //Bool_t plotPseudoData = 0;
+    Int_t paramSet = 1;
+
+    Color_t projCol = kRed+1;
+    Double_t Rmin = 0.8; 
+    Double_t Rmax = 3000;
+    if (convertToR) {
+        Rmin = 0.01;
+        Rmax = 6.5;//fm
+    }
+
+    Double_t pToA = 0.75;
+    Double_t pToAb3 = 0.733;
+    Double_t pToAb3pp = 0.8;
+    Double_t pToAb3Lambda = 1.;
+    Double_t pToAb4 = 0.75; 
+    Double_t pToAb4Lambda = 0.75; 
+
+    //-----------------------------
+    //    data
+    //-----------------------------
+    Int_t Fill_Style = 1001;
+    Int_t Line_Style = 1;
+    Int_t Line_Style_Blast = 2;
+    Int_t Line_Width = 1; 
+    Int_t Line_Width_Blast = 3;
+    Float_t Marker_Size = 1.3;
+    //nb: manual hack to avoid loop over all parameterisations
+    const Int_t nParamSet = 1;
+    Int_t ip = paramSet-1;
+
+    TGraphErrors* gB2vsR_pp7TeVINELg0[nParamSet];
+    TGraphErrors* gB2vsR_pp7TeVINELg0_sys[nParamSet];
+    gB2vsR_pp7TeVINELg0[ip] = (TGraphErrors *) getB2_pp7TeVINELg0(kFALSE, pToA, paramSet);
[…]

### 2019-03-30 FrascatiPlot/MapMulti2R.C

@@ -1,0 +1,164 @@
+//mapping multiplicity into radius
+void getRadiusFromParameterisation(Double_t * multi = 0x0, Double_t * radius = 0x0, Int_t paramSet = 1)
+{
+  // parameterisation to convert multiplicity into Rside
+  // this is the parameterisation for the pion radius
+  //
+  if (!multi || !radius) return;
+  Double_t  multi3 = TMath::Power(multi[0], 1./3.);  
+  //
+  // Here is the crucial mapping between HBT radii and multi^(1/3)
+  //
+  // VERSION (5th February 2018):
+  // We assume 0.85fm for pp as Kfir (at dNdeta 6.01)
+  // We assume R=4.5fm for central Pb-Pb based on arXiv:1012.4035 (figure 2)
+  // We interpolate linearly and take the highest kT bin, because
+  // a pT/A of 0.8 GeV/c corresponds to mT=1.23GeV which is a kT of pions of 1.2GeV
+  // radiusVal = 0.177825 + 0.36733 * multi3;
+
+  // VERSION (17th May 2018):
+  // We fit linearly the ALICE data at the kT = 0.887 
+  Double_t radiusVal = 0.0;
+  if (paramSet == 3){
+    //manual hack to reproduce Donigus, Ko arXiv:1812.05175 where HBT parameter is based on results for kT = 0.25
+    radiusVal = 0.0 + 0.83 * multi3;
+  } else if (paramSet==2) {
+    //manual hack to have the data points fall onto the U. Heinz curve for 3He
+    radiusVal = 0.190 + 0.380 * multi3;
+  } else  if (paramSet==1) {
+    //manual hack to have the data points fall onto the U. Heinz curve for deuteron
+    radiusVal = 0.0 + 0.472949 * multi3; //radius = 0 at 0 dN/deta
+    //radiusVal = 0.07412 + 0.46637 * multi3; //radius = 0.85 fm for pp, dN/deta = 4.60 (INELg0)
+    //radiusVal = -0.009 + 0.4738 * multi3; //radius = 0.85 fm for pp, dN/deta = 5.98 (INELg0>0)
+    //radiusVal = -0.3949 + 0.507865 * multi3; //most central and peripheral PbPb 2.76 TeV on the curve
+  } else {
+    //fit to the HBT data, kT = 0.887
[…]

### 2019-03-30 Paper/NucleiB2.tex
Moved Paper folder in main

--- 2018-09-05 FrascatiPlot/Paper/NucleiB2.tex
@@
 F. Bellini and A. Kalweit \footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch}
-\\CERN, EP Department, Geneva (Switzerland)
+\\European Organization for Nuclear Research (CERN), Geneva, Switzerland
 
@@
 
-16$^{th}$ July 2018
+5$^{\mathrm{th}}$ September 2018
 \end{center}
@@
 \newpage
-
 \section{Introduction} 
@@
 In addition, these studies might shed light on the internal structure of the formed objects themselves.
-In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, protons, kaons, etc.), because their size (i.e.
+In this context, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size (i.e.
 the extension of their wave-function) is comparable to a fraction or the whole system created in the collision~\cite{Adam:2015vna}.
-The relevant known properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
-As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
+The relevant known properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
+As quantum-mechanical objects, their size is typically defined as the rms of their (charge) wave-function, which corresponds to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments.
 Not much is known experimentally about the wave-functions of hyper-nuclei and other exotic QCD objects.
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange $A = 3$ nuclei.
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, which is significantly larger than that of non-strange nuclei with mass number $A = 3$.
 This is driven by the average separation of the $\Lambda$ with respect to the two other nucleons which is expected to amount to up to 10 fm \cite{Nemura:1999qp}.
@@
 Based on this, the deuterons produced at chemical freeze-out would be expected not to survive the hadronic phase of the medium expansion, yet their production is measured to be consistent to the predictions from statistical-thermal models and they develop also a non-zero elliptic flow which is consistent with a common radial expansion together with the non-composite hadrons \cite{Acharya:2017dmc}.
-Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+Several solutions have been proposed to solve this ``light (anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, and (c.) the coincidence of the coalescence mechanism with that of thermal production \cite{Scheibl:1998tk, HeinzTorino}.
 Data from rescattering of short-lived hadronic resonances indicate that the system undergoes a long-lasting hadronic phase before decoupling \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.).
@@
 $B_{E}$ is the binding energy in MeV.
-The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius.
+The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius.
 The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced.
@@
 \begin{center}
-\includegraphics[width=.9\textwidth]{theory_coalescence_Cd_B2.png}
-\caption{{The quantum mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
+\includegraphics[width=\textwidth]{theory_coalescence_Cd_B2.png}
+\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (left panel, see Eq.
 \ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (right panel, see Eq.
-\ref{eq:B2approx}) as a function of the radius of the source, $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
+\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
 The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
@@
 \caption{Parameterisation of the dependence of the source radius on multiplicity assumed in this paper, compared to HBT data from \cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}.
-The radius $R$ and the parameters $a$ and $b$ are in units of fm.}
+The radius $R$ and the parameters $a$ and $b$ are in units of fm.
+Parameterisation A is shown here, see text for details.}
 \label{fig:radiiparam}
@@
 We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be $a = 0.473$ and $b = 0$.
-With this second parameterisation (labeled as "B" in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree, \bthree.
+With this second parameterisation (labeled as``B'' in the following), we investigate the agreement of the model with the measured coalescence parameter for \hethree, \bthree.
 As shown in the lower panels of Fig.~\ref{fig:CompareB2B3forDifferentParamWithData}, also in the case of \bthree, a tension between the model and the data is found for parameterisation A, which ameliorates for the parameterisation B, tuned to the (anti-)deuteron data.
-The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the latter is the same for all anti- and hyper-nuclei.
-It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
+The strength of this approach is given by the fact that the coalescence volume is constrained with the more differential (anti-)deuteron data assuming that the coalescence volume is the same for all anti- and hyper-nuclei.
+It is also noteworthy that any change of the radii parameterisation would result in a shift along the x-axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.
 
-The necessity of introducing a second parameterisation for the radius could point to the fact that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered here, but by a slightly larger system.
+The necessity of introducing a second parameterisation for the radius could point to the fact that the kinetic freeze-out volume relevant for coalescence is not given by the $m_{T}$-scaled pion HBT volume considered in parameterisation A, but by a slightly larger system as given by parameterisation B.
 
@@
 \subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
-In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and \hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
+In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions.
 For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}.
@@
 		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the thermal+BW model expectations (dotted line) and the coalescence predictions (solid lines).
+		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper left panel), \hethree\ (lower left panel) and \hthreelambda\ (lower right panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
 Parameterisation B has been used to map the charged particle multiplicity density into the radius $R$ of the source (see text for details).
@@
 Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton.
-Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.
+Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.
 

### 2019-03-30 Paper/aps/submit_28112018/main_aps.tex
Moved Paper folder in main

--- 2018-12-10 FrascatiPlot/Paper/aps/main.tex
@@
 \label{tab:nucleusradii}
-\end{table*}%
+\end{table*}
 
@@
 Thus, its possible production via coalescence in pp collisions would be subject to a similar suppression as the hyper-triton.
-The upcoming high-luminosity phase of the LHC
-%, where $A = 4$ (hyper-)nuclei and other rare composite objects will become experimentally accessible, 
-will provide a unique opportunity for the final understanding of \mbox{(anti-)(hyper-)nuclei} production.
+The upcoming high-luminosity phase of the LHC will provide a unique opportunity for the final understanding of \mbox{(anti-)(hyper-)nuclei} production.
 Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
+
+\begin{acknowledgments}
+We would like to thank Kfir Blum for inspiring this work.
+We thank U.
+Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
+We further acknowledge discussions with Benjamin Doenigus, in particular about the production of \hthreelambda\ in pp collisions, and with Eulogio Serradilla Rodriguez.
+In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Marco Van Leuween, Maximiliano Puccio, Roman Lietava, Natasha Sharma and the colleagues from the ALICE Collaboration for their valuable input.
+\end{acknowledgments}
+
+\bibliography{main_aps}
+\end{document}

### 2019-03-30 FrascatiPlot/GetB3inpToA.C
Updated macro for 3He pPb paper figur

@@ -179,9 +179,10 @@ void GetB3inpToA_PbPb5TeV()
 }
 
 
-void GetB3inpToA_pPb5TeV(Double_t pToA = 0.9)
+void GetB3inpToA_pPb5TeV(Double_t pToA = 0.9, 
+                         TString dataFile = "B3_Average_pPb_5TeV_08022019.root")
 {
-  TFile * fin = TFile::Open("B3_Average_pPb_5TeV_08022019.root");
+  TFile * fin = TFile::Open(dataFile.Data());
   if (!fin) return;
 
   Int_t cent[5] = {0, 10, 20, 40, 100}; 

### 2019-03-30 FrascatiPlot/Make3HepPbPaperFigure.C

@@ -1,10 +1,14 @@
 #include "./B2vsVolume.C"
+#include "./GetB3inpToA.C"
 
 TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA = 0.733, Bool_t plotLinX = 0, Int_t RmappingParam = 1, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0, Bool_t plotpPb = 0);
 
   
 TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, Bool_t plotPbPb5TeV, Bool_t plotpPb)
 {
+
+  //prepare input file
+  GetB3inpToA_pPb5TeV(pToA, "B3_Average_pPb_5TeV_15032019.root");
 
   Int_t ip = RmappingParam;
   Float_t textLabelSize = 0.033;

### 2019-03-30 FrascatiPlot/B2vsVolume.C
Fixed new path

@@ -792,11 +792,11 @@ void MakePaperFigure1(Bool_t plotLinX, Double_t pToA,
   legB2_coal->Draw();
   
   if (plotvert) {
-    coalcanv->SaveAs("Paper/theory_coalescence_Cd_B2_vert.eps");
-    coalcanv->SaveAs("Paper/theory_coalescence_Cd_B2_vert.png");
+    coalcanv->SaveAs("../Paper/theory_coalescence_Cd_B2_vert.eps");
+    coalcanv->SaveAs("../Paper/theory_coalescence_Cd_B2_vert.png");
   } else {
-    coalcanv->SaveAs("Paper/theory_coalescence_Cd_B2.eps");
-    coalcanv->SaveAs("Paper/theory_coalescence_Cd_B2.png");
+    coalcanv->SaveAs("../Paper/theory_coalescence_Cd_B2.eps");
+    coalcanv->SaveAs("../Paper/theory_coalescence_Cd_B2.png");
   }
   return;
 }

### 2019-03-30 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
INtroduction and motivation - taking a break and continuing later

@@
 \title{Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC}
-\author{F. Bellini (CERN, Geneva) \\and A. P. Kalweit (CERN, Geneva)}
-\thanks{Proceedings of the XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}%
-\address{Contact: francesca.bellini@cern.ch}
-
+\author{F. Bellini (CERN, Geneva) \footnote{Presenter. For correspondence: francesca.bellini@cern.ch} 
+	    \\and A. P. Kalweit (CERN, Geneva)}
+\thanks{XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}%
+\address{}
 \maketitle
@@
 
-\section{Introduction}
-In the last few years A Large Ion Collider Experiment (ALICE) Collaboration has reported on the measurement of the production of light nuclei in pp, p--Pb and Pb--Pb collisions at TeV centre-of-mass energies \cite{}, based on data collected during the first ten years of operations of the CERN Large Hadron Collider (LHC).
-The measurements of deuteron, ,
+\section{Introduction and motivation}
+The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these reactions, and can be used to understand both the internal structure and the formation mechanisms of loosely-bound composite objects.
+The production of (anti-)(hyper-)nuclei in high-energy collisions is commonly described by following two distinct approaches: formation by nucleon coalescence at the system (kinetic) freeze-out \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Blum:2017qnn} or thermal-statistical production at the chemical freeze-out \cite{Andronic:2010qu,Andronic:2017}.
+Thanks to the large data samples of pp, \pPb~and \PbPb~collisions collected during the first ten years of operations of the CERN Large Hadron Collider (LHC), A Large Ion Collider Experiment (ALICE) Collaboration
+has measured the production of light nuclei and anti-nuclei at several centre-of-mass energies \cite{ALICE:deuteronppPbPb2015, Adam:2015yta, anielski-HQ14, Puccio:2019oyd, ALICE:nucleipp2017, Acharya:2017dmc, Acharya:2019rgc}, thus providing a crucial experimental input and boost to theoretical and phenomenological investigations \cite{Mrowczynski:2016xqm, Bellini:2018epz, Bazak:2018hgl, Zhao:2018lyf, Sun:2018mqq, Xu:2018jff, Oliinychenko:2018ugs}.
+
+It is to be stressed, that a comprehension of (anti-)nuclei production mechanisms is not only relevant for nuclear and hadronic physics, but has applications in astrophysics and indirect Dark Matter searches \cite{Aramaki:2015pii}.
+In recent years, it has been suggested that the detection of light anti-nuclei in space could provide a signature for the presence of Dark Matter in the Cosmos, see for instance \cite{Cirelli:2014qia, Korsmeier:2017xzj}.
+Anti-deuterons and \antihethree~might indeed be produced by coalescence of antiprotons and antineutrons coming from the annihilation of Weakly Interacting Massive Particles into Standard Model particles, for which anti-nuclei created in reactions between primary cosmic ray protons and interstellar matter (pp, pA collisions) represent a source of background.
+
+STOP HERE FOR NOW.
+
+\section{Production models}
+Thermal-statistical models have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
+In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV.
+Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
+Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
+Once the mean free path for elastic collisions is larger than the system size, the fireball freezes-out kinetically at $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}. 
+In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile''. 
+For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2~MeV~$\ll~T_{chem},~T_{kin}$.
+The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}.
+Similarly, the elastic cross-section driving deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}
+(Anti-)nuclei produced at chemical freeze-out are not expected to survive the hadronic phase, yet their measured production is consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc, Puccio:2019oyd}.
+Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary \cite{Castorina:2019pnb}, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, (c.) the continuous interplay of breakup and formation reactions resulting in the coincidence of thermal and kinetic equilibration \cite{Oliinychenko:2018ugs, Xu:2018jff}, (d.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+Data from rescattering of short-lived hadronic resonances suggest a long-lasting hadronic phase \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
+Hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei yields with statistical-thermal model predictions.
+Calculations for (c.) are currently available only for deuterons.
+Hypothesis (d.) is scrutinised in this letter.
+To this purpose, we propose a new method to compare models that also allows for a direct comparison with LHC data.
+
+Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, protons, etc.), because their size is comparable to a fraction or the whole system created in high-energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions~\cite{Adam:2015vna}.
+Their size is typically defined as the rms of their (charge) wave-function, corresponding to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ relative to the two other nucleons.
+This difference in the wave-functions results in dramatic consequences for the production scenarios, as discussed in the following.
+The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
 
@@
 
-\section{The coalescence approach}
+\subsection{The coalescence approach}
 
@@
 
-\subsection{Comparison with data}
+\section{Comparison with data}
 
@@
 }
-\label{Fig:BA}
+\label{Fig:comparison}
 \end{center}
@@
 
-\bibliographystyle{utphys} 	
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{B3vsMult073.png}
+\caption{(Color online) Coalescence parameter $B_3$ for \hethree~as a function of the average charged particle multiplicity density.
+The coalescence calculation (continuous black line) is compared to two thermal+blast-wave predictions (dashed lines), obtained by using the Grand Canonical (GC, red)~\cite{Andronic:2017} and Canonical Statistical Model (CSM, blue) \cite{Vovchenko:2018fiy} expectations for the \hethree~yield, respectively.
+ALICE data from pp (green circles) and \PbPb~(red circles) collisions~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015} are reported.
+}
+\label{Fig:3He}
+\end{center}
+\end{figure}
+
+\newpage
+\bibliographystyle{utphysnt} 	
 \bibliography{biblio}

### 2019-03-30 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Finished with the intro and motivation for the proceedings.

--- 2019-03-30 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
@@
 
-\section{Introduction}
-In the last few years A Large Ion Collider Experiment (ALICE) Collaboration has reported on the measurement of the production of light nuclei in pp, p--Pb and Pb--Pb collisions at TeV centre-of-mass energies \cite{}, based on data collected during the first ten years of operations of the CERN Large Hadron Collider (LHC).
-The measurements of deuteron, ,
+\section{Introduction: the ''anti-nuclei'' puzzle}
+The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these reactions, and can be used to understand both the internal structure and the formation mechanisms of loosely-bound composite objects.
+The production of (anti-)(hyper-)nuclei in high-energy collisions is commonly described by following two distinct approaches: formation by nucleon coalescence at the system (kinetic) freeze-out~\cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Blum:2017qnn} or thermal-statistical production at the chemical freeze-out~\cite{Andronic:2010qu,Andronic:2017}.
+Thanks to the large data samples of pp, \pPb~and \PbPb~collisions collected during the first ten years of operations of the CERN Large Hadron Collider (LHC), A Large Ion Collider Experiment (ALICE) Collaboration
+has measured the production of light nuclei and anti-nuclei at several centre-of-mass energies~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta, anielski-HQ14, Puccio:2019oyd, ALICE:nucleipp2017, Acharya:2017dmc, Acharya:2019rgc}, thus providing a crucial experimental input and a boost to theoretical and phenomenological investigations~\cite{Mrowczynski:2016xqm, Bellini:2018epz, Bazak:2018hgl, Zhao:2018lyf, Sun:2018mqq, Xu:2018jff, Oliinychenko:2018ugs}.
+In small collision systems, the experimental results seem to confirm the validity of the coalescence picture, with the most recent multiplicity-differential measurements pointing toward a dependence of the coalescence process on the volume of the particle-emitting source (''source size'' hereafter).
+In heavy-ion collisions, coalescence approaches that do not take into account the source size are not able to reproduce the data. 
+At the same time, the production of light nuclei, anti-nuclei and hypertriton as measured in \PbPb~collisions is found to be consistent with statistical-thermal model predictions and a non-zero deuteron elliptic flow is observed.
+This is surprising as (anti-)nuclei produced at chemical freeze-out are not expected to survive the hadronic phase: the deuteron is a ``fragile object'' when surrounded by the fireball created in heavy-ion collisions, because its binding energy ($B_E = 2.2$ MeV) is much lower than the characteristic temperatures of the system ($T_{chem} \approx 153$ MeV, $T_{kin} \approx 100$ MeV).
+Moreover, the cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}.
+These observations pose the ``(anti-)nuclei puzzle'': how can loosely-bound composite objects survive in the 
+dense and hot fireball, freeze-out and develop collective flow like the other light-flavour non-composite hadrons?
+
+In our study~\cite{Bellini:2018epz} we have extended and combined known formalisms used to describe (anti-)(hyper-)nuclei production in order to allow, for the first time, a direct comparison of the thermal and coalescence models as well as a direct comparison to the ALICE data.
+Identifying the coalescence parameter ($B_A$) as the key observable, we present a consistent picture across different collision systems (pp, \pPb, \PbPb) for light (anti-)(hyper-)nuclei with mass number $A = 2, 3$ and 4.
+We also suggest to address the open questions by looking at the production of nuclei and hyper-nuclei up to $A = 4$ that differ by size and properties, measured as a function of multiplicity used as a proxy for the source size.
+Whereas the (anti-)deuteron production has been measured multi-differentially and quite precisely with the LHC Run 1 and 2 data, the study of heavier objects with $A=3$ and 4 will greatly profit from the increase in integrated luminosity foreseen at the LHC Runs 3 and 4 in all collision systems~\cite{Citron:2018lsq}.
+A comprehension of (anti-)nuclei production mechanisms is not only relevant for nuclear and hadronic physics, but has applications in astrophysics and indirect Dark Matter searches~\cite{Aramaki:2015pii}.
+In recent years, it has been suggested that the detection of light anti-nuclei in space could provide a signature for the presence of Dark Matter in the Cosmos, see for instance~\cite{Cirelli:2014qia, Korsmeier:2017xzj}.
+Anti-deuterons and \antihethree~might indeed be produced by coalescence of antiprotons and antineutrons coming from the annihilation of Weakly Interacting Massive Particles into Standard Model particles, for which anti-nuclei created in reactions between primary cosmic ray protons and interstellar matter (pp, pA collisions) represent a source of background.
+
+The main features of the theoretical frameworks employed for our study are briefly summarised in Sec.~\ref{sec:prod}, whereas we address the reader to~\cite{Bellini:2018epz} for the full details.
+Section~\ref{sec:results} presents the main results and conclusions follow.
+
+\section{Modelling Light (anti-)(hyper-)nuclei production} \label{sec:prod}
+
+Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, protons, etc.), because their size is comparable to a fraction or the whole system created in high-energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions~\cite{Adam:2015vna}.
+Their size is typically defined as the rms of their (charge) wave-function, corresponding to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
+For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ relative to the two other nucleons.
+This difference in the wave-functions results in dramatic consequences for the production scenarios, as discussed in the following.
+The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
 
@@
 
-\section{The coalescence approach}
+\subsection{Thermal-statistical models} 
+Thermal-statistical models ~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
+In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV.
+
+\subsection{The coalescence approach}
 
@@
 
-\subsection{Comparison with data}
+\section{Comparison with data} \label{sec:results}
 

### 2019-03-31 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Continuing

@@
 
-\section{Introduction: the ''anti-nuclei'' puzzle}
+\section{Introduction: the ``anti-nuclei'' puzzle}
 The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these reactions, and can be used to understand both the internal structure and the formation mechanisms of loosely-bound composite objects.
@@
 
-The main features of the theoretical frameworks employed for our study are briefly summarised in Sec.~\ref{sec:prod}, whereas we address the reader to~\cite{Bellini:2018epz} for the full details.
+The main features of the theoretical frameworks employed for our study are briefly summarised in Sec.~\ref{sec:prod}, while we address the reader to~\cite{Bellini:2018epz} for the full details.
 Section~\ref{sec:results} presents the main results and conclusions follow.
 
-\section{Modelling Light (anti-)(hyper-)nuclei production} \label{sec:prod}
+\section{Modelling light (anti-)(hyper-)nuclei production} \label{sec:prod}
 
-Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, protons, etc.), because their size is comparable to a fraction or the whole system created in high-energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions~\cite{Adam:2015vna}.
-Their size is typically defined as the rms of their (charge) wave-function, corresponding to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ relative to the two other nucleons.
-This difference in the wave-functions results in dramatic consequences for the production scenarios, as discussed in the following.
-The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
+For our study, we consider nuclei and hyper-nuclei with mass number $A = 2, 3$ and 4, whose properties are summarised in Tab.
+\ref{tab:nucleusradii}.
+Those properties are the same as for their anti-matter counterparts and we assume that the same formation mechanisms are at play for matter and anti-matter\footnote{For brevity, in the following we refer to ``nuclei'' and ``hyper-nuclei'' but we imply both matter and anti-matter.}.
+Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, protons, etc.), because their size is comparable to a fraction or the whole system created in pp, \pPb~and \PbPb~collisions.
+The size is typically defined in two ways: a) as the rms of the (charge) distribution ($\lambda_A$), typically measured in electron scattering experiments, or b) as the size parameter of the object wave-function ($r_A$), typically taken as the gaussian solution of an isotropic harmonic oscillator potential in coalescence models.
+For light nuclei, $\lambda_A\approx$~2~fm.
+For the hyper-triton, theoretical calculations indicate a charge rms radius $\lambda_A\approx$~5~fm \cite{Nemura:1999qp}, driven by the average separation of the $\Lambda$ relative to the two other nucleons.
+Assuming a similar structure (e.g. a s-wave interaction for a bound state of a n or a $\Lambda$ with a
+deuteron), the hypertriton results in a much larger object than the other non-strange nuclei with $A=3$.
+A simple relation holds between $\lambda_A$ and $r_A$, see \cite{Bellini:2018epz}. 
+In Tab.~\ref{tab:nucleusradii} the binding energy ($B_E$) is also reported.
+The most tightly bound nucleus is \hefour, whereas the most loosely bound object is \hthreelambda, that is also the largest one.
+For the latter, we report the separation energy of the $\Lambda$ baryon from the deuteron ($B_\Lambda=0.13$~MeV).
+The large size and the low binding energy of the \hthreelambda~with respect to the other (hyper-)nuclei has important consequences on its production, as discussed in what follows.
 
@@
 $B_{E}$ is the binding energy in MeV.
-The size of the nucleus is given in terms of the (charge) rms radius of the wave-function, \rmsradius.
-The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced.
-Please note that the proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+The size parameter $r_{A}$, is chosen to approximately reproduce the measured/expected rms,  \rmsradius$^{meas}$~(fm).
+The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
 Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
- References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
+The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
 \label{tab:nucleusradii}
 \end{table}
-
-\subsection{Thermal-statistical models} 
-Thermal-statistical models ~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
-In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV.
 
@@
 \end{figure}
+
+\subsection{Thermal-statistical models} 
+Thermal-statistical models ~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
+In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV.
 

### 2019-03-31 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Continuing with models

@@
 Nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (pions, protons, etc.), because their size is comparable to a fraction or the whole system created in pp, \pPb~and \PbPb~collisions.
-The size is typically defined in two ways: a) as the rms of the (charge) distribution ($\lambda_A$), typically measured in electron scattering experiments, or b) as the size parameter of the object wave-function ($r_A$), typically taken as the gaussian solution of an isotropic harmonic oscillator potential in coalescence models.
+The size is typically defined in two ways: a) as the rms of the (charge) distribution ($\lambda_A$), typically measured in electron scattering experiments, or b) as the size parameter of the object wave-function ($r_A$), typically taken as the gaussian solution of an isotropic harmonic oscillator potential in coalescence calculations.
 For light nuclei, $\lambda_A\approx$~2~fm.
@@
 The size parameter $r_{A}$, is chosen to approximately reproduce the measured/expected rms,  \rmsradius$^{meas}$~(fm).
-The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm \cite{bernauer10} is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
-Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.
-The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
+The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
+Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
 \label{tab:nucleusradii}
@@
 \subsection{The coalescence approach}
-
-Starting from the model described in~\cite{Scheibl:1998tk, Blum:2017qnn}, we have obtained in \cite{Bellini:2018epz} a generalised expression for the coalescence parameter $B_A$
-
+In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk}.
+The coalescence probability is encoded in the coalescence parameter, $B_{A}$.
+Considering that at LHC energies the number of produced protons and neutrons at midrapidity as well as their momentum distributions are expected to be equal, $B_{A}$ is defined as
+%
+%
+\begin{equation}
+E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.,
+\label{eq:BA}
+\end{equation}
+%
+%
+where $p_{\mathrm{p,n}}$ are the proton and neutron momenta and $E_{p,n}$ their energies. 
+Equation~\ref{eq:BA} represents also the operative definition of $B_A$ that is used by experiments like ALICE to extract the coalescence probability starting from the measured nucleus and nucleon (proton) distributions.
+Starting from the model described in~\cite{Scheibl:1998tk, Blum:2017qnn}, we have obtained in \cite{Bellini:2018epz} a generalised expression for $B_A$
+%
+%
 \begin{equation}\label{eq:master}
-	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} } \;\;,
+B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} \;\;,
 \end{equation}
-
+%
+%
 \noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\rm T}$, its size parameter $r_A$ and the source radius $R$.
-Figure \ref{Fig:BA} shows the source radius dependence of $B_A$ for different composite objects, including the nuclei and hyper-nuclei with $A = 2, 3$ and 4 whose properties are reported in Tab.~\ref{tab:nucleusradii}.
-
+Very importantly, Eq.~\ref{eq:master} takes explicitly into account the source size ($R$), as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space.
+Moreover, the source size is identified with the  effective sub-volume of the whole system that is governed by the (momentum-dependent) homogeneity length of the interacting nucleons and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry~\cite{Scheibl:1998tk, Blum:2017qnn}.
+Figure~\ref{Fig:BA} shows the source radius dependence of $B_A$ for nuclei and hyper-nuclei with $A = 2, 3$ and 4 whose properties are reported in Tab.~\ref{tab:nucleusradii}. 
+For the cases in which more than one estimate for $r_A$ is available, we have adopted the lowest value for the calculations in Fig.~\ref{Fig:BA}.
+%
+%
 \begin{figure}[htb]
@@
 \end{figure} 
+%
+%
+We observe that the coalescence probability decreases with increasing mass number and $B_A$ decreases with increasing volume. 
+For a given $A$, the larger the object radius, the lower is $B_A$, as clearly visible by comparing \hethree~and \hthreelambda. 
+For objects with same $A$, mass and spin (e.g. the isobars \tritium~and \hethree), $B_A$ differs only due to the different radius $r_A$. 
+This difference is more relevant in small systems, because in large systems the difference between nucleus radii is much smaller than the size of the source.
 
-\subsection{Thermal-statistical models} 
+The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the lenght scale defined by the object radius relative to the source radius.
+
+\subsection{Thermal + blast-wave model} 
 Thermal-statistical models ~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
 In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV.
+The thermal model cannot -- alone -- be compared to the \pt-dependent coalescence description because it provides only predictions for \pt-integrated yields. 
+A thermal particle production implies a Boltzmann distribution of the momenta only for a static source, which is not the case of the rapidly expanding system produced in heavy-ion collisions. 
+The thermal model (i.e. the GSI-Heidelberg implementation we have considered) needs to be complemented by a
+hydrodynamic description of the rapidly expanding source. 
+To that end, we chose to use the Blast-Wave model, which has been proven to describe reasonably well the measured momentum distributions of protons. 
+Our ``thermal+blast-wave'' approach results from the combination of the two models: the \pt-dependence is modelled by the blast-wave whereas the normalisation (i.e.
+the \pt-integrated yield) is taken from the thermal model predictions.
 
 \section{Comparison with data} \label{sec:results}
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=\textwidth]{coal2Thermal2alice.png}
-\caption{(Color online) Coalescence parameter $B_A$ as a function of the average charged particle multiplicity density for various (hyper-)nuclei, up to $A = 4$.
-The coalescence calculations (continuous or dashed-dotted black lines) are compared to the thermal+blast-wave predictions (dashed blue line), as well as to pp (green square) and \PbPb~(red circles) collision data from ALICE~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Adam:2015yta}.
-}
-\label{Fig:comparison}
-\end{center}
-\end{figure}
 
@@
 
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=\textwidth]{coal2Thermal2alice.png}
+\caption{(Color online) Coalescence parameter $B_A$ as a function of the average charged particle multiplicity density for various (hyper-)nuclei, up to $A = 4$.
+The coalescence calculations (continuous or dashed-dotted black lines) are compared to the thermal+blast-wave predictions (dashed blue line), as well as to pp (green square) and \PbPb~(red circles) collision data from ALICE~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015,Adam:2015yta}.
+}
+\label{Fig:comparison}
+\end{center}
+\end{figure}
+
 \newpage

### 2019-03-31 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Thermal+blast wave

@@
 The formation of light anti- and hyper-nuclei in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions provides unique observables for the study of the system created in these reactions, and can be used to understand both the internal structure and the formation mechanisms of loosely-bound composite objects.
-The production of (anti-)(hyper-)nuclei in high-energy collisions is commonly described by following two distinct approaches: formation by nucleon coalescence at the system (kinetic) freeze-out~\cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Blum:2017qnn} or thermal-statistical production at the chemical freeze-out~\cite{Andronic:2010qu,Andronic:2017}.
+The production of (anti-)(hyper-)nuclei in high-energy collisions is commonly described by following two distinct approaches: formation by nucleon coalescence at the system (kinetic) freeze-out~\cite{Butler:1963, Kapusta:1980, Scheibl:1998tk, Blum:2017qnn} or thermal-statistical production at the chemical freeze-out~\cite{Andronic:2010qu,Andronic:2017}.
 Thanks to the large data samples of pp, \pPb~and \PbPb~collisions collected during the first ten years of operations of the CERN Large Hadron Collider (LHC), A Large Ion Collider Experiment (ALICE) Collaboration
-has measured the production of light nuclei and anti-nuclei at several centre-of-mass energies~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta, anielski-HQ14, Puccio:2019oyd, ALICE:nucleipp2017, Acharya:2017dmc, Acharya:2019rgc}, thus providing a crucial experimental input and a boost to theoretical and phenomenological investigations~\cite{Mrowczynski:2016xqm, Bellini:2018epz, Bazak:2018hgl, Zhao:2018lyf, Sun:2018mqq, Xu:2018jff, Oliinychenko:2018ugs}.
+has measured the production of light nuclei and anti-nuclei at several centre-of-mass energies~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta, ALICE:nucleipp2017, Acharya:2017dmc, Puccio:2019oyd, Acharya:2019rgc}, thus providing a crucial experimental input and a boost to theoretical and phenomenological investigations~\cite{Mrowczynski:2016xqm, Bellini:2018epz, Bazak:2018hgl, Zhao:2018lyf, Sun:2018mqq, Xu:2018jff, Oliinychenko:2018ugs}.
 In small collision systems, the experimental results seem to confirm the validity of the coalescence picture, with the most recent multiplicity-differential measurements pointing toward a dependence of the coalescence process on the volume of the particle-emitting source (''source size'' hereafter).
@@
 \subsection{The coalescence approach}
-In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk}.
+In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963, Kapusta:1980, Scheibl:1998tk}.
 The coalescence probability is encoded in the coalescence parameter, $B_{A}$.
@@
 This difference is more relevant in small systems, because in large systems the difference between nucleus radii is much smaller than the size of the source.  
-
+Incidentally, this could be experimentally verified with high precision measurements of the production of \tritium~relative to \hethree~in pp collisions. 
 The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the lenght scale defined by the object radius relative to the source radius.
@@
 \subsection{Thermal + blast-wave model} 
-Thermal-statistical models ~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
+Thermal-statistical models~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
 In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV. 
+Particle yields are derived from the partition function assuming a Grand Canonical ensemble\footnote{Extensions to small systems employ a canonical ensemble partition function to account for the exact conservation of quantum numbers in a finite size system, see for instance~\cite{Vovchenko:2018fiy}.} and they depend only on the mass of the particle and the temperature of chemical freeze-out, d$N$/d$y\propto$~exp$(-m/T_{\mathrm{chem}})$.
 The thermal model cannot -- alone -- be compared to the \pt-dependent coalescence description because it provides only predictions for \pt-integrated yields. 
 A thermal particle production implies a Boltzmann distribution of the momenta only for a static source, which is not the case of the rapidly expanding system produced in heavy-ion collisions. 
-The thermal model (i.e. the GSI-Heidelberg implementation we have considered) needs to be complemented by a
-hydrodynamic description of the rapidly expanding source. 
-To that end, we chose to use the Blast-Wave model, which has been proven to describe reasonably well the measured momentum distributions of protons. 
+The thermal model (i.e. the GSI-Heidelberg implementation we have considered here) needs to be complemented by a hydrodynamic description of the rapidly expanding source. 
+To that end, we use the Blast-Wave model~\cite{Schnedermann:1993ws}, which has been proven to describe reasonably well the measured momentum distributions of protons~\cite{Abelev:2013vea}. 
 Our ``thermal+blast-wave'' approach results from the combination of the two models: the \pt-dependence is modelled by the blast-wave whereas the normalisation (i.e.

### 2019-03-31 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Thermal+blast wave finished

@@
 the \pt-integrated yield) is taken from the thermal model predictions.
+In particular, to shape the (hyper-)nucleus transverse momentum distributions we use the blast-wave parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in \PbPb~collisions by ALICE for several centralities/multiplicities and reported in~\cite{Abelev:2013vea}.
+We therefore inherit the multiplicity-dependence of the radial expansion of the system from the measurements.
+The object size does not enter in the formulation of the blast-wave model.
+In our thermal+blast-wave model, for each centrality/multiplicity class, the coalescence parameter is extracted according to Eq.~\ref{eq:BA} (as done for data) from the predicted (hyper-)nucleus spectrum and the proton spectrum measured by ALICE~\cite{Abelev:2013vea}.
 
-\section{Comparison with data} \label{sec:results}
+\section{Results and discussion} \label{sec:results}
+As discussed in the previous sections, the coalescence model describe the coalescence parameter
 

### 2019-03-31 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Results part. Discussion and conclusions missing - sigh. I have to go for my lunch appointment ---will continue later.

@@
 Incidentally, this could be experimentally verified with high precision measurements of the production of \tritium~relative to \hethree~in pp collisions. 
-The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the lenght scale defined by the object radius relative to the source radius.
+The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the length scale defined by the object radius relative to the source radius.
 
@@
 \section{Results and discussion} \label{sec:results}
-As discussed in the previous sections, the coalescence model describe the coalescence parameter
+As discussed in the previous sections, the coalescence model provides an analytical expression for $B_A$ as a function of the source size $R$. 
+The thermal+blast-wave approach allows us to extract the $B_A$ as a function of the average charged particle multiplicity density, \avdNdeta. Data are also available as a function of multiplicity.
+In order to compare models and data, we therefore need to map multiplicity into source radius or viceversa. 
+As discussed more extensively in~\cite{Bellini:2018epz}, we perform this mapping based on the parameterisation $R = 0.473 \avdNdeta^{1/3}$. 
+The value of the empirical slope parameter is obtained by tuning the parameterisation such that the measured (anti-)deuteron \btwo~in the most central \PbPb~class falls onto the coalescence prediction.
+In this way, we constrain the coalescence volume with the more differential (anti-)deuteron data and assume that it is the same for all anti- and hyper-nuclei.
+In~\cite{Bellini:2018epz}, we used the parameterisation to map the \avdNdeta~into $R$.
+Here, we chose to apply the inverse relation and show the comparison between $B_A$ from models and data as a function of the experimentally accessible observable  \avdNdeta.
+The two choices are equivalent.
 
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.8\textwidth]{B3vsMult073.png}
-\caption{(Color online) Coalescence parameter $B_3$ for \hethree~as a function of the average charged particle multiplicity density.
-The coalescence calculation (continuous black line) is compared to two thermal+blast-wave predictions (dashed lines), obtained by using the Grand Canonical (GC, red)~\cite{Andronic:2017} and Canonical Statistical Model (CSM, blue) \cite{Vovchenko:2018fiy} expectations for the \hethree~yield, respectively.
-ALICE data from pp (green circles) and \PbPb~(red circles) collisions~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015} are reported.
-}
-\label{Fig:3He}
-\end{center}
-\end{figure}
+We compare $B_A$ as obtained from the coalescence  (Eq.~\ref{eq:master}) and the ther\-mal+\-blast-wa\-ve model approach in Fig.~\ref{Fig:comparison} as a function of \avdNdeta.
+With respect to~\cite{Bellini:2018epz}, we have extended our study up to $A=4$ \mbox{(hyper-)nuclei}.
+The available data from ALICE are also reported.
 
@@
 
+As an example, we have also computed $B_A$ for \hethree~according to the thermal+blast-wave approach for the \pPb~system, by using yield predictions from the Canonical Statistical Model from~\cite{Vovchenko:2018fiy} and the blast-wave parameters from~\cite{Abelev:2013haa}.
+The result is reported in Fig.
+\ref{Fig:3He}.
+
+Sigh! To be finished.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{B3vsMult073.png}
+\caption{(Color online) Coalescence parameter $B_3$ for \hethree~as a function of the average charged particle multiplicity density~\avdNdeta.
+The coalescence calculation (continuous black line) is compared to two thermal+blast-wave predictions (dashed lines), obtained by using the Grand Canonical (GC, red)~\cite{Andronic:2017} and Canonical Statistical Model (CSM, blue) \cite{Vovchenko:2018fiy} expectations for the \hethree~yield, respectively.
+ALICE data from pp (green circles) and \PbPb~(red circles) collisions~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015} are reported.
+}
+\label{Fig:3He}
+\end{center}
+\end{figure}
+
+\section{Conclusions}
+Sic! To be finished.
 \newpage

### 2019-06-04 Paper/aps/submit_12032019/main_aps.tex
Implemented comments from journal proofs for the hopefully last arxiv version

--- 2019-03-21 FrascatiPlot/Paper/aps/submit_12032019/main_aps.tex
@@
 
-\title{Testing production scenarios for (anti-)(hyper-)nuclei and exotica at LHC energies}
+\title{Testing production scenarios for (anti-)(hyper-)nuclei and exotica at energies available at the CERN Large Hadron Collider}
 
@@
 \email{alexander.kalweit@cern.ch}
-\affiliation{European Organisation for Nuclear Research (CERN) \\Geneva, Switzerland}
+\affiliation{European Organisation for Nuclear Research (CERN) \\1211 Geneva, Switzerland}
 
@@
 We propose to address experimentally the comparison of the production models by measuring the coalescence parameter systematically for different (anti-)(hyper-)nuclei in different collision systems and differentially in multiplicity.
-Such measurements are feasible with the current and upgraded LHC experiments. 
+Such measurements are feasible with the current and upgraded Large Hadron Collider experiments. 
 Our findings highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects and can serve as a basis for more refined calculations in the future.
@@
 Their size is typically defined as the rms of their (charge) wave-function, corresponding to about 2 fm for light (anti-)nuclei as obtained from electron scattering experiments. 
-For the hyper-triton, theoretical calculations indicate a rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ relative to the two other nucleons.
+For the hyper-triton, theoretical calculations indicate an rms of the wave-function of about 5 fm \cite{Nemura:1999qp}, significantly larger than that of non-strange nuclei with mass number $A = 3$ and driven by the average separation of the $\Lambda$ relative to the other two nucleons.
 This difference in the wave-functions results in dramatic consequences for the production scenarios, as discussed in the following.
-The properties of the objects under study here are summarised in Tab. \ref{tab:nucleusradii}.
+The properties of the objects under study here are summarised in Table \ref{tab:nucleusradii}.
 
-For about sixty years, coalescence models have been used to describe the formation of composite objects \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf}.
+For about 60 years, coalescence models have been used to describe the formation of composite objects \cite{Butler:1963, Kapusta:1980, Sato:1981ez, Nagle:1996vp, Scheibl:1998tk, Cho:2017dcy, Blum:2017qnn, Bazak:2018hgl, Zhao:2018lyf}.
 Surprisingly, thermal-statistical models have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions \cite{Andronic:2010qu,Andronic:2017}.
@@
 Particle abundances are fixed at chemical freeze-out, when inelastic collisions cease.
-Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, that affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
-Once the mean free path for elastic collisions is larger than the system size, the fireball freezes-out kinetically at $T_{kin} \approx$ 90 MeV~\cite{Abelev:2013vea}. 
-In such a dense and hot environment, composite objects with binding energies that are small with respect to the temperature of the system, appear as ``fragile''. 
+Further elastic and pseudo-elastic collisions occur among the components of the expanding fireball, which affect the spectral shapes and the measurable yields of short-lived (strongly decaying) hadronic resonances.
+Once the mean free path for elastic collisions is larger than the system size, the fireball freezes-out kinetically at $T_{kin} \approx$ 90~MeV~\cite{Abelev:2013vea}. 
+In such a dense and hot environment, composite objects with binding energies that are low with respect to the temperature of the system, appear as ``fragile''. 
 For instance, the binding energy of the deuteron is $B_{E, d}$ = 2.2~MeV~$\ll~T_{chem},~T_{kin}$.
-The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo)-elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}.
+The cross-section for pion-induced deuteron breakup is significantly larger than the typical (pseudo-)elastic cross-sections for the re-scattering of hadronic resonance decay products \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}.
 Similarly, the elastic cross-section driving deuteron spectra to kinetic equilibration in central heavy-ion collisions \cite{Acharya:2017dmc} is smaller than the breakup cross-section \cite{Garcilazo:1982yc, Bass:1998ca, Schukraft:2017nbn, Oliinychenko:2018ugs}
 (Anti-)nuclei produced at chemical freeze-out are not expected to survive the hadronic phase, yet their measured production is consistent with statistical-thermal model predictions and a non-zero elliptic flow is observed \cite{Acharya:2017dmc, Puccio:2019oyd}.
-Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary \cite{Castorina:2019pnb}, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, (c.) the continuous interplay of breakup and formation reactions resulting in the coincidence of thermal and kinetic equilibration \cite{Oliinychenko:2018ugs, Xu:2018jff}, (d.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
+Several solutions have been proposed to solve this ``(anti-)nuclei puzzle'': (a.) a sudden freeze-out at the QGP-hadron phase boundary \cite{Castorina:2019pnb}, (b.) the thermal production of these objects as compact quark bags \cite{Andronic:2017}, (c.) the continuous interplay of breakup and formation reactions resulting in the coincidence of thermal and kinetic equilibration \cite{Oliinychenko:2018ugs, Xu:2018jff},
+and (d.) the coincidence of coalescence and thermal production \cite{Scheibl:1998tk, HeinzTorino}.
 Data from rescattering of short-lived hadronic resonances suggest a long-lasting hadronic phase \cite{Abelev:2014uua}, thus strongly disfavouring hypothesis (a.). 
 Hypothesis (b.) cannot presently be tested beyond the agreement of measured (anti-)nuclei yields with statistical-thermal model predictions. 
-Calculations for (c.) are currently available only for deuterons.
-Hypothesis (d.) is scrutinised in this letter.
+Calculations for hypothesis (c.) are currently available only for deuterons. Hypothesis (d.) is scrutinised in this paper.
 To this purpose, we propose a new method to compare models that also allows for a direct comparison with LHC data. 
@@
                 & \hethree                         & ppn                 &   7.7180428  (23) & 1/2   & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
-                & \hthreelambda               & p$\Lambda$n &    0.13 $\pm$ 0.05  \footnote{For hypertriton, we report here the separation energy of the $\Lambda$ from the two other nucleons.} & 1/2  &  4.9 --  10.0                     &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]
+                & \hthreelambda               & p$\Lambda$n &    0.13 $\pm$ 0.05  \footnote{For the hypertriton, we report here the separation energy of the $\Lambda$ from the other two nucleons.} & 1/2  &  4.9 --  10.0                     &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]
 \end{tabular}
@@
 \indent For the first time, LHC data allow for the study of \mbox{(anti-)(hyper-)nuclei} production as a function of the system- and object-size. 
-A quantitative comparison of the production scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
+A quantitative comparison of the production scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea of studying the production rates of nuclei with similar masses but very different internal structures, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}.
 As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters proposed here.
@@
 In a simple coalescence approach, \bA~is expected to be independent of momentum and of the object size relative to the volume of particle emission (hereafter referred to as ``source size'').
-While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, Acharya:2019rgc, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease of $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
+While this picture is found to be approximately valid in pp and \pPb~collisions~\cite{ALICE:nucleipp2017, Acharya:2019rgc, anielski-HQ14}, it breaks down in \PbPb~collisions, which exhibit a strong decrease in $B_{A}$ with centrality \cite{ALICE:deuteronppPbPb2015}.
 The elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.
@@
 \noindent for point-like constituents. 
-We follow the gaussian ansatz to obtain fully analytic solutions.
+We follow the Gaussian ansatz to obtain fully analytic solutions.
 In Tab.~\ref{tab:nucleusradii}, we list the measured rms of the wave-function, $\rmsradius^{meas}$, and the $r_{A}$ parameter derived from these relations. 
@@
 where \dradius~is the size parameter, \rperp~and \rpar~are the lengths of homogeneity of the coalescence volume and $m_{T}$ is the transverse mass of the coalescing nucleons.
-The nucleus size enters in the  calculation of \btwo~via $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation~\cite{Scheibl:1998tk}
+The nucleus size enters the calculation of \btwo~via $\langle C_{d} \rangle$, as well as the homogeneity volume $\rperp^{2}\rpar$, according to the relation~\cite{Scheibl:1998tk}
 %
@@
 %
-Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of $\langle C_{d} \rangle$ and \btwo, calculated assuming (a.) $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, irrealistic $\dradius = 10$ fm.
-As shown in Fig. \ref{fig:radiusDependence}, $\langle C_{d} \rangle$ suppresses significantly the production of objects with radius larger than the source.
+Figure \ref{fig:radiusDependence} shows the source radius ($R$) dependence of $\langle C_{d} \rangle$ and \btwo, calculated assuming (a.) $\dradius = 0$, (b.) $\dradius = 0.3$ fm, (c.) the actual value $\dradius = 3.2$ fm~\cite{Mohr:2015ccw}, (d.) a larger, unrealistic $\dradius = 10$ fm.
+As shown in Fig. \ref{fig:radiusDependence}, $\langle C_{d} \rangle$ suppresses significantly the production of objects with a radius larger than the source.
 
@@
 \includegraphics[width=\columnwidth]{theory_coalescence_Cd_B2_vert.png}
-\caption{{The quantum-mechanical correction factor $\langle C_{d} \rangle$ (top, see Eq.~\ref{eq:Cdapprox}) and the coalescence parameter \btwo~for deuteron (bottom, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
-The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the vertical dotted line for $\dradius = 3.2$ fm.}}
+\caption{{Quantum-mechanical correction factor $\langle C_{d} \rangle$ (top, see Eq.~\ref{eq:Cdapprox}) and coalescence parameter \btwo~for the deuteron (bottom, see Eq.~\ref{eq:B2approx}) as a function of the radius of the source $R$, calculated assuming a size parameter for the deuteron $\dradius = 0, 0.3, 3.2$ and $10$ fm.
+The inflection point of $\langle C_{d} \rangle$ corresponds to $R = \dradius/\sqrt{6}$ and is indicated in the left panel by the dotted vertical line for $\dradius = 3.2$ fm.}}
 \label{fig:radiusDependence}
@@
 Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
-For a large source where $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space. 
+For a large source where $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation and, thus, decreases for large distances in configuration space. 
 %
 
-\section{Statistical-thermal approach combined with blast-wave}\label{sec:thermal}
-In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and approximately scale as d$N$/d$y \propto (2J_{A} + 1)\exp(-m/T_{chem})$.
+\section{Statistical-thermal approach combined with the blast-wave model}\label{sec:thermal}
+In the statistical-thermal approach \cite{Petran:2013dva,Wheaton:2004qb,Andronic:2005yp}, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to $T_{chem}$ due to their large mass and scale approximately as d$N$/d$y \propto (2J_{A} + 1)\exp(-m/T_{chem})$.
 The thermal model implements eigenvolume corrections by fixing the object radius as an external parameter.
@@
 With the resulting spectra, we calculate \bA~for a given \pt/$A$ and compare it with coalescence expectations. 
-In the following, we label this model as ``thermal+blast-wave''.
+In the following, we label this model ``thermal+blast-wave''.
 
@@
 Experimentally, the source size can be controlled by selecting different collision geometries, i.e. different centralities \cite{Abelev:2013qoq}. 
-This mapping is based on the following parameterisation:
+This mapping is based on the parameterisation
 %
@@
 We justify the choice of Eq.~\ref{eq:radiusParameterisation} by identifying the source volume as the effective sub-volume of the whole system that is governed by the homogeneity length of the interacting nucleons (as in \cite{Scheibl:1998tk}) and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry~\footnote{To match the Bertsch-Pratt parameterisation ($R_{out}, R_{side}, R_{long}$) employed by experiments, with the Yano-Koonin-Podgoretskii (\rperp, \rpar, $R_{0}$) parameterisation used in the coalescence model,  we identify $\rperp = R_{side}$, $\rpar = R_{long}$ and then take $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.}.
-The HBT radii scale with \avdNdeta$^{1/3}$ and we make the simplifying assumption that this scaling holds across collision systems, which is approximately fulfilled in data \cite{Adam:2015vna,Adam:2015pya}.
+The HBT radii scale with \avdNdeta$^{1/3}$ and we make the simplifying assumption that this scaling holds across collision systems, which is approximately fulfilled in the data \cite{Adam:2015vna,Adam:2015pya}.
 We also note that the HBT radii, and thus also the source size, depend on the pair average transverse momentum $\langle k_{\mathrm{T}}\rangle$~\cite{Aamodt:2011mr}. 
 In contrast to \cite{Blum:2017qnn}, we do not explicitly use the measured HBT radii in our study because using a linear fit to the ALICE HBT data \cite{Abelev:2012sq,Adam:2015vna} would result in a smaller source size ($R \approx$~4~fm) than required by the measured \btwo~to agree with the coalescence prediction ($R \approx$~5.5~fm) in central \PbPb~collisions.
-We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence of the source size, in contrast to a similar coalescence study reported in \cite{Sun:2018mqq} (for a detailed discussion on possible alternative source volume parameterisations, see Appendix \ref{appendixA}).
+We do however take into account the experimentally observed $\langle k_{\mathrm{T}}\rangle$ dependence of the source size, in contrast to a similar coalescence study reported in \cite{Sun:2018mqq} (for a detailed discussion of possible alternative source volume parameterisations, see the Appendix \ref{appendixA}).
 %
-Production via coalescence could also be investigated by looking at the transverse momentum dependence of $B_{A}$. However, 
-the advantage of studying these effects as a function of multiplicity/centrality is that system size offers a larger lever arm. 
-For a fixed \pt/$A$, \btwo~changes by about a factor 50 going from pp to central \PbPb~collisions, whereas \btwo~changes by a factor two going from \pt/$A$~=~0.4~GeV/$c$ to \pt/$A$~=~2.2~GeV/$c$  in most central \PbPb~collisions \cite{ALICE:deuteronppPbPb2015}, and by less than a factor two in the measured \pt/$A$ range in pp collisions \cite{ALICE:nucleipp2017, Acharya:2019rgc}.
+Production via coalescence could also be investigated by looking at the transverse momentum dependence of $B_{A}$. 
+However, the advantage of studying these effects as a function of the multiplicity/centrality is that the system size offers a larger lever arm. 
+For a fixed \pt/$A$, \btwo~changes by a factor of about 50 going from pp to central \PbPb~collisions, whereas \btwo~changes by a factor of two going from \pt/$A$~=~0.4~GeV/$c$ to \pt/$A$~=~2.2~GeV/$c$  in most central \PbPb~collisions \cite{ALICE:deuteronppPbPb2015}, and by a factor of less than two in the measured \pt/$A$ range in pp collisions \cite{ALICE:nucleipp2017, Acharya:2019rgc}.
 
@@
 		\includegraphics[width=.95\columnwidth]{compareThermalAndCoalescence.png}
-		\caption{Comparison of the coalescence parameters measured by ALICE (solid markers) for deuterons (upper panel), \hethree\ (middle panel) and \hthreelambda\ (lower panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
+		\caption{Comparison of the coalescence parameters measured by ALICE (filled symbols) for deuterons (upper panel), \hethree\ (middle panel) and \hthreelambda\ (lower panel) in pp \cite{ALICE:nucleipp2017} and Pb--Pb~\cite{ALICE:deuteronppPbPb2015, Adam:2015yta} collisions with the  thermal+blast-wave model expectations (dotted line) and the coalescence predictions (solid lines).
 The dashed line in the lower right panel corresponds to the coalescence prediction for the \hthreelambda\ with a larger radius.
@@
 For \hethree, the models exhibit a qualitatively similar $R$-dependence but differ by a factor of about 1.5 to 2. 
-The currently available data are consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on data. 
-Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
+The currently available data are consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty in the data. 
+Both approaches show large differences (a factor of 5 to 6 for central Pb--Pb collisions and a factor of more than 50 for $R < 2$~fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
 The only data point available so far in Pb--Pb collisions is in agreement with the thermal+blast-wave model but differs by 6$\sigma$ from our coalescence calculation.
-This discrepancy might differ for calculations that use a more realistic (non-gaussian) wave-function.
+This discrepancy might differ for calculations that use a more realistic (non-Gaussian) wave-function.
 In \cite{Zhang:2018euf} it is argued that the difference between data and coalescence might be explained by a later formation through coalescence of $\Lambda$s and deuterons. 
-A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda~is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}.
+A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda~is not considered here, as there is no evidence for its existence~\cite{Mart:1996ay}.
 
-Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing $R$, underlining the need for additional multiplicity-differential data to distinguish between the two production scenarios.
+Most importantly, Fig.~\ref{fig:CompareThermalAndCoalescence} shows that the difference between the two approaches increases with decreasing $R$, highlighting the need for additional multiplicity-differential data to distinguish between the two production scenarios.
 For \hthreelambda~we considered also a prediction from coalescence for a wider wave-function (see Fig.
@@
 \section{(Anti-)triton production}
-For isobars with same spin but different wave-function, like \tritium~(\antitritium)~and \hethree~(\antihethree), Eq.~\ref{eq:master} provides a relation between the relative coalescence probabilities as corollary:
+For isobars with the same spin but different wave-functions, like \tritium~(\antitritium)~and \hethree~(\antihethree), Eq.~\ref{eq:master} provides a relation between the relative coalescence probabilities as the corollary:
 
@@
 It is to be noted that the transverse momentum dependence of this ratio originates solely from the \pt-dependence of the source volume.
-The ratio $\rho$ is reported in Fig.~\ref{fig:sourceVolume} for \pt/$A$~=~0.75 \GeVc~of the two isobars and as a function of the average charged particle multiplicity.
-Multiplicity is obtained from the system radius by inverting Eq.~\ref{eq:radiusParameterisation}.
+The ratio $\rho$ is reported in Fig.~\ref{fig:rhoratio} for \pt/$A$~=~0.75 \GeVc~of the two isobars and as a function of the average charged particle multiplicity. 
+The multiplicity is obtained from the system radius by inverting Eq.~\ref{eq:radiusParameterisation}.
 The coalescence model predicts a dependence of $\rho$ on the system size and thus on the charged particle multiplicity.
-In particular, the production of \tritium~(\antitritium) is predicted by our model to be up to a factor two more abundant than the production of \hethree~(\antihethree) in small systems.
+In particular, the production of \tritium~(\antitritium) is predicted by our model to be more abundant by up to a factor of two than the production of \hethree~(\antihethree) in small systems.
 Such an excess of (anti-)tritons is not expected in thermal-statistical hadronisation.
-Since the two isobars have the same mass, spin and baryon number, the Grand Canonical thermal model~\cite{Andronic:2010qu,Andronic:2017} predicts a \tritium/\hethree~ratio equal to unity.
-The same holds true when taking into account the potential suppression of \mbox{(anti-)nuclei} yields due to explicit conservation of baryon number, as in Canonical Statistical Model calculations~\cite{Vovchenko:2018fiy}.
-Existing (anti-)triton measurements in pp collisions~\cite{ALICE:nucleipp2017} are limited by statistical precision and thus do not allow yet for a distinction between the two scenarios.
+Since the two isobars have the same mass, spin, and baryon number, the Grand Canonical thermal model~\cite{Andronic:2010qu,Andronic:2017} predicts a \tritium/\hethree~ratio equal to unity.
+The same holds true when taking into account the potential suppression of \mbox{(anti-)nucleus} yields due to explicit conservation of the baryon number, as in Canonical Statistical Model calculations~\cite{Vovchenko:2018fiy}.
+Existing (anti-)triton measurements in pp collisions~\cite{ALICE:nucleipp2017} are limited by statistical precision and thus do not yet allow for a distinction between the two scenarios.
 
@@
 		\caption{Yield of \tritium~relative to \hethree~for \pt/$A$~=~0.75~\GeVc~as defined by Eq.~\ref{eq:rho} in the coalescence picture (black line).
-The source radius has been mapped into average charged particle multiplicity by using the parameterisation constrained to the ALICE \btwo~measurement described in Sec.~\ref{sec:radiiParamet}.
-The orange dashed line represents the expectation from statistical hadronisation models.
+The source radius has been mapped into the average charged particle multiplicity by using the parameterisation constrained to the ALICE \btwo~measurement described in Sec.~\ref{sec:radiiParamet}.
+The dashed orange line represents the expectation from statistical hadronisation models.
 Colored arrows highlight the multiplicity range spanned by ALICE measurements in different collision systems.}
-		\label{fig:sourceVolume}
+		\label{fig:rhoratio}
 	\end{center}
@@
 In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to \hethree~due to its wider wave-function.
-	\item In \PbPb~collisions, the very limited amount of data available favours the thermal+blast-wave model prediction within our assumptions.
+	\item In \PbPb~collisions, the very limited number of data available favours the thermal+blast-wave model prediction within our assumptions.
 	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects.
@@
 Thus, its possible production via coalescence in pp collisions would be subject to a similar suppression as the hyper-triton.
-Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
+Setting a final word on the production mechanisms also has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space within ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments.
 
@@
 \section{Comparison of alternative source volume parameterisations} \label{appendixA} 
-For the considerations discussed in this work and in similar ones, one crucial aspect has to be taken into account, namely how the source radius is parameterised as a function of multiplicity and transverse momentum.
+For the considerations discussed in this work and in similar reports, one crucial aspect has to be taken into account, namely how the source radius is parameterised as a function of the multiplicity and transverse momentum.
 As discussed in Sec.~\ref{sec:radiiParamet}, for our main result we rely on the parameterisation given by Eq.~\ref{eq:radiusParameterisation}, which assumes a linear dependence between the cubic root of the measured average charged particle multiplicity density and the radius of the source.
 In order to extract the $a$ and $b$ coefficients of Eq.~\ref{eq:radiusParameterisation}, several solutions can be adopted. 
-One possibility is to fix the coefficients by fitting the available HBT data from ALICE~\cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq} with Eq.~\ref{eq:radiusParameterisation}, as shown in Fig.~\ref{fig:sourceVolume} by the data points fitted with the gray dotted line.
+One possibility is to fix the coefficients by fitting the available HBT data from ALICE~\cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq} with Eq.~\ref{eq:radiusParameterisation}, as shown in Fig.~\ref{fig:sourceVolume} by the data points fitted with the dotted gray line.
 %
@@
 The dotted gray line is the result of a linear fit to the ALICE HBT data~\cite{Adam:2015vna, Adam:2015pya, Abelev:2012sq}, according to Eq.~\ref{eq:radiusParameterisation} with $a$~=~0.339~fm and $b$~=~0.128~fm.
-		The blue dashed line represents the parameterisation used in \cite{Sun:2018mqq}, corresponding to $a$~=~0.83~fm and $b$~=~0.
-		The continuous black line represents the parameterisation used in our study ($a$~=~0.473~fm and $b$~=~0) and obtained by a constraint from the \btwo~measured in central (0-10$\%$) \PbPb~collisions.}
+		The dashed blue line represents the parameterisation used in \cite{Sun:2018mqq}, corresponding to $a$~=~0.83~fm and $b$~=~0.
+		The solid black line represents the parameterisation used in our study ($a$~=~0.473~fm and $b$~=~0) and obtained by a constraint from the \btwo~measured in central (0-10$\%$) \PbPb~collisions.}
 		\label{fig:sourceVolume}
@@
 %
-In order to preserve the momentum dependence of the source volume, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) from pion HBT is chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nuclei production.
+In order to preserve the momentum dependence of the source volume, the highest available $k_{\mathrm{T}}$ ($\approx$ 0.9 \GeVc) from pion HBT is chosen as it is closest in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon ($p_{\mathrm{T}} \approx$ 0.8 \GeVc) accessible by ALICE for the measurement of nucleus production.
 Ideally, one would use the proton femtoscopic radii, but given the availability of these measurements in only some of the collision systems and centralities, we assume that $m_{\mathrm{T}}$-scaling holds.
 The fit to the ALICE data results in $a$~=~0.339~fm and $b$~=~0.128~fm.
-However, this approach does not describe the deuteron \btwo~data: we observe that in order for the measured \btwo~to agree with the coalescence prediction in most central \PbPb~collisions, a larger source radius of $R \approx 5.5$ fm is required instead of $R \approx 4$ fm as resulting from the HBT fit.
+However, this approach does not describe the deuteron \btwo~data: we observe that in order for the measured \btwo~to agree with the coalescence prediction in most central \PbPb~collisions, a larger source radius of $R \approx 5.5$ fm is required instead of the $R \approx 4$ fm resulting from the HBT fit.
 This might also indicate that the volume relevant for the coalescence process is slightly larger than the homogeneity volume that can be extracted from HBT studies.
 Because of this, we chose to constrain the parameterisation to the measured \btwo~in central \PbPb~collisions for \pt~=~0.75 \GeVc~as well as to the origin ($b = 0$). 
-The resulting parameterisation, with $a = 0.473$ fm, is reported in Fig.~\ref{fig:sourceVolume} with a continuous black line, and it is used for the results of our study discussed in Sec.~\ref{sec:results}.
+The resulting parameterisation, with $a = 0.473$ fm, is represented in Fig.~\ref{fig:sourceVolume} with a solid black line, and it is used for the results of our study discussed in Sec.~\ref{sec:results}.
 
@@
 However, their approach deviates from ours as they neglect the momentum dependence of the source volume and constrain it with HBT data at low momentum ($k_{\rm T} = 0.25$ \GeVc). 
-The parameterisation from \cite{Sun:2018mqq} ($a$~=~0.83~fm and $b$~=~0) is shown for comparison in Fig.~\ref{fig:sourceVolume} as the blue dashed line.
-While this choice allows for a good description of \pt-integrated yield ratios (e.g.
-d/p, \hethree/p, \hthreelambda/$\Lambda$)~\cite{Sun:2018mqq}, using this parameterisation for the \pt-differential study would lead to a significantly lower coalescence probability than measured caused by a much larger source volume (e.g.
-a \btwo~lower by a factor 5.6 for \pt~=~0.75~\GeVc, corresponding to a a factor two larger radius).
-In other words, by integrating over transverse momentum, one looses sensitivity to the \pt-dependence of the coalescence probability as the object radius becomes dominated by the large source volumina for small $k_{\rm T}$ (see Eq.~\ref{eq:master}).
+The parameterisation from \cite{Sun:2018mqq} ($a$~=~0.83~fm and $b$~=~0) is shown for comparison in Fig.~\ref{fig:sourceVolume} as the dashed blue line.
+While this choice allows for a good description of \pt-integrated yield ratios (e.g., d/p, \hethree/p, \hthreelambda/$\Lambda$)~\cite{Sun:2018mqq}, using this parameterisation for the \pt-differential study would lead to a significantly lower coalescence probability than measured, caused by the much larger source volume (e.g., a \btwo~lower by a factor of 5.6 for \pt~=~0.75~\GeVc, corresponding to a factor of two larger radius).
+In other words, by integrating over the transverse momentum, one loses sensitivity to the \pt-dependence of the coalescence probability as the object radius becomes dominated by the large source volumina for small $k_{\rm T}$ (see Eq.~\ref{eq:master}).
 

### 2020-04-01 FrascatiPlot/generateBWpredictionsB2.C
Updated 5 TeV PbPb Blast wave and yields with published values

@@ -232,8 +232,7 @@ void GetParams_PbPb502TeV(Double_t *parT, Double_t *parTerr, Double_t *parN, Dou
   //BW Results from Livio (email 27/01/2017): fit of the spectra from 24.01.2017 (approval forum, iteration 1)
   //Parameters and proton yield can be found at:
   //https://gitlab.cern.ch/njacazio/SpectraAnalysisRun2/tree/master/results/spectra/spectra-pag/Preliminaries/QM2017
-
-  Double_t bt[10]    = {0.086, 0.088, 0.091, 0.094, 0.099, 0.106, 0.104, 0.127, 0.147, 0.163};
+ /* Double_t bt[10]    = {0.086, 0.088, 0.091, 0.094, 0.099, 0.106, 0.104, 0.127, 0.147, 0.163};
   Double_t bterr[10] = {0.004, 0.004, 0.004, 0.004, 0.004, 0.005, 0.005, 0.006, 0.007, 0.008};
 
   Double_t bn[10]    = {0.751, 0.753, 0.752, 0.778, 0.824, 0.890, 1.027, 1.213, 1.627, 2.254};
@@ -252,6 +251,27 @@ void GetParams_PbPb502TeV(Double_t *parT, Double_t *parTerr, Double_t *parN, Dou
   //pi+  + pi- 
   Double_t dNdyPion[10]    = {1702.3, 1376.59, 1037.78, 710.13, 466.401, 291.383, 170.758, 88.6999, 41.6013, 16.2665};
   Double_t dNdyErrPion[10] = {87.4099, 71.5484, 51.191, 32.7179, 21.4739, 13.3082, 8.10989, 4.42991, 2.05458, 0.840404};
+  end preliminary results */
+  //Published   
+  Double_t bb[10]    = {0.663, 0.660, 0.655, 0.643, 0.622, 0.595, 0.557, 0.506, 0.435, 0.355};
+  Double_t bberr[10] = {0.003, 0.003, 0.003, 0.003, 0.003, 0.004, 0.005, 0.008, 0.011, 0.016};
+  
+  Double_t bt[10]    = {0.090, 0.091, 0.094, 0.097, 0.101, 0.108, 0.115, 0.129, 0.147, 0.161};
[…]

### 2020-04-01 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Final version of the proceedings

@@
 \title{Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC}
-\author{F. Bellini (CERN, Geneva) \footnote{Presenter. For correspondence: francesca.bellini@cern.ch} 
-	    \\and A. P. Kalweit (CERN, Geneva)}
-\thanks{XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}%
-\address{}
+\author{F. Bellini\footnote{Presenter.} and A. P. Kalweit 
+	\address{European Organisation for Nuclear Research, Geneva \\E-mail: francesca.bellini@cern.ch}}
+\thanks{Proceedings of the XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}%
+
 \maketitle
@@
 This difference is more relevant in small systems, because in large systems the difference between nucleus radii is much smaller than the size of the source.  
-Incidentally, this could be experimentally verified with high precision measurements of the production of \tritium~relative to \hethree~in pp collisions. 
+Incidentally, this could be experimentally verified with high-precision measurements of the production of \tritium~relative to \hethree~in pp and \pPb~collisions. 
 The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the length scale defined by the object radius relative to the source radius.
@@
 In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV. 
-Particle yields are derived from the partition function assuming a Grand Canonical ensemble\footnote{Extensions to small systems employ a canonical ensemble partition function to account for the exact conservation of quantum numbers in a finite size system, see for instance~\cite{Vovchenko:2018fiy}.} and they depend only on the mass of the particle and the temperature of chemical freeze-out, d$N$/d$y\propto$~exp$(-m/T_{\mathrm{chem}})$.
+Particle yields are derived from the partition function assuming a Grand Canonical ensemble\footnote{Extensions to small systems employ a canonical ensemble partition function to account for the exact conservation of quantum numbers in a finite size system, see for instance~\cite{Vovchenko:2018fiy}.} and they depend only on the mass of the particle and the temperature of chemical freeze-out, d$N$/d$y\propto$~(2$J_A$+1)exp$(-m_{A}/T_{\mathrm{chem}})$.
 The thermal model cannot -- alone -- be compared to the \pt-dependent coalescence description because it provides only predictions for \pt-integrated yields. 
@@
 the \pt-integrated yield) is taken from the thermal model predictions.
-In particular, to shape the (hyper-)nucleus transverse momentum distributions we use the blast-wave parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in \PbPb~collisions by ALICE for several centralities/multiplicities and reported in~\cite{Abelev:2013vea}.
+In particular, to describe the (hyper-)nucleus transverse momentum distributions we use the blast-wave parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in \PbPb~collisions by ALICE for several centralities/multiplicities and reported in~\cite{Abelev:2013vea}.
 We therefore inherit the multiplicity-dependence of the radial expansion of the system from the measurements.
@@
 As discussed in the previous sections, the coalescence model provides an analytical expression for $B_A$ as a function of the source size $R$. 
-The thermal+blast-wave approach allows us to extract the $B_A$ as a function of the average charged particle multiplicity density, \avdNdeta. Data are also available as a function of multiplicity.
+The thermal+blast-wave approach allows us to extract the $B_A$ as a function of the average charged particle multiplicity density, \avdNdeta.
+Measurements are performed differentially in centrality/multiplicity.
 In order to compare models and data, we therefore need to map multiplicity into source radius or viceversa. 
-As discussed more extensively in~\cite{Bellini:2018epz}, we perform this mapping based on the parameterisation $R = 0.473 \avdNdeta^{1/3}$. 
+As discussed more extensively in~\cite{Bellini:2018epz}, we perform this mapping based on the parameterisation $R = 0.473 \avdNdeta^{1/3}$ for \pt/$A$~=~0.75 \GeVc.
+The slope is smaller for larger \pt's and larger for lower \pt.
 The value of the empirical slope parameter is obtained by tuning the parameterisation such that the measured (anti-)deuteron \btwo~in the most central \PbPb~class falls onto the coalescence prediction.
-In this way, we constrain the coalescence volume with the more differential (anti-)deuteron data and assume that it is the same for all anti- and hyper-nuclei.
+In other words, we constrain the coalescence volume with the more differential (anti-)deuteron data and assume that it is the same for all (hyper-)nuclei.
 In~\cite{Bellini:2018epz}, we used the parameterisation to map the \avdNdeta~into $R$.
-Here, we chose to apply the inverse relation and show the comparison between $B_A$ from models and data as a function of the experimentally accessible observable  \avdNdeta.
+Here, we chose to apply the inverse relation and compare $B_A$ from models with ALICE data as a function of the experimentally accessible observable~\avdNdeta.
 The two choices are equivalent.
+This comparison is reported in Fig.~\ref{Fig:comparison}.
+%We compare $B_A$ as obtained from the coalescence  (Eq.~\ref{eq:master}) and the ther\-mal+\-blast-wa\-ve model approach in Fig.~\ref{Fig:comparison} as a function of \avdNdeta. 
+With respect to~\cite{Bellini:2018epz}, we have now extended our study up to $A=4$ \mbox{(hyper-)nuclei}.
 
-We compare $B_A$ as obtained from the coalescence  (Eq.~\ref{eq:master}) and the ther\-mal+\-blast-wa\-ve model approach in Fig.~\ref{Fig:comparison} as a function of \avdNdeta.
-With respect to~\cite{Bellini:2018epz}, we have extended our study up to $A=4$ \mbox{(hyper-)nuclei}.
-The available data from ALICE are also reported.
+We observe that for deuterons, the coalescence and thermal+blast-wave approaches lead to similar predictions and describe reasonably the \PbPb~data. 
+For \hethree, the models exhibit a qualitatively similar mul\-ti\-pli\-ci\-ty-dependence with the magnitude of $B_A$ differing by a factor 1.5 to 2 going from large to small systems.
+The currently available data for \hethree~are consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on data.
+Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for \avdNdeta~<~100) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree.
+The only data point available so far in \PbPb~collisions is in agreement with the thermal+blast-wave model but differs by 6$\sigma$ from our coalescence calculation. 
+Also for \hefour~and \hefourlambda~the coalescence probability is a steeply falling function of multiplicity in both approaches, which differ in magnitude from few units at high multiplicities to O(10$^{2}$) in small systems.
+We conclude that the difference between the two approaches increases from large to small systems, which advocates for new multiplicity-differential data in all collision systems to distinguish between the two production scenarios.
+For \hthreelambda~and \hefourlambda~we also report in Fig.~\ref{Fig:comparison} the coalescence calculations obtained assuming wider wave-functions, which result in even lower production probabilities.
 
-\begin{figure}[htb]
+\begin{figure}[!htb]
 \begin{center}
-\includegraphics[width=\textwidth]{coal2Thermal2alice.png}
+\includegraphics[width=0.88\textwidth]{coal2Thermal2alice.png}
 \caption{(Color online) Coalescence parameter $B_A$ as a function of the average charged particle multiplicity density for various (hyper-)nuclei, up to $A = 4$.
@@
 
+The Grand Canonical thermal ansatz is no longer valid when going to small collision systems, because one needs to account for the exact conservation of quantum numbers in a finite volume and thus a canonical ensemble has to be used.
 As an example, we have also computed $B_A$ for \hethree~according to the thermal+blast-wave approach for the \pPb~system, by using yield predictions from the Canonical Statistical Model from~\cite{Vovchenko:2018fiy} and the blast-wave parameters from~\cite{Abelev:2013haa}.
 The result is reported in Fig.
-\ref{Fig:3He}.
+\ref{Fig:3He} with the blue dashed line.
+We notice that the thermal+blast-wave prediction in this case does not exhibit a significant dependence on multiplicity and is relatively close to the coalescence curve.
+As expected, in high multiplicity \pPb~collisions the CSM+blast-wave curve tends to merge with the Grand Canonical prediction.
 
-Sigh! To be finished.
-
-\begin{figure}[htb]
 \begin{center}
@@
 \section{Conclusions}
-Sic! To be finished.
-\newpage
+We have presented a direct comparison of the coalescence and ther\-mal+blast-wa\-ve production scenarios for light nuclei and hyper-nuclei as a function of multiplicity, used as a proxy for the source size.
+To clarify the production mechanism of composite loosely-bound QCD objects, we show the importance of new and precise measurements of (hyper-)nuclei production up to $A=4$ as a function of multiplicity in different collision systems, in order to fully exploit the sensitivity of production mechanisms to the size of the object relative to the size of the source.
+Particularly sensitive to production mechanisms is the hyper-triton with its large size. 
+The increase in integrated luminosity foreseen in all collision systems during the LHC Runs 3 and 4 in years 2021-2029 should allow the ALICE Collaboration to perform these multi-differential measurements, which will provide crucial insights on the ``anti-nuclei puzzle'' and the (hyper-)nuclei formation.
+
 \bibliographystyle{utphysnt} 	

### 2020-04-01 FrascatiPlot/MakeFiguresEpiphany.C
Save curves to file

@@ -1,13 +1,13 @@
 #include "./CoalescenceBA.C"
-#include "./MapMulti2R.C"
-
+//#include "./MapMulti2R.C"
+//#include "./Make3HepPbPaperFigure.Cs"
 void MakeFiguresEpiphany()
 {
     TString figPath = "../EPIPHANY2019proceedings";
 
     //Figure 1: BA from coalescence
     CoalescenceBA(0.75, figPath.Data());
-    Make3HepPbPaperFigure(figPath.Data(), 0.733, 0, Int_t 1, 1, 0, 0);
+   //Make3HepPbPaperFigure(figPath.Data(), 0.733, 0, 1, 1, 0, 0);
 
     gStyle->SetOptStat(0);
     gStyle->SetOptTitle(0);
@@ -508,7 +508,19 @@ void MakeFiguresEpiphany()
     cr4->SaveAs(Form("%s/coal2Thermal2alice.pdf", figPath.Data()));
     cr4->SaveAs(Form("%s/coal2Thermal2alice.eps", figPath.Data()));
     cr4->SaveAs(Form("%s/coal2Thermal2alice.png", figPath.Data()));
- 
+
+    TFile * fout = new TFile(Form("%s/BApredictions_Epiphany.root",figPath.Data()),"RECREATE");
+    fout->cd();
+    hframe3->Write();
+    hB3_coalescence->Write();
+    gBlastB3vsR_PbPb276TeV->SetName("gBlastB3vsR_PbPb276TeV");
+    gBlastB3vsR_PbPb276TeV->Write();
+    hframe4->Write();
+    hB4_coalescence->Write();
+    gBlastB4vsR_PbPb276TeV->SetName("gBlastB4vsR_PbPb276TeV");
+    gBlastB4vsR_PbPb276TeV->Write();
+    //cr4->Write();
+
     return;
 }
 

### 2020-04-01 FrascatiPlot/Make13TeVPaperFigure.C
some functions moved to the macro MapMulti2R.C

@@ -1,8 +1,10 @@
 #include "./B2vsVolume.C"
 
+/* //the following have been moved to the macro MapMulti2R.C
 void convertRadiusToMulti(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 1);
 void convertRadiusToMulti(TGraphErrors * graph = 0x0, Int_t paramSet = 1);
 void getMultiFromR(Double_t * multi = NULL, Double_t * radius = NULL, Int_t paramSet = 1);
+*/
 void Make13TeVPaperFigure(Bool_t plotLinX = 0, Double_t pToA = 0.75, Int_t RmappingParam = 1);
 
   
@@ -190,6 +192,7 @@ void Make13TeVPaperFigure(Bool_t plotLinX, Double_t pToA, Int_t RmappingParam)
   
 }
 
+/*
 void getMultiFromR(Double_t * multi, Double_t * radius, Int_t paramSet)
 {
   // Here is the crucial mapping between HBT radii and multi^(1/3)
@@ -259,3 +262,4 @@ void convertRadiusToMulti(TGraphAsymmErrors * graph, Int_t paramSet)
 
   return;
 }
+*/

### 2020-04-01 FrascatiPlot/CoalescenceBA.C
Added radius range covered in each system

@@ -552,7 +552,52 @@ void CoalescenceBA(Double_t pToA, TString figPath)
   masterLeg->AddEntry(hBA_coalescence[6], "^{4} _{#Lambda#Lambda}H, #it{r} = 5.5 fm", "l");
   masterLeg->AddEntry(hBA_coalescence[7], "^{4} _{#Lambda}He, #it{r} = 2.4 fm", "l");
 
+Float_t arrowsize = 0.02;
+TArrow * arrpp = new TArrow(0.7, 0.8, 1.5, 0.8, arrowsize, "<|>");
+arrpp->SetLineColor(kGreen+2);
+arrpp->SetFillColor(kGreen+2);
+arrpp->SetFillStyle(1001);
+arrpp->SetLineWidth(3);
 
+TPaveText * pavepp = new TPaveText(0.7, 0.70, 1.5, 0.75);
+  pavepp->SetFillStyle(0);
+  pavepp->SetTextFont(42);
+  pavepp->SetBorderSize(0);
+  pavepp->SetTextSize(0.04);
+  pavepp->SetTextAlign(22);
+  pavepp->SetTextColor(kGreen+2);
+  pavepp->AddText("pp 14 TeV");
+
+TArrow * arrpPb = new TArrow(0.7, 0.6, 2.0, 0.6, arrowsize, "<|>");
+arrpPb->SetLineColor(kBlue);
+arrpPb->SetFillColor(kBlue);
+arrpPb->SetFillStyle(1001);
+arrpPb->SetLineWidth(3);
+
+TPaveText * paveppb = new TPaveText(0.7, 0.48, 2.0, 0.53);
+  paveppb->SetFillStyle(0);
+  paveppb->SetTextFont(42);
+  paveppb->SetBorderSize(0);
+  paveppb->SetTextSize(0.04);
+  paveppb->SetTextAlign(22);
+  paveppb->SetTextColor(kBlue);
+  paveppb->AddText("p-Pb 8.8 TeV");
+
+TArrow * arrPbPb = new TArrow(2.0, 0.4, 6.0, 0.4, arrowsize);
+arrPbPb->SetOption("<>");
+arrPbPb->SetLineColor(kRed+1);
+arrPbPb->SetFillColor(kRed+1);
+arrPbPb->SetFillStyle(1001);
+arrPbPb->SetLineWidth(3);
+
+TPaveText * pavepbpb = new TPaveText(2.0, 0.30, 6.0, 0.35);
[…]

### 2020-04-01 FrascatiPlot/Make3HepPbPaperFigure.C
Updated figures

@@ -1,14 +1,16 @@
 #include "./B2vsVolume.C"
 #include "./GetB3inpToA.C"
 
-TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA = 0.733, Bool_t plotLinX = 0, Int_t RmappingParam = 1, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0, Bool_t plotpPb = 0);
+TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA = 0.733, Bool_t plotLinX = 0, 
+                                Int_t RmappingParam = 1, Bool_t plotcSHM = 1, Bool_t plotPbPb5TeV = 0, 
+                                Bool_t plotpPb = 1);
 
   
 TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, Bool_t plotPbPb5TeV, Bool_t plotpPb)
 {
 
   //prepare input file
-  GetB3inpToA_pPb5TeV(pToA, "B3_Average_pPb_5TeV_15032019.root");
+  GetB3inpToA_pPb5TeV(pToA, "B3_Average_pPb_5TeV_30052019.root");
 
   Int_t ip = RmappingParam;
   Float_t textLabelSize = 0.033;
@@ -31,17 +33,25 @@ TCanvas * Make3HepPbPaperFigure(TString figPath = ".", Double_t pToA, Bool_t plo
   for (Int_t jj = 0; jj < nParamSet; jj++){
     gB3vsR_pp7TeV[jj] = (TGraphErrors *) getB3_pp7TeVINELg0(kFALSE, 0.8, jj, kFALSE);
     gB3vsR_pp7TeV_sys[jj] = (TGraphErrors *) getB3_pp7TeVINELg0(kTRUE, 0.8, jj, kFALSE);
+    gB3vsR_pp7TeV[jj]->SetMarkerStyle(33);
+    gB3vsR_pp7TeV[jj]->SetMarkerSize(1.3);
+    gB3vsR_pp7TeV_sys[jj]->SetMarkerStyle(33);
+    gB3vsR_pp7TeV_sys[jj]->SetMarkerSize(1.3);
     gB3vsR_pp7TeV_sys[jj]->SetFillStyle(1001);    
[…]

### 2020-12-07 EPIPHANY2019proceedings_arXiv/Bellini_Epiphany2019_proc.tex
Macros and output for additional figures derived from the Frascati paper

--- 2020-04-01 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
@@
-\documentclass{appolb}
-\usepackage{graphicx}
+\documentclass[a4paper,11pt]{article} 
+\usepackage[margin=2.5cm]{geometry}\usepackage{graphicx}
 \usepackage{multirow}
@@
 \usepackage{lineno}
-\linenumbers
+%\linenumbers
 
-% graphicx package included for placing figures in the text
 %------------------------------------------------------
@@
 \begin{document}
-% \eqsec  % uncomment this line to get equations numbered by (sec.num)
-\title{Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC}
-\author{F. Bellini\footnote{Presenter.} and A. P. Kalweit 
-	\address{European Organisation for Nuclear Research, Geneva \\E-mail: francesca.bellini@cern.ch}}
-\thanks{Proceedings of the XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}%
 
-\maketitle
+\begin{center}
+
+{\Large \textbf{Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC}}
+
+\medskip
+
+Francesca Bellini\footnote{Presented at the XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}\footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch} and Alexander P. Kalweit
+\\European Organization for Nuclear Research (CERN), Geneva, Switzerland
+
+\medskip
+
+\end{center}
+
 \begin{abstract}
@@
 \centering
-\begin{tabularx}{1.25\textwidth}{cccccccc}
+\begin{tabularx}{1.\textwidth}{cccccccc}
 \hline \hline \\[-2ex]
@@
 %
-\noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\rm T}$, its size parameter $r_A$ and the source radius $R$.
+\noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\mathrm{T}}$, its size parameter $r_A$ and the source radius $R$.
 Very importantly, Eq.~\ref{eq:master} takes explicitly into account the source size ($R$), as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space.
@@
 \subsection{Thermal + blast-wave model} 
-Thermal-statistical models~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
+Thermal-statistical models~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light (anti-) (hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC.
 In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV. 
@@
 
+\begin{figure}[!htb]
 \begin{center}

### 2020-12-07 FrascatiPlot/B2vsVolume.C

@@ -1,8 +1,12 @@
 /*
    akalweit@cern.ch, fbellini@cern.ch
    17.01.2018 - The Frascati plot
-   last update: 27.09.2018
+   last update: 24.07.2020 by fbellini
 */
+
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+//The Frascati project - main figures
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
 #include "TMath.h"
 #include "TGraphAsymmErrors.h"
 #include "TGraphErrors.h"
@@ -10,52 +14,9 @@
 #include "TLegend.h"
 #include "TH1D.h"
 #include "TH2D.h"
-#include "./generateBWpredictionsB2.C"
-#include "./MapMulti2R.C"
-//coalescence predictions up to A=4
-TF1 *          MakeB2TheoryGraphQMfactor(Double_t objSize = 3.2);
-TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 3.2);
-TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 2.48);
-TGraphErrors * MakeB4TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 1.9);
-
-//thermal model + blast-wave predictions up to A=4
-TGraphAsymmErrors * getBlastB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphAsymmErrors * getBlastB2_PbPb502TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphAsymmErrors * getBlastB2_pPb502TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-TGraphAsymmErrors * getBlastB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
-
-TGraphAsymmErrors * getBlastB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
[…]

### 2020-12-07 FrascatiPlot/GetALICEdata.cpp

@@ -1,0 +1,345 @@
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+//The Frascati project - ALICE data - colaescence parameters
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+#include "TGraphErrors.h"
+#include "./MapMulti2R.C"
+
+//deuteron
+TGraphErrors * getB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_pp13TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_pPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_PbPb5TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors * getB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+
+//helium-3
+TGraphErrors      * getB3_PbPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors      * getB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphErrors      * getB3_pPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphAsymmErrors * getB3_pp7TeVINELg0(Bool_t plotSys = 0, Double_t pToAb3pp = 0.800, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+
+//hypertriton
[…]

### 2020-12-07 FrascatiPlot/GetCoalescence.cpp

@@ -1,0 +1,151 @@
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+//The Frascati project - coalescence predictions up to A=4
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+#include "TGraphErrors.h"
+#include "TF1.h"
+
+Double_t getB2fromRadius(Double_t homogR, Double_t mT, Double_t objSize);
+Double_t getB3fromRadius(Double_t homogR, Double_t mT, Double_t objSize);
+Double_t getB4fromRadius(Double_t homogR, Double_t mT, Double_t objSize);
+
+TF1 *          MakeB2TheoryGraphQMfactor(Double_t objSize = 3.2);
+TGraphErrors * MakeB2TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 3.2);
+TGraphErrors * MakeB3TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 2.48);
+TGraphErrors * MakeB4TheoryGraphCoalescence(Double_t mT = 1.0, Double_t objSize = 1.9);
+
+
+Double_t getB2fromRadius(Double_t homogR, Double_t mT, Double_t objSize)
+{
+ 
+  // formula 6.3, 4.12 from Scheibl, Heinz 1999 paper arXiv:nucl-th/9809092v2
+  Double_t Rpar = homogR;
+  Double_t Rperp = homogR;
+  Double_t convFactor_fm2InvGeV = 0.197;
+
+  Double_t invCd = (1.0 + TMath::Power( objSize / (2.0 * Rperp ), 2.0) ) *
+		     TMath::Power((1.0 + TMath::Power( objSize / (2.0 * Rpar ), 2.0) ), 0.5);
+
+  Double_t invCdApprox = TMath::Power( (1.0 + TMath::Power( objSize / (2.0 * Rperp ), 2.0)), 1.5);
+  
+  Double_t Cd = 1.0/invCd;
+  Double_t B2 = (3.0 * TMath::Power(TMath::Pi(), 1.5) * Cd ) /
+    (2 * mT * Rpar /convFactor_fm2InvGeV * Rperp /convFactor_fm2InvGeV * Rperp / convFactor_fm2InvGeV) ; 
+
+  return B2;
+
+}
+
+
[…]

### 2020-12-07 FrascatiPlot/GetThermalBlastWave.cpp

@@ -1,0 +1,342 @@
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+//The Frascati project - thermal + blastwave
+/////////////////////////////////////////////////////////////////////////////////////////////////////////
+#include "TGraphErrors.h"
+#include "./GetALICEdata.cpp"
+#include "./generateBWpredictionsB2.C"
+
+//---------------------------------------------------------------------------------------------------------------------
+//thermal model + blast-wave predictions up to A=4
+//---------------------------------------------------------------------------------------------------------------------
+TGraphAsymmErrors * getBlastB2_PbPb276TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphAsymmErrors * getBlastB2_PbPb502TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphAsymmErrors * getBlastB2_pPb502TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+TGraphAsymmErrors * getBlastB2_pp7TeV(Bool_t plotSys = 0, Double_t pToA = 0.75, Int_t paramSet = 0);
+
+TGraphAsymmErrors * getBlastB3_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+TGraphAsymmErrors * getBlastB3_pPb5TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE, Bool_t plotcSHM = 0);
+TGraphAsymmErrors * getBlastB3_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3 = 0.733, Int_t paramSet = 0, Bool_t convertToR = kTRUE);
+
+TGraphAsymmErrors * getBlastB3Lambda_PbPb276TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1.0, Int_t paramSet = 0);
+TGraphAsymmErrors * getBlastB3Lambda_pp7TeV(Bool_t plotSys = 0, Double_t pToAb3Lambda = 1.0, Int_t paramSet = 0);
+
[…]

### 2020-12-07 FrascatiPlot/MakeERCfigure.C

@@ -1,0 +1,873 @@
+/*
+   fbellini@cern.ch
+   17.09.2018 - Yellow Report plot
+*/
+
+#include "./CoalescenceBA.C"
+
+void ConfigTwoPanelsPad(TPad* pad1, TPad* pad2, Float_t leftmargin, Float_t rightmargin);
+void ConfigThreePanelsPad(TPad* pad1, TPad* pad2, TPad* pad3, Float_t leftmargin = 0.15, Float_t rightmargin = 0.001);
+
+//pseudodata
+TGraphErrors * GetPseudoBAvsMulti(TString particle = "deuteron",  Int_t paramSet = 1);
+TGraphErrors * GetPseudoBAvsMultiUnc(TString particle = "deuteron",  Int_t paramSet = 1, Color_t color = 0);
+TGraphErrors * GetMeasBAvsMultiUnc(TString particle = "he3",  Int_t paramSet = 1, Color_t color = kGreen+2);
+
+//main
+void MakeERCfigure(Double_t pToAb3 = 0.77, Double_t pToAb3Lambda = 1.17, Double_t pToAb4 = 0.75, Double_t pToAb4Lambda = 0.62, Bool_t plotPseudoData = 1)
+{
+  //
+  // main function which generates Figure 1 for the LF chapter of the yellow report
+  //
+  gStyle->SetOptStat(0);
+  gStyle->SetOptTitle(0);
+  gStyle->SetPadTopMargin(0.02);
+  gStyle->SetPadBottomMargin(0.1);
+  gStyle->SetPadLeftMargin(0.15);
+  gStyle->SetPadRightMargin(0.02); 
+
+
+  Color_t projCol = kRed+1;
+  Double_t Rmin = 0.01; Double_t Rmax = 6.5;
+  
+  //------------------------------
+  // Pseudodata
+  //------------------------------
+  TGraphErrors * gPseudo3He = (TGraphErrors *) GetPseudoBAvsMulti("he3", 1);
+  TGraphErrors * gPseudo3LambdaH = (TGraphErrors *) GetPseudoBAvsMulti("hyperH3", 1);
+  TGraphErrors * gPseudo4He = (TGraphErrors *) GetPseudoBAvsMulti("he4", 1);
[…]

### 2020-12-07 FrascatiPlot/MakeFigures5TeVHeliumPaper.C

@@ -1,0 +1,545 @@
+#include "./CoalescenceBA.C"
+//#include "./MapMulti2R.C"
+//#include "./Make3HepPbPaperFigure.Cs"
+void MakeFigures5TeVHeliumPaper()
+{
+    TString figPath = "./paper4HePbPb";
+
+    //Figure 1: BA from coalescence
+    //CoalescenceBA(0.75, figPath.Data());
+   //Make3HepPbPaperFigure(figPath.Data(), 0.733, 0, 1, 1, 0, 0);
+
+    gStyle->SetOptStat(0);
+    gStyle->SetOptTitle(0);
+    gStyle->SetPadTopMargin(0.03);
+    gStyle->SetPadBottomMargin(0.17);
+    gStyle->SetPadLeftMargin(0.17);
+    gStyle->SetPadRightMargin(0.02); 
+
+    Bool_t convertToR = kFALSE;    //Bool_t plotPseudoData = 0;
+    Int_t paramSet = 1;
+
+    Color_t projCol = kRed+1;
+    Double_t Rmin = 0.8; 
+    Double_t Rmax = 3000;
+    if (convertToR) {
+        Rmin = 0.01;
+        Rmax = 6.5;//fm
+    }
+
+    Double_t pToA = 0.75;
+    Double_t pToAb3 = 0.733;
+    Double_t pToAb3pp = 0.8;
+    Double_t pToAb3Lambda = 1.;
+    Double_t pToAb4 = 0.875; 
+    Double_t pToAb4Lambda = 0.75; 
+
+    //-----------------------------
+    //    data
+    //-----------------------------
+    Int_t Fill_Style = 1001;
+    Int_t Line_Style = 1;
+    Int_t Line_Style_Blast = 2;
+    Int_t Line_Width = 1; 
+    Int_t Line_Width_Blast = 3;
+    Float_t Marker_Size = 1.3;
+    //nb: manual hack to avoid loop over all parameterisations
+    const Int_t nParamSet = 1;
+    Int_t ip = paramSet-1;
+
+    TGraphErrors* gB2vsR_pp7TeVINELg0[nParamSet];
+    TGraphErrors* gB2vsR_pp7TeVINELg0_sys[nParamSet];
[…]

### 2020-12-07 FrascatiPlot/MakeLDtalkFigure.C

@@ -5,10 +5,10 @@ void convertRadiusToMulti(TGraphAsymmErrors * graph = 0x0, Int_t paramSet = 1);
 void convertRadiusToMulti(TGraphErrors * graph = 0x0, Int_t paramSet = 1);
 void getMultiFromR(Double_t * multi = NULL, Double_t * radius = NULL, Int_t paramSet = 1);
 */
-void Make13TeVPaperFigure(Bool_t plotRun2 = 1, Bool_t plotLinX = 0, Double_t pToA = 0.75, Int_t RmappingParam = 1);
+void MakeLDtalkFigure(Bool_t plotLinX = 0, Double_t pToA = 0.75, Int_t RmappingParam = 1);
 
   
-void Make13TeVPaperFigure(Bool_t plotRun2, Bool_t plotLinX, Double_t pToA, Int_t RmappingParam)
+void MakeLDtalkFigure(Bool_t plotLinX, Double_t pToA, Int_t RmappingParam)
 {
 
   Int_t ip = RmappingParam;
@@ -25,8 +25,6 @@ void Make13TeVPaperFigure(Bool_t plotRun2, Bool_t plotLinX, Double_t pToA, Int_t
   TGraphErrors* gB2vsR_pPb502TeV_sys[nParamSet];
   TGraphErrors* gB2vsR_PbPb276TeV[nParamSet];
   TGraphErrors* gB2vsR_PbPb276TeV_sys[nParamSet];
-  TGraphErrors* gB2vsR_PbPb502TeV[nParamSet];
-  TGraphErrors* gB2vsR_PbPb502TeV_sys[nParamSet];
 
   for (Int_t jj = 0; jj < nParamSet; jj++){
     gB2vsR_pp7TeV[jj] = (TGraphErrors *) getB2_pp7TeV(kFALSE, pToA, jj, kFALSE);
@@ -37,29 +35,43 @@ void Make13TeVPaperFigure(Bool_t plotRun2, Bool_t plotLinX, Double_t pToA, Int_t
     gB2vsR_pPb502TeV_sys[jj] = (TGraphErrors *) getB2_pPb5TeV(kTRUE, pToA, jj, kFALSE);
[…]

### 2020-12-07 FrascatiPlot/MakeLDtalkPlotHe.C

@@ -1,0 +1,312 @@
+#include "./B2vsVolume.C"
+#include "./GetB3inpToA.C"
+
+TCanvas * MakeLDtalkPlotHe(TString figPath = ".", Double_t pToA = 0.733, Bool_t plotLinX = 0, 
+                                Int_t RmappingParam = 1, Bool_t plotcSHM = 0, Bool_t plotPbPb5TeV = 0, 
+                                Bool_t plotpPb = 1);
+
+  
+TCanvas * MakeLDtalkPlotHe(TString figPath = ".", Double_t pToA, Bool_t plotLinX, Int_t RmappingParam, Bool_t plotcSHM, Bool_t plotPbPb5TeV, Bool_t plotpPb)
+{
+
+  //prepare input file
+  GetB3inpToA_pPb5TeV(pToA, "B3_Average_pPb_5TeV_30052019.root");
+
+  Int_t ip = RmappingParam;
+  Float_t textLabelSize = 0.033;
+  Short_t modelCurvesLineWidth = 4;
+  //----------------------------
+  //Get data
+  //----------------------------
+  const Int_t nParamSet = 4;
+  TGraphErrors* gB3vsR_pp7TeV[nParamSet];
+  TGraphErrors* gB3vsR_pp7TeV_sys[nParamSet];
+  // TGraphErrors* gB3vsR_pp13TeV[nParamSet];
+  // TGraphErrors* gB3vsR_pp13TeV_sys[nParamSet];
+  TGraphErrors* gB3vsR_pPb502TeV[nParamSet];
+  TGraphErrors* gB3vsR_pPb502TeV_sys[nParamSet];
+  TGraphErrors* gB3vsR_PbPb276TeV[nParamSet];
+  TGraphErrors* gB3vsR_PbPb276TeV_sys[nParamSet];
+  TGraphErrors* gB3vsR_PbPb502TeV[nParamSet];
+  TGraphErrors* gB3vsR_PbPb502TeV_sys[nParamSet];
+  
+  for (Int_t jj = 0; jj < nParamSet; jj++){
+    gB3vsR_pp7TeV[jj] = (TGraphErrors *) getB3_pp7TeVINELg0(kFALSE, 0.8, jj, kFALSE);
[…]
